### 2021-12-10 smelt_2019_allseasons/f_clean_conditionfactor_survival.Rmd
Commit of clean data, code for cleaning data, code for plotting CF

---
title: "Clean_Condition_Survival"
author: "Catarina Pien"
date: "12/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(readr)
```

Tasks:
1. Read winter/spring, summer/fall data in
2. Clean names and bind together
3. Calculate Pre and Post condition factors
4. Make survival file

# Condition Factor, Length, Weight
1. Read data
```{r}
summerdata <- read_csv("smelt_2019_allseasons/Raw_Smelt-Length-Weight_Summer2019.csv", col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
  rename(K0 = K) 
falldata <- read_csv("smelt_2019_allseasons/Raw_Smelt-Length-Weight_Fall2019.csv", col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
  rename(K0 = K)

winterspringdata <- read_csv("smelt_2019_allseasons/Cagetype_data.csv") %>%
  rename(Pre_FL=Pre_FL_cm,
         Post_FL=Post_FL_cm,
         Pre_Weight=Pre_Weight_g,
         Post_Weight=Post_Weight_g)
```

2. Reformat
```{r}
winspring_long <- winterspringdata %>% 
  select(-Delta_CF, -X1) %>%
  pivot_longer(cols = c(Pre_FL:Post_CF),
               names_to = c("Period", ".value"),
               names_sep = "_")

# Filter to only large mesh and RV
winspring_clean <- winspring_long %>%
  filter(Site != "DWSC",
         Mesh == "large") %>%
  rename(FL_cm = FL,
         Weight_g = Weight,
         K0 = CF) %>%
  mutate(Deployment = ifelse(Site =="DWSC", "Spring",
                             ifelse(Site == "RV", "Winter", NA )),
         ID = NA,
         ID = as.character(ID),
         Deployment = as.factor(Deployment),
         Period = as.factor(Period),
         Site = as.factor(Site),
         Cage = as.factor(Cage))%>%
  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage)

summerfall_clean <- rbind(summerdata, falldata) %>%
  mutate(FL_mm = replace(FL_mm, FL_mm == "-", NA),
         FL_mm = as.numeric(FL_mm),
         FL_mm = FL_mm/10, na.rm = TRUE) %>%
  rename(FL_cm = FL_mm) %>%
  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage)

```

Bind 
```{r}
CF_2019 <- rbind(winspring_clean, summerfall_clean) %>%
  mutate(K= round(100 * Weight_g/(FL_cm^3),3)) 
```

Write file
```{r}
write.csv(CF_2019, "smelt_2019_allseasons/data_clean/clean_smelt_cf_2019.csv", row.names = FALSE)
```

# Survival
```{r}
Survival <- data.frame(Deployment = factor(), Site = factor(), Survived = numeric(), Total = numeric())

```

Winter
RV: 60, 64, 64, 64, 62, 56 / 64

Spring
DWSC: 59, 60, 58, 60, 60, 58 / 60

Summer
Yolo: 0 / 60
RV: / 60

Fall
Yolo: 
RV:
SM:
'
```{r}
(152-21)/180 #RV
(161-5)/180 #RV
(177-5-3)/180 #SM
(161-2)/180

Survivors_bycage <- CF_2019 %>%
  filter(Period == "Post",
         !Cage %in% c("FCCL1", "FCCL2")) %>%
  group_by(Deployment, Site, Cage) %>%
  summarize(n=n()) %>%
  mutate(Total = ifelse(Site == "RV", 64, 
                        ifelse(Site == "FCCL", 30, 60))) %>%
  filter(!is.na(Cage))

Survivors_bydeployment <-  Survivors_bycage %>%
  group_by(Deployment, Site) %>%
  summarize(Survived = sum(n),
            TotalFish = sum(Total)) %>%
  mutate(Prop = Survived/TotalFish) %>%
  ungroup()

Survivors_final <- Survivors_bydeployment %>% add_row(Deployment = "Summer", Site ="Yolo", Survived = 0, TotalFish = 30, Prop = 0)

```

```{r}
Cage_survival_RV <- as.data.frame(matrix(0, ncol = 2, nrow = 384))
colnames(Cage_survival_RV) <- c("Cage", "Survived")

Cage_survival_RV$Cage <- c(rep("A", 64), rep("B", 64), rep("C", 64), rep("D", 64), rep("E", 64), rep("F", 64))
Cage_survival_RV$Survived <- c(rep("1", 60), rep("0", 4), 
                               rep("1", 64), rep("0", 0),
                               rep("1", 64), rep("0", 0),
                               rep("1", 64), rep("0", 0),
                               rep("1", 62), rep("0", 2),
                               rep("1", 56), rep("0", 8))
```

### 2021-12-10 smelt_2019_allseasons/plot_weight_length_cf.Rmd
Commit of clean data, code for cleaning data, code for plotting CF

---
title: "plot_weight_length_cf"
author: "Catarina Pien"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
smeltdata <- read_csv("data_clean/clean_smelt_cf_2019.csv", col_types = cols(.default="f", FL_cm = "d", Weight_g = "d", K = "d", ID = "c"))
glimpse(smeltdata)
```

```{r}
smeltdata2 <- filter(smeltdata, Site !="DWSC")%>%
  filter(!is.na(K)) 
```

Summarize data
```{r}
summarydata <- smeltdata2 %>%
  group_by(Deployment, Site, Period) %>%
  summarize(meanCF = mean(K, na.rm = TRUE),
            sdCF = sd(K, na.rm = TRUE),
            meanFL = mean(FL_cm, na.rm = TRUE),
            sdFL = sd(FL_cm, na.rm = TRUE),
            meanWeight = mean(Weight_g, na.rm = TRUE),
            sdWeight = sd(Weight_g, na.rm = TRUE),
            n = n())
```

Plot data
```{r}
ggplot(smeltdata2, aes(x = Period, y = K, fill = Site)) + 
  geom_boxplot() + 
  facet_wrap(Deployment~.) + 
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
```

### 2021-12-11 smelt_2019_allseasons/f_clean_conditionfactor_survival.Rmd
Added figure of boxplots, table of survival

@@
 ---
-
+This code takes raw summer, fall, winter data and combines it into one file of length, weight, condition factor. 
 ```{r setup, include=FALSE}
@@
 library(readr)
+root <- "smelt_2019_allseasons"
 ```
@@
 Yolo: 0 / 60
-RV: / 60
+RV: 152 fish on data sheet - 21 died in cage / 60 60 60
 
@@
 Yolo: 
-RV:
-SM:
-'
+RV: 161 fish on data sheet - 5 cage mortality in comments = 156/ 60 60 60
+SM: 177 fish on data sheet - 5 cage mortality in comments/ 60 60 60
+YB: 161 fish on data sheet - 2 "Dead in cage) = 159/ 60 60 60
+
+Original table: https://cawater.sharepoint.com/sites/dwrdoc-aes/Shared%20Documents/Forms/AllItems.aspx?viewid=5f80dd60%2D5e8b%2D4f46%2Dab49%2D609d1052bd85&id=%2Fsites%2Fdwrdoc%2Daes%2FShared%20Documents%2FDelta%20Smelt%20Enclosure%20Study%2FPermits%2FAnnual%20Reports%2F2019%2FDelta%20Smelt%20Enclosure%20Study%202019%20Annual%20Report%20FINAL%2Epdf&parent=%2Fsites%2Fdwrdoc%2Daes%2FShared%20Documents%2FDelta%20Smelt%20Enclosure%20Study%2FPermits%2FAnnual%20Reports%2F2019
+
+Info for this data: "V:\Data\Summer'19\August Measurements and Dissections" & "V:\Data\Summer'19\October Measurements and Dissections"
 ```{r}
-(152-21)/180 #RV
-(161-5)/180 #RV
-(177-5-3)/180 #SM
-(161-2)/180
+cage <- read.csv("smelt_2019_allseasons/data_raw/Cagetype_data.csv")
+# Cages B + F are large mesh
+# Winter
+(64+56)/(64+64) # RV 0.94
 
-Survivors_bycage <- CF_2019 %>%
-  filter(Period == "Post",
-         !Cage %in% c("FCCL1", "FCCL2")) %>%
-  group_by(Deployment, Site, Cage) %>%
-  summarize(n=n()) %>%
-  mutate(Total = ifelse(Site == "RV", 64, 
-                        ifelse(Site == "FCCL", 30, 60))) %>%
-  filter(!is.na(Cage))
+# Summer
+(152-21)/180 #RV 0.73
 
-Survivors_bydeployment <-  Survivors_bycage %>%
-  group_by(Deployment, Site) %>%
-  summarize(Survived = sum(n),
-            TotalFish = sum(Total)) %>%
-  mutate(Prop = Survived/TotalFish) %>%
-  ungroup()
+#Fall
+(161-5)/180 #RV 0.87
+(177-5)/180 #SM 0.96
+(161-2)/180 #YB 0.88
+```
 
-Survivors_final <- Survivors_bydeployment %>% add_row(Deployment = "Summer", Site ="Yolo", Survived = 0, TotalFish = 30, Prop = 0)
+Make survival table
+```{r}
+Cage_survival <- as.data.frame(matrix(0, ncol = 4, nrow = 6))
+colnames(Cage_survival) <- c("Deployment", "Site", "Survived", "TotalFish")
+Cage_survival$Deployment = c("Winter", "Summer", "Summer", "Fall", "Fall", "Fall")
+Cage_survival$Site = c("RV", "RV", "Yolo", "RV", "SM", "Yolo")
+Cage_survival$Survived = c(120, 131, 0, 156, 172, 159)
+Cage_survival$TotalFish = c(128, 180, 60, 180, 180, 180)
+
+Cage_survival_total <- Cage_survival %>%
+  mutate(Prop = round(Survived/TotalFish,3))
 
@@
 ```{r}
-Cage_survival_RV <- as.data.frame(matrix(0, ncol = 2, nrow = 384))
-colnames(Cage_survival_RV) <- c("Cage", "Survived")
-
-Cage_survival_RV$Cage <- c(rep("A", 64), rep("B", 64), rep("C", 64), rep("D", 64), rep("E", 64), rep("F", 64))
-Cage_survival_RV$Survived <- c(rep("1", 60), rep("0", 4), 
-                               rep("1", 64), rep("0", 0),
-                               rep("1", 64), rep("0", 0),
-                               rep("1", 64), rep("0", 0),
-                               rep("1", 62), rep("0", 2),
-                               rep("1", 56), rep("0", 8))
+write.csv(Cage_survival_total, "smelt_2019_allseasons/data_clean/cage_survival_table.csv", row.names = FALSE)
 ```

### 2021-12-11 smelt_2019_allseasons/plot_weight_length_cf.Rmd
Added figure of boxplots, table of survival

@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-Plot data
+Plot K
 ```{r}
-ggplot(smeltdata2, aes(x = Period, y = K, fill = Site)) + 
+box_K <- ggplot(smeltdata2, aes(x = Period, y = K, fill = Site)) + 
   geom_boxplot() + 
@@
 ```
+
+Plot Length
+```{r}
+box_FL <- ggplot(smeltdata2, aes(x = Period, y = FL_cm, fill = Site)) + 
+  geom_boxplot() + 
+  facet_wrap(Deployment~.) + 
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
+```
+
+Plot Weight
+```{r}
+box_Wt <- ggplot(smeltdata2, aes(x = Period, y = Weight_g, fill = Site)) + 
+  geom_boxplot() + 
+  facet_wrap(Deployment~.) + 
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
+```
+
+```{r}
+getwd()
+library(ggpubr)
+tiff(filename = file.path("smelt_2019_allseasons/figures/FL-Wt-K.tiff"), res = 300, width = 7, height = 7, units = "in", pointsize = 10, type = "cairo", compression = "lzw")
+ggarrange(box_FL, box_Wt, box_K, nrow = 3)
+dev.off()
+
+```

### 2021-12-13 smelt_2019_winterspring/RelativeCF_2019Winter.Rmd
Commit of files from first manuscript (winter/spring) - added average survival

---
title: "Relative Condition Factor"
author: "Catarina Pien"
date: "8/31/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls(all=TRUE))
library(tidyverse)

```

Read in data

```{r import}
setwd("V:/Analysis/")
Cagetype_data <- read.csv("CSV_Output/Cagetype_data.csv")
Cagetype_data$Site <- ordered(Cagetype_data$Site, levels = c("RV", "DWSC"))
```

Complete cases

```{r complete, echo=FALSE}
# Make complete cases from column 9
Delta_CF <- Cagetype_data[,9]
Cagetype_CF <- Cagetype_data[complete.cases(Delta_CF),]
```

Gather length weight data and log transform
```{r}
LWData <- Cagetype_CF %>%
 select(-contains("CF")) %>%
  rename(FL_Pre = Pre_FL_cm,
         FL_Post = Post_FL_cm,
         Weight_Pre = Pre_Weight_g,
         Weight_Post = Post_Weight_g) %>%
  mutate(Site2 = ifelse(Mesh == "control", "FCCL", as.character(Site)))

# .value: this tells pivot_longer() that that part of the column name specifies the “value” being measured (which will become a variable in the output)
LWlong <- LWData %>% 
  pivot_longer(cols = -c(X, Cage, Site2, Site, Mesh),
               names_to = c(".value", "Event"),
               names_sep = "_")

LWlongT <- LWlong %>%
  mutate(logFL = log(FL/10),
         logWeight = log(Weight))

```

Plot data
```{r plot}
# Overall
ggplot(LWlongT, aes(x = FL, y = Weight)) + geom_point() + 
  labs(x = "Fork Length (cm)",
       y = "Weight (g)") + 
  theme_bw()

# Site
ggplot(LWlongT, aes(x = logFL, y = logWeight, shape = Site2, color = Site)) + geom_point() + 
  geom_smooth(aes(color = Site), method = "lm", se = TRUE)+
  scale_shape_manual(values = c(19, 2))+
  labs(x = "Log10 Fork Length (mm)",
       y = "Log10 Weight (g)") + 
  theme_bw()

# Pre-Post
ggplot(LWlongT, aes(x = logFL, y = logWeight, shape = Event, color = Event)) + geom_point() + 
  geom_smooth(aes(color = Event), method = "lm", se = TRUE)+
  facet_wrap(~Site2) + 
  labs(x = "Log10 Fork Length (mm)",
       y = "Log10 Weight (g)") + 
  theme_bw()
```

Fit a model to the LW-data
```{r glm}
library(visreg)
library(lsmeans)
# Linear model  - all data
m1 <- lm(logWeight ~ logFL, data = LWlongT)
summary(m1)
par(mfrow = c(2,2))
plot(m1) #3.31
visreg(m1)

# RV only
RV_LW = filter(LWlongT, Site2 == "RV")
m2 <- lm(logWeight ~ logFL, data = RV_LW)
summary(m2)
plot(m2) #3.35
visreg(m2)

# DWSC only

DWSC_LW = filter(LWlongT, Site2 == "DWSC")
m3 <- lm(logWeight ~ logFL, data = DWSC_LW)
summary(m3) #3.51
plot(m3)
visreg(m3)

# DWSC only

FCCL_LW = filter(LWlongT, Site2 == "FCCL")
m4 <- lm(logWeight ~ logFL, data = FCCL_LW)
summary(m4) #3.62
plot(m4)
visreg(m4)

```

### Testing differences in L-W Relationship (ANCOVA)
```{r}
# Are sites different? Yes.
m5 <- lm(logWeight ~ logFL*Site2, data = LWlongT)
anova(m5)
m5$coefficients
(m.lst <- lstrends(m5, "Site2", var="logFL"))
pairs(m.lst)

# Plot Sites
ggplot(LWlongT, aes(x = logWeight, y = logFL, color = Site2)) + 
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) + 
  facet_wrap(~Event) + theme_bw()

# Are Pre-Post different?
m6 <- lm(logWeight ~ logFL*Event + Site2, data = LWlongT)
anova(m6)
m6$coefficients
(m.lst2 <- lstrends(m6, "Event", var="logFL")) # 3.387
pairs(m.lst2)

# Plot Event
ggplot(LWlongT, aes(x = logWeight, y = logFL, color = Event)) + 
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +  
  facet_wrap(~Site2) + theme_bw()

# Including Both
m7 <- lm(logWeight ~ logFL*Event + logFL*Site2, data = LWlongT)
anova(m7)
m7$coefficients
(m.lst3 <- lstrends(m6, "Event", var="logFL")) # 3.387
pairs(m.lst3)

```

Condition Factor
LW regression: logW = 2.01266 + 3.30975 x logFL
Relative CF: Kn = W/(a x L^b)
Fulton's CF: W/L^3
Ricker's CF = W/L^b
```{r CF}
# a = 10^intercept
# b = slope of line

a = 102.958
b = 3.30975

CFData <- LWData %>%
  mutate(
    FL_Pre_mm = FL_Pre/10,
    FL_Post_mm = FL_Post/10,
    RelCF_Pre = Weight_Pre/(a * FL_Pre_mm^b) ,
    RelCF_Post = Weight_Post/(a * FL_Post_mm^b),
    Delta_RelCF = RelCF_Post-RelCF_Pre,
    RickCF_Pre = (Weight_Pre/(FL_Pre^b)) * 100,
    RickCF_Post = (Weight_Post/(FL_Post^b)) * 100,
    Delta_RickCF = RickCF_Post-RickCF_Pre,
    CF_Pre = Weight_Pre/(FL_Pre^3)*100,
    CF_Post = Weight_Post/(FL_Post^3)*100,
    Delta_CF = CF_Post-CF_Pre)

```

Mean CF for plots

```{r meancf Plots}
# Summarize mean, sd, median, n for condition factor
Cage.CF <- CFData %>%
  na.omit() %>%
#  filter(Cage!="FCCL1") %>%
 # filter(Cage!="FCCL2") %>%
  group_by(Site, Mesh)%>%
  summarize(
    Delta_CF_Mean = mean(Delta_CF),
    Delta_CF_sd = sd(Delta_CF),
    Delta_CF_median = median(Delta_CF),
    N = n(),
    Delta_RCF_Mean = mean(Delta_RickCF),
    Delta_RCF_sd = sd(Delta_RickCF),
    Delta_RCF_median = median(Delta_RickCF),
    NRick = n())

# Calculate Average CF for FCCL
FCCL_CF <- CFData %>%
  filter(Cage == "FCCL1" | Cage == "FCCL2") %>%
  group_by(Site, Mesh)%>%
  summarize(
    Delta_CF_Mean = mean(Delta_CF),
    Delta_CF_sd = sd(Delta_CF),
    Delta_CF_median = median(Delta_CF),
    N = n(),
    Delta_RCF_Mean = mean(Delta_RickCF),
    Delta_RCF_sd = sd(Delta_RickCF),
    Delta_RCF_median = median(Delta_RickCF),
    NRick = n()
  )
```

Plots
```{r plots}
# Overview of data (geom_point)
ggplot(CFData, aes(Mesh, Delta_CF, col = Mesh)) + 
  facet_wrap(~Site) +
  geom_jitter(size = 3) +
  scale_fill_brewer(palette="Dark2")+
  theme_bw() +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 20),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 18))

# CF mean and sd by site
# CF mean by site
ggplot(Cage.CF, aes(Mesh, Delta_CF_Mean,  fill = Mesh)) + 
  facet_wrap(~Site)+
  geom_bar(width = 0.8, position = "dodge2", stat = "identity") +
  scale_fill_brewer(palette="Dark2")+
  labs(y = "Delta Condition Factor") +
  geom_errorbar(aes(ymin = Delta_CF_Mean - Delta_CF_sd, ymax = Delta_CF_Mean + Delta_CF_sd), width = 0.1, 
                position = position_dodge(0.9), color = "black") +
  theme_bw() +
  theme(axis.text = element_text(size = 18),
        axis.title = element_text(size = 18),
        strip.text = element_text(size = 18),
        legend.position = "none")

# Mean point plot
ggplot(Cage.CF, aes(Mesh, Delta_CF_Mean,  col = Mesh)) + 
  facet_wrap(~Site)+
  geom_point(size = 8, shape = 18) +
  scale_colour_brewer(palette="Dark2")+
  labs(y = "Delta Condition Factor") +
  geom_errorbar(aes(ymin = Delta_CF_Mean - Delta_CF_sd, ymax = Delta_CF_Mean + Delta_CF_sd), width = 0.1, 
                position = position_dodge(0.9), color = "black") +
  theme_bw() +
  theme(axis.text = element_text(size = 18),
        axis.title = element_text(size = 18),
        strip.text = element_text(size = 18),
        legend.position = "none")

# Mean point plot - Ricker
ggplot(Cage.CF, aes(Mesh, Delta_RCF_Mean,  col = Mesh)) + 
  facet_wrap(~Site)+
  geom_point(size = 8, shape = 18) +
  scale_colour_brewer(palette="Dark2")+
  labs(y = "Delta Condition Factor") +
  geom_errorbar(aes(ymin = Delta_RCF_Mean - Delta_RCF_sd, ymax = Delta_RCF_Mean + Delta_RCF_sd), width = 0.1, 
                position = position_dodge(0.9), color = "black") +
  theme_bw() +
  theme(axis.text = element_text(size = 18),
        axis.title = element_text(size = 18),
        strip.text = element_text(size = 18),
        legend.position = "none")

### CF boxplot by site #####################
Cageonly <- CFData %>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2") %>%
  mutate(Group = ifelse(Site == "RV" & Mesh == "wrap", "B", ifelse(Site == "DWSC", " ", "A")))

windowsFonts(Times = windowsFont("Times New Roman"))

# Specify FCCL Delta CF label position
ann_text <- data.frame(
  label = c("FCCL Delta CF = 0.0048","FCCL Delta CF = 0.0027"),
  Site = c("RV", "DWSC"),
  x = c(2,2),
  y = c(0.08, 0.07))

# By mesh type
ggplot(data=Cageonly) +
  geom_boxplot(aes(x=Mesh, y=Delta_CF,  fill = Mesh)) +
  facet_wrap(~Site) +
  labs(y = "Delta Condition Factor") +
  geom_text(aes(label = Group, x = Mesh, y = -0.05), family = "Times", size = 6) +
  geom_hline(data = FCCL_CF, aes(yintercept=Delta_CF_median), size = 1) +
  geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_brewer(palette="Dark2")+
  labs(y = "Delta Condition Factor") +
  theme_minimal() +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        panel.spacing = unit(2, "lines"))

# Specify FCCL Delta CF label position
ann_text2 <- data.frame(
  label = c("FCCL Delta CF = 0.0135","FCCL Delta CF = 0.024"),
  Site = c("RV", "DWSC"),
  x = c(2,2),
  y = c(0.08, 0.07))

# By mesh type - Ricker
ggplot(data=Cageonly) +
  geom_boxplot(aes(x=Mesh, y=Delta_RelCF,  fill = Mesh)) +
  facet_wrap(~Site) +
  labs(y = "Delta Condition Factor") +
  geom_text(aes(label = Group, x = Mesh, y = -0.05), family = "Times", size = 6) +
  geom_hline(data = FCCL_CF, aes(yintercept=Delta_RCF_median), size = 1) +
  geom_text(data = ann_text2, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_brewer(palette="Dark2")+
  labs(y = "Delta Condition Factor") +
  theme_minimal() +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        panel.spacing = unit(2, "lines"))
# By cage
ggplot(data=Cageonly, aes(x=Cage, y=Delta_CF,  fill = Mesh)) +
  facet_wrap(~Site) +
  labs(y = "Delta Condition Factor") +
  geom_boxplot()+
  geom_hline(data = FCCL_CF, aes(yintercept=Delta_CF_median)) +
  scale_fill_brewer(palette="Dark2")+
  labs(y = "Delta Condition Factor") +
  theme_bw() +
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 16),
        legend.position = "none")

```

ANOVA

```{r anova, warning = FALSE, message = FALSE}
library(car)
library(FSA)
## RV ---------------------------------------------------------------------------
# Run ANOVA -----------------------------

Cage_only_RVR <- CFData %>%
  filter(Site == "RV")%>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2")

rv.cf.aov <- aov(Delta_CF~Mesh, data = Cage_only_RVR)
summary(rv.cf.aov)

# Check assumptions -----------------------------------
# Homogeneity of variances
par(mfrow = c(1,2))
plot(rv.cf.aov, 1)
leveneTest(Delta_CF ~ Mesh, data = Cage_only_RVR) # p<0.05 means not homogeneous

# Normality
plot(rv.cf.aov, 2)

rv_cf_residuals <- residuals(object = rv.cf.aov)
shapiro.test(x = rv_cf_residuals ) # p<0.05 means not normal

# Does not meet assumptions: do non-parametric Kruskal-Wallis test--------------------
kruskal.test(Delta_CF~Mesh, data = Cage_only_RVR) # still significant

# Post-hoc Dunn test --------------
# Dunn test can be used if sample size are heterogeneous
RV.dunn <- dunnTest(Delta_CF~Mesh,
                    data = Cage_only_RVR,
                    method = "bonferroni") # bonferroni corrects for number of comparisons
RV.dunn
RV.dunn = RV.dunn$res

library(rcompanion)

cldList(comparison = RV.dunn$Comparison,
        p.value    = RV.dunn$P.adj,
        threshold  = 0.05)

## DWSC ---------------------------------------------------------------------------

# Run ANOVA -------------------------------------

Cage_only_DWSC <- CFData %>%
  filter(Site == "DWSC") %>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2")

Cage_only_DWSC$Mesh <- as.factor(Cage_only_DWSC$Mesh)

dwsc.cf.aov <- aov(Delta_CF~Mesh, data = Cage_only_DWSC)
summary(dwsc.cf.aov)

TukeyHSD(dwsc.cf.aov)

# Check assumptions -----------------------------------
# Homogeneity of variances
plot(dwsc.cf.aov, 1)
leveneTest(Delta_CF ~ Mesh, data = Cage_only_DWSC) # p<0.05 means not homogeneous

# Normality
plot(dwsc.cf.aov, 2)

dwsc_cf_residuals <- residuals(object = dwsc.cf.aov)
shapiro.test(x = dwsc_cf_residuals ) # p<0.05 means not normal

# Does not meet assumptions: do non-parametric Kruskal-Wallis test---------------
kruskal.test(Delta_CF~Mesh, data = Cage_only_DWSC)
```

Ricker CF - ANOVA /Kruskal Wallis
```{r Rickeranova, warning = FALSE, message = FALSE}
library(car)
library(FSA)
## RV ---------------------------------------------------------------------------
# Run ANOVA -----------------------------

Cage_only_RVR <- CFData %>%
  filter(Site == "RV")%>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2")

rv.cf.aov <- aov(Delta_RickCF~Mesh, data = Cage_only_RVR)
summary(rv.cf.aov)

# Check assumptions -----------------------------------
# Homogeneity of variances
par(mfrow = c(1,2))
plot(rv.cf.aov, 1)
leveneTest(Delta_RickCF ~ Mesh, data = Cage_only_RVR) # p<0.05 means not homogeneous

# Normality
plot(rv.cf.aov, 2)

rv_cf_residuals <- residuals(object = rv.cf.aov)
shapiro.test(x = rv_cf_residuals ) # p<0.05 means not normal

# Does not meet assumptions: do non-parametric Kruskal-Wallis test--------------------
kruskal.test(Delta_RickCF~Mesh, data = Cage_only_RVR) # still significant

# Post-hoc Dunn test --------------
# Dunn test can be used if sample size are heterogeneous
RV.dunn <- dunnTest(Delta_RickCF~Mesh,
                    data = Cage_only_RVR,
                    method = "bonferroni") # bonferroni corrects for number of comparisons
RV.dunn
RV.dunn = RV.dunn$res

library(rcompanion)

cldList(comparison = RV.dunn$Comparison,
        p.value    = RV.dunn$P.adj,
        threshold  = 0.05)

## DWSC ---------------------------------------------------------------------------

# Run ANOVA -------------------------------------

Cage_only_DWSC <- CFData %>%
  filter(Site == "DWSC") %>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2")

Cage_only_DWSC$Mesh <- as.factor(Cage_only_DWSC$Mesh)

dwsc.cf.aov <- aov(Delta_RickCF~Mesh, data = Cage_only_DWSC)
summary(dwsc.cf.aov)

TukeyHSD(dwsc.cf.aov)

# Check assumptions -----------------------------------
# Homogeneity of variances
plot(dwsc.cf.aov, 1)
leveneTest(Delta_RickCF ~ Mesh, data = Cage_only_DWSC) # p<0.05 means not homogeneous

# Normality
plot(dwsc.cf.aov, 2)

dwsc_cf_residuals <- residuals(object = dwsc.cf.aov)
shapiro.test(x = dwsc_cf_residuals ) # p<0.05 means not normal

# Does not meet assumptions: do non-parametric Kruskal-Wallis test---------------
kruskal.test(Delta_RickCF~Mesh, data = Cage_only_DWSC)
```

# Mixed Modeling to incorporate the effect of cage? Reach out to Britt or Rosie for advice. 
```{r}
library(lme4)
library(lmerTest)

M.RVR = lmer(Delta_CF ~ Mesh + (1|Cage), data = Cage_only_RVR, na.action = na.omit)
summary(M.RVR)
anova(M.RVR)

M1.resid <- resid(M.RVR, type = "pearson")
plot(M.RVR)
par(mfrow = c(2,2))

# normality
qqnorm(residuals(M.RVR))
# leverage
ggplot(data.frame(lev=hatvalues(M.RVR),pearson=residuals(M.RVR,type="pearson")),
      aes(x=lev,y=pearson)) +
    geom_point() +
    theme_bw()

ggplot(Cage_only_RVR, aes(y = Mesh, x = M1.resid)) + geom_point()

plot(hist(residuals(M.RVR)))

M.RVR2 = lmer(Delta_CF ~ Mesh + (1|Cage), data = Cage_only_RVR, na.action = na.omit)
summary(M.RVR)
anova(M.RVR)

par(mfrow = c(1,2))
qqnorm(residuals(M.RVR))
plot(residuals(M.RVR))

M.DWSC = lmer(Delta_CF ~ Mesh + (1|Cage), data = Cage_only_DWSC, na.action = na.omit)
summary(M.DWSC)
qqnorm(residuals(M.DWSC))
plot(residuals(M.DWSC))

```

### 2021-12-13 smelt_2019_winterspring/ANOVA_Survival_CF.R

@@ -1,0 +1,793 @@
+# 12/19/19
+# Catarina Pien
+# Comparison of Mesh types 
+# Anova for Delta Smelt Condition Factor 
+# Chi Square for Delta Smelt Survival 
+
+# Set up workspace and load data --------------------------
+rm(list=ls(all=TRUE))
+
+library(car)
+library(FSA)
+library(tidyverse)
+library(ggthemes)
+
+Cagetype_data <- read.csv("smelt_2019_winterspring/Cagetype_data.csv")
+Cagetype_data$Site <- ordered(Cagetype_data$Site, levels = c("RV", "DWSC"))
+
+
+# Summary Table Info ----
+# Pre
+Pre_info <- Cagetype_data %>%
+  select(c(Cage:Pre_CF), Site:Mesh) %>%
+  mutate(Treatment = "Pre") %>%
+  rename(Weight = Pre_Weight_g,
+         FL = Pre_FL_cm,
+         CF = Pre_CF)
+# Post
+Post_info <- Cagetype_data %>%
+  select(c(Cage, Post_FL_cm:Post_CF,Site:Mesh)) %>%
+  mutate(Treatment = "Post") %>%
+  rename(Weight = Post_Weight_g,
+         FL = Post_FL_cm,
+         CF = Post_CF)
+
+Table_info <- rbind(Pre_info, Post_info)
+
+NAs <- filter(Table_info, is.na(CF))
+
+# Combined
+Table_summary <- Table_info %>%
+  filter(!is.na(CF)) %>%
+  group_by(Site, Mesh, Treatment) %>%
+  summarize(meanFL = mean(FL),
+            meanWeight = mean(Weight),
+            n = n())
+
+
+
+
+
+
+
+################## Condition Factor ----
+
+# Make complete cases from column 9
+Delta_CF <- Cagetype_data[,9]
+Cagetype_CF <- Cagetype_data[complete.cases(Delta_CF),]
+
+#write.csv(Cagetype_CF, "CSV_Output/CageCFData_Clean_Jan2019Deploy.csv")
+
+
+# Summarize mean, sd, median, n for condition factor
+Cage.CF <- Cagetype_CF %>%
+  na.omit() %>%
+  filter(Cage!="FCCL1") %>%
+  filter(Cage!="FCCL2") %>%
+  group_by(Site, Mesh)%>%
+  summarize(
+    Delta_CF_Mean = mean(Delta_CF),
+    Delta_CF_sd = sd(Delta_CF),
[…]

### 2021-12-14 smelt_2019_allseasons/2019Diets.Rmd
brought in prior diet code and data, checked to make sure it still runs

---
title: "2019 Diet Data"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

# load packages
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(FSA)
```

# bring in contractor (UW) data
```{r}
diet2 <- read_csv('smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv') #new data, not edited at all

#format 
#rename columns
diet2 <- diet2 %>% rename(Cage.ID = "Cage ID", Contents.Weight = "Total Contents Weight", Prey.Taxa = "Prey Taxa", LH.Stage = "LH Stage")

#add taxa column (choose taxa based on what is present in the dataframe)
diet2$Taxa <- as.character(NA)

diet2[diet2$Prey.Taxa %in% c("Bosmina sp.", "Chydorus sp.", "Daphnia sp.", "Ceriodaphnia sp.", "Chydoridae", "Crangonyx sp.", "Scapholeberis sp.", "Simocephalus sp.", "Eurycercus sp.", "Leydigia sp.", "Cladocera", "Sida sp.", "Alona sp.", "Diaphanosoma sp."),]$Taxa <- "Cladocera"

diet2[diet2$Prey.Taxa %in% c("Americorophium sp.", "Americorophium spinicorne", "Eogammarus confervicolus", "Gammaridea", "Hyallela azteca", "Crangonyx sp.", "Corophiidae", "Amphipoda"),]$Taxa <- "Amphipoda"

diet2[diet2$Prey.Taxa %in% c("Pseudodiaptomus forbesi", "Calanoida", "Eurytemora affinis", "Diaptomidae", "Sinocalanus doerrii", "Osphranticum labronectum"),]$Taxa <- "Calanoida"

diet2[diet2$Prey.Taxa %in% c("Acanthocyclops sp.", "Macrocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Cyclopoida", "Halicyclops sp.", "Mesocyclops sp.", "Tropocyclops sp.", "Tropocyclops sp."),]$Taxa <- "Cyclopoida"

diet2[diet2$Prey.Taxa %in% c("Chironomidae", "Diptera"),]$Taxa <- "Diptera"

diet2[diet2$Prey.Taxa %in% c("empty", "EMPTY"),]$Taxa <- "empty"

diet2[diet2$Prey.Taxa %in% c("Harpacticoida"),]$Taxa <- "Harpacticoida"

diet2[diet2$Prey.Taxa %in% c("Ostracoda"),]$Taxa <- "Ostracoda"

diet2[diet2$Prey.Taxa %in% c("Fish", "Acari", "Insecta", "Bivalvia", "Culicidae", "egg unidentified", "Corixidae", "Hemiptera", "plant seed", "plant matter", "Unidentified", "Mysidacea", "Cumacea"),]$Taxa <- "Other"

new_DF <- diet2[is.na(diet2$Taxa),] #update code above with new prey.taxa that weren't found in previous diets
#there are two "copepoda" entries with no count or location...don't seem that important so I am going to just go ahead and remove them
diet2[diet2$Taxa %in% c("empty"),]$Count <- "0"
diet2 <- diet2[!is.na(diet2$Count),]

#Tag column currently has rows with just the Tag and others with location, date, and tag
#first break those two kinds of columns apart
weird.tag <- diet2[is.na(diet2$Location),]
norm.tag <- diet2[!is.na(diet2$Location),]

#then for break out the Tag ID into Location and tag (remove date)
weird.tag <- weird.tag %>% separate(Tag, c("Location", "X.date", "Tag"))

#remove new date column
weird.tag <- subset(weird.tag, select = -6)

#add mesh types for prototype experiment
#create new column for mesh types
Cage_type <- as.data.frame(matrix(0, ncol = 2, nrow = 6))
colnames(Cage_type) <- c("Cage.ID", "Mesh")

Cage_type$Cage.ID <- c("A", "B", "C", "D", "E", "F")
Cage_type$Mesh <- c("wrap", "large", "small", "small", "wrap", "large")

norm.tag2 <- merge(norm.tag, Cage_type, by = "Cage.ID", all.x = TRUE)

#add mesh types (NA) for summer/fall experiements
weird.tag$Mesh <- NA

#merge the two
diet <- rbind(weird.tag, norm.tag2)

#change location titles 
diet$Location[diet$Location =="RIVERS"] <- "RV.Feb"
diet$Location[diet$Location =="Sac DWSC"] <- "DWSC.Apr"
diet$Location[diet$Location =="SM"] <- "SM.Nov"
diet$Location[diet$Location =="YB"] <- "YB.Nov"
#RV a little trickier with two dates
diet$ld = paste(diet$Location, diet$Date)
diet$Location[diet$ld =="RV 8/28/2019"] <- "RV.Aug"
diet$Location[diet$ld =="RV 11/6/2019"] <- "RV.Nov"
RV <- filter(diet, Location == "RV")
diet$Location[diet$ld =="RV 11/7/2019"] <- "RV.Nov"

diet <- subset(diet, select = -16)
```

# prep merged data for taxa proportion
```{r}
unique(diet$Location)

#remove FCCL controls
diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
diet<-diet[diet$Cage.ID != "FCCL Control",]

#fix fish that were assigned the wrong cage (came up during summary stats, check against dissected fish data, likely E and F were misread)
diet[diet$Tag=='RK10', 'Cage.ID'] <- "E"
diet[diet$Tag=='RN93', 'Cage.ID'] <- "E"

str(diet)
#change count to numeric
diet$Count<-as.numeric(diet$Count)
#output says NAs introduced by coercion - check NA's
newDF <- diet[is.na(diet$Count),]
#one NA next to a gammaridae - comment says that it was too digested and could be more than one individual, to be safe just going to add a count of "1" for this observation; found it on row 413
diet<-diet %>% replace_na(list(Count=1))
#change count to numeric
diet$Count<-as.numeric(diet$Count)

diet$tlc = paste(diet$Tag, diet$Location, diet$Cage.ID)

#sum for taxa abundance among individual fish
taxa_tag<- diet %>% 
  group_by(Location, Mesh, tlc, Taxa) %>% 
  summarize("count.sum"= sum(Count))

#sum taxa across stomach
stomach<- diet %>% 
  group_by(Location, Mesh, tlc) %>% 
  summarize("stomach.sum"= sum(Count))

stomach_abundance<-merge(taxa_tag, stomach, by = "tlc")

stomach_abundance$proportion<-(stomach_abundance$count.sum/stomach_abundance$stomach.sum)*100

#add rows for all taxa for all fish so every taxa shows up for every stomach
full.prop<-stomach_abundance %>% complete(tlc, Taxa) %>%
  as.data.frame()

full.prop.2<-merge(full.prop, stomach, by = "tlc")

#replace count.sum Nas with zeros
full.count<-full.prop.2 %>% replace_na(list(count.sum=0))

#select columns I want for count
full.count<-subset(full.count, select=c("Location", "Mesh", "tlc", "Taxa", "count.sum"))

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Location", "Mesh", "tlc", "Taxa", "proportion"))
#replace proportion Nas with zeros
diet.prop<-full.prop.3 %>% replace_na(list(proportion=0))

#average across fish
diet.prop.mean<- diet.prop %>% 
  group_by(Taxa, Location) %>% 
  summarize("prop.mean"= mean(proportion))
```

# plot number of empty stomachs
## these will not be included in the 100% stacked bar later
```{r}
#order locations
stomach_abundance$Location <- stomach_abundance$Location.x
stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("RV.Feb", "DWSC.Apr", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

#subset for only empty stomachs
empty <- filter(stomach_abundance, Taxa == "empty")

ggplot(empty, aes(Location)) + geom_bar() + scale_x_discrete(drop=FALSE)
```

# plot mean proportion in 100% stacked bar
```{r}
#remove empty
prop<-diet.prop.mean[diet.prop.mean$Taxa != "empty",]

#order locations
prop$Location <- ordered(prop$Location, levels = c("RV.Feb", "DWSC.Apr", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
legend_title <- "Taxa"

ggplot(data=prop, aes(x=Location, y =prop.mean)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))),  position="fill", stat="identity") +
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Mean Contribution to Diet")
```

### Plot methods text (from manuscript): To visualize the relative abundance of different taxa among mesh types, we calculated taxa proportion (taxa abundance/total abundance) for each individual fish’s diet and then averaged these taxa proportions across individuals from each mesh type. These means were then fit to a 100% scale to estimate the mean percent contribution of each taxa to overall mesh type diets. Averaging proportions instead of abundance across fish allowed for the diets of different sizes fish to contribute equally.

### 2022-02-28 smelt_2019_winterspring/check_length_distributions.Rmd
Commit of data and code previously written

---
title: "check_length-distribution"
author: "Catarina Pien"
date: "12/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(car)
library(FSA)
library(tidyverse)
library(ggthemes)
```

```{r}
Cagetype_data <- read.csv("smelt_2019_winterspring/Cagetype_data.csv")
Cagetype_data$Site <- ordered(Cagetype_data$Site, levels = c("RV", "DWSC"))
```

```{r}
NAs <- Cagetype_data %>%
  filter(is.na(Delta_CF),
         Mesh!= "Control")

```

### 2022-02-28 smelt_2019_winterspring/DWSC_RVR_Summary_Stats.R

@@ -1,0 +1,348 @@
+# Look at summary stats of Cage Data
+# 5/2/19
+# Catarina Pien
+
+rm(list=ls(all=TRUE))
+library(tidyverse)
+
+# Load data --------------------------------------------
+DWSC <- read.csv("smelt_2019_winterspring/data_raw/DWSC_Edited_Pre-Post_Data.csv")
+DWSC$Site <- "DWSC"
+RVR <- read.csv("smelt_2019_winterspring/data_raw/RVERS_Edited_Pre-Post_Data.csv")
+RVR$Site <- "RV"
+FCCL <- read.csv("smelt_2019_winterspring/data_raw/FCCL_Weight_Length_CF.csv")
+FCCL_ed <- FCCL %>%
+  select(c(1,4,5,6,9,10,11,12,13))
+Cage1 <- rbind(DWSC, RVR)
+Cage2 <- Cage1 %>%
+  select(-c(Tag, Pre_post_Match))
+Cage <- rbind(Cage2, FCCL_ed) %>%
+  filter(Cage != "FC1") %>%
+  filter(Cage != "FC2")
+
+# Add cage type in --------------------------------------
+Cage_type <- as.data.frame(matrix(0, ncol = 2, nrow = 8))
+colnames(Cage_type) <- c("Cage", "Mesh")
+
+Cage_type$Cage <- c("A", "B", "C", "D", "E", "F", "FCCL1", "FCCL2")
+Cage_type$Mesh <- c("wrap", "large", "small", "small", "wrap", "large", "control", "control")
+
+Cagetype_data <- merge(Cage, Cage_type, by = "Cage", all.x = TRUE)
+
+# Write files
+# write.csv(Cagetype_data, "CSV_Output/Cagetype_data.csv")
+
+# Reorganize data -------------------------------
+Cage$Site <- ordered(Cagetype_data$Site, levels = c("RV", "DWSC"))
+Cage$Delta_Wt <- Cage$Post_Weight_g-Cage$Pre_Weight_g
+Cage$Site <- ordered(Cage$Site, levels = c("RV", "DWSC"))
+
+# Rearrange data to be able to look at pre-post differences 
+Cage_FL <- pivot_longer(Cagetype_data, cols = c(Pre_FL_cm, Post_FL_cm), names_to = "Pre_Post", 
+                        values_to = "FL" ) # for FL
[…]

### 2022-03-01 smelt_2019_allseasons/plot_weight_length_cf.Rmd
Updated code to change Mesh to enclosure type and add the delta symbol

@@
 ```{r}
-smeltdata <- read_csv("data_clean/clean_smelt_cf_2019.csv", col_types = cols(.default="f", FL_cm = "d", Weight_g = "d", K = "d", ID = "c"))
+library(dplyr)
+library(ggplot2)
+library(readr)
+library(here)
+```
+
+```{r}
+smeltdata <- read_csv(here("smelt_2019_allseasons", "data_clean", "clean_smelt_cf_2019.csv"), col_types = cols(.default="f", FL_cm = "d", Weight_g = "d", K = "d", ID = "c"))
 glimpse(smeltdata)

### 2022-03-01 smelt_2019_winterspring/Length_Weight _Figure_HH.R

@@ -9,10 +9,10 @@ library(car)
 library(FSA)
 library(tidyverse)
 library(ggthemes)
-setwd("//cnrastore-des/DS Enclosures/Analysis")
-Cagetype_data <- read.csv("CSV_Output/Cagetype_data.csv") %>%
-  mutate(Mesh = recode(Mesh, large = "B", small = "A", wrap = "C")) 
-Cagetype_data$Site <- ordered(Cagetype_data$Site, levels = c("RV", "DWSC"))
+
+Cagetype_data <- read.csv(here("smelt_2019_winterspring", "data_clean", "Cagetype_data.csv")) %>%
+  mutate(Site = factor(Site, levels = c("RV", "DWSC")),
+         Enclosure = ifelse(Mesh == "wrap", "A", ifelse(Mesh == "large", "B", ifelse(Mesh == "small", "C", ifelse(Mesh == "control", "control", NA)))))
 
 # ----------------------------------------------------------------------------------
 ################## Condition Factor ################################################
@@ -109,8 +109,8 @@ FCCL <- Cagetype_CF %>%
 
 ## Plots ------------------------------------------------------------------------
 
-### Length boxplot by site #####################
 
+### Length barplot by site #####################
 Cageonly <- Cagetype_data %>%
   filter(Cage != "FCCL1") %>%
   filter(Cage != "FCCL2") %>%
@@ -194,15 +194,18 @@ ann_text <- data.frame(
 CagePrePost$PrePost <- factor(CagePrePost$PrePost,
                        levels = c('Pre_FL_cm','Post_FL_cm'),ordered = TRUE)
 
+
+################# MANUSCRIPT:: Length box plot by site ---------
+
 MeanLenghtplot<- ggplot(data=CagePrePost) +
-  geom_boxplot(outlier.size=-1,aes(x=Mesh, y=Length1,  fill = PrePost)) +
+  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=Length1,  fill = PrePost)) +
   facet_wrap(~Site) +
   labs(y = "Length (cm)") +
   #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
   #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
   #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)++
[…]

### 2022-03-01 smelt_2019_winterspring/Length_Weight_CF_Figures_Manuscript.R
Committing figures and renamed code

@@ -1,7 +1,8 @@
 # 5/10/21
-# Haley Hudson 
-# Creating Figures/Tables for Weight and Length
-#for additional information along with condition factor
+# Last modified 3/1/2022
+# Haley Hudson / Catarina Pien
+# Creating Figures/Tables for Weight and Length, Condition factor
+# All Cat's 2019 winter/spring manuscript plots are here
 
 # Set up workspace and load data ----------------------------------------------------------------------
 rm(list=ls(all=TRUE))
@@ -14,9 +15,7 @@ Cagetype_data <- read.csv(here("smelt_2019_winterspring", "data_clean", "Cagetyp
   mutate(Site = factor(Site, levels = c("RV", "DWSC")),
          Enclosure = ifelse(Mesh == "wrap", "A", ifelse(Mesh == "large", "B", ifelse(Mesh == "small", "C", ifelse(Mesh == "control", "control", NA)))))
 
-# ----------------------------------------------------------------------------------
-################## Condition Factor ################################################
-# -----------------------------------------------------------------------------------
+################## Condition Factor ---------------------------------------------------------------------------------
 
 # Make complete cases from column 9
 Delta_CF <- Cagetype_data[,9]
@@ -47,8 +46,7 @@ FCCL_CF <- Cagetype_CF %>%
   mutate(delta.CF = round(mean.PostCF - mean.PreCF,2))
 #write.csv(Cage.CF, "Condition_Factors.csv")
 
-###############################################################################
-#                      Length and Weight
+#Length and Weight###########################-------------------            
 
 # Summarize mean, sd, median, n for Pre and Post Length and Width
 Cagedata <- Cagetype_CF %>%
@@ -92,8 +90,7 @@ FCCL <- Cagetype_CF %>%
   mutate(delta.Length = round(PoL_Mean - PreL_Mean,2)) %>%
   mutate(delta.weight = round(PoW_Mean - PreW_Mean,2))
 
-###############################################################################
-#------------Tables-------------------------------------------------------
+#Tables##################################################------------------
 
 #Rename column
 #FCCL<- FCCL %>% 
@@ -107,7 +104,7 @@ FCCL <- Cagetype_CF %>%
 #DWSC_survival <- table(Cagetype_survival_DWSC$Mesh, Cagetype_survival_DWSC$Survived)
 
 
-## Plots ------------------------------------------------------------------------
[…]

### 2022-09-21 smelt_2019_allseasons/plot_weight_length_cf.Rmd

--- 2021-12-10 smelt_2019_allseasons/plot_weight_length_cf.Rmd
@@
 ```{r}
+level_key = c(Pre = "Pre-Deployment", Post = "Post-Deployment")
+level_key = c(`Pre-Deployment` = "Pre", `Post-Deployment` = "Post")
 summarydata <- smeltdata2 %>%
@@
             sdWeight = sd(Weight_g, na.rm = TRUE),
-            n = n())
+            n = n())%>%
+  ungroup() %>%
+  mutate(Period = recode(Period,"Pre" = "Pre-Deployment", "Post" = "Post-Deployment"))
 ```
 
-Plot data
+Plot K
 ```{r}
-ggplot(smeltdata2, aes(x = Period, y = K, fill = Site)) + 
+box_K <- ggplot(smeltdata2, aes(x = Period, y = K, fill = Site)) + 
   geom_boxplot() + 
   facet_wrap(Deployment~.) + 
-  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + theme_bw()
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  labs(y = "Condition Factor (K)") + 
+  theme_bw()+
+  theme(axis.title.x = element_blank(),
+        axis.text = element_text(size = 11),
+        strip.text = element_text(size = 11),
+        legend.text = element_text(size = 11),
+        legend.title = element_text(size = 11.5))
 ```
+
+Plot Length
+```{r}
+box_FL <- ggplot(smeltdata2, aes(x = Period, y = FL_cm, fill = Site)) + 
+  geom_boxplot() + 
+  facet_wrap(Deployment~.) + 
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  labs(y = "Fork Length (cm)") +
+  theme_bw()+
+  theme(axis.title.x = element_blank(),
+        axis.text = element_text(size = 11),
+        strip.text = element_text(size = 11))
+```
+
+Plot Weight
+```{r}
+box_Wt <- ggplot(smeltdata2, aes(x = Period, y = Weight_g, fill = Site)) + 
+  geom_boxplot() + 
+  facet_wrap(Deployment~.) + 
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  labs(y = "Weight (g)") + 
+  theme_bw()+
+  theme(axis.title.x = element_blank(),
+        axis.text = element_text(size = 11),
+        strip.text = element_text(size = 11))
+```
+
+```{r}
+library(ggpubr)
+figure_comb <- ggarrange(box_FL, box_Wt, box_K, nrow = 3, common.legend = TRUE)
+
+tiff(filename = file.path("smelt_2019_allseasons/figures/FL-Wt-K.tiff"), res = 300, width = 7, height = 7, units = "in", pointsize = 10, type = "cairo", compression = "lzw")
+annotate_figure(figure_comb, bottom = text_grob("Deployment Period", size = 11) )
+dev.off()
+
+```

### 2022-09-21 smelt_2019_winterspring/RelativeCF_2019Winter.Rmd

@@
 library(tidyverse)
+library(here)
 
@@
 ```{r import}
-setwd("V:/Analysis/")
-Cagetype_data <- read.csv("CSV_Output/Cagetype_data.csv")
+Cagetype_data <- read.csv(here("smelt_2019_winterspring", "data_clean", "Cagetype_data.csv"))
 Cagetype_data$Site <- ordered(Cagetype_data$Site, levels = c("RV", "DWSC"))

### 2022-09-21 smelt_2019_winterspring/tag_loss.Rmd

---
title: "tag_loss"
author: "Catarina Pien"
date: '2022-09-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r}
DWSC_raw <- read.csv(here("smelt_2019_winterspring", "data_raw", "DWSC_Edited_Pre-Post_Data.csv"))%>%
  filter(!(grepl("FC", Cage))) 
RV_raw <- read.csv(here("smelt_2019_winterspring", "data_raw", "RVERS_Edited_Pre-Post_Data.csv")) %>%
  filter(!(grepl("FC", Cage)))

```

Look at no tags
```{r}
NT_DWSC <- DWSC_raw %>%
  mutate(NT = ifelse(grepl("NT", Tag), "NT", "Tag")) %>%
  mutate(Site = "DWSC")
NT_RV <- RV_raw %>%
  mutate(NT = ifelse(grepl("NT", Tag), "NT", "Tag")) %>%
  mutate(Site = "RV")
NT <- rbind(NT_DWSC, NT_RV) %>%
  mutate(Site = factor(Site, levels = c("RV", "DWSC")),
         Enclosure = ifelse(Cage %in% c("B","F"), "large", ifelse(Cage %in% c("A", "E" ), "wrap", ifelse(Cage %in% c("C", "D"), "small", "FC"))))

```

Tag loss rates - used these numbers in manuscript
```{r}
NT_prop <- NT %>%
  group_by(Site, Enclosure, NT) %>%
  summarize(n = n()) %>%
  pivot_wider(names_from = "NT", values_from = "n") %>%
  mutate(prop = NT/(NT+Tag)*100)
```

Plot
```{r}
NT_summary <- NT %>%
  filter(grepl("NT", Tag)) %>%
  group_by(Site, Enclosure) %>%
  summarize(n = n())

ggplot(NT_summary) + geom_col(aes(x = Enclosure,  y = n, fill = Site), position = "dodge2") + theme_bw()
```

### 2022-09-21 smelt_2019_winterspring/ZoopPlotting.Rmd
adding zoop data and analysis to project

---
librarytitle: "Zoop Plotting"
output: html_document
editor_options: 
  chunk_output_type: console
---

# load packages
```{r}
library(tidyverse)
library(lubridate)
library(emmeans)
library(multcomp)
setwd("C:/Users/nkwan/Desktop/Zoop'19")
```

# load data
```{r}
zoop <- read_csv("ZoopDataCombined_biomass_qc'ed_12.19.19.csv")

zoop$Date<-mdy(zoop$Date)

zoop$RingSize_m <- zoop$RingSize_cm/100

split<- split(zoop, zoop$Method)

write_excel_csv(split[["Throw"]], "C:/Users/nkwan/Desktop/Zoop'19/throw_method_zoop.csv")

write_excel_csv(split[["Tow"]], "C:/Users/nkwan/Desktop/Zoop'19/tow_method_zoop.csv")

throw<- read_csv("throw_method_zoop.csv")
tow<- read_csv("tow_method_zoop.csv")
```

# calculate abundance
```{r}
#calculate abundance for tow samples

tow$distance<-(tow$Rotations)*26873/999999 #R: Rotor constant (Regular flow = 26873, Low flow = 57560) - used Reg flow meter for this study
tow$volumesampled<-((pi*(tow$RingSize_m^2))/4)*tow$distance
tow$samplecount<-(tow$TotalVolume_ml/tow$Subsampled_ml)*tow$Count
tow$ind_m3<-tow$samplecount/tow$volumesampled

#to incorporate biomass
tow$samplebiomass<-(tow$TotalVolume_ml/tow$Subsampled_ml)*tow$Total.Biomass
tow$bio_m3<-tow$samplebiomass/tow$volumesampled

#ind_m3 = individuals/m3

#calculate abundance for throw samples

throw$distance<- "NA"
throw$radius<-throw$RingSize_m/2
throw$volumesampled<- throw$radius*2*pi*throw$TowDistance_m+(2*pi*(throw$radius^2))
throw$samplecount<-(throw$TotalVolume_ml/throw$Subsampled_ml)*throw$Count
throw$ind_m3<-throw$samplecount/throw$volumesampled

#to incorporate biomass
throw$samplebiomass<-(throw$TotalVolume_ml/throw$Subsampled_ml)*throw$Total.Biomass
throw$bio_m3<-throw$samplebiomass/throw$volumesampled
```

# bind throw and tow methods & calcualte species abundance for Table 6
```{r}
#combine
tow$radius<-tow$RingSize_m*2
abundance <- rbind(tow, throw)
abundance$Date<-ymd(abundance$Date)
abundance$Taxa<-as.factor(abundance$Taxa)
abundance$ind_m3<-as.numeric(abundance$ind_m3)

#put together results for Table 6
top.sp<-abundance %>% 
  group_by(SiteName, Taxa, ID) %>% 
  summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))

#remove microzooplankton
top.sp <- top.sp[top.sp$Taxa != "Microzoo",]

#sum by site (to get denominator)
sum<-top.sp %>% 
  group_by(SiteName) %>% 
  summarize("sum"= sum(bio))

#break into DWSC and RV
dw <- top.sp %>% filter(SiteName == "DWSC")
rv <- top.sp %>% filter(SiteName == "RV")

dw$DWSC.Bio <- dw$bio
dw$DWSC.Perc <- (dw$DWSC.Bio/12832.26)*100
dw <- dw[c(2,3,7,8)]
dw2 <- subset(dw, DWSC.Bio!=0)

rv$RV.Bio <- rv$bio
rv$RV.Perc <- (rv$RV.Bio/32782.81)*100
rv <- rv[c(2,3,7,8)]
rv2 <- subset(rv, RV.Bio!=0)

#merge
all <- merge(rv2,dw2,by=c("ID","Taxa"),all=TRUE)

#change NA to 0  
all[is.na(all)] <- 0

write_excel_csv(all, "species.table.csv")
```

# stacked bar across week plot
```{r}
taxa<-abundance %>% 
  group_by(SiteName, Date, Taxa) %>% 
  summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))

#create week column
taxa$Week <- epiweek(taxa$Date)

#zeros already exist, go ahead and average 
taxa.week<-taxa %>% 
  group_by(SiteName, Week, Taxa) %>% 
  summarize("bio.mean"=mean(bio))

taxa.week$Week2 <- NA

taxa.week$Week2[taxa.week$Week == 9] <- 1
taxa.week$Week2[taxa.week$Week == 10] <- 2
taxa.week$Week2[taxa.week$Week == 11] <- 3
taxa.week$Week2[taxa.week$Week == 12] <- 4
taxa.week$Week2[taxa.week$Week == 13] <- 5
taxa.week$Week2[taxa.week$Week == 4] <- 1
taxa.week$Week2[taxa.week$Week == 5] <- 2
taxa.week$Week2[taxa.week$Week == 6] <- 3
taxa.week$Week2[taxa.week$Week == 7] <- 4
taxa.week$Week2[taxa.week$Week == 8] <- 5

#plot all zoop

cbPalette <- c("#009E73", "#E69F00", "#56B4E9", "#D55E00", "#F0E442", "#999999", "#CC79A7")
legend_title <- "Taxa"

ggplot(data = taxa.week, aes(x=Week2, y=bio.mean)) +
  geom_bar(stat = "identity", data=taxa.week, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Macrozoo", "Microzoo"))), colour="black", width = .5) +
  facet_wrap(~SiteName)+
  theme_bw() + 
    scale_fill_manual(legend_title, values=cbPalette)+theme(axis.title.x = element_blank()) +
  labs(x = "Week") +
  labs(y = "Biomass (ugC/m3)")+
 theme(legend.position="bottom")+theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 25))

#remove microzooplankton
taxa.week.2 <- taxa.week[taxa.week$Taxa != "Microzoo",]

taxa.week.2$SiteName = factor(taxa.week.2$SiteName, levels=c('RV','DWSC'))

taxa.week.2$Taxa <- as.character(taxa.week.2$Taxa)
taxa.week.2$Taxa[taxa.week.2$Taxa=='Macrozoo'] <- 'Other'

windowsFonts(Times = windowsFont("Times New Roman"))

#plot just macrozoop
z<-ggplot(data = taxa.week.2, aes(x=Week2, y=bio.mean)) +
  geom_bar(stat = "identity", data=taxa.week.2, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Other"))), colour="black", width = .5) +
    facet_wrap(~SiteName)+
  theme_bw() + 
    scale_fill_manual(legend_title, values=cbPalette)+
  labs(x = "Week") +
  labs(y = "Biomass (ugC/m3)")+
 theme(legend.position="right")+
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size =17),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 17),
        strip.text.x = element_text(size = 17),
        text=element_text(family = "Times"))
z
print(z)

tiff(filename="Fig5.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=3.75, #height you can adjust according to your plot
    res=600, compression="lzw")
print(z)
dev.off()
```

# repeated measures ANOVA
```{r}
#combine taxa 
for.mod<-taxa.week.2 %>% 
  group_by(SiteName, Week, Week2) %>% 
  summarize("bio.all"=sum(bio.mean))

shapiro.test(for.mod$bio.all) #not significant

model<-lm(bio.all~SiteName*Week2, data=for.mod)
anova(model)

shapiro.test(resid(model)) #insigificant

leveneobject<- lm(abs(resid(model))~SiteName*Week2, data=for.mod)
anova(leveneobject) #insignificant

marginal = emmeans(model, 
                   ~ SiteName*Week2)

cld(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey") #DWSC and RV different
```

### 2022-09-21 smelt_2019_winterspring/Diet.Rmd
adding diet data and analysis to project

---
editor_options: 
  chunk_output_type: console
---

# load packages
```{r}
library(tidyverse)
library(lubridate)
library(emmeans)
library(multcompView)
```

# bring in data
```{r}
diet <- read_csv("smelt_2019_winterspring/data_raw/DSM Cage Diets 2019 update_taxa.csv")
diet$Location <- ordered(diet$Location, levels = c("RVR", "DWSC"))
diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
diet<-diet[diet$Cage.ID != "FCCL Control",]

#fix fish that were assigned the wrong cage (came up during summary stats, check against dissected fish data, likely E and F were misread)
diet[diet$Tag=='RK10', 'Cage.ID'] <- "E"
diet[diet$Tag=='RN93', 'Cage.ID'] <- "E"

#create new column for mesh types
Cage_type <- as.data.frame(matrix(0, ncol = 2, nrow = 6))
colnames(Cage_type) <- c("Cage.ID", "Mesh")

Cage_type$Cage.ID <- c("A", "B", "C", "D", "E", "F")
Cage_type$Mesh <- c("wrap", "large", "small", "small", "wrap", "large")

diet_type <- merge(diet, Cage_type, by = "Cage.ID", all.x = TRUE)

#pull in weight data
DWSC <- read.csv("smelt_2019_winterspring/data_raw/DWSC_Edited_Pre-Post_Data.csv")
DWSC$Site <- "DWSC"
RVR <- read.csv("smelt_2019_winterspring/data_raw/RVERS_Edited_Pre-Post_Data.csv")
RVR$Site <- "RVR"
Cage <- rbind(DWSC, RVR)

#bind fish measurements with stomach contents (note- some lost due to missing letters in ID's-update for final)
total <- merge(diet_type, Cage, by=c("Tag"))

#create instantaneous ration column
total$IR <- (total$Contents.Weight/total$Post_Weight_g)*100

#average for IR & fullness
mean.IR<- total %>% 
  group_by(Location, Mesh, Tag) %>% 
  summarize("mean.IR"= mean(IR), "mean.full"=mean(Fullness))

#split into RV and DWSC
split<- split(mean.IR, mean.IR$Location)
write_excel_csv(split[["RVR"]], "smelt_2019_winterspring/data_raw/diet.RVR.csv")
write_excel_csv(split[["DWSC"]], "smelt_2019_winterspring/data_raw/diet.DWSC.csv")
RVR<- read_csv("smelt_2019_winterspring/data_raw/diet.RVR.csv")
DWSC<- read_csv("smelt_2019_winterspring/data_raw/diet.DWSC.csv")

RVR$Mesh<-as.factor(RVR$Mesh)
DWSC$Mesh<-as.factor(DWSC$Mesh)
```

# stats on IR
```{r}
##Shapiro-Wilk's method
shapiro.test(RVR$mean.IR) #significant
shapiro.test(DWSC$mean.IR) #significant

#log transform
RVR[,6] <- log(RVR[c(4)] +1)
shapiro.test(RVR$mean.IR.1) #insiginificant
plotNormalHistogram(RVR$mean.IR.1)

DWSC$mean.IR.1 <- log(DWSC[c(4)] +1)
shapiro.test(DWSC$mean.IR.1) #insiginificant
plotNormalHistogram(DWSC$mean.IR.1)

#RVR anova 
RVR.IR.mod <- lm(mean.IR.1 ~ Mesh, data=RVR)
anova(RVR.IR.mod) #significant

shapiro.test(resid(RVR.IR.mod)) #insignificant

leveneobject<- lm(abs(resid(RVR.IR.mod))~Mesh, data=RVR)
anova(leveneobject) #good

#post hoc test
marginal = emmeans(RVR.IR.mod, 
                   ~ Mesh)

CLD(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey")

#DWSC anova 
DW.IR.mod <- lm(mean.IR.1 ~ Mesh, data=DWSC)
anova(DW.IR.mod) #insignificant

shapiro.test(resid(DW.IR.mod)) #insignificant

leveneobject<- lm(abs(resid(DW.IR.mod))~Mesh, data=DWSC)
anova(leveneobject) #good

#post hoc test
marginal = emmeans(DW.IR.mod, 
                   ~ Mesh)

CLD(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey")
```

# percent of each taxa for new Table 7 created on 3/7/2022
```{r}
diet_type$Count[which(diet_type$Count == "1 maybe 2")] <- 2

diet_type$Count <- as.numeric(diet_type$Count)

taxa.perct<- diet_type %>% 
  group_by(Location, Taxa, Prey.Taxa) %>% 
  summarize("count.sum"= sum(Count, na.rm=TRUE))

taxa.tot<- diet_type %>% 
  group_by(Location) %>% 
  summarize("count.sum"= sum(Count, na.rm=TRUE))

taxa.perct$Total <- ifelse(taxa.perct$Location=="RVR", 1548,
        ifelse(taxa.perct$Location=="DWSC", 5831, NA))

taxa.perct$percent <- (taxa.perct$count.sum/taxa.perct$Total)*100

split<- split(taxa.perct, taxa.perct$Location)
write_excel_csv(split[["RVR"]], "C:/Users/nkwan/Desktop/diet winter '19/perc.RVR.csv")
write_excel_csv(split[["DWSC"]], "C:/Users/nkwan/Desktop/diet winter '19/perc.DWSC.csv")
RVR.p<- read_csv("perc.RVR.csv")
DWSC.p<- read_csv("perc.DWSC.csv")

taxa.perct2 <- merge(RVR.p, DWSC.p, by="Prey.Taxa", all = TRUE)

taxa.perct2[is.na(taxa.perct2)] = 0

taxa.perct3 <- taxa.perct2[c(1,3,4,6,8,9,11)]

write_excel_csv(taxa.perct3, "C:/Users/nkwan/Desktop/diet winter '19/tableresults.csv")
```

# proportion taxa
```{r}
diet_type$Count<-as.numeric(diet_type$Count)

#sum for taxa abundance among individual fish
taxa_tag<- diet_type %>% 
  group_by(Location, Mesh, Cage.ID, Tag, Taxa, LH.Stage) %>% 
  summarize("count.sum"= sum(Count))

#mean for stomach mass
taxa<- taxa_tag %>% 
  group_by(Location, Mesh, Cage.ID, Tag) %>% 
  summarize("stomach.sum"= sum(count.sum))

stomach_abundance<-merge(taxa_tag, taxa, by = "Tag")

stomach_abundance$proportion<-(stomach_abundance$count.sum/stomach_abundance$stomach.sum)*100

#add rows for all taxa for all fish
full.prop<-stomach_abundance %>% complete(Tag, Taxa) %>%
  as.data.frame()

full.prop.2<-merge(full.prop, taxa, by = "Tag")

#replace count.sum Nas with zeros
full.count<-full.prop.2 %>% replace_na(list(count.sum=0))

#select columns I want for count
full.count<-subset(full.count, select=c("Location", "Mesh", "Tag", "Taxa", "LH.Stage", "count.sum"))

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Tag", "Taxa", "proportion", "Location", "Mesh"))
#replace proportion Nas with zeros
diet.prop<-full.prop.3 %>% replace_na(list(proportion=0))

#average across fish
diet.prop.mean<- diet.prop %>% 
  group_by(Taxa, Location, Mesh) %>% 
  summarize("prop.mean"= mean(proportion))
```

# plot count proportion in 100% stacked bar - final figure
```{r}
#remove empty
full.count.e<-full.count[full.count$Taxa != "empty",]

cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
legend_title <- "Taxa"

ggplot(data=full.count.e, aes(x=Mesh, y =count.sum)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))),  position="fill", stat="identity") +
  facet_grid(~Location)+
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Proportion of Prey Consumed") +  
  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.title = element_text(size = 23), 
    axis.text = element_text(size = 20), 
    axis.text.x = element_text(size = 20), 
    axis.text.y = element_text(size = 20), 
    legend.text = element_text(size = 20), 
    legend.title = element_text(size = 20))+
  theme(strip.text.x = element_text(size = 20))
```

# plot mean proportion in bar plot and 100% stacked bar
```{r}
#remove empty
diet.prop.mean.e<-diet.prop.mean[diet.prop.mean$Taxa != "empty",]

#bar plot
ggplot(data=diet.prop.mean.e, aes(x=Mesh, y =prop.mean)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))), position="dodge", stat="identity") +
  facet_grid(~Location)+
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Average Proportion of Diet") +  
  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.title = element_text(size = 23), 
    axis.text = element_text(size = 20), 
    axis.text.x = element_text(size = 20), 
    axis.text.y = element_text(size = 20), 
    legend.text = element_text(size = 20), 
    legend.title = element_text(size = 25))+
  theme(strip.text.x = element_text(size = 20))

#stack bar plot
windowsFonts(Times = windowsFont("Times New Roman"))

d<-ggplot(data=diet.prop.mean.e, aes(x=Mesh, y =prop.mean)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))), position="fill", stat="identity") +
  facet_grid(~Location)+
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  scale_y_continuous(labels=percent)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Mean Contribution to Diet") +  
  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.title = element_text(size = 17), 
    axis.text = element_text(size = 16), 
    legend.text = element_text(size = 16), 
    legend.title = element_text(size = 17),
    strip.text.x = element_text(size = 17),
    text=element_text(family = "Times"))
print(d)

tiff(filename="Fig6.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=4.00, #height you can adjust according to your plot
    res=600, compression="lzw")
print(d)
dev.off()

write_excel_csv(diet.prop.mean.e, "C:/Users/Nicole Aha/Desktop/Analysis/Analysis/Data/diet.prop.mean.csv")
```

### 2022-09-21 smelt_2019_winterspring/ZoopPlotting.Rmd
updates to zoop code

@@
 library(multcomp)
-setwd("C:/Users/nkwan/Desktop/Zoop'19")
 ```
@@
 ```{r}
-zoop <- read_csv("ZoopDataCombined_biomass_qc'ed_12.19.19.csv")
+zoop <- read_csv("smelt_2019_winterspring/data_raw/ZoopDataCombined_biomass_qc'ed_12.19.19.csv")
 
@@
 
-write_excel_csv(split[["Throw"]], "C:/Users/nkwan/Desktop/Zoop'19/throw_method_zoop.csv")
+write_excel_csv(split[["Throw"]], "smelt_2019_winterspring/data_raw/throw_method_zoop.csv")
 
-write_excel_csv(split[["Tow"]], "C:/Users/nkwan/Desktop/Zoop'19/tow_method_zoop.csv")
+write_excel_csv(split[["Tow"]], "smelt_2019_winterspring/data_raw/tow_method_zoop.csv")
 
-throw<- read_csv("throw_method_zoop.csv")
-tow<- read_csv("tow_method_zoop.csv")
+throw<- read_csv("smelt_2019_winterspring/data_raw/throw_method_zoop.csv")
+tow<- read_csv("smelt_2019_winterspring/data_raw/tow_method_zoop.csv")
 ```
@@
 
-write_excel_csv(all, "species.table.csv")
+write_excel_csv(all, "smelt_2019_winterspring/data_clean/species.table.csv")
 ```
@@
 
-tiff(filename="Fig5.tiff", 
+tiff(filename="smelt_2019_winterspring/figures/zoopfig.tiff", 
     units="in", 

### 2022-09-22 smelt_2019_winterspring/Diet.Rmd
updates to diet analysis to explore random effect of cage

@@
 library(emmeans)
-library(multcompView)
+library(multcomp)
+library(rcompanion)
+library(lme4)
+library(Rcpp)
 ```
@@
 mean.IR<- total %>% 
-  group_by(Location, Mesh, Tag) %>% 
+  group_by(Location, Mesh, Tag, Cage.ID) %>% 
   summarize("mean.IR"= mean(IR), "mean.full"=mean(Fullness))
@@
 split<- split(mean.IR, mean.IR$Location)
-write_excel_csv(split[["RVR"]], "smelt_2019_winterspring/data_raw/diet.RVR.csv")
-write_excel_csv(split[["DWSC"]], "smelt_2019_winterspring/data_raw/diet.DWSC.csv")
+#write_excel_csv(split[["RVR"]], "smelt_2019_winterspring/data_raw/diet.RVR.csv")
+#write_excel_csv(split[["DWSC"]], "smelt_2019_winterspring/data_raw/diet.DWSC.csv")
 RVR<- read_csv("smelt_2019_winterspring/data_raw/diet.RVR.csv")
@@
 #log transform
-RVR[,6] <- log(RVR[c(4)] +1)
-shapiro.test(RVR$mean.IR.1) #insiginificant
-plotNormalHistogram(RVR$mean.IR.1)
+RVR$mean.IR.log <- log(RVR$mean.IR +1)
+shapiro.test(RVR$mean.IR.log) #insignificant
+plotNormalHistogram(RVR$mean.IR.log)
 
-DWSC$mean.IR.1 <- log(DWSC[c(4)] +1)
-shapiro.test(DWSC$mean.IR.1) #insiginificant
-plotNormalHistogram(DWSC$mean.IR.1)
+DWSC$mean.IR.log <- log(DWSC$mean.IR +1)
+shapiro.test(DWSC$mean.IR.log) #insignificant
+plotNormalHistogram(DWSC$mean.IR.log)
 
 #RVR anova 
-RVR.IR.mod <- lm(mean.IR.1 ~ Mesh, data=RVR)
+RVR.IR.mod <- lm(mean.IR.log ~ Mesh, data=RVR)
 anova(RVR.IR.mod) #significant
@@
 
-CLD(marginal,
+cld(marginal,
     alpha   = 0.05, 
@@
 
+#Should Cage.ID be included as a random effect? Looked over with Rosie and lmer model gives singularity issue, seperate models with Cage.ID don't show significance - okay to leave out
+  #ggplot(RVR,aes(x=Mesh,y=mean.IR.log,col=Cage.ID)) + geom_jitter() + geom_boxplot(alpha=0.2)
+  #RVR.IR.mod2 <- lmer(mean.IR.log ~ Mesh + (1|Cage.ID), data=RVR)
+  #summary(mod)
+  #ranef(RVR.IR.mod2) #saying no variance by cage
+  #RVR.IR.mod3 <- lm(mean.IR.log ~ Cage.ID, data=RVR)
+  #RVR.IR.mod4 <- lm(mean.IR.log ~ Mesh + Cage.ID, data=RVR)
+
 #DWSC anova 
-DW.IR.mod <- lm(mean.IR.1 ~ Mesh, data=DWSC)
+DW.IR.mod <- lm(mean.IR.log ~ Mesh, data=DWSC)
 anova(DW.IR.mod) #insignificant
+
+DW.IR.mod2 <- lmer(mean.IR.log ~ Mesh + (1|Cage.ID), data=DWSC)
+
+ranef(DW.IR.mod2) #close to 0 but some variance
+
+ggplot(DWSC,aes(x=Mesh,y=mean.IR.log,col=Cage.ID)) + geom_jitter() + geom_boxplot(alpha=0.2)
+
+anova(DW.IR.mod2)
 
@@
     adjust  = "tukey")
-```
-
-# percent of each taxa for new Table 7 created on 3/7/2022
-```{r}
-diet_type$Count[which(diet_type$Count == "1 maybe 2")] <- 2
-
-diet_type$Count <- as.numeric(diet_type$Count)
-
-taxa.perct<- diet_type %>% 
-  group_by(Location, Taxa, Prey.Taxa) %>% 
-  summarize("count.sum"= sum(Count, na.rm=TRUE))
-
-taxa.tot<- diet_type %>% 
-  group_by(Location) %>% 
-  summarize("count.sum"= sum(Count, na.rm=TRUE))
-
-taxa.perct$Total <- ifelse(taxa.perct$Location=="RVR", 1548,
-        ifelse(taxa.perct$Location=="DWSC", 5831, NA))
-
-taxa.perct$percent <- (taxa.perct$count.sum/taxa.perct$Total)*100
-
-split<- split(taxa.perct, taxa.perct$Location)
-write_excel_csv(split[["RVR"]], "C:/Users/nkwan/Desktop/diet winter '19/perc.RVR.csv")
-write_excel_csv(split[["DWSC"]], "C:/Users/nkwan/Desktop/diet winter '19/perc.DWSC.csv")
-RVR.p<- read_csv("perc.RVR.csv")
-DWSC.p<- read_csv("perc.DWSC.csv")
-
-taxa.perct2 <- merge(RVR.p, DWSC.p, by="Prey.Taxa", all = TRUE)
-
-taxa.perct2[is.na(taxa.perct2)] = 0
-
-taxa.perct3 <- taxa.perct2[c(1,3,4,6,8,9,11)]
-
-write_excel_csv(taxa.perct3, "C:/Users/nkwan/Desktop/diet winter '19/tableresults.csv")
 ```
@@
 
-# plot count proportion in 100% stacked bar - final figure
-```{r}
-#remove empty
-full.count.e<-full.count[full.count$Taxa != "empty",]
-
-cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
-legend_title <- "Taxa"
-
-ggplot(data=full.count.e, aes(x=Mesh, y =count.sum)) +
-    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))),  position="fill", stat="identity") +
-  facet_grid(~Location)+
-  theme_bw() + 
-  scale_fill_manual(legend_title, values=cbPalette)+
-  theme(legend.position="right", axis.title.x = element_blank())+
-  labs(y = "Proportion of Prey Consumed") +  
-  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
-  theme(plot.title = element_text(hjust = 0.5)) + 
-  theme(axis.title = element_text(size = 23), 
-    axis.text = element_text(size = 20), 
-    axis.text.x = element_text(size = 20), 
-    axis.text.y = element_text(size = 20), 
-    legend.text = element_text(size = 20), 
-    legend.title = element_text(size = 20))+
-  theme(strip.text.x = element_text(size = 20))
-```
-
 # plot mean proportion in bar plot and 100% stacked bar
@@
 
-#bar plot
-ggplot(data=diet.prop.mean.e, aes(x=Mesh, y =prop.mean)) +
-    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))), position="dodge", stat="identity") +
-  facet_grid(~Location)+
-  theme_bw() + 
-  scale_fill_manual(legend_title, values=cbPalette)+
-  theme(legend.position="right", axis.title.x = element_blank())+
-  labs(y = "Average Proportion of Diet") +  
-  theme(panel.grid.major = element_line(colour = "gray93",size=0.01), panel.grid.minor = element_blank()) +
-  theme(plot.title = element_text(hjust = 0.5)) + 
-  theme(axis.title = element_text(size = 23), 
-    axis.text = element_text(size = 20), 
-    axis.text.x = element_text(size = 20), 
-    axis.text.y = element_text(size = 20), 
-    legend.text = element_text(size = 20), 
-    legend.title = element_text(size = 25))+
-  theme(strip.text.x = element_text(size = 20))
+#change labels
+diet.prop.mean.e$Mesh[diet.prop.mean.e$Mesh == "large"] <- "B"
+diet.prop.mean.e$Mesh[diet.prop.mean.e$Mesh == "small"] <- "A"
+diet.prop.mean.e$Mesh[diet.prop.mean.e$Mesh == "wrap"] <- "C"
 
-#stack bar plot
+#plot
 windowsFonts(Times = windowsFont("Times New Roman"))
@@
   scale_fill_manual(legend_title, values=cbPalette)+
-  scale_y_continuous(labels=percent)+
+  scale_y_continuous(labels = scales::percent)+
   theme(legend.position="right", axis.title.x = element_blank())+
@@
     text=element_text(family = "Times"))
-print(d)
+d
 
-tiff(filename="Fig6.tiff", 
+tiff(filename="smelt_2019_winterspring/figures/dietfig.tiff", 
     units="in", 
@@
 dev.off()
+```
 
-write_excel_csv(diet.prop.mean.e, "C:/Users/Nicole Aha/Desktop/Analysis/Analysis/Data/diet.prop.mean.csv")
+# percent of each taxa for potential supplemental table
+```{r}
+diet_type$Count[which(diet_type$Count == "1 maybe 2")] <- 2
+
+diet_type$Count <- as.numeric(diet_type$Count)
+
+taxa.perct<- diet_type %>% 
+  group_by(Location, Taxa, Prey.Taxa) %>% 
+  summarize("count.sum"= sum(Count, na.rm=TRUE))
+
+taxa.tot<- diet_type %>% 
+  group_by(Location) %>% 
+  summarize("count.sum"= sum(Count, na.rm=TRUE))
+
+taxa.perct$Total <- ifelse(taxa.perct$Location=="RVR", 1548,
+        ifelse(taxa.perct$Location=="DWSC", 5831, NA))
+
+taxa.perct$percent <- (taxa.perct$count.sum/taxa.perct$Total)*100
 ```

### 2022-10-03 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
Weight comparison figure, remade weight-length figure to include K. Some analyses re-done using weight change

---
title: "weight_analyses"
author: "Catarina Pien"
date: '2022-09-30'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls(all=TRUE))

library(car)
library(FSA)
library(tidyverse)
library(ggthemes)
library(here)
library(dplyr)
```

# Read in data
```{r}
# Add change in weight
Cagetype_data <- read.csv(here("smelt_2019_winterspring", "data_clean", "Cagetype_data.csv")) %>%
  mutate(deltaWt = Post_Weight_g - Pre_Weight_g,
         changeWt = round(deltaWt/Pre_Weight_g,2),
        deltaFL = Post_FL_cm - Pre_FL_cm,
         changeFL = round(deltaFL/Pre_FL_cm,2),
        Site = factor(Site, levels = c("RV", "DWSC")),
         Enclosure = ifelse(Mesh == "wrap", "A", ifelse(Mesh == "large", "B", ifelse(Mesh == "small", "C", ifelse(Mesh == "control", "control", NA)))))

# Make complete cases from column 9
Delta_CF <- Cagetype_data$Delta_CF
Cagetype_CF <- Cagetype_data[complete.cases(Delta_CF),]
Cageonly <- Cagetype_data %>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2") %>%
  mutate(Group = ifelse(Site == "RV" & Mesh == "wrap", "B", ifelse(Site == "DWSC", " ", "A")))

```

# Make manuscript boxplot
```{r}
windowsFonts(Times = windowsFont("Times New Roman"))

(Boxplot <- ggplot(data=Cageonly) +
   geom_boxplot(aes(x=Enclosure, y=deltaWt,  fill = Enclosure)) +
   geom_hline(yintercept = 0, size = 0.5) +
   facet_wrap(~Site) +
   # geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
   scale_fill_brewer(palette="Dark2")+
   labs(y = "\u0394 Weight", x = "Enclosure Type") +
   theme_minimal() +
   annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
   annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
   theme(text = element_text(family = "Times"),
         axis.text = element_text(size = 16),
         axis.title = element_text(size = 17),
         strip.text = element_text(size = 17),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         legend.position = "none",
         panel.spacing = unit(2, "lines")))

(Boxplot2 <- ggplot(data=Cageonly) +
    geom_boxplot(aes(x=Enclosure, y=changeWt,  fill = Enclosure)) +
    geom_hline(yintercept = 0, size = 0.5) +
    facet_wrap(~Site) +
    # geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
    scale_fill_brewer(palette="Dark2")+
    labs(y = "Proportional Change in Weight", x = "Enclosure Type", labs = "Proportional Change in Weight") +
    theme_minimal() +
    annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
    annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
    theme(text = element_text(family = "Times"),
          axis.text = element_text(size = 16),
          axis.title = element_text(size = 17),
          strip.text = element_text(size = 17),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black"),
          legend.position = "none",
          panel.spacing = unit(2, "lines")))
```

Export figure
```{r}
tiff(filename=file.path("smelt_2019_winterspring/figures/Fig4_WeightByCage.tiff"), units="in",type="cairo", bg="white", height=4, 
     width=6, res=300, pointsize=12,compression="lzw")
Boxplot2
dev.off()
```

# Run analyses

## Pre-Post changes in weight and length
### RVR
```{r}
Cage_only_RVR <- Cagetype_CF %>%
  filter(Site == "RV")%>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2")
```

Mean
```{r}
Cage_only_RVR %>%
  summarize(meanWtPre = mean(Pre_Weight_g),
            meanWtPost = mean(Post_Weight_g),
            meandeltaWt = mean(deltaWt),
            n = n(),
            sddeltaWt = sd(deltaWt),
            sedeltaWt = sddeltaWt/n,
            meanchangeWt = mean(changeWt*100),
            sdchangeWt = sd(changeWt),
            sechangeWt = sdchangeWt/n,
            meanchangeFL =mean(changeFL*100),
            sechangeFL = sd(changeFL)/n,
            meanCFPre = mean(Pre_CF),
            meanCFPost = mean(Post_CF),
            seCF = sd(Pre_CF)/n,
            meandeltaCF = mean(Delta_CF),
            sedeltaCF = sd(Delta_CF)/n)
```

Does weight change in RVR? Yes
```{r}
hist(Cage_only_RVR$Pre_Weight_g)
hist(Cage_only_RVR$changeWt)
hist(log(Cage_only_RVR$changeWt+1))
hist(Cage_only_RVR$Post_Weight_g)
t.test(log(Cage_only_RVR$Pre_Weight_g+1), log(Cage_only_RVR$Post_Weight_g)+1)
```

Does length change in RVR? Yes
```{r}
hist(Cage_only_RVR$Pre_FL_cm)
hist(Cage_only_RVR$Post_FL_cm)
t.test(Cage_only_RVR$Pre_FL_cm, Cage_only_RVR$Post_FL_cm)
```

Does CF change in RVR?
```{r}
hist(Cage_only_RVR$Pre_CF)
hist(Cage_only_RVR$Post_CF)
t.test(log(Cage_only_RVR$Pre_CF+1), log(Cage_only_RVR$Post_CF+1))
```

### DWSC
```{r}
Cage_only_DWSC <- Cagetype_CF %>%
  filter(Site == "DWSC") %>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2")
```

Summary Stats
```{r}
Cage_only_DWSC %>%
  summarize(meanWtPre = mean(Pre_Weight_g),
            meanWtPost = mean(Post_Weight_g),
            meandeltaWt = mean(deltaWt),
            n = n(),
            sddeltaWt = sd(deltaWt),
            sedeltaWt = sddeltaWt/n,
            meanchangeWt = mean(changeWt*100),
            sdchangeWt = sd(changeWt),
            sechangeWt = sdchangeWt/n,
            meanchangeFL =mean(changeFL*100),
            sechangeFL = sd(changeFL)/n,
            meanCFPre = mean(Pre_CF),
            meanCFPost = mean(Post_CF),
            seCF = sd(Pre_CF)/n,
            meandeltaCF = mean(Delta_CF),
            sedeltaCF = sd(Delta_CF)/n)
```

T-test: Does weight change in DWSC? Yes
```{r}
hist(Cage_only_DWSC$Pre_Weight_g)
hist(Cage_only_DWSC$Post_Weight_g)
hist(Cage_only_DWSC$changeWt)
hist(log(Cage_only_DWSC$changeWt+1))
t.test(log(Cage_only_DWSC$Pre_Weight_g+1), log(Cage_only_DWSC$Post_Weight_g)+1)
```

Does length change in DWSC? No
```{r}
hist(Cage_only_DWSC$Pre_FL_cm)
hist(Cage_only_DWSC$Post_FL_cm)
t.test(Cage_only_DWSC$Pre_FL_cm, Cage_only_DWSC$Post_FL_cm)
```

Does CF change in DWSC? Yes
```{r}
t.test(log(Cage_only_DWSC$Pre_CF+1), log(Cage_only_DWSC$Post_CF)+1)
```

## Weight differences by cage type
### RVR

```{r}
library(lme4)
library(effects)
library(lmerTest)

# Checking if fish of each cage started at the same length
m_wtstart <- lm(Pre_Weight_g ~ Cage, data = Cage_only_RVR)
summary(m_wtstart)
anova((m_wtstart))
plot(m_wtstart)

# Simple LM
RV1 <- lm(changeWt ~ Enclosure, data = Cage_only_RVR)
summary(RV1)
anova(RV1)
# Residual standard dev = 0.117

# LMER - used this in manuscript
RV2 <- lmer(log(changeWt+1) ~ Mesh + (1|Cage), data = Cage_only_RVR, REML = TRUE)
summary(RV2)
anova(RV2)
plot(RV2)
qqnorm(resid(RV2))
# Residual standard dev = 0.113

confint(RV2)

```

```{r}
rv_residuals <- residuals(object = RV2)

par(mfrow = c(2,2))
plot(RV1)
leveneTest(log(changeWt+1) ~ Enclosure, data = Cage_only_RVR) # p<0.05 means not homogeneous; however, not too deviant in this case

shapiro.test(x = rv_residuals)

tab_model(RV2)
```

### DWSC

```{r}

# Checking if fish of each cage started at the same length
m_wtstart2 <- lm(Pre_Weight_g ~ Cage, data = Cage_only_DWSC)
summary(m_wtstart2)
anova((m_wtstart2))
plot(m_wtstart2)

# LM
DWSC1 <- lm(log(changeWt+1) ~ Enclosure, data = Cage_only_DWSC)
summary(DWSC1)
anova(DWSC1)
# Residual standard dev = 0.1675

# LMER
DWSC2 <- lmer(changeWt ~ Mesh + (1|Cage), data = Cage_only_DWSC, REML = TRUE)
summary(DWSC2)
anova(DWSC2)
# Residual standard dev = 0.1675

```

Check assumptions
```{r}
dwsc_resid= resid(DWSC1,type = "pearson")
par(mfrow = c(2,2))
plot(DWSC1)

leveneTest(DWSC1)
shapiro.test(log(Cage_only_DWSC$changeWt+1))
```

```{r}
library(sjPlot)
library(sjmisc)
library(sjlabelled)

tab_model(DWSC1)
```

## Length-Weight-CF Figures
```{r}
# Summarize mean, sd, median, n for Pre and Post Length and Width
Cagedata <- Cagetype_CF %>%
  na.omit() %>%
  filter(Cage!="FCCL1") %>%
  filter(Cage!="FCCL2") %>%
  group_by(Site, Mesh)%>%
  summarize(
    PreL_Mean = mean(Pre_FL_cm),
    PreL_sd = sd(Pre_FL_cm),
    PreL_median = median(Pre_FL_cm),
    PoL_Mean = mean(Post_FL_cm),
    PoL_sd = sd(Post_FL_cm),
    PoL_median = median(Post_FL_cm), 
    PreW_Mean = mean(Pre_Weight_g),
    PreW_sd = sd(Pre_Weight_g),
    PreW_median = median(Pre_Weight_g),
    PoW_Mean = mean(Post_Weight_g),
    PoW_sd = sd(Post_Weight_g),
    PoW_median = median(Post_Weight_g),  N = n()) %>%
    mutate(delta.Length = round(PoL_Mean - PreL_Mean,2)) %>%
  mutate(delta.weight = round(PoW_Mean - PreW_Mean,2)) %>%
  ungroup()
```

```{r}
Cageonly2 <- Cagetype_data %>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2")

Cageonly <- Cagetype_data %>%
  filter(Cage != "FCCL1") %>%
  filter(Cage != "FCCL2") %>%
  mutate(Group = ifelse(Site == "RV" & Mesh == "wrap", "B", ifelse(Site == "DWSC", " ", "A")))  %>%
  mutate(delta.L = round(Post_FL_cm - Pre_FL_cm,2))%>%
  mutate(delta.W = round(Post_Weight_g - Pre_Weight_g,2))

windowsFonts(Times = windowsFont("Times New Roman"))
```

Make length plot
```{r}
CagePrePost <- gather(Cageonly2, PrePost,Length1,Pre_FL_cm, Post_FL_cm)
CagePrePost$Site <- factor(CagePrePost$Site, levels = c("RV", "DWSC"))

MeanLengthplot<- ggplot(data=CagePrePost) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=Length1,  fill = PrePost)) +
  facet_wrap(~Site) +
  labs(y = "Length (cm)") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)++
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "", labels = c("Pre-Deployment", "Post-Deployment")) +
  labs(y = "Length (cm)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  theme_minimal() + theme(axis.title.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
  #scale_fill_discrete(name = "", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanLengthplot
```

Make weight plot
```{r}
CagePrePostW <- gather(Cageonly2, PrePostW,Weight1,Pre_Weight_g, Post_Weight_g)
windowsFonts(Times = windowsFont("Times New Roman"))

CagePrePostW$PrePostW <- factor(CagePrePostW$PrePostW,
                              levels = c('Pre_Weight_g','Post_Weight_g'),ordered = TRUE)
CagePrePostW$Site <- factor(CagePrePostW$Site, levels = c("RV", "DWSC"))

MeanWeightplot<- ggplot(data=CagePrePostW) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=Weight1,  fill = PrePostW)) +
  facet_wrap(~Site) +
  labs(y = "Mean Weight (g)") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment"))+
  #palette="Dark2" 
   labs(y = "Weight (g)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  theme_minimal() + theme(strip.text.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) + 
  #scale_fill_discrete(name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size = 16),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanWeightplot
```

Make CF plot

```{r}
CagePrePostK <- gather(Cageonly2, PrePostK,K1,Pre_CF, Post_CF)
windowsFonts(Times = windowsFont("Times New Roman"))

CagePrePostK$PrePostK <- factor(CagePrePostK$PrePostK,
                              levels = c('Pre_CF','Post_CF'),ordered = TRUE)
CagePrePostK$Site <- factor(CagePrePostK$Site, levels = c("RV", "DWSC"))

MeanKplot<- ggplot(data=CagePrePostK) +
  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=K1,  fill = PrePostK)) +
  facet_wrap(~Site) +
  labs(y = "Mean K") +
  #geom_text(aes(label = Group, x = Mesh, y = -0.32), family = "Times", size = 6) +
  #geom_hline(data = FCCL, aes(yintercept=delta.weight), size = 1) +
  #geom_text(data = ann_text, mapping = aes(x = x, y = y, label = label), family = "Times", size = 5.5)+
  scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment"))+
  #palette="Dark2" 
   labs(y = expression(K~(g~cm^-3)), x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
  theme_minimal() + theme(strip.text.x = element_blank()) +
  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) + 
  #scale_fill_discrete(name = "Deployment", labels = c("Pre-Deployment", "Post-Deployment")) +
  theme(text = element_text(family = "Times"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 17),
        strip.text = element_text(size = 17),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        #legend.position = "none",
        panel.spacing = unit(2, "lines"))
MeanKplot
```

```{r}
library(patchwork)

lwkplot <- MeanLengthplot+MeanWeightplot+MeanKplot + plot_layout(nrow = 3, guides = "collect") &
  theme(legend.position = "bottom")
```

Export
```{r}
tiff(filename=file.path("smelt_2019_winterspring/figures/WeightLengthKPlot.tiff"), units="in",type="cairo", bg="white", height=7, 
     width=7, res=300, pointsize=12,compression="lzw")
lwkplot
dev.off()
```

## Survival

### RVR
Make data for RVR
```{r}
# Reorganize data
# Make complete cases from column 7 (post_weight)
post_fish <- Cagetype_data$Post_Weight_g
Cagetype_s <- Cagetype_data[complete.cases(post_fish),]

# ----------------Rio Vista-----------------------------------------
# Calculate sample sizes for alive and dead
surv_RV <- Cagetype_s %>%
  filter(Site == "RV") %>%
  group_by(Site, Cage, Mesh)%>%
  summarize(
    Alive = n(),
    Dead = 64-n()
  ) %>%
  mutate(rate = Alive/(Alive + Dead)*100)

# Create data frame of each individual fish - survived or did not survive
Cage_survival_RV <- as.data.frame(matrix(0, ncol = 2, nrow = 384))
colnames(Cage_survival_RV) <- c("Cage", "Survived")

# Add dead fish from data sheet
  # Add RN82 from cage A that was decomposed
  # RG49 from cage A already included in the dead count (no Weight data)
  # Add RJ08 from cage E that was dead prior, stomach torn open

Cage_survival_RV$Cage <- c(rep("A", 64), rep("B", 64), rep("C", 64), rep("D", 64), rep("E", 64), rep("F", 64))
Cage_survival_RV$Survived <- c(rep("1", 60), rep("0", 4),
                               rep("1", 64), rep("0", 0),
                               rep("1", 64), rep("0", 0),
                               rep("1", 64), rep("0", 0),
                               rep("1", 62), rep("0", 2),
                               rep("1", 56), rep("0", 8))

Cagetype_survival_RV <- left_join(Cage_survival_RV, surv_RV, by = "Cage")

Cagetype_survival_RV <- Cagetype_survival_RV %>%
  mutate(Cage = factor(Cage),
         Survived = factor(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))
```

Survival rate
```{r}
surv_RV %>%
  ungroup() %>%
  filter(Cage != "FCCL1") %>%
  summarize(meanRate = mean(rate),
            n = n(),
            seRate = sd(rate)/n)
```

Logistic Mixed Model
```{r}
mRV_surv <- glmer(Survived ~ Mesh + (1|Cage), data = Cagetype_survival_RV, family = binomial(link = "logit"))

summary(mRV_surv)
se <- sqrt(diag(vcov(mRV_surv)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mRV_surv), LL = fixef(mRV_surv) - 1.96 * se, UL = fixef(mRV_surv) + 1.96 *
                se))
```

### DWSC
```{r}

surv_DWSC <- Cagetype_s %>%
  filter(Site == "DWSC") %>%
  group_by(Site, Cage, Mesh)%>%
  summarize(
    Alive = n(),
    Dead = 60-n()
  ) 
# Add dead fish
  # Add NTF4 to dead in Cage F - "decomposed"
  # Add RB61 to dead in Cage F - "partly decomposed"

Cage_survival_DWSC <- as.data.frame(matrix(0, ncol = 2, nrow = 360))
colnames(Cage_survival_DWSC) <- c("Cage", "Survived")

Cage_survival_DWSC$Cage <- c(rep("A", 60), rep("B", 60), rep("C", 60), rep("D", 60), rep("E", 60), rep("F", 60))
Cage_survival_DWSC$Survived <- c(rep("1", 59), rep("0", 1),
                                 rep("1", 60), rep("0", 0),
                                 rep("1", 58), rep("0", 2),
                                 rep("1", 60), rep("0", 0),
                                 rep("1", 60), rep("0", 0),
                                 rep("1", 58), rep("0", 2))

Cagetype_survival_DWSC <- left_join(Cage_survival_DWSC, surv_DWSC, by = "Cage")

Cagetype_survival_DWSC <- Cagetype_survival_DWSC %>%
  mutate(Cage = factor(Cage),
         Survived = factor(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  mutate(rate = Alive/(Alive + Dead)*100)
```

Survival rate
```{r}
Cagetype_survival_DWSC %>%
  select(-Survived) %>%
  distinct() %>%
  summarize(meanRate = mean(rate),
            n = n(),
            seRate = sd(rate)/n)
```

```{r}
mDWSC_surv <- glmer(Survived ~ Mesh + (1|Cage), data = Cagetype_survival_DWSC, family = binomial(link = "logit"))
# is singular

summary(mDWSC_surv)

se <- sqrt(diag(vcov(mDWSC_surv)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mDWSC_surv), LL = fixef(mDWSC_surv) - 1.96 * se, UL = fixef(mDWSC_surv) + 1.96 *
                se))
plot(mDWSC_surv)

r.squaredGLMM(mDWSC_surv)
plot_model(mDWSC_surv, type = "pred", terms = c("Mesh"))
tab_model(mDWSC_surv)
```

### Plots
```{r}
# Survival Plot ---------------------------------------
# * By Mesh ----
RV_survival_sum <- Cagetype_survival_RV %>%
  group_by(Mesh) %>%
  summarize(Survive = sum(Survived == 1),
            Died = -1 * sum(Survived == 0),
            n = n()) %>%
  pivot_longer(cols = c(Survive, Died), names_to = "Survival", values_to = "Count")

DWSC_survival_sum <- Cagetype_survival_DWSC %>%
  group_by(Mesh) %>%
  summarize(Survive = sum(Survived == 1),
            Died = -1 * sum(Survived == 0),
            n = n()) %>%
  pivot_longer(cols = c(Survive, Died), names_to = "Survival", values_to = "Count")

DWSC_survival_sum$Site <- "DWSC"
RV_survival_sum$Site <- "RV"

Survival_sum <- rbind(DWSC_survival_sum, RV_survival_sum)
Survival_sum <- Survival_sum %>%
  mutate(prop = ifelse(Survival == "Survive", round(Count/n * 100,1), round((-1 * Count/n * 100),1)))

# Survival plot
ggplot(Survival_sum, aes(Mesh, Count, fill = Survival)) +
  facet_wrap(~Site) +
  geom_col(width = 0.55) +
  coord_cartesian(y = c(-30,130)) +
  scale_y_continuous(breaks = seq(0, 125, by = 25)) +
  geom_text(aes(label = paste0(prop, "%")), vjust = 1.5, size = 5)+
  geom_hline(yintercept=0)+
  scale_fill_brewer(palette="Set1")+
  theme_bw() +
  theme(axis.text = element_text(size = 15),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title = element_text(size = 17),
        axis.ticks.y = element_blank(),
        strip.text = element_text(size = 16),
        legend.position = "none")

# * By Cage ----
RV_survival_sum2 <- Cagetype_survival_RV %>%
  group_by(Mesh, Cage) %>%
  summarize(Survive = sum(Survived == 1),
            Died = -1 * sum(Survived == 0),
            n = n()) %>%
  pivot_longer(cols = c(Survive, Died), names_to = "Survival", values_to = "Count")

DWSC_survival_sum2 <- Cagetype_survival_DWSC %>%
  group_by(Mesh, Cage) %>%
  summarize(Survive = sum(Survived == 1),
            Died = -1 * sum(Survived == 0),
            n = n()) %>%
  pivot_longer(cols = c(Survive, Died), names_to = "Survival", values_to = "Count")

DWSC_survival_sum2$Site <- "DWSC"
RV_survival_sum2$Site <- "RV"

Survival_sum2 <- rbind(DWSC_survival_sum2, RV_survival_sum2)
Survival_sum2 <- Survival_sum2 %>%
  mutate(prop = ifelse(Survival == "Survive", round(Count/n * 100,1), round((-1 * Count/n * 100),1)))

ggplot(Survival_sum2, aes(Cage, Count, fill = Survival)) +
  facet_wrap(~Site) +
  geom_col(width = 0.7, aes(colour = Mesh), size = 3) +
  coord_cartesian(y = c(-30,130)) +
  scale_y_continuous(breaks = seq(0, 125, by = 25)) +
  scale_color_brewer(palette="Dark2")+
  geom_text(aes(label = paste0(prop, "%")), vjust = 1.5, size = 5)+
  geom_hline(yintercept=0)+
  scale_fill_brewer(palette="Set1")+
  theme_bw() +
  theme(axis.text = element_text(size = 15),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title = element_text(size = 17),
        axis.ticks.y = element_blank(),
        strip.text = element_text(size = 16),
        legend.position = "none")

### Mean survival

Survival_sum3 <- Survival_sum2 %>%
  mutate(prop = ifelse(Survival == "Survive", Count/n * 100, -1 * Count/n * 100))

propSurvival <- filter(Survival_sum3, Survival == "Survive") %>%
  ungroup() %>%
group_by(Site) %>%
  summarize(meanSurvival = mean(prop),
            n = n(),
            seSurvival = sd(prop)/n)

```

### Old Code
```{r}
# Logistic mixed model ----

library(lme4)
library(lmerTest)

mRV_surv <- glmer(Survived ~ Mesh + (1|Cage), data = Cagetype_survival_RV, family = binomial(link = "logit"))

summary(mRV_surv)
se <- sqrt(diag(vcov(mRV_surv)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mRV_surv), LL = fixef(mRV_surv) - 1.96 * se, UL = fixef(mRV_surv) + 1.96 *
                se))
# * * Check assumptions ----
Ms1.resid <- resid(mRV_surv, type = "pearson")
plot(mRV_surv)
plot(mRV_surv, form = resid(., type = "pearson") ~ fitted(.) | Mesh, abline = 0,
     cex = .5, pch = 20, col = "black")

# normality
par(mfrow = c(1,1))
qqnorm(Ms1.resid)
qqline(Ms1.resid)
hist(Ms1.resid)

# observed vs fitted
# There is no funnel
plot(mRV_surv, Survived ~ fitted(.), id = 0.05, adj = -0.3,
     cex = .8, pch = 20, col = "blue")
# leverage
ggplot(data.frame(lev=hatvalues(mRV_surv),pearson=residuals(mRV_surv,type="pearson")),
       aes(x=lev,y=pearson)) +
  geom_point() +
  theme_bw()

# variance by mesh
ggplot(Cagetype_survival_RV, aes(x = Mesh, y = Ms1.resid)) + geom_boxplot()

leveneTest(Survived ~ Mesh, data = Cage_only_DWSC)

# * * Plot results ----
library(MuMIn) #extract R2
library(sjPlot)
library(sjstats) # for intraclass-correlation coefficient
library(caret) # model comparison & utility functions

r.squaredGLMM(mRV_surv)
plot_model(mRV_surv, type = "pred", terms = c("Mesh"))
tab_model(mRV_surv)

library(ggeffects)
ggpredict(mRV_surv, "Survived")

# Logistic mixed model ----

library(lme4)
library(lmerTest)

#logit transform survival data
#lmer with random effect cage
#anova

mDWSC_surv <- glmer(Survived ~ Mesh + (1|Cage), data = Cagetype_survival_DWSC, family = binomial(link = "logit"))
# is singular

summary(mDWSC_surv)

se <- sqrt(diag(vcov(mDWSC_surv)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mDWSC_surv), LL = fixef(mDWSC_surv) - 1.96 * se, UL = fixef(mDWSC_surv) + 1.96 *
                se))
plot(mDWSC_surv)

# * * Check assumptions ----
Ms2.resid <- resid(mDWSC_surv, type = "pearson")
plot(mDWSC_surv)
plot(mDWSC_surv, form = resid(., type = "pearson") ~ fitted(.) | Mesh, abline = 0,
     cex = .5, pch = 20, col = "black")

# normality
par(mfrow = c(1,1))
qqnorm(Ms2.resid)
qqline(Ms2.resid)
hist(Ms2.resid)

# leverage
ggplot(data.frame(lev=hatvalues(mDWSC_surv),pearson=residuals(mDWSC_surv,type="pearson")),
       aes(x=lev,y=pearson)) +
  geom_point() +
  theme_bw()

# check variance
ggplot(Cagetype_survival_DWSC, aes(x = Mesh, y = Ms2.resid)) + geom_boxplot()

# * * Plot results ----
library(MuMIn) #extract R2
library(sjPlot)
library(sjstats) # for intraclass-correlation coefficient
library(caret) # model comparison & utility functions

### 2022-10-03 smelt_2019_winterspring/ANOVA_Survival_CF.R

@@ -1,8 +1,8 @@
 # 12/19/19
 # Catarina Pien
-# Comparison of Mesh types 
-# Anova for Delta Smelt Condition Factor 
-# Chi Square for Delta Smelt Survival 
+# Comparison of Mesh types
+# Anova for Delta Smelt Condition Factor
+# Chi Square for Delta Smelt Survival
 
 # Set up workspace and load data --------------------------
 rm(list=ls(all=TRUE))
@@ -15,7 +15,9 @@ library(here)
 library(dplyr)
 
 Cagetype_data <- read.csv(here("smelt_2019_winterspring", "data_clean", "Cagetype_data.csv")) %>%
-  mutate(Site = factor(Site, levels = c("RV", "DWSC")),
+  mutate(deltaWt = Post_Weight_g - Pre_Weight_g,
+         changeWt = round(deltaWt/Pre_Weight_g,2),
+        Site = factor(Site, levels = c("RV", "DWSC")),
          Enclosure = ifelse(Mesh == "wrap", "A", ifelse(Mesh == "large", "B", ifelse(Mesh == "small", "C", ifelse(Mesh == "control", "control", NA)))))
 
 unique(Cagetype_data$Enclosure)
@@ -76,6 +78,20 @@ Cage.CF <- Cagetype_CF %>%
     N = n()
   )
 
+# Means by site
+Cage.CF.site <- Cagetype_CF %>%
+  na.omit() %>%
+  filter(Cage!="FCCL1") %>%
+  filter(Cage!="FCCL2") %>%
+  group_by(Site)%>%
+  summarize(
+    Delta_CF_Mean = mean(Delta_CF),
+    Delta_CF_sd = sd(Delta_CF),
+    Delta_CF_median = median(Delta_CF),
+    N = n(),
+    se = Delta_CF_sd/sqrt(N)
+  )
+
 # Summarize mean, sd, median, n for condition factor
 Cage.LW <- Cagetype_CF %>%
   na.omit() %>%
@@ -106,7 +122,7 @@ FCCL_CF <- Cagetype_CF %>%
 # Plots -----
 
 # * Overview of data (geom_point) ----
-ggplot(Cagetype_CF, aes(Mesh, Delta_CF, col = Mesh)) + 
+ggplot(Cagetype_CF, aes(Mesh, Delta_CF, col = Mesh)) +
   facet_wrap(~Site) +
   geom_jitter(size = 3) +
   scale_fill_brewer(palette="Dark2")+
[…]

### 2022-10-14 smelt_2019_winterspring/Diet.Rmd
add in color palette for final plot
updated dataframe name

@@
 ```{r}
-diet <- read_csv("smelt_2019_winterspring/data_raw/DSM Cage Diets 2019 update_taxa.csv")
+diet <- read_csv("smelt_2019_winterspring/data_raw/2019_smeltstudy_diet_data.csv")
 diet$Location <- ordered(diet$Location, levels = c("RVR", "DWSC"))
@@
 
+cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
+
 d<-ggplot(data=diet.prop.mean.e, aes(x=Mesh, y =prop.mean)) +

### 2022-10-18 smelt_2019_allseasons/Diet 2019.Rmd
moving over files I had in a seperate folder for diet and zoop, removing old diet code

--- 2021-12-14 smelt_2019_allseasons/2019Diets.Rmd
@@
 ---
-title: "2019 Diet Data"
+title: "Delta Smelt Enclosure Study 2019 Hybrid Paper Analysis"
 output:
@@
 ```{r}
-diet2 <- read_csv('smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv') #new data, not edited at all
+diet2 <- read_csv("hybrid study/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
+
+diet2$Date <- mdy(diet2$Date)
 
@@
 diet2$Taxa <- as.character(NA)
+
+str(diet2)
 
@@
 diet$ld = paste(diet$Location, diet$Date)
-diet$Location[diet$ld =="RV 8/28/2019"] <- "RV.Aug"
-diet$Location[diet$ld =="RV 11/6/2019"] <- "RV.Nov"
+diet$Location[diet$ld =="RV 2019-08-28"] <- "RV.Aug"
+diet$Location[diet$ld =="RV 2019-11-06"] <- "RV.Nov"
 RV <- filter(diet, Location == "RV")
-diet$Location[diet$ld =="RV 11/7/2019"] <- "RV.Nov"
+diet$Location[diet$ld =="RV 2019-11-07"] <- "RV.Nov"
 
@@
 diet<-diet[diet$Cage.ID != "FCCL Control",]
+
+#remove DWSC
+diet<-diet[diet$Location != "DWSC.Apr",]
 
@@
 stomach_abundance$Location <- stomach_abundance$Location.x
-stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("RV.Feb", "DWSC.Apr", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
+stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
 
@@
 #order locations
-prop$Location <- ordered(prop$Location, levels = c("RV.Feb", "DWSC.Apr", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
+prop$Location <- ordered(prop$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
 
-cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2", "#8C8C8C")
+cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2")
 legend_title <- "Taxa"

### 2022-10-18 smelt_2019_allseasons/Zoop 2019.Rmd
moving over files I had in a seperate folder for diet and zoop, removing old diet code

---
librarytitle: "Zoop Plotting"
output: html_document
editor_options: 
  chunk_output_type: console
---
# load packages
```{r}
library(tidyverse)
library(lubridate)
library(Polychrome)
```

# load & prep summer/fall data
```{r}
zoop <- read_csv("hybrid study/ZoopData_SummerFall_2019.csv")

zoop$Date <- mdy(zoop$Date)
zoop$Day <- day(zoop$Date)
zoop$Month <- month(zoop$Date)
zoop$Month <- month.abb[zoop$Month]
zoop$MD <- paste(zoop$Month, zoop$Day, sep="-")

#add ring size (0.5m for 50um net)
zoop$RingSize_m <- 0.5

#add 0s for count with NA
zoop$Count[is.na(zoop$Count)] <- 0

#bring in tow data
aug <- read_csv("hybrid study/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
oct <- read_csv("hybrid study/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
aug$Date <- mdy(aug$Date)
oct$Date <- mdy(oct$Date)

#condense to columns of interest
aug2 <- aug[c(1,4,22,24:27)]
oct2 <- oct[c(1,4,26,28:31)]

tow <- rbind(aug2,oct2)
tow2 <- tow[!is.na(tow$Location),]

#merge
#rename column
zoop <- zoop %>% rename(Location = "Station")

#make locations match
unique(zoop$Location)
unique(tow2$Location)

zoop[zoop$Location %in% c("STTD", "STTD-YOLO", "YOLO"),]$Location <- "Yolo"

all <- merge(zoop, tow2, by = c('Location', 'Date'))

#calculate abundance -----------------------
all$distance <- (all$Revs)*57560/999999
all$volumesampled <- ((pi*(all$RingSize_m^2))/4)*all$distance
all$samplecount <- (all$TotalVolume_ml/all$Subsampled_ml)*all$Count

#calculate ind/m3
all$ind_m3 <- all$samplecount/all$volumesampled

#remove 0's
caught <- all[!(all$ind_m3==0),]
```
# plot summer/fall data
```{r}
#order factors
unique(caught$MD)
caught$MD <- factor(caught$MD, levels=c("Jul-31", "Aug-1", "Aug-2",  "Aug-5", "Aug-6", "Aug-8",  "Aug-12", "Aug-15", "Aug-19", "Aug-22", "Aug-26", "Oct-10", "Oct-11", "Oct-15", "Oct-16", "Oct-18", "Oct-21", "Oct-25", "Oct-28", "Nov-4"))

legend_title <- "Species"

pal36 <- palette36.colors(36)
pal36 <- as.vector(t(pal36))

ggplot(data = caught, aes(x=MD, y=samplecount)) +
  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

ggsave("hybrid study/plots/allzoop.png", dpi=250, height=6, width=10, units="in")

#plot with microzoop removed
macro <- caught[!(caught$ID=="Copepod nauplii"),]
macro <- macro[!(macro$ID=="Rotifers"),]
macro <- macro[!(macro$ID=="Ostracods"),]

ggplot(data = macro, aes(x=MD, y=samplecount)) +
  geom_bar(position = "fill", stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of Macrozoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

ggsave("hybrid study/plots/macrozoop.png", dpi=250, height=6, width=10, units="in")
```
#bring in winter data
```{r}
#prep of this dataset (code and raw data) can be found here: https://cawater.sharepoint.com/:f:/r/sites/dwrdoc-aes/Shared%20Documents/Delta%20Smelt%20Enclosure%20Study/Analysis/Zooplankton/Zoop%2719?csf=1&web=1&e=YhKzMy

winter <- read_csv("hybrid study/zoop_abundance.csv")

winter$Day <- day(winter$Date)
winter$Month <- month(winter$Date)
winter$Month <- month.abb[winter$Month]
winter$MD <- paste(winter$Month, winter$Day, sep="-")

#remove throw samples
winter <- winter[!(winter$Method=="Throw"),]

#remove DWSC samples
winter <- winter[!(winter$SiteName=="DWSC"),]

#merge with catch df

#condense to columns of interest
winter2 <- winter[c(1,2,13,16,32,25,26)]
caught2 <- caught[c(1,2,7,10,20,29,30)]

#rename column
winter2 <- winter2 %>% rename(Location = "SiteName")

#make locations match
unique(winter2$Location)
unique(caught2$Location)

all2019 <- rbind(winter2, caught2)

#remove 0's
caught.19 <- all2019[!(all2019$ind_m3==0),]
```
# plot all 2019
```{r}
#order factors
unique(caught.19$MD)
caught.19$MD <- factor(caught.19$MD, levels=c("Jan-24", "Jan-29", "Jan-31", "Feb-6", "Feb-8", "Feb-12", "Feb-15", "Feb-22", "Jul-31", "Aug-1", "Aug-2",  "Aug-5", "Aug-6", "Aug-8",  "Aug-12", "Aug-15", "Aug-19", "Aug-22", "Aug-26", "Oct-10", "Oct-11", "Oct-15", "Oct-16", "Oct-18", "Oct-21", "Oct-25", "Oct-28", "Nov-4"))

ggplot(data = caught.19, aes(x=MD, y=samplecount)) +
  geom_bar(position = "fill", stat = "identity", data=caught.19, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

ggsave("hybrid study/plots/allzoop19.png", dpi=250, height=6, width=10, units="in")

#plot with microzoop removed
macro2 <- caught.19[!(caught.19$ID=="Copepod nauplii"),]
macro2 <- macro2[!(macro2$ID=="Rotifers"),]
macro2 <- macro2[!(macro2$ID=="Ostracods"),]

ggplot(data = macro2, aes(x=MD, y=samplecount)) +
  geom_bar(position = "fill", stat = "identity", data=macro2, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of Macrozoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

ggsave("hybrid study/plots/macrozoop19.png", dpi=250, height=6, width=10, units="in")
```

### 2022-10-19 smelt_2019_allseasons/Diet 2019.Rmd
diet code updates

@@
 ---
-title: "Delta Smelt Enclosure Study 2019 Hybrid Paper Analysis"
+title: "Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis"
 output:
@@
 library(FSA)
+library(lubridate)
 ```
@@
 ```{r}
-diet2 <- read_csv("hybrid study/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
+diet2 <- read_csv("smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
 
@@
 #remove DWSC
-diet<-diet[diet$Location != "DWSC.Apr",]
+#diet<-diet[diet$Location != "DWSC.Apr",]
 
@@
 stomach_abundance$Location <- stomach_abundance$Location.x
-stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
+stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
 
@@
 #order locations
-prop$Location <- ordered(prop$Location, levels = c("RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
+prop$Location <- ordered(prop$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "RV.Nov", "YB.Nov", "SM.Nov"))
 

### 2022-10-26 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
minor change to survival table, publishing format

@@
 # ----------------Rio Vista-----------------------------------------
-# Calculate sample sizes for alive and dead
-surv_RV <- Cagetype_s %>%
-  filter(Site == "RV") %>%
-  group_by(Site, Cage, Mesh)%>%
-  summarize(
-    Alive = n(),
-    Dead = 64-n()
-  ) %>%
-  mutate(rate = Alive/(Alive + Dead)*100)
-
 # Create data frame of each individual fish - survived or did not survive
@@
 
-Cagetype_survival_RV <- Cagetype_survival_RV %>%
+survival_RV <- Cagetype_survival_RV %>%
    mutate(Cage = factor(Cage),
-         Survived = factor(Survived),
+         fSurvived = factor(Survived),
+         Survived = as.numeric(Survived),
          Site = factor(Site),
-         Mesh = factor(Mesh))
+         Mesh = factor(Mesh))%>%
+  group_by(Mesh, Cage) %>%
+  summarize(Survived = sum(Survived),
+            n= n()) %>%
+  mutate(rate = Survived/n*100)
 ```
@@
 ```{r}
-
-surv_DWSC <- Cagetype_s %>%
-  filter(Site == "DWSC") %>%
-  group_by(Site, Cage, Mesh)%>%
-  summarize(
-    Alive = n(),
-    Dead = 60-n()
-  ) 
 # Add dead fish
@@
 
-Cagetype_survival_DWSC <- Cagetype_survival_DWSC %>%
+survival_DWSC <- Cagetype_survival_DWSC %>%
   mutate(Cage = factor(Cage),
-         Survived = factor(Survived),
+         fSurvived = factor(Survived),
+         Survived = as.numeric(Survived),
          Site = factor(Site),
          Mesh = factor(Mesh))%>%
-  mutate(rate = Alive/(Alive + Dead)*100)
+  group_by(Mesh, Cage) %>%
+  summarize(Survived = sum(Survived),
+            n= n()) %>%
+  mutate(rate = Survived/n*100)
+```
+
+EDI table for survival
+```{r}
+survival_bind <- rbind(survival_DWSC, survival_RV) %>%
+  mutate(rate = round(rate,2))
+write_csv(survival_bind, here::here("smelt_2019_winterspring", "data_clean", "2019_smeltstudy_survival_data.csv"))
 ```

### 2022-10-26 smelt_2019_winterspring/clean_growth_survival_datasets_for_publication.R
EDI cleaned tables

@@ -1,0 +1,17 @@
+
+library(here)
+library(dplyr)
+
+Cagetype_data <- read.csv(here::here("smelt_2019_winterspring", "data_clean", "Cagetype_data.csv")) %>%
+  mutate(Delta_Weight = Post_Weight_g - Pre_Weight_g,
+         PropChange_Weight = round(Delta_Weight/Pre_Weight_g,2),
+         Delta_FL = Post_FL_cm - Pre_FL_cm,
+         PropChange_FL = round(Delta_FL/Pre_FL_cm,2),
+         Site = factor(Site, levels = c("RV", "DWSC")),
+         Enclosure = ifelse(Mesh == "wrap", "A", ifelse(Mesh == "large", "B", ifelse(Mesh == "small", "C", ifelse(Mesh == "control", "control", NA)))))%>%
+  select(Site, Cage, Enclosure, Mesh, Pre_FL_cm, Post_FL_cm, PropChange_FL, Pre_Weight_g, Post_Weight_g, PropChange_Weight, Pre_CF, Post_CF, Delta_CF) %>%
+  filter(Mesh!= "control")
+
+write_csv(Cagetype_data, here::here("smelt_2019_winterspring", "data_clean", "2019_smeltstudy_growth-cf_data.csv"))
+
+# See EDI table for survival in manuscript_weight_length_k_survival.Rmd

### 2022-10-26 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
Minor updates to tables - changed "Site" to "Location" to match Nicole and added Location to survival table

@@
          Mesh = factor(Mesh))%>%
-  group_by(Mesh, Cage) %>%
+  group_by(Site, Mesh, Cage) %>%
   summarize(Survived = sum(Survived),
@@
 survival_bind <- rbind(survival_DWSC, survival_RV) %>%
-  mutate(rate = round(rate,2))
+  mutate(rate = round(rate,2)) %>%
+  rename(Location = Site)
 write_csv(survival_bind, here::here("smelt_2019_winterspring", "data_clean", "2019_smeltstudy_survival_data.csv"))

### 2022-10-26 smelt_2019_winterspring/edi/run_EMLassemblyline_for_edi.R
pushing edi folder with more complete data files

@@ -1,0 +1,102 @@
+# This script executes an EMLassemblyline workflow.
+
+# Initialize workspace --------------------------------------------------------
+
+# Update EMLassemblyline and load
+
+remotes::install_github("EDIorg/EMLassemblyline")
+library(EMLassemblyline)
+
+# Define paths for your metadata templates, data, and EML
+
+path_templates <- "smelt_2019_winterspring/edi/metadata_templates"
+path_data <- "smelt_2019_winterspring/edi/data_objects"
+path_eml <- "smelt_2019_winterspring/edi/eml"
+
+# Create metadata templates ---------------------------------------------------
+
+# Below is a list of boiler plate function calls for creating metadata templates.
+# They are meant to be a reminder and save you a little time. Remove the
+# functions and arguments you don't need AND ... don't forget to read the docs!
+# E.g. ?template_core_metadata
+
+# Create core templates (required for all data packages)
+
+EMLassemblyline::template_core_metadata(
+  path = path_templates,
+  license = "CCBY",
+  file.type = ".md")
+
+# Create table attributes template (required when data tables are present)
+
+EMLassemblyline::template_table_attributes(
+  path = path_templates,
+  data.path = path_data,
+  data.table = c("2019_smeltstudy_diet_data.csv",
+                 "2019_smeltstudy_growth-cf_data.csv",
+                 "2019_smeltstudy_survival_data.csv",
+                 "2019_smeltstudy_zoop_data.csv",
+                 "2019_smeltstudy_cagevelocity_data.csv",
+                 "2019_smeltstudy_deploy_retrieve_data.csv",
+                 "2019_smeltstudy_dailycheck_data.csv",
+                 "2019_smeltstudy_stations.csv"))
+# Look at standard units in the package. Need to create custom units if they aren't in here.
+# Run view_unit_dictionary() to look at the units EML has standard. See custom units example for filling out custom units.
+
+# Create categorical variables template (required when attributes templates
+# contains variables with a "categorical" class)
+
+EMLassemblyline::template_categorical_variables(
+  path = path_templates,
+  data.path = path_data)
+
+# Create geographic coverage (required when more than one geographic location
+# is to be reported in the metadata).
+
+EMLassemblyline::template_geographic_coverage(
+  path = path_templates,
+  data.path = path_data,
+  data.table = "",
[…]

### 2022-10-26 smelt_2019_winterspring/clean_growth_survival_datasets_for_publication.R
Changed site to location

@@ -9,7 +9,7 @@ Cagetype_data <- read.csv(here::here("smelt_2019_winterspring", "data_clean", "C
          PropChange_FL = round(Delta_FL/Pre_FL_cm,2),
          Site = factor(Site, levels = c("RV", "DWSC")),
          Enclosure = ifelse(Mesh == "wrap", "A", ifelse(Mesh == "large", "B", ifelse(Mesh == "small", "C", ifelse(Mesh == "control", "control", NA)))))%>%
-  select(Site, Cage, Enclosure, Mesh, Pre_FL_cm, Post_FL_cm, PropChange_FL, Pre_Weight_g, Post_Weight_g, PropChange_Weight, Pre_CF, Post_CF, Delta_CF) %>%
+  select(Location = Site, Cage, Enclosure, Mesh, Pre_FL_cm, Post_FL_cm, PropChange_FL, Pre_Weight_g, Post_Weight_g, PropChange_Weight, Pre_CF, Post_CF, Delta_CF) %>%
   filter(Mesh!= "control")
 
 write_csv(Cagetype_data, here::here("smelt_2019_winterspring", "data_clean", "2019_smeltstudy_growth-cf_data.csv"))

### 2022-11-16 smelt_2019_winterspring/ZoopPlotting.Rmd
updated dataframe name
updated to match new column headers

@@
 ```{r}
-zoop <- read_csv("smelt_2019_winterspring/data_raw/ZoopDataCombined_biomass_qc'ed_12.19.19.csv")
+zoop <- read_csv("smelt_2019_winterspring/data_raw/2019_smeltstudy_zoop_data.csv")
 
@@
 
-zoop$RingSize_m <- zoop$RingSize_cm/100
+zoop$RingSize_m <- zoop$RingSize/100
 
@@
 tow$volumesampled<-((pi*(tow$RingSize_m^2))/4)*tow$distance
-tow$samplecount<-(tow$TotalVolume_ml/tow$Subsampled_ml)*tow$Count
+tow$samplecount<-(tow$TotalVolume/tow$SubsampledVolume)*tow$Count
 tow$ind_m3<-tow$samplecount/tow$volumesampled
@@
 #to incorporate biomass
-tow$samplebiomass<-(tow$TotalVolume_ml/tow$Subsampled_ml)*tow$Total.Biomass
+tow$samplebiomass<-(tow$TotalVolume/tow$SubsampledVolume)*tow$TotalBiomass
 tow$bio_m3<-tow$samplebiomass/tow$volumesampled
@@
 throw$radius<-throw$RingSize_m/2
-throw$volumesampled<- throw$radius*2*pi*throw$TowDistance_m+(2*pi*(throw$radius^2))
-throw$samplecount<-(throw$TotalVolume_ml/throw$Subsampled_ml)*throw$Count
+throw$volumesampled<- throw$radius*2*pi*throw$TowDistance+(2*pi*(throw$radius^2))
+throw$samplecount<-(throw$TotalVolume/throw$SubsampledVolume)*throw$Count
 throw$ind_m3<-throw$samplecount/throw$volumesampled
@@
 #to incorporate biomass
-throw$samplebiomass<-(throw$TotalVolume_ml/throw$Subsampled_ml)*throw$Total.Biomass
+throw$samplebiomass<-(throw$TotalVolume/throw$SubsampledVolume)*throw$TotalBiomass
 throw$bio_m3<-throw$samplebiomass/throw$volumesampled
@@
 #combine
-tow$radius<-tow$RingSize_m*2
+tow$radius<-tow$RingSize*2
 abundance <- rbind(tow, throw)
 abundance$Date<-ymd(abundance$Date)
-abundance$Taxa<-as.factor(abundance$Taxa)
+abundance$Taxa<-as.factor(abundance$TaxonomicGrouping)
 abundance$ind_m3<-as.numeric(abundance$ind_m3)
+
+#write file for use in analysis for another project
+write_excel_csv(all, "smelt_2019_allseasons/data_clean/zoop_abundance.csv")
 
@@
 top.sp<-abundance %>% 
-  group_by(SiteName, Taxa, ID) %>% 
+  group_by(Location, Taxa, Taxon) %>% 
   summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))
@@
 sum<-top.sp %>% 
-  group_by(SiteName) %>% 
+  group_by(Location) %>% 
   summarize("sum"= sum(bio))
@@
 #break into DWSC and RV
-dw <- top.sp %>% filter(SiteName == "DWSC")
-rv <- top.sp %>% filter(SiteName == "RV")
+dw <- top.sp %>% filter(Location == "DWSC")
+rv <- top.sp %>% filter(Location == "RV")
 
@@
 dw$DWSC.Perc <- (dw$DWSC.Bio/12832.26)*100
-dw <- dw[c(2,3,7,8)]
+dw <- dw[c(2,3,6,7)]
 dw2 <- subset(dw, DWSC.Bio!=0)
@@
 rv$RV.Perc <- (rv$RV.Bio/32782.81)*100
-rv <- rv[c(2,3,7,8)]
+rv <- rv[c(2,3,6,7)]
 rv2 <- subset(rv, RV.Bio!=0)
@@
 #merge
-all <- merge(rv2,dw2,by=c("ID","Taxa"),all=TRUE)
+all <- merge(rv2,dw2,by=c("Taxa","Taxon"),all=TRUE)
 
@@
 taxa<-abundance %>% 
-  group_by(SiteName, Date, Taxa) %>% 
+  group_by(Location, Date, Taxa) %>% 
   summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))
@@
 taxa.week<-taxa %>% 
-  group_by(SiteName, Week, Taxa) %>% 
+  group_by(Location, Week, Taxa) %>% 
   summarize("bio.mean"=mean(bio))
@@
   geom_bar(stat = "identity", data=taxa.week, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Macrozoo", "Microzoo"))), colour="black", width = .5) +
-  facet_wrap(~SiteName)+
+  facet_wrap(~Location)+
   theme_bw() + 
@@
 
-taxa.week.2$SiteName = factor(taxa.week.2$SiteName, levels=c('RV','DWSC'))
+taxa.week.2$SiteName = factor(taxa.week.2$Location, levels=c('RV','DWSC'))
 
@@
   geom_bar(stat = "identity", data=taxa.week.2, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Other"))), colour="black", width = .5) +
-    facet_wrap(~SiteName)+
+    facet_wrap(~Location)+
   theme_bw() + 
@@
 for.mod<-taxa.week.2 %>% 
-  group_by(SiteName, Week, Week2) %>% 
+  group_by(Location, Week, Week2) %>% 
   summarize("bio.all"=sum(bio.mean))
@@
 
-model<-lm(bio.all~SiteName*Week2, data=for.mod)
+model<-lm(bio.all~Location*Week2, data=for.mod)
 anova(model)
@@
 
-leveneobject<- lm(abs(resid(model))~SiteName*Week2, data=for.mod)
+leveneobject<- lm(abs(resid(model))~Location*Week2, data=for.mod)
 anova(leveneobject) #insignificant
@@
 marginal = emmeans(model, 
-                   ~ SiteName*Week2)
+                   ~ Location*Week2)
 

### 2022-11-16 smelt_2019_allseasons/Zoop 2019.Rmd
updates to zoop data prep and figures

@@
 ```{r}
-zoop <- read_csv("hybrid study/ZoopData_SummerFall_2019.csv")
+zoop <- read_csv("smelt_2019_allseasons/data_raw/ZoopData_SummerFall_2019.csv")
 
@@
 #bring in tow data
-aug <- read_csv("hybrid study/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
-oct <- read_csv("hybrid study/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
+aug <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
+oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
 aug$Date <- mdy(aug$Date)
@@
 #calculate abundance -----------------------
-all$distance <- (all$Revs)*57560/999999
+all$distance <- (all$Revs)*57560/999999 #57,560 = low speed rotor constant
 all$volumesampled <- ((pi*(all$RingSize_m^2))/4)*all$distance
@@
 caught <- all[!(all$ind_m3==0),]
+
+#add taxa
+
+caught[caught$ID %in% c("Rotifers", "Copepod nauplii"),]$Taxa <- "Microzoo"
+
+caught[caught$ID %in% c("Ostracods"),]$Taxa <- "Ostracod"
+
+caught[caught$ID %in% c("Bosmina", "Ceriodaphnia", "Diaphanosoma", "Alona", "Chydorus", "Eurycercus", "Monospilus", "Alonella", "Daphnia", "Ilyocryptus", "Camptocercus", "Simocephalus", "Pleuroxus", "Graptoleberis", "Macrothrix"),]$Taxa <- "Cladocera"
+
+caught[caught$ID %in% c("Cyclopoid copepodid", "Tropocyclops prasinus", "Limnoithona tetraspina", "Diacyclops thomasi", "Eucyclops sp.", "Mesocyclops edax", "Microcyclops rubellus", "Tropocylcops prasinus", "Acanthocyclops vernalis adult", "Eucyclops pectinifer", "Paracyclops spp."),]$Taxa <- "Cyclopoid"
+
+caught[caught$ID %in% c("Calanoid copepodid", "Pseudodiaptomus forbesi adult", "Pseudodiaptomus forbesi copepodid", "Eurytemora affinis adult", "Sinocalanus doerrii adult"),]$Taxa <- "Calanoid"
+
+caught[caught$ID %in% c("Harpacticoids"),]$Taxa <- "Harpacticoid"
+
+caught[caught$ID %in% c("Maeotias marginata (large)"),]$Taxa <- "Other"
 ```
+
 # plot summer/fall data
@@
 
-ggplot(data = caught, aes(x=MD, y=samplecount)) +
+ggplot() +
   geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
@@
 
-ggsave("hybrid study/plots/allzoop.png", dpi=250, height=6, width=10, units="in")
+ggsave("smelt_2019_allseasons/figures/allzoop.png", dpi=250, height=6, width=10, units="in")
 
@@
 macro <- macro[!(macro$ID=="Rotifers"),]
-macro <- macro[!(macro$ID=="Ostracods"),]
 
-ggplot(data = macro, aes(x=MD, y=samplecount)) +
+ggplot() +
   geom_bar(position = "fill", stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
@@
 
-ggsave("hybrid study/plots/macrozoop.png", dpi=250, height=6, width=10, units="in")
+ggsave("smelt_2019_allseasons/figures/macrozoop.png", dpi=250, height=6, width=10, units="in")
 ```
+
 #bring in winter data
 ```{r}
-#prep of this dataset (code and raw data) can be found here: https://cawater.sharepoint.com/:f:/r/sites/dwrdoc-aes/Shared%20Documents/Delta%20Smelt%20Enclosure%20Study/Analysis/Zooplankton/Zoop%2719?csf=1&web=1&e=YhKzMy
+#prep of this dataset (code and raw data) can be found on GitHub under Smelt Cages > smelt_2019_winterspring
 
-winter <- read_csv("hybrid study/zoop_abundance.csv")
+winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
 
@@
 
-#remove DWSC samples
-winter <- winter[!(winter$SiteName=="DWSC"),]
-
 #merge with catch df
-
 #condense to columns of interest
-winter2 <- winter[c(1,2,13,16,32,25,26)]
+winter2 <- winter[c(1,2,13,27,30,22,23)]
 caught2 <- caught[c(1,2,7,10,20,29,30)]
@@
 #rename column
-winter2 <- winter2 %>% rename(Location = "SiteName")
+winter2 <- winter2 %>% rename(ID = "Taxon")
+
+#change ostracod taxa
+winter2[winter2$ID %in% c("Ostracods"),]$Taxa <- "Ostracod"
 
@@
 ```
+
 # plot all 2019
 ```{r}
-#order factors
-unique(caught.19$MD)
-caught.19$MD <- factor(caught.19$MD, levels=c("Jan-24", "Jan-29", "Jan-31", "Feb-6", "Feb-8", "Feb-12", "Feb-15", "Feb-22", "Jul-31", "Aug-1", "Aug-2",  "Aug-5", "Aug-6", "Aug-8",  "Aug-12", "Aug-15", "Aug-19", "Aug-22", "Aug-26", "Oct-10", "Oct-11", "Oct-15", "Oct-16", "Oct-18", "Oct-21", "Oct-25", "Oct-28", "Nov-4"))
+#create season column
+caught.19$Season <- as.character(NA)
 
-ggplot(data = caught.19, aes(x=MD, y=samplecount)) +
-  geom_bar(position = "fill", stat = "identity", data=caught.19, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
-  facet_wrap(~Location, ncol = 1) +
+caught.19[caught.19$MD %in% c("Jan-24", "Jan-29", "Jan-31", "Feb-6", "Feb-8", "Feb-12", "Feb-15", "Feb-22", "Feb-28", "Mar-1", "Mar-4", "Mar-8", "Mar-13", "Mar-19", "Mar-25"),]$Season <- "Winter"
+
+caught.19[caught.19$MD %in% c("Jul-31", "Aug-1", "Aug-2",  "Aug-5", "Aug-6", "Aug-8",  "Aug-12", "Aug-15", "Aug-19", "Aug-22", "Aug-26"),]$Season <- "Summer"
+
+caught.19[caught.19$MD %in% c("Oct-10", "Oct-11", "Oct-15", "Oct-16", "Oct-18", "Oct-21", "Oct-25", "Oct-28", "Nov-4"),]$Season <- "Fall"
+
+caught.sea <- caught.19 %>% 
+  group_by(Season, Location, Taxa) %>% 
+  summarize("sum.count"= sum(samplecount))
+
+#order seasons
+caught.sea$Season <- factor(caught.sea$Season, levels=c("Winter", "Summer", "Fall"))
+
+#order locations
+caught.sea$Location <- factor(caught.sea$Location, levels=c("DWSC", "RV", "Yolo", "SM"))
+
+ggplot() +
+  geom_bar(position = "fill", stat = "identity", data=caught.sea, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .5) +
+  facet_wrap(~Season, ncol = 1) +
   theme_bw() + 
-  scale_fill_manual(values=pal36)+
-  labs(x = "Date") +
-  labs(y = "Relative Abundance of all Zoop in Sample")+
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  labs(x = "Location") +
+  labs(y = "Relative Abundance")+
   theme(legend.position="right")+
@@
 
-ggsave("hybrid study/plots/allzoop19.png", dpi=250, height=6, width=10, units="in")
+ggsave("smelt_2019_allseasons/figures/allzoop19.png", dpi=250, height=6, width=6, units="in")
 
 #plot with microzoop removed
-macro2 <- caught.19[!(caught.19$ID=="Copepod nauplii"),]
-macro2 <- macro2[!(macro2$ID=="Rotifers"),]
-macro2 <- macro2[!(macro2$ID=="Ostracods"),]
+caught.sea2 <- caught.sea[!(caught.sea$Taxa=="Microzoo"),]
 
-ggplot(data = macro2, aes(x=MD, y=samplecount)) +
-  geom_bar(position = "fill", stat = "identity", data=macro2, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
-  facet_wrap(~Location, ncol = 1) +
+ggplot() +
+  geom_bar(position = "fill", stat = "identity", data=caught.sea2, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .5) +
+  facet_wrap(~Season, ncol = 1) +
   theme_bw() + 
-  scale_fill_manual(values=pal36)+
-  labs(x = "Date") +
-  labs(y = "Relative Abundance of Macrozoop in Sample")+
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  labs(x = "Location") +
+  labs(y = "Relative Abundance")+
   theme(legend.position="right")+
@@
 
-ggsave("hybrid study/plots/macrozoop19.png", dpi=250, height=6, width=10, units="in")
+ggsave("smelt_2019_allseasons/figures/macrozoop19.png", dpi=250, height=6, width=6, units="in")
 ```
+
+# repeated measures ANOVA
+```{r}
+#combine taxa 
+for.mod<-caught.19 %>% 
+  group_by(Location, Date, Taxa, Season) %>% 
+  summarize("ind.all"=sum(ind_m3))
+
+shapiro.test(for.mod$ind.all) #very significant, no ANOVA
+```

### 2022-11-18 smelt_2019_allseasons/Zoop 2019.Rmd
small edit to zoop fig axis

@@
       legend.text = element_text(size = 8),
-      legend.title = element_text(size = 10),
-      axis.text.x = element_text(angle = 90))
+      legend.title = element_text(size = 10))
 

### 2022-11-18 smelt_2019_allseasons/Zoop 2019.Rmd
few more figure edits

@@
 
-zoop[zoop$Location %in% c("STTD", "STTD-YOLO", "YOLO"),]$Location <- "Yolo"
+zoop[zoop$Location %in% c("STTD", "STTD-YOLO", "YOLO"),]$Location <- "YB"
+tow2[tow2$Location %in% c("Yolo"),]$Location <- "YB"
 
@@
 
-ggsave("smelt_2019_allseasons/figures/allzoop.png", dpi=250, height=6, width=10, units="in")
-
 #plot with microzoop removed
@@
       axis.text.x = element_text(angle = 90))
-
-ggsave("smelt_2019_allseasons/figures/macrozoop.png", dpi=250, height=6, width=10, units="in")
 ```
@@
 #order locations
-caught.sea$Location <- factor(caught.sea$Location, levels=c("DWSC", "RV", "Yolo", "SM"))
+caught.sea$Location <- factor(caught.sea$Location, levels=c("DWSC", "RV", "YB", "SM"))
 

### 2022-11-18 smelt_2019_allseasons/Zoop 2019.Rmd
zoop plot edits

@@
 ggplot() +
-  geom_bar(position = "fill", stat = "identity", data=caught.sea, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .5) +
+  geom_bar(position = "fill", stat = "identity", data=caught.sea, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .75) +
   facet_wrap(~Season, ncol = 1) +
@@
 ggplot() +
-  geom_bar(position = "fill", stat = "identity", data=caught.sea2, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .5) +
+  geom_bar(position = "fill", stat = "identity", data=caught.sea2, aes (x=Location, y=sum.count, fill=Taxa), colour="black", width = .75) +
   facet_wrap(~Season, ncol = 1) +

### 2022-11-19 smelt_2019_allseasons/Diet 2019.Rmd
updating diet plots

@@
 
-diet2[diet2$Prey.Taxa %in% c("Americorophium sp.", "Americorophium spinicorne", "Eogammarus confervicolus", "Gammaridea", "Hyallela azteca", "Crangonyx sp.", "Corophiidae", "Amphipoda"),]$Taxa <- "Amphipoda"
+diet2[diet2$Prey.Taxa %in% c("Americorophium sp.", "Americorophium spinicorne", "Eogammarus confervicolus", "Gammaridea", "Hyallela azteca", "Crangonyx sp.", "Corophiidae", "Amphipoda"),]$Taxa <- "Amphipod"
 
-diet2[diet2$Prey.Taxa %in% c("Pseudodiaptomus forbesi", "Calanoida", "Eurytemora affinis", "Diaptomidae", "Sinocalanus doerrii", "Osphranticum labronectum"),]$Taxa <- "Calanoida"
+diet2[diet2$Prey.Taxa %in% c("Pseudodiaptomus forbesi", "Calanoida", "Eurytemora affinis", "Diaptomidae", "Sinocalanus doerrii", "Osphranticum labronectum"),]$Taxa <- "Calanoid"
 
-diet2[diet2$Prey.Taxa %in% c("Acanthocyclops sp.", "Macrocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Cyclopoida", "Halicyclops sp.", "Mesocyclops sp.", "Tropocyclops sp.", "Tropocyclops sp."),]$Taxa <- "Cyclopoida"
+diet2[diet2$Prey.Taxa %in% c("Acanthocyclops sp.", "Macrocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Cyclopoida", "Halicyclops sp.", "Mesocyclops sp.", "Tropocyclops sp.", "Tropocyclops sp."),]$Taxa <- "Cyclopoid"
 
@@
 
-diet2[diet2$Prey.Taxa %in% c("Harpacticoida"),]$Taxa <- "Harpacticoida"
+diet2[diet2$Prey.Taxa %in% c("Harpacticoida"),]$Taxa <- "Harpacticoid"
 
-diet2[diet2$Prey.Taxa %in% c("Ostracoda"),]$Taxa <- "Ostracoda"
+diet2[diet2$Prey.Taxa %in% c("Ostracoda"),]$Taxa <- "Ostracod"
 
@@
 Cage_type$Cage.ID <- c("A", "B", "C", "D", "E", "F")
-Cage_type$Mesh <- c("wrap", "large", "small", "small", "wrap", "large")
+Cage_type$Mesh <- c("small", "large", "wrap", "wrap", "small", "large")
 
@@
 #change location titles 
-diet$Location[diet$Location =="RIVERS"] <- "RV.Feb"
-diet$Location[diet$Location =="Sac DWSC"] <- "DWSC.Apr"
-diet$Location[diet$Location =="SM"] <- "SM.Nov"
-diet$Location[diet$Location =="YB"] <- "YB.Nov"
+diet$Location[diet$Location =="RIVERS"] <- "RV.Winter"
+diet$Location[diet$Location =="Sac DWSC"] <- "DWSC.Winter"
+diet$Location[diet$Location =="SM"] <- "SM.Fall"
+diet$Location[diet$Location =="YB"] <- "YB.Fall"
 #RV a little trickier with two dates
 diet$ld = paste(diet$Location, diet$Date)
-diet$Location[diet$ld =="RV 2019-08-28"] <- "RV.Aug"
-diet$Location[diet$ld =="RV 2019-11-06"] <- "RV.Nov"
+diet$Location[diet$ld =="RV 2019-08-28"] <- "RV.Summer"
+diet$Location[diet$ld =="RV 2019-11-06"] <- "RV.Fall"
 RV <- filter(diet, Location == "RV")
-diet$Location[diet$ld =="RV 2019-11-07"] <- "RV.Nov"
+diet$Location[diet$ld =="RV 2019-11-07"] <- "RV.Fall"
 
@@
 ```{r}
-unique(diet$Location)
-
 #remove FCCL controls
@@
 
-#remove DWSC
-#diet<-diet[diet$Location != "DWSC.Apr",]
-
 #fix fish that were assigned the wrong cage (came up during summary stats, check against dissected fish data, likely E and F were misread)
@@
 
-str(diet)
 #change count to numeric
 diet$Count<-as.numeric(diet$Count)
+
 #output says NAs introduced by coercion - check NA's
 newDF <- diet[is.na(diet$Count),]
+
 #one NA next to a gammaridae - comment says that it was too digested and could be more than one individual, to be safe just going to add a count of "1" for this observation; found it on row 413
 diet<-diet %>% replace_na(list(Count=1))
+
 #change count to numeric
@@
 full.prop.3<-subset(full.prop.2, select=c("Location", "Mesh", "tlc", "Taxa", "proportion"))
+
 #replace proportion Nas with zeros
@@
 stomach_abundance$Location <- stomach_abundance$Location.x
-stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))
+stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("DWSC.Winter", "RV.Winter", "RV.Summer", "SM.Fall", "YB.Fall", "RV.Fall"))
 
@@
 #order locations
-prop$Location <- ordered(prop$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "RV.Nov", "YB.Nov", "SM.Nov"))
+prop$Location <- ordered(prop$Location, levels = c("DWSC.Winter", "RV.Winter", "RV.Summer", "RV.Fall", "YB.Fall", "SM.Fall"))
 
-cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2")
-legend_title <- "Taxa"
+#order taxa to match zoop plot
+prop$Taxa <- factor(prop$Taxa, levels=c("Calanoid", "Cladocera", "Cyclopoid", "Harpacticoid", "Ostracod", "Other", "Amphipod", "Diptera"))
 
-ggplot(data=prop, aes(x=Location, y =prop.mean)) +
-    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))),  position="fill", stat="identity") +
+ggplot(data=prop, aes(x=Location, y =prop.mean, fill=Taxa)) +
+    geom_bar(position="fill", stat="identity", colour="black") +
   theme_bw() +
-  scale_fill_manual(legend_title, values=cbPalette)+
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
   theme(legend.position="right", axis.title.x = element_blank())+
   labs(y = "Mean Contribution to Diet")
+
+ggsave("smelt_2019_allseasons/figures/diet19_onepanel.png", dpi=250, height=4.5, width=7, units="in")
+
+#facet by season
+
+#create season column
+prop2 <- prop
+prop2$Season <- "NA"
+prop2[prop2$Location %in% c("DWSC.Winter", "RV.Winter"),]$Season <- "Winter"
+prop2[prop2$Location %in% c("RV.Summer"),]$Season <- "Summer"
+prop2[prop2$Location %in% c("RV.Fall", "YB.Fall", "SM.Fall"),]$Season <- "Fall"
+
+#change Location to drop season
+prop2$Location <- as.character(prop2$Location)
+prop2$Location[prop$Location =="DWSC.Winter"] <- "DWSC"
+prop2[prop2$Location %in% c("RV.Winter", "RV.Summer", "RV.Fall"),]$Location <- "RV"
+prop2$Location[prop$Location =="YB.Fall"] <- "YB"
+prop2$Location[prop$Location =="SM.Fall"] <- "SM"
+
+#order seasons
+prop2$Season <- factor(prop2$Season, levels=c("Winter", "Summer", "Fall"))
+
+#order locations
+prop2$Location <- factor(prop2$Location, levels=c("DWSC", "RV", "YB", "SM"))
+
+#order taxa to match zoop plot
+prop2$Taxa <- factor(prop2$Taxa, levels=c("Calanoid", "Cladocera", "Cyclopoid", "Harpacticoid", "Ostracod", "Other", "Amphipod", "Diptera"))
+
+#plot
+ggplot(data=prop2, aes(x=Location, y =prop.mean, fill=Taxa)) +
+  geom_bar(position="fill", stat="identity", colour="black", width=0.75) +
+  facet_wrap(~Season, ncol=1) +
+  theme_bw() +
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  theme(legend.position="right", axis.title.x = element_blank())+
+  labs(y = "Mean Contribution to Diet") +
+   theme(legend.position="right")+
+      theme(axis.text = element_text(size = 12),
+      axis.title = element_text(size = 12),
+      legend.text = element_text(size = 8),
+      legend.title = element_text(size = 10))
+
+library(scales)
+show_col(viridis_pal(option = "plasma")(8))
+viridis_pal(option = "plasma")(8)
+
+ggsave("smelt_2019_allseasons/figures/diet19_multipanel.png", dpi=250, height=6, width=6, units="in")
 ```

### 2022-11-21 smelt_2019_allseasons/Diet 2019.Rmd
zoop and diet plot updates

@@
 taxa_tag<- diet %>% 
-  group_by(Location, Mesh, tlc, Taxa) %>% 
+  group_by(Location, tlc, Taxa) %>% 
   summarize("count.sum"= sum(Count))
@@
 stomach<- diet %>% 
-  group_by(Location, Mesh, tlc) %>% 
+  group_by(Location, tlc) %>% 
   summarize("stomach.sum"= sum(Count))
@@
 
-#replace count.sum Nas with zeros
-full.count<-full.prop.2 %>% replace_na(list(count.sum=0))
-
-#select columns I want for count
-full.count<-subset(full.count, select=c("Location", "Mesh", "tlc", "Taxa", "count.sum"))
-
 #select columns I want for proportion
-full.prop.3<-subset(full.prop.2, select=c("Location", "Mesh", "tlc", "Taxa", "proportion"))
+full.prop.3<-subset(full.prop.2, select=c("Location", "tlc", "Taxa", "proportion"))
 
@@
 
+ggsave("smelt_2019_allseasons/figures/diet19_multipanel.png", dpi=250, height=6, width=6, units="in")
+
 library(scales)
@@
 viridis_pal(option = "plasma")(8)
-
-ggsave("smelt_2019_allseasons/figures/diet19_multipanel.png", dpi=250, height=6, width=6, units="in")
 ```
-
-### Plot methods text (from manuscript): To visualize the relative abundance of different taxa among mesh types, we calculated taxa proportion (taxa abundance/total abundance) for each individual fish’s diet and then averaged these taxa proportions across individuals from each mesh type.
-These means were then fit to a 100% scale to estimate the mean percent contribution of each taxa to overall mesh type diets.
-Averaging proportions instead of abundance across fish allowed for the diets of different sizes fish to contribute equally.

### 2022-11-21 smelt_2019_allseasons/Zoop 2019.Rmd
zoop and diet plot updates

@@
 
+#create custom palette from viridis to match taxa from diet plot
+zoopPalette <- c("#0D0887FF", "#5402A3FF", "#8B0AA5FF", "#B93289FF", "#DB5C68FF", "#F48849FF")
+
 ggplot() +
@@
   theme_bw() + 
-  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  scale_fill_manual(values=zoopPalette)+
   labs(x = "Location") +

### 2023-01-26 smelt_2019_allseasons/Zoop 2019.Rmd
added multivariate stats

@@
 library(Polychrome)
+library(here)
 ```
@@
 ```{r}
-zoop <- read_csv("smelt_2019_allseasons/data_raw/ZoopData_SummerFall_2019.csv")
+
+#zoop <- read_csv("smelt_2019_allseasons/data_raw/ZoopData_SummerFall_2019.csv")
+zoop <- read_csv("data_raw/ZoopData_SummerFall_2019.csv")
 
@@
 #bring in tow data
-aug <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
-oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
+#aug <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
+#oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
+aug <- read_csv("data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
+oct <- read_csv("data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
+
 aug$Date <- mdy(aug$Date)
@@
 
-winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
+#winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
+winter <- read_csv("data_clean/zoop_abundance.csv")
 
@@
 ```
+
+## Multivariate statistics
+
+```{r}
+
+library(vegan)
+source("../PlotNMDS.R")
+
+zoops = mutate(caught.19, SampleID = paste(Location, Date)) %>%
+  pivot_wider(id_cols = c(SampleID, Location, Date, MD, Season), names_from = Taxa, values_from = ind_m3, values_fn = sum, values_fill = 0) %>%
+  mutate(datatype = "Zoops")
+
+#first let's look at Rio Vista across seasons
+RVzoops = filter(zoops, Location == "RV")
+
+#raw abundance matrix
+RVzoopmat = as.matrix(RVzoops[,6:12])
+
+#relative abundance matrix
+RVzoopmat2 = RVzoopmat/rowSums(RVzoopmat)
+
+RVa = adonis2(RVzoopmat~Season, data = RVzoops)
+RVa
+#
+
+RVb = adonis2(RVzoopmat2~Season, data = RVzoops)
+RVb
+
+```
+pretty big differences between seasons, R2 of 54% on the absolute abundance, 64% on relative abundance
+
+THough I may need to update this with some sort of variable to account for day of year. Not sure.
+
+Now I'll look for changes by location
+
+```{r}
+Fallzoops = filter(zoops, Season == "Fall")
+
+#raw abundance matrix
+Fallzoopmat = as.matrix(Fallzoops[,6:12])
+
+#relative abundance matrix
+Fallzoopmat2 = Fallzoopmat/rowSums(Fallzoopmat)
+
+Falla = adonis2(Fallzoopmat~Location, data = Fallzoops)
+Falla
+#
+
+Fallb = adonis2(Fallzoopmat2~Location, data = Fallzoops)
+Fallb
+#
+
+```
+
+Wow! Even larger differences in relative and absolute abundance by region
+
+I'm going to try an NMDS just for funzies
+
+```{r}
+
+#raw abundance matrix
+zoopmat = as.matrix(zoops[,6:12])
+
+#relative abundance matrix
+zoopmat2 = zoopmat/rowSums(zoopmat)
+
+N1 = metaMDS(zoopmat2)
+zoops = mutate(zoops, Season  = as.factor(Season), Location = as.factor(Location))
+PlotNMDS(N1, zoops, group = "Season")
+PlotNMDS(N1, zoops, group = "Location")
+
+RVN1 = metaMDS(RVzoopmat2)
+RVzoops = mutate(RVzoops, Season  = as.factor(Season), Location = as.factor(Location))
+PlotNMDS(RVN1, RVzoops, group = "Season")
+PlotNMDS(RVN1, RVzoops, group = "Location")
+
+```
+
+## Diet data comparison
+
+```{r}
+#diet2 <- read_csv("smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
+diet2 <- read_csv("data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
+
+diet2$Date <- mdy(diet2$Date)
+
+#format 
+#rename columns
+diet2 <- diet2 %>% rename(Cage.ID = "Cage ID", Contents.Weight = "Total Contents Weight", Prey.Taxa = "Prey Taxa", LH.Stage = "LH Stage")
+
+#add taxa column (choose taxa based on what is present in the dataframe)
+diet2$Taxa <- as.character(NA)
+
+str(diet2)
+
+diet2[diet2$Prey.Taxa %in% c("Bosmina sp.", "Chydorus sp.", "Daphnia sp.", "Ceriodaphnia sp.", "Chydoridae", "Crangonyx sp.", "Scapholeberis sp.", "Simocephalus sp.", "Eurycercus sp.", "Leydigia sp.", "Cladocera", "Sida sp.", "Alona sp.", "Diaphanosoma sp."),]$Taxa <- "Cladocera"
+
+diet2[diet2$Prey.Taxa %in% c("Americorophium sp.", "Americorophium spinicorne", "Eogammarus confervicolus", "Gammaridea", "Hyallela azteca", "Crangonyx sp.", "Corophiidae", "Amphipoda"),]$Taxa <- "Amphipod"
+
+diet2[diet2$Prey.Taxa %in% c("Pseudodiaptomus forbesi", "Calanoida", "Eurytemora affinis", "Diaptomidae", "Sinocalanus doerrii", "Osphranticum labronectum"),]$Taxa <- "Calanoid"
+
+diet2[diet2$Prey.Taxa %in% c("Acanthocyclops sp.", "Macrocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Cyclopoida", "Halicyclops sp.", "Mesocyclops sp.", "Tropocyclops sp.", "Tropocyclops sp."),]$Taxa <- "Cyclopoid"
+
+diet2[diet2$Prey.Taxa %in% c("Chironomidae", "Diptera"),]$Taxa <- "Diptera"
+
+diet2[diet2$Prey.Taxa %in% c("empty", "EMPTY"),]$Taxa <- "empty"
+
+diet2[diet2$Prey.Taxa %in% c("Harpacticoida"),]$Taxa <- "Harpacticoid"
+
+diet2[diet2$Prey.Taxa %in% c("Ostracoda"),]$Taxa <- "Ostracod"
+
+diet2[diet2$Prey.Taxa %in% c("Fish", "Acari", "Insecta", "Bivalvia", "Culicidae", "egg unidentified", "Corixidae", "Hemiptera", "plant seed", "plant matter", "Unidentified", "Mysidacea", "Cumacea"),]$Taxa <- "Other"
+
+new_DF <- diet2[is.na(diet2$Taxa),] #update code above with new prey.taxa that weren't found in previous diets
+#there are two "copepoda" entries with no count or location...don't seem that important so I am going to just go ahead and remove them
+diet2[diet2$Taxa %in% c("empty"),]$Count <- "0"
+diet2 <- diet2[!is.na(diet2$Count),]
+
+#Tag column currently has rows with just the Tag and others with location, date, and tag
+#first break those two kinds of columns apart
+weird.tag <- diet2[is.na(diet2$Location),]
+norm.tag <- diet2[!is.na(diet2$Location),]
+
+#then for break out the Tag ID into Location and tag (remove date)
+weird.tag <- weird.tag %>% separate(Tag, c("Location", "X.date", "Tag"))
+
+#remove new date column
+weird.tag <- subset(weird.tag, select = -6)
+
+#add mesh types for prototype experiment
+#create new column for mesh types
+Cage_type <- as.data.frame(matrix(0, ncol = 2, nrow = 6))
+colnames(Cage_type) <- c("Cage.ID", "Mesh")
+
+Cage_type$Cage.ID <- c("A", "B", "C", "D", "E", "F")
+Cage_type$Mesh <- c("small", "large", "wrap", "wrap", "small", "large")
+
+norm.tag2 <- merge(norm.tag, Cage_type, by = "Cage.ID", all.x = TRUE)
+
+#add mesh types (NA) for summer/fall experiements
+weird.tag$Mesh <- NA
+
+#merge the two
+diet <- rbind(weird.tag, norm.tag2)
+
+#change location titles 
+diet = mutate(diet, Location2 = case_when(Location %in% c("RV", "RIVERS") ~ "RV", 
+                                       Location == "Sac DWSC" ~ "DWSC",
+                                       Location == "SM" ~ "SM",
+                                       Location == "YB" ~ "YB"),
+              Month = month(Date),
+              Season = case_when(Month %in% c(2,3,5) ~ "Winter",
+                                 Month == 8 ~ "Summer",
+                                 Month == 11 ~ "Fall"),
+              Location = Location2,
+              datatype = "diet")
+
+#OMG DON"T PUT COMMENTS IN THE COUNT COLUMN
+diet$Count[which(diet$Count == "1 maybe 2")] = "1"
+diet$Count = as.numeric(diet$Count)
+
+#pivot_wider
+dietwide = mutate(diet, SampleID = paste(Location, Tag)) %>%
+  pivot_wider(id_cols = c(SampleID, Location, Date, Season, datatype), names_from = Taxa, values_from = Count, values_fn = sum, values_fill = 0)
+
+```
+
+Now put the zoop data and diet data together
+
+```{r}
+
+zoopdiet = bind_rows(zoops, dietwide) %>%
+  mutate(Amphipod = case_when(is.na(Amphipod) ~0, TRUE ~ Amphipod),
+         Diptera = case_when(is.na(Diptera) ~0, TRUE ~ Diptera)) %>%
+  select(-empty, -Microzoo)
+
+rowSums(zoopdiet[,c(6:11, 13, 14)])
+
+#remove empty rows
+zoopdiet = zoopdiet[which(rowSums(zoopdiet[,c(6:11, 13, 14)]) !=0),] %>%
+  mutate(datatype = as.factor(datatype), Season = as.factor(Season), Location = as.factor(Location))
+
+#Convert to reletive abundance
+zoopdietmat = as.matrix(zoopdiet[,c(6:11, 13, 14)])
+zoopdietmat2 = zoopdietmat/rowSums(zoopdietmat)
+
+#look at just Rio Vista
+RVdietzoops = filter(zoopdiet, Location == "RV")
+
+#Convert to reletive abundance
+RVzoopdietmat = as.matrix(RVdietzoops[,c(6:11, 13, 14)])
+RVzoopdietmat2 = RVzoopdietmat/rowSums(RVzoopdietmat)
+
+RVda = adonis2(RVzoopdietmat2~ datatype + Season, data = RVdietzoops)
+RVda
+
+zdM = metaMDS(zoopdietmat2)
+
+PlotNMDS(zdM, data = zoopdiet, group = "datatype")
+
+PlotNMDS(zdM, data = zoopdiet, group = "Location")
+
+RVM = metaMDS(RVzoopdietmat2, trymax = 100)
+
+PlotNMDS(RVM, data = RVdietzoops, group = "Season")
+```
+
+Basic plot of zoops versus diet
+
+```{r}
+zoopdietlong = pivot_longer(zoopdiet, cols = c(Ostracod, Cyclopoid, Calanoid, Cladocera, Harpacticoid, Other, Amphipod, Diptera),
+                            names_to = "Taxa", values_to= "count")
+
+ggplot(zoopdietlong, aes(x = datatype, y = count, fill = Taxa))+
+  geom_col(position = "fill")+
+  facet_grid(Location~Season)
+
+```

### 2023-02-27 smelt_2019_allseasons/analyze_growth.Rmd

---
title: "analyze_growth"
author: "Catarina Pien"
date: '2022-09-16'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(readr)
library(here)
library(lme4)
library(car)
root <- "smelt_2019_allseasons"
```

# Condition Factor, Length, Weight
1. Read data

* a, e = wrap
* b, f = large. F = lots of dead smelt
* c, d = small

* We can keep c, d, b
```{r}
data <- read_csv(here(root,"data_clean","clean_smelt_cf_2019.csv")) %>%
  filter(!(grepl("FCCL", Cage) & Season == "Winter"),
         !(Cage %in% c("A", "E","F") & Season == "Winter")) %>%
  filter(!(Site == "RV" & is.na(Cage))) %>%
mutate(Season = factor(Season))

# Note there are a few fish in the summer that are cage-less. They may need to be identified as to which cage they should belong to??

str(data)
RV = filter(data, Site == "RV")
DWSC = filter(data, Site == "DWSC")
```

Weight pre-posts by season
```{r}
Summer <- data %>% filter(Season == "Summer")
Summer_wide <- Summer %>%
  pivot_wider(names_from = "Period",
              values_from = c("FL_cm", "Weight_g", "K"))

Fall <- data %>% filter(Season == "Fall")

Fall_wide <- Fall %>%
  pivot_wider(names_from = "Period",
              values_from = c("FL_cm", "Weight_g", "K"))
```

```{r}
hist(Summer$FL_cm_Pre)
hist(filter(Summer, Site=="RV")$FL_cm_Post)
hist(Summer$Weight_g_Pre)
hist(filter(Summer, Site=="RV")$Weight_g_Post)

hist(filter(data, Site == "RV")$FL_cm)
hist(filter(data, Site == "RV")$Weight_g)
hist(filter(data, Site == "RV")$K)

hist(filter(data, Site == "RV")$FL_cm)
hist(filter(data, Site == "RV")$Weight_g)
hist(filter(data, Site == "RV")$K)

hist(filter(data, Site == "DWSC")$FL_cm)
hist(filter(data, Site == "DWSC")$Weight_g)
hist(filter(data, Site == "DWSC")$K)

hist(Summer$FL_cm)
hist(Summer$Weight_g)
hist(sqrt(Summer$Weight_g))
hist(Summer$K)

hist(Fall$FL_cm)
hist(Fall$Weight_g)
hist(Fall$K)

shapiro.test(filter(data, Site == "DWSC")$FL_cm)
shapiro.test(filter(data, Site == "DWSC")$Weight_g)
shapiro.test(filter(data, Site == "DWSC")$K)

leveneTest(DWSC$FL_cm ~ DWSC$Period, data = data)
leveneTest(DWSC$Weight_g ~ DWSC$Period, data = data)
leveneTest(DWSC$K ~ DWSC$Period, data = data)

shapiro.test(Summer$FL_cm)
shapiro.test(sqrt(Summer$Weight_g))
shapiro.test(Summer$K)

leveneTest(Summer$FL_cm~Summer$Period)
leveneTest(Summer$Weight_g~Summer$Period)
leveneTest(Summer$K~Summer$Period)

shapiro.test(Fall$FL_cm)
shapiro.test(Fall$Weight_g)
shapiro.test(Fall$K)

leveneTest(Fall$FL_cm~Fall$Period)
leveneTest(Fall$Weight_g~Fall$Period)
leveneTest(Fall$K~Fall$Period)
```

## Summer
```{r}
t_sRV <- t.test(Summer$FL_cm_Pre, filter(Summer, Site=="RV")$FL_cm_Post) #no
t_sFC <- t.test(Summer$FL_cm_Pre, filter(Summer, Site=="FCCL")$FL_cm_Post) #yes

t.test(Summer$Weight_g_Pre, filter(Summer, Site=="RV")$Weight_g_Post) #on the border
t.test(Summer$Weight_g_Pre, filter(Summer, Site=="FCCL")$Weight_g_Post) #on the border

t.test(Summer$K_Pre, filter(Summer, Site=="RV")$K_Post) #yes
t.test(Summer$K_Pre, filter(Summer, Site=="FCCL")$K_Post) #yes

wilcox.test(Summer_wide$FL_cm_Pre, filter(Summer_wide, Site=="RV")$FL_cm_Post) #no
wilcox.test(Summer_wide$FL_cm_Pre, filter(Summer_wide, Site=="FCCL")$FL_cm_Post) #yes

wilcox.test(Summer_wide$Weight_g_Pre, filter(Summer_wide, Site=="RV")$Weight_g_Post) #no
wilcox.test(Summer_wide$Weight_g_Pre, filter(Summer_wide, Site=="FCCL")$Weight_g_Post) #no

wilcox.test(Summer_wide$K_Pre, filter(Summer_wide, Site=="RV")$K_Post) #yes
wilcox.test(Summer_wide$K_Pre, filter(Summer_wide, Site=="FCCL")$K_Post) #yes
```

```{r}
Summer$Period = factor(Summer$Period, levels = c("Pre", "Post"))
ggplot(Summer) + geom_boxplot(aes(Site, FL_cm, fill = Period)) 
ggplot(Summer) + geom_boxplot(aes(Site, K, fill = Period))

Fall$Period = factor(Fall$Period, levels = c("Pre", "Post"))
ggplot(Fall) + geom_boxplot(aes(Site, FL_cm, fill = Period))
ggplot(Fall) + geom_boxplot(aes(Site, Weight_g, fill = Period))
ggplot(Fall) + geom_boxplot(aes(Site, K, fill = Period)) 
```

# Fall
```{r}
wilcox.test(Fall_wide$FL_cm_Pre, filter(Fall_wide, Site=="RV")$FL_cm_Post) #no
wilcox.test(Fall_wide$FL_cm_Pre, filter(Fall_wide, Site=="Yolo")$FL_cm_Post) #yes
wilcox.test(Fall_wide$FL_cm_Pre, filter(Fall_wide, Site=="SM")$FL_cm_Post) #yes
wilcox.test(Fall_wide$FL_cm_Pre, filter(Fall_wide, Site=="FCCL")$FL_cm_Post) #yes

wilcox.test(Fall_wide$Weight_g_Pre, filter(Fall_wide, Site=="RV")$Weight_g_Post) #yes
wilcox.test(Fall_wide$Weight_g_Pre, filter(Fall_wide, Site=="Yolo")$Weight_g_Post) #yes
wilcox.test(Fall_wide$Weight_g_Pre, filter(Fall_wide, Site=="SM")$Weight_g_Post) #yes
wilcox.test(Fall_wide$Weight_g_Pre, filter(Fall_wide, Site=="FCCL")$Weight_g_Post) #yes

wilcox.test(Fall_wide$K_Pre, filter(Fall_wide, Site=="RV")$K_Post) #yes
wilcox.test(Fall_wide$K_Pre, filter(Fall_wide, Site=="Yolo")$K_Post) #yes
wilcox.test(Fall_wide$K_Pre, filter(Fall_wide, Site=="SM")$K_Post) #yes
wilcox.test(Fall_wide$K_Pre, filter(Fall_wide, Site=="FCCL")$K_Post) #yes
```

## Models
```{r}
RV_analysis <- data %>%
  group_by(Season, Site, Period, Cage) %>%
  summarize(meanK = mean(K, na.rm = TRUE),
            meanWt = mean(Weight_g, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(!Site %in% c("SM", "Yolo", "DWSC"))

Post <- filter(RV_analysis, Period == "Post")%>%
  pivot_wider(names_from = "Period", values_from = "meanK")

# Use this to figure out means for batch pre for summer and fall
Pre <- filter(RV_analysis, Period == "Pre") %>%
  pivot_wider(names_from = "Period", values_from = c("meanK", "meanWt"))

# Now bring those values in here
RV_allfish <- data %>%
  filter(!Site %in% c("SM", "Yolo", "DWSC")) %>%
  pivot_wider(names_from = "Period",
              values_from = c("FL_cm", "Weight_g", "K")) %>%
  mutate(K_Pre = case_when(Season == "Fall"~ 0.7214667,
                         Season == "Summer" ~ 0.6626667,
                         Season == "Winter" ~ K_Pre),
         Weight_g_Pre = case_when(Season == "Fall" ~ 1.7213333,
                                Season == "Summer" ~ 0.8206667,
                                Season == "Winter" ~ Weight_g_Pre)) %>%
  mutate(deltaK = K_Post - K_Pre,
         deltaWt = Weight_g_Post - Weight_g_Pre) %>%
  filter(Site != "FCCL")

RV_sumfall <- filter(RV_allfish, Season != "Winter")
```

### Effect of Season at RV
```{r}
library(lmerTest)

# CF
m1 <- lmer(deltaK ~ Season + (1|Cage), data = RV_allfish)
summary(m1)
plot(m1)

m1b <- lmer(deltaK ~ Season + (1|Cage), data = RV_sumfall)
summary(m1b)
plot(m1b)

# Weight
m2 <- lmer(deltaWt~ Season + (1|Cage), data = RV_allfish)
summary(m2)
plot(m2)

m2b <- lmer(deltaWt ~ Season + (1|Cage), data = RV_sumfall)
summary(m2b)
plot(m2b)

library(emmeans)
m1.emm <- emmeans(m1, "Season", data=RV_allfish)
pairs(m1.emm, adjust = "sidak")
plot(m1.emm, comparisons = TRUE) + theme_bw()

m2.emm <- emmeans(m2, "Season", data=RV_allfish)
pairs(m2.emm, adjust = "sidak")
plot(m2.emm, comparisons = TRUE) + theme_bw()
```

### Effect of Site in the Fall 
```{r}
Fallfish_avg <- data %>%
  group_by(Season, Site, Period, Cage) %>%
  summarize(meanK = mean(K, na.rm = TRUE),
            meanWt = mean(Weight_g, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(Season == "Fall")

# Now bring those values in here
Fallfish <- data %>%
  filter(Season == "Fall") %>%
  pivot_wider(names_from = "Period",
              values_from = c("FL_cm", "Weight_g", "K")) %>%
  mutate(K_Pre = 0.7214667,
         Weight_g_Pre = 1.721333,
         deltaK = K_Post - K_Pre,
         deltaWt = Weight_g_Post - Weight_g_Pre) %>%
  filter(!is.na(K_Post))

```

### Effect of Site in the Fall
```{r}
library(lmerTest)

# CF ------
m3a <- lm(deltaK ~ Site, data = Fallfish)
summary(m3a)
plot(m3)

m3 <- lmer(deltaK ~ Site + (1|Cage), data = Fallfish, REML = TRUE)
summary(m3)
plot(m3)

# Not much difference in residual error by including cage effect. (0.09875 to 0.09787)

# Weight -----
m4a <- lm(deltaWt~ Site, data = Fallfish)
summary(m4a)
plot(m4a)

m4 <- lmer(deltaWt~ Site + (1|Cage), data = Fallfish)
summary(m4)
plot(m4)

# Not much difference in residual error by including cage effect. (0.471 to 0.466)

library(emmeans)
m3.emm <- emmeans(m3, "Site", data=Fallfish)
pairs(m3.emm, adjust = "sidak")
plot(m3.emm, comparisons = TRUE, type = "response") + theme_bw()

m4.emm <- emmeans(m4, "Site", data=Fallfish)
pairs(m4.emm, adjust = "sidak")
plot(m4.emm, comparisons = TRUE) + theme_bw()
```

```{r}
Fallfish <- Fallfish %>%
  mutate(res3 = resid(m3, type = "pearson"),
         res4 = resid(m4, type = "pearson"))
ggplot(Fallfish) + geom_histogram(aes(res3))
ggplot(Fallfish) + geom_boxplot(aes(Site, res3))

#hello

```

```{r}
m3
fixef(m3)
coef(summary(m3))
confint(m3, method = "Wald")
library(sjPlot)
plot_model(m3)
tab_model(m3,digits = 3)
```

```{r}
# set up to for loop through the cages
plot_cage = unique(Fallfish$Cage)
col_mat = matrix(data = c(140,81,10, 1,102,94, 118,42,131),
nrow = 3, ncol = 3, byrow = TRUE)
# create a vector that spans the observed range of temperatures for simulations
deltaK_seq = seq(min(Fallfish$deltaK), max(Fallfish$deltaK),
length.out=100)
# Use the effects package to calculate a 95% CI around the grand mean model
library(effects)
m3_eff=Effect(focal.predictors = "Site", mod=m3,
xlevels=list(deltaK=deltaK_seq))

# Use the random effect coefficients to generate random effect predictions
# across the observed range of temperatures
y_F1 = coef(m3)$Cage["B3",1] + coef(m3)$Cage["B3",2]*deltaK_seq
y_F2 = coef(m3)$Cage["B4",1] + coef(m3)$Cage["B4",2]*deltaK_seq
y_F3 = coef(m3)$Cage["B5",1] + coef(m3)$Cage["B5",2]*deltaK_seq

y_A = coef(m3)$Cage["A",1] + coef(m3)$Cage["A",2]*deltaK_seq
y_B = coef(m3)$Cage["B",1] + coef(m3)$Cage["B",2]*deltaK_seq
y_C = coef(m3)$Cage["C",1] + coef(m3)$Cage["C",2]*deltaK_seq

# plot it
par(mfrow=c(1,1), mar=c(4, 4.5, 1, 1)+0.1, oma=rep(0,4))
plot(Fallfish$deltaK ~ Fallfish$Site, type="n", 
     las=1,
ylab="deltaK", xlab = "Site")

for(i in 1:length(plot_cage)){
sub = subset(Fallfish, Fallfish$Cage == plot_cage[i])
points(sub$deltaK ~ sub$Site, pch=20,
col=rgb(col_mat[i,1],col_mat[i,2],col_mat[i,3],
maxColorValue = 255, alpha = 200))
}
lines(deltaK_seq, y_F1, type="l", lwd=1.5,
col=rgb(col_mat[1,1],col_mat[1,2],col_mat[1,3],
maxColorValue = 255, alpha = 225))

lines(deltaK_seq, y_F2, type="l", lwd=1.5,
col=rgb(col_mat[2,1],col_mat[2,2],col_mat[2,3],
maxColorValue = 255, alpha = 225))

lines(deltaK_seq, y_F3, type="l", lwd=1.5,
col=rgb(col_mat[3,1],col_mat[3,2],col_mat[3,3],
maxColorValue = 255, alpha = 225))

lines(deltaK_seq, y_A, type="l", lwd=1.5,
col=rgb(col_mat[3,1],col_mat[3,2],col_mat[3,3],
maxColorValue = 255, alpha = 225))

lines(deltaK_seq, y_B, type="l", lwd=1.5,
col=rgb(col_mat[3,1],col_mat[3,2],col_mat[3,3],
maxColorValue = 255, alpha = 225))

lines(deltaK_seq, y_C, type="l", lwd=1.5,
col=rgb(col_mat[3,1],col_mat[3,2],col_mat[3,3],
maxColorValue = 255, alpha = 225))

polygon(x = c(deltaK_seq, deltaK_seq[100], rev(deltaK_seq), deltaK_seq[1]),
y=c(m3_eff$lower, m3_eff$upper[100],
rev(m3_eff$upper), m3_eff$lower[1]),
col=gray(0.25,0.25),
border=NA)
lines(m3_eff$fit~deltaK_seq, lwd=3.5, col="black")
box(which="outer")
```

### 2023-03-06 recaps.Rmd
added smelt recapture stats

---
title: "Recpature distances"
author: "Rosie"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
load("Recaps.RData")
```

## Spatial stats on Delta Smelt releases

We have four different release types and a few questions we can ask.

1. How far did smelt from each release group travel before being recaptured?
2. How variable was the distance between release and recapture?
3. How close together were fish from a particular release when they were recaptured?
4. How variable was the distance between fish on recapture?

Sam Bashevkin has written some nifty functions for calculating in=water distance between points (fish) and a reference point (release location) or between a group of points (fish from a particular release).

https://github.com/sbashevkin/spacetools

Fist let's calcualte distance from release location to recapture location.

```{r}
#Bring in the data and check it out

recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft.xlsx", 
                    sheet = "Adult Recaptures") %>%
  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)
recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
                Type = case_when(Type == "header" ~ "Soft",
                                 TRUE ~ Type))
str(recaps)

```

This just needs a little data manipulation

```{r}

recapsf = st_as_sf(filter(recaps, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)

#Now make a data frame of the release locations
release = data.frame(Site = c("SDWSC", "SDWSC", "Rio Vista", "Rio Vista"), Type = c("Soft", "Hard", "Hard", "Hard (Trailer)"),
                     Latitude = c(38.237842, 38.275563, 38.124736, 38.139752), 
                     Longitude = c(-121.673802, -121.661374, -121.699521, -121.694706)) 
releasesf = st_as_sf(release,  coords = c("Longitude", "Latitude"), crs = 4326)

#merge recap points with release points

recaps2 = left_join(recaps, release)

#make a quick plot to make sure I did it right
ggplot()+
  geom_sf(data = WW_Delta)+
  geom_sf(data = recapsf, aes(color = Type))+
  geom_sf(data = releasesf, aes(color = Type), size = 5)+

  coord_sf(xlim = c(-121.5, -122.2), ylim = c(37.8, 38.5))

```

Now we can calculate the distance between each point and the release location. I'm going to do it one release at a time. THere is probalby a way to vectorize this and do it all at once, but I'm too lazy to figure it out.

```{r, eval=FALSE}
#one release at a time
Dwschard = filter(recaps2, Type == "Hard", Site == "SDWSC")
dwsch = filter(release, Site == "SDWSC", Type == "Hard") %>%
  select(Latitude, Longitude)
tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwsch)

#now let's do DWSC soft
Dwscsoft = filter(recaps2, Type == "Soft", Site == "SDWSC")
dwscs = filter(release, Site == "SDWSC", Type == "Soft") %>%
  select(Latitude, Longitude)
tesst2 = GGdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwscs)

#now let's do Rio Vista hard
RVhard = filter(recaps2, Type == "Hard", Site == "Rio Vista", !is.na(Latitude))
rvh = filter(release, Site == "Rio Vista", Type == "Hard") %>%
  select(Latitude, Longitude)
tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvh)

#now the trailer
RVhardt = filter(recaps2, Type == "Hard (Trailer)", Site == "Rio Vista")
rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
  select(Latitude, Longitude)
tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvht)

distances = bind_rows(tesst, tesst2, tesst3, tesst4)
```

OK, now let's bind all the distances together and join them back to the origional dataset

```{r}

recaps3 = left_join(recaps2, distances) %>%
  mutate(SiteType = paste(Type, Site))

recaps3
```

Plot to visually look at mean and variatoin.

```{r}
ggplot(recaps3, aes(x = SiteType, y = Distance))+ geom_boxplot(aes(fill = Type))+
  ylab("Distance from Release Site (m)")+
  theme_bw()
```

Map with color variation by distance, to make sure I got it right.

```{r}
recapsf = st_as_sf(filter(recaps3, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)

ggplot()+
  geom_sf(data = WW_Delta)+
  geom_sf(data = recapsf, aes(color = Distance), size =3)+
  geom_sf(data = releasesf, aes(shape = Type), size = 5)+
  scale_color_viridis_c(option = "B")+
  coord_sf(xlim = c(-121.5, -122.2), ylim = c(37.8, 38.5))

recapsum = group_by(recaps3, Site, Type, SiteType) %>%
  summarize(Nsmelt = n(), MeanDist = mean(Distance, na.rm = T), sdDist = sd(Distance, na.rm =T))

recapsum

```

NOw we move on to distance bewteen recaptured fish. I'm doing it oen release at a tiem again.

```{r, eval=FALSE}

RVhdist = Waterdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
                    Longitude_column = `Longitude`, PointID_column = fishID)

RVhdistx = Waterdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                    Longitude_column = `Longitude`, PointID_column = fishID)

SCsoft  = Waterdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
                       Longitude_column = `Longitude`, PointID_column = fishID)

SChard = Waterdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
                   Longitude_column = `Longitude`, PointID_column = fishID)

RVhdist
RVhdistx
SCsoft
SChard

```

I'm not quite sure the best way to summarize this. I'll start by just the mean of the distance matrix, but i might want do just half the matrix. I'll look into that later.

```{r}

Cluster = data.frame(Release = c("RV Hard", "RV Hard Trailer", "DWSC hard", "DWSC soft"),
                     meadist = c(mean(RVhdistx), mean(RVhdist), mean(SCsoft), mean(SChard)),
                     SD = c(sd(RVhdistx), sd(RVhdist), sd(SCsoft), sd(SChard)))
Cluster = mutate(Cluster, CV = SD/meadist)
Cluster
```

### 2023-03-06 recapdistance.R

@@ -1,0 +1,115 @@
+#recapture data
+
+library(tidyverse)
+library(readxl)
+library(sf)
+library(lubridate)
+library(spacetools)
+library(deltamapr)
+
+# install.packages("devtools")
+#devtools::install_github("sbashevkin/spacetools")
+
+recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft.xlsx", 
+                    sheet = "Adult Recaptures") %>%
+  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)
+recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
+                Type = case_when(Type == "header" ~ "Soft",
+                                 TRUE ~ Type))
+str(recaps)
+
+recapsf = st_as_sf(filter(recaps, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)
+
+release = data.frame(Site = c("SDWSC", "SDWSC", "Rio Vista", "Rio Vista"), Type = c("Soft", "Hard", "Hard", "Hard (Trailer)"),
+                     Latitude = c(38.237842, 38.275563, 38.124736, 38.139752), 
+                     Longitude = c(-121.673802, -121.661374, -121.699521, -121.694706)) 
+releasesf = st_as_sf(release,  coords = c("Longitude", "Latitude"), crs = 4326)
+
+ggplot()+
+  geom_sf(data = WW_Delta)+
+  geom_sf(data = recapsf, aes(color = Type))+
+  geom_sf(data = releasesf, aes(color = Type), size = 5)+
+  
+  coord_sf(xlim = c(-121.5, -122.2), ylim = c(37.8, 38.5))
+  
+#merge recap points with release points
+
+recaps2 = left_join(recaps, release)
+
+#Calculate distance with GGdist
+#one release at a time
+Dwschard = filter(recaps2, Type == "Hard", Site == "SDWSC")
+dwsch = filter(release, Site == "SDWSC", Type == "Hard") %>%
+  select(Latitude, Longitude)
+tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
+               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwsch)
+
+#now let's do DWSC soft
[…]

### 2023-03-17 smelt_2019_winterspring/map_enclosure_sites.Rmd
Made enclosure sites map

---
title: "map_enclosure_sites"
author: "Catarina Pien"
date: '2023-03-16'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(viridis)
library(sf)
library(dplyr)
library(ggplot2)
library(spData)
library(here)
library(readr)
library(janitor)
library(deltamapr)
library(cowplot)
library(ggspatial)

library(here)
library(readxl)
```

```{r}
latlon <- read_excel(here::here("smelt_2019_winterspring", "data_raw", "cage_locations_winterspring.xls"))

stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326)
data("us_states", package = "spData")
California = dplyr::filter(us_states, NAME == "California")
stations_sf_4269 <- st_transform(stations_sf, crs = st_crs(California))
WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
```

```{r}
(smelt_map <- ggplot() +
    geom_sf(data = WW_Watershed_4269, fill = "gray80", colour = "gray80", alpha = 0.8, inherit.aes = FALSE) +
    geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size = 4, color = "black")+
   geom_sf_label(data = stations_sf_4269, aes(label = factor(Location)), inherit.aes = FALSE, size = 4, color = "black",
                 nudge_x = c(-0.08, -0.05),
                 nudge_y = c(0.01, -0.03))+
    annotate(geom = "text", x = -121.75, y = 38.10, size = 3.2, label = "Sacramento River", fontface = "italic",angle = 36) +
    annotate(geom = "text", x = -121.62, y = 38.09, size = 3.2, label = "San Joaquin River", fontface = "italic", angle = 10) +
    annotate(geom = "text", x = -121.96, y = 38.07, size = 3.2, label = "Suisun Bay", fontface = "italic") +
    annotate(geom = "text", x = -121.68, y = 38.26, size =3.2 , label = "Liberty Island", fontface = "italic") +
    scale_x_continuous(limits = c(-122.2, -121.45)) +
  scale_y_continuous(limits = c(37.95, 38.4))+
    annotation_north_arrow(location = "tr", which_north = "true",
                           pad_x = unit(.005, "in"), pad_y = unit(0.15, "in"),
                           style = north_arrow_fancy_orienteering) +
    annotation_scale(location = "bl", bar_cols = c("darkgray", "white", "darkgray", "white"), text_cex = 1.1)+
  theme_bw() +
    theme(axis.title = element_blank(),
        axis.text = element_text(size = 13) ,
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 0.5, vjust = 0.5)))
```

```{r}
insetbbox = st_bbox(c(xmin = -122.2, xmax = -121.45, ymax = 37.95, ymin = 38.4), crs = st_crs(4326))
box_sf <- st_as_sfc(insetbbox)

(inset <- ggplot() +
    geom_sf(data = California, fill = "white") +
    geom_sf(data = WW_Delta, colour = "steelblue4", size = 0.3) +
    geom_sf(data = box_sf, fill = NA, color = "red", size = 0.5) +

    theme_bw() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()))
```

```{r}
(gg_inset_map = ggdraw() +
   draw_plot(smelt_map) +
   draw_plot(inset, x = 0.1, y = 0.63, width = 0.26, height = 0.31))
```

```{r}
tiff(filename = here::here("smelt_2019_winterspring",  "figures", "map_sites.tiff"), width = 8, height = 7, units = "in", pointsize = 12, family = "sans", res = 300, compress = "lzw")
gg_inset_map
dev.off()
```

### 2023-03-17 histopathology.Rmd

---
title: "Smelt Cage Histopathology"
author: "Rosie"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(readxl)
library(car)
library(emmeans)
library(effects)
library(ordinal)
library(sure)

```

## Stats

```{r cars}
#start with liver lesions
livers = read_excel("histopathology data caging study_to share with dwr.xlsx")

#
ggplot(livers, aes(x = season, y = `liver lesion score`, fill = treatment))+
  geom_boxplot()

#quick linear model
goodlivers = filter(livers, !treatment %in% c("Suisun Marsh", "Yolo Bypass", "DWSC")) %>%
  mutate(treatment = case_when(treatment == "RV" ~ "Rio Vista",
                               TRUE ~ treatment),
         lls = log(`liver lesion score`+1))

m1 = lm(`liver lesion score`~ treatment*season, data = goodlivers)
summary(m1)

```

Interaction not significant, let's drop it.

```{r}
m2 = lm(`liver lesion score`~ treatment + season, data = goodlivers)
Anova(m2)

plot(m2)
hist(residuals(m2))

```
The QQ plot is a little wonky. Let's try a log transformation

```{r}
m2.1 = lm(lls~ treatment + season, data = goodlivers)
Anova(m2.1)
plot(m2.1)

```
Better, still not great

```{r}

#look at partial effects plot
plot(allEffects(m2.1))

#post hocs
#look just at the effects of treatment
treat = emmeans(m2.1, ~treatment)
treat
plot(treat)

#Now the effects of season
seas = emmeans(m2, pairwise ~season)
seas
plot(seas)

```

We could also compare each deployment individually if we wanted to.

```{r}

goodlivers = mutate(livers, deploy = paste(treatment, season), lls = log(`liver lesion score`+1))

m3 = lm(`liver lesion score`~deploy, data = goodlivers)
plot(m3)
#yuck
m3 = lm(lls~deploy, data = goodlivers)
#better. Maybe I should log transform all the liver models

emmeans(m3, pairwise ~ deploy)
plot(emmeans(m3, pairwise ~ deploy), comparison = T)

```

## Now let's look at glycogen

```{r}
glycogen = read_excel("histopathology data caging study_to share with dwr.xlsx", sheet = "liver GD stats") %>%
  rename(glyDep = `liver glycogen depletion`)

#just Rio Vista and FCCL
gly = filter(glycogen, !treatment %in% c("Suisun Marsh", "Yolo Bypass", "DWSC")) %>%
  mutate(treatment = case_when(treatment == "RV" ~ "Rio Vista",
                               TRUE ~ treatment))

#a few quick exploritory plots
ggplot(glycogen, aes(x = treatment, y = glyDep, fill = season)) +
  geom_boxplot()

ggplot(gly, aes(x = treatment, y = glyDep, fill = season)) +
  geom_boxplot()
```

Now the statistics

```{r}
g1 = lm(glyDep~ season + treatment, data = gly)
plot(g1)
```

Not too bad.

```{r}
summary(g1)
Anova(g1)
plot(allEffects(g1))
emmeans(g1, pairwise ~ season)
plot(emmeans(g1, pairwise ~ season), comparison = T)
```

So, winter is definitely lower than fall and summer, FCCL definitely lower than Rio Vista

## Gill lesions

```{r}

gills = read_excel("histopathology data caging study_to share with dwr.xlsx", sheet = "gill lesions stats") %>%
  rename(gill = `gill lesion score`)

goodgills = filter(gills, !treatment %in% c("Suisun Marsh", "Yolo Bypass", "DWSC")) %>%
  mutate(treatment = case_when(treatment == "RV" ~ "Rio Vista",
                               TRUE ~ treatment))

#exploritory plots
ggplot(gills, aes(x = treatment, y = gill, fill = season)) +
  geom_boxplot()

ggplot(goodgills, aes(x = treatment, y = gill, fill = season)) +
  geom_boxplot()
```

Now the statistics

```{r}
gl1 = lm(gill~ season + treatment, data = goodgills)
plot(gl1)
```
Yuck. need some sort of transformation on that

```{r}

#try a log transformation
goodgills = mutate(goodgills, gls = log(gill+1))
gl1 = lm(gls~ season + treatment, data = goodgills)
plot(gl1)
#still yuck

#square root transformation

goodgills = mutate(goodgills, gls = sqrt(gill))
gl1 = lm(gls~ season + treatment, data = goodgills)
plot(gl1)
#still yuck.

```

Maybe an ordinal regression would be more appropriate since it's integers between zero and 4?

```{r}

library(ordinal)

goodgills = mutate(goodgills, Fgill = factor(gill, ordered = T))
c1 = clm(Fgill ~ treatment + season, data = goodgills)
summary(c1)

convergence(c1)
library(sure)
autoplot.clm(c1)
#beautiful!

#so, no real difference in gill leasions between treatments or seasons

```

### 2023-03-17 recaps.Rmd

@@
 library(deltamapr)
-load("Recaps.RData")
+#load("Recaps.RData")
 ```
@@
   rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)
+
 recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
                 Type = case_when(Type == "header" ~ "Soft",
-                                 TRUE ~ Type))
+                                 TRUE ~ Type)) %>%
+  rename(Adclip = `Ad clip`, Mark = `VIE Color/Position`) %>%
+  select(-Type, -Site)
 str(recaps)
@@
 
-recapsf = st_as_sf(filter(recaps, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)
-
 #Now make a data frame of the release locations
-release = data.frame(Site = c("SDWSC", "SDWSC", "Rio Vista", "Rio Vista"), Type = c("Soft", "Hard", "Hard", "Hard (Trailer)"),
-                     Latitude = c(38.237842, 38.275563, 38.124736, 38.139752), 
-                     Longitude = c(-121.673802, -121.661374, -121.699521, -121.694706)) 
-releasesf = st_as_sf(release,  coords = c("Longitude", "Latitude"), crs = 4326)
+release = read_excel("releases.xlsx") %>%
+  rename(LatitudeR = Latitude, LongitudeR = Longitude)
+releasesf = st_as_sf(filter(release, !is.na(LatitudeR)),  coords = c("LongitudeR", "LatitudeR"), crs = 4326)
 
@@
 
-recaps2 = left_join(recaps, release)
+recaps2 = left_join(recaps, release) %>%
+  mutate(DaysSinceRelease = Date - ReleaseDate)
+recapsf = st_as_sf(filter(recaps2, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)
 
@@
 dwsch = filter(release, Site == "SDWSC", Type == "Hard") %>%
-  select(Latitude, Longitude)
+  select(LatitudeR, LongitudeR) %>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR)
 tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
@@
 dwscs = filter(release, Site == "SDWSC", Type == "Soft") %>%
-  select(Latitude, Longitude)
+  select(LatitudeR, LongitudeR)%>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR)
 tesst2 = GGdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
@@
 rvh = filter(release, Site == "Rio Vista", Type == "Hard") %>%
-  select(Latitude, Longitude)
+  select(LatitudeR, LongitudeR)%>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
+  distinct()
 tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
@@
 rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
-  select(Latitude, Longitude)
+  select(LatitudeR, LongitudeR)%>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR)
 tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
@@
 
-Plot to visually look at mean and variatoin.
+Plot to visually look at mean and variation.
 
@@
 
-Cluster = data.frame(Release = c("RV Hard", "RV Hard Trailer", "DWSC hard", "DWSC soft"),
-                     meadist = c(mean(RVhdistx), mean(RVhdist), mean(SCsoft), mean(SChard)),
+Cluster = data.frame(Release = c("RV Hard", "RV Hard Trailer", "DWSC soft", "DWSC hard"),
+                     meadist = c(mean(RVhdistx[lower.tri(RVhdistx)]), 
+                                 mean(RVhdist[lower.tri(RVhdist)]), 
+                                 mean(SCsoft[lower.tri(SCsoft)]), 
+                                 mean(SChard[lower.tri(SChard)])),
                      SD = c(sd(RVhdistx), sd(RVhdist), sd(SCsoft), sd(SChard)))
+
 Cluster = mutate(Cluster, CV = SD/meadist)
@@
 ```
+
+OK, now how to I put these all together to graph them?
+
+```{r}
+
+RVhdistx[lower.tri(RVhdistx, diag = T)] = NA
+RVhdist[lower.tri(RVhdist, diag = T)] = NA
+SCsoft[lower.tri(SCsoft, diag = T)] = NA
+SChard[lower.tri(SChard, diag = T)] = NA
+RVdtx = as.data.frame(RVhdistx) %>%
+  mutate(Fish1 = row.names(RVhdistx)) %>%
+  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
+  filter(!is.na(Distance)) %>%
+  mutate(Release = "Rio Vista Hard")
+
+RVdt = as.data.frame(RVhdist) %>%
+  mutate(Fish1 = row.names(RVhdist)) %>%
+  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
+  filter(!is.na(Distance)) %>%
+  mutate(Release = "Trailer")
+
+SCs = as.data.frame(SCsoft) %>%
+  mutate(Fish1 = row.names(SCsoft)) %>%
+  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
+  filter(!is.na(Distance)) %>%
+  mutate(Release = "DWSC Soft")
+
+SCh = as.data.frame(SChard) %>%
+  mutate(Fish1 = row.names(SChard)) %>%
+  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
+  filter(!is.na(Distance)) %>%
+  mutate(Release = "DWSC Hard")
+
+nndist = bind_rows(RVdtx, RVdt, SCs, SCh)
+
+ggplot(nndist, aes(x = Release, y = Distance, fill = Release)) + geom_boxplot()+
+  ylab("Distance Between Recaptures")
+
+```
+
+Now let's bring in the time aspect
+
+```{r}
+
+recapstime = read_excel("RecapturesSummary_1.xlsx", sheet = "REcapture Distances")
+
+```

### 2023-03-17 smelt_2019_allseasons/Zoop 2019.Rmd

@@
 library(Polychrome)
-library(here)
+library(zooper)
 ```
@@
 
-#zoop <- read_csv("smelt_2019_allseasons/data_raw/ZoopData_SummerFall_2019.csv")
-zoop <- read_csv("data_raw/ZoopData_SummerFall_2019.csv")
+zoop <- read_csv("smelt_2019_allseasons/data_raw/ZoopData_SummerFall_2019.csv")
+#zoop <- read_csv("data_raw/ZoopData_SummerFall_2019.csv")
 
@@
 #bring in tow data
-#aug <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
-#oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
+aug <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
+oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
 aug <- read_csv("data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
@@
 caught <- all[!(all$ind_m3==0),]
+biomass = read_csv("zooptaxa.csv")
+caught = left_join(caught, biomass) %>%
+  mutate(bio_m3 = Mass*ind_m3)
 
@@
 
+#First to CPUE
 ggplot() +
-  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
+  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=ind_m3, fill=ID), colour="black", width = .5) +
   facet_wrap(~Location, ncol = 1) +
@@
   labs(y = "Relative Abundance of all Zoop in Sample")+
+  theme(legend.position="right")+
+      theme(axis.text = element_text(size = 12),
+      axis.title = element_text(size = 12),
+      legend.text = element_text(size = 8),
+      legend.title = element_text(size = 10),
+      axis.text.x = element_text(angle = 90))
+
+#now try BPUE
+ggplot() +
+  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
+  facet_wrap(~Location, ncol = 1) +
+  theme_bw() + 
+  scale_fill_manual(values=pal36)+
+  labs(x = "Date") +
+  labs(y = "Relative Biomass of all Zoop in Sample")+
   theme(legend.position="right")+
@@
 
-#winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
+winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
 winter <- read_csv("data_clean/zoop_abundance.csv")
@@
 winter <- winter[!(winter$Method=="Throw"),]
-
+#change ostracod taxa
+winter[winter$Taxon %in% c("Ostracods"),]$Taxa <- "Ostracod"
 #merge with catch df
 #condense to columns of interest
-winter2 <- winter[c(1,2,13,27,30,22,23)]
-caught2 <- caught[c(1,2,7,10,20,29,30)]
+winter2 <- winter %>%
+  rename(ID = Taxon) %>%
+  select(Location, Date, Taxa, samplecount, ind_m3, bio_m3, Day, Month, MD) %>%
+  group_by(Location, Date, Taxa, Day, Month, MD) %>%
+  summarize(ind_m3 = sum(ind_m3), bio_m3 = sum(bio_m3))
+
+caught2 <- caught %>%
+  select(Location, Date, Taxa, samplecount, ind_m3, bio_m3, Day, Month, MD) %>%
+  group_by(Location, Date, Taxa, Day, Month, MD) %>%
+  summarize(ind_m3 = sum(ind_m3), bio_m3 = sum(bio_m3))
 
 #rename column
-winter2 <- winter2 %>% rename(ID = "Taxon")
-
-#change ostracod taxa
-winter2[winter2$ID %in% c("Ostracods"),]$Taxa <- "Ostracod"
+#winter2 <- winter2 %>% rename(ID = "Taxon")
 
@@
   group_by(Season, Location, Taxa) %>% 
-  summarize("sum.count"= sum(samplecount))
+  summarize(sum.count= sum(ind_m3))
 
@@
 library(vegan)
-source("../PlotNMDS.R")
+source("PlotNMDS.R")
 
@@
 RVa
+#
+
+RVb = adonis2(RVzoopmat2~Season, data = RVzoops)
+RVb
+
+#Britt and Bruce wanted biomass instead of abundance
+
+zoopsBM = mutate(caught.19, SampleID = paste(Location, Date)) %>%
+  filter(Taxa != "Microzoo") %>%
+  pivot_wider(id_cols = c(SampleID, Location, Date, MD, Season), names_from = Taxa, values_from = bio_m3, values_fn = sum, values_fill = 0) %>%
+  mutate(datatype = "Zoops")
+
+#first let's look at Rio Vista across seasons
+RVzoopsBM = filter(zoopsBM, Location == "RV")
+
+#raw abundance matrix
+RVzoopmatBM = as.matrix(RVzoopsBM[,6:11])
+
+#relative abundance matrix
+RVzoopmat2BM = RVzoopmatBM/rowSums(RVzoopmatBM)
+
+RVa2 = adonis2(RVzoopmatBM~Season, data = RVzoopsBM)
+RVa2
 #
@@
 ```{r}
-#diet2 <- read_csv("smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
+diet2 <- read_csv("smelt_2019_allseasons/data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
 diet2 <- read_csv("data_raw/DSM Cage Diets 2019-2020.csv") #new data, not edited at all
@@
 ```
+
+Can I do a permanova that takes date and location into accoutn?
+
+```{r}
+
+zda = adonis2(zoopdietmat2 ~ datatype*Season + Location, strata = zoopdiet$Location, data = zoopdiet)
+zda
+
+zda1 = adonis2(zoopdietmat2 ~ datatype*Season + Location,data = zoopdiet)
+zda1
+
+with(zoopdiet, adonis2(zoopdietmat2 ~ datatype+ Season , strata = Location, data = zoopdiet, permutations = 199))
+
+with(zoopdiet, adonis2(zoopdietmat2 ~ datatype+ Season +Location, strata = Season, data = zoopdiet, permutations = 199))
+
+```

### 2023-03-20 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
Added some summary stats and fixed FL label

@@
             sddeltaWt = sd(deltaWt),
-            sedeltaWt = sddeltaWt/n,
+            sedeltaWt = sddeltaWt/sqrt(n),
             meanchangeWt = mean(changeWt*100),
             sdchangeWt = sd(changeWt),
-            sechangeWt = sdchangeWt/n,
+            sechangeWt = sdchangeWt/sqrt(n),
+            meandeltaFL = mean(deltaFL),
+            sddeltaFL = sd(deltaFL),
+            sedeltaFL = sddeltaFL/sqrt(n),
             meanchangeFL =mean(changeFL*100),
-            sechangeFL = sd(changeFL)/n,
+            sechangeFL = sd(changeFL)/sqrt(n),
             meanCFPre = mean(Pre_CF),
             meanCFPost = mean(Post_CF),
-            seCF = sd(Pre_CF)/n,
+            seCF = sd(Pre_CF)/sqrt(n),
             meandeltaCF = mean(Delta_CF),
-            sedeltaCF = sd(Delta_CF)/n)
+            sedeltaCF = sd(Delta_CF)/sqrt(n))
 ```
@@
 ```{r}
-CagePrePost <- gather(Cageonly2, PrePost,Length1,Pre_FL_cm, Post_FL_cm)
+CageClean <- Cageonly2 %>% select(Site, Enclosure, Pre_FL_cm, Post_FL_cm, changeFL) %>%
+  filter(!is.na(Pre_FL_cm)) %>%
+  filter(!is.na(Post_FL_cm)) %>%
+  filter(changeFL>-0.05)
+
+CagePrePost <- gather(CageClean, PrePost,FL,Pre_FL_cm, Post_FL_cm)
 CagePrePost$Site <- factor(CagePrePost$Site, levels = c("RV", "DWSC"))
+CagePrePost$PrePost <- factor(CagePrePost$PrePost,
+                              levels = c('Pre_FL_cm','Post_FL_cm'),ordered = TRUE)
 
 MeanLengthplot<- ggplot(data=CagePrePost) +
-  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=Length1,  fill = PrePost)) +
+  geom_boxplot(outlier.size=-1,aes(x=Enclosure, y=FL,  fill = PrePost)) +
   facet_wrap(~Site) +
@@
   scale_fill_manual(values=c("#E7298A", "#66A61E"), name = "", labels = c("Pre-Deployment", "Post-Deployment")) +
-  labs(y = "Length (cm)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
-  theme_minimal() + theme(axis.title.x = element_blank()) +
+  labs(y = "Fork Length (cm)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
+    scale_y_continuous(breaks = seq(4,8,0.5)) + 
+  theme_bw() + theme(axis.title.x = element_blank()) +
   annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
@@
    labs(y = "Weight (g)", x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
-  theme_minimal() + theme(strip.text.x = element_blank()) +
+  scale_y_continuous(breaks = seq(0,3,0.5)) + 
+  theme_bw() + theme(strip.text.x = element_blank()) +
   annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
@@
    labs(y = expression(K~(g~cm^-3)), x = "Enclosure Type") + scale_x_discrete(labels=c("control" = "FCCL")) +
-  theme_minimal() + theme(strip.text.x = element_blank()) +
+  theme_bw() + theme(strip.text.x = element_blank()) +
   annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
@@
 ```{r}
-tiff(filename=file.path("smelt_2019_winterspring/figures/WeightLengthKPlot.tiff"), units="in",type="cairo", bg="white", height=7, 
+tiff(filename=file.path("smelt_2019_winterspring/figures/WeightLengthKPlot.tiff"), units="in",type="cairo", bg="white", height=7.5, 
      width=7, res=300, pointsize=12,compression="lzw")

### 2023-03-22 smelt_2019_winterspring/tow_vs_throw_zoop_samples.R
Updated zooplankton analysis to include ONLY tow data. Also including updated data.

@@ -1,0 +1,38 @@
+zoop <- read_csv("smelt_2019_winterspring/edi/data_objects/2019_smeltstudy_zoop_data.csv") %>%
+  filter(TaxonomicGrouping!="Microzoo")
+samples <- zoop %>%
+  group_by(Location, Method, Date) %>%
+  summarize(n = n()) %>%
+  distinct()
+
+taxa<-abundance %>% 
+  group_by(Location, Method, Date, Taxa) %>% 
+  summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))
+
+taxa.week.2 <- taxa[taxa$Taxa != "Microzoo",]
+
+taxa.week.2$SiteName = factor(taxa.week.2$Location, levels=c('RV','DWSC'))
+
+taxa.week.2$Taxa <- as.character(taxa.week.2$Taxa)
+taxa.week.2$Taxa[taxa.week.2$Taxa=='Macrozoo'] <- 'Other'
+
+for.mod<-taxa.week.2 %>% 
+  group_by(Date, Location, Taxa, Method) %>% 
+  summarize("bio.all"=sum(bio))
+
+
+ggplot(data = for.mod, aes(x=factor(Date), y=bio.all, fill = Taxa, colour = Method)) +
+  geom_bar(stat = "identity", width = 0.7) +
+  facet_wrap(~Location, scales = "free_x")+
+  theme_bw() + 
+  scale_colour_manual(values = c("black", "yellow")) + 
+ # scale_fill_manual(legend_title, values=cbPalette)+
+ # labs(x = "Week") +
+ # labs(y = "Biomass (ugC/m3)")+
+  theme(legend.position="right")+
+  theme(axis.text = element_text(size = 10, angle = 90),
+        axis.title = element_text(size =17),
+        legend.text = element_text(size = 16),
+        legend.title = element_text(size = 17),
+        strip.text.x = element_text(size = 17),
+        text=element_text(family = "Times"))

### 2023-03-22 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
Updated weight length K plot to include a little more on the y axis

@@
     PoL_sd = sd(Post_FL_cm),
+    PreL_Min = min(Pre_FL_cm), 
+    PreL_Max = max(Pre_FL_cm),
     PoL_median = median(Post_FL_cm), 
@@
 
+# Calculate sample sizes for alive and dead
+surv_RV <- Cagetype_s %>%
+  filter(Site == "RV") %>%
+  group_by(Site, Cage, Mesh)%>%
+  summarize(
+    Alive = n(),
+    Dead = 64-n()
+  )
+
 Cagetype_survival_RV <- left_join(Cage_survival_RV, surv_RV, by = "Cage")
@@
 ```{r}
-surv_RV %>%
+survival_RV %>%
   ungroup() %>%
-  filter(Cage != "FCCL1") %>%
+  group_by(Mesh) %>%
   summarize(meanRate = mean(rate),
             n = n(),
-            seRate = sd(rate)/n)
+            seRate = sd(rate)/sqrt(n))
 ```
@@
 
+surv_DWSC <- Cagetype_s %>%
+  filter(Site == "DWSC") %>%
+  group_by(Site, Cage, Mesh)%>%
+  summarize(
+    Alive = n(),
+    Dead = 60-n()
+  )
+
 Cagetype_survival_DWSC <- left_join(Cage_survival_DWSC, surv_DWSC, by = "Cage")
@@
   mutate(rate = Survived/n*100)
+
+```
+
+Survival rate
+```{r}
+survival_DWSC %>%
+  ungroup() %>%
+  group_by(Mesh) %>%
+  summarize(meanRate = mean(rate),
+            n = n(),
+            seRate = sd(rate)/sqrt(n))
 ```

### 2023-04-04 recapdistance.R
Smelt recapture analyses

@@ -10,12 +10,15 @@ library(deltamapr)
 # install.packages("devtools")
 #devtools::install_github("sbashevkin/spacetools")
 
-recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft.xlsx", 
-                    sheet = "Adult Recaptures") %>%
+recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft (2).xlsx", 
+                    sheet = "Full DSM Data") %>%
   rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)
 recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
                 Type = case_when(Type == "header" ~ "Soft",
-                                 TRUE ~ Type))
+                                 is.na(Type) ~ "Wild",
+                                 TRUE ~ Type),
+                Site = case_when(is.na(Site) ~ "Wild",
+                                 TRUE ~ Site))
 str(recaps)
 
 recapsf = st_as_sf(filter(recaps, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)

### 2023-04-04 smelt_2019_winterspring/Diet.Rmd

@@
 diet$Location <- ordered(diet$Location, levels = c("RVR", "DWSC"))
-diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
-diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
-diet<-diet[diet$Cage.ID != "FCCL Control",]
+diet<-diet[diet$Cage != "FCCL Control Tank 1",]
+diet<-diet[diet$Cage != "FCCL Control Tank 2",]
+diet<-diet[diet$Cage != "FCCL Control",]
+diet <- diet %>% rename(Cage.ID = Cage) # Cat: I added this because there was no Cage.ID before
 
@@
 #bind fish measurements with stomach contents (note- some lost due to missing letters in ID's-update for final)
-total <- merge(diet_type, Cage, by=c("Tag"))
+total <- merge(diet_type, Cage, by=c("Tag")) %>%
+  filter(!is.na(Delta_CF))
 
 #create instantaneous ration column
-total$IR <- (total$Contents.Weight/total$Post_Weight_g)*100
+total$IR <- (total$ContentsWeight/total$Post_Weight_g)*100
 
@@
 taxa_tag<- diet_type %>% 
-  group_by(Location, Mesh, Cage.ID, Tag, Taxa, LH.Stage) %>% 
+  group_by(Location, Mesh, Cage.ID, Tag, TaxonomicGrouping, LHStage) %>% 
   summarize("count.sum"= sum(Count))
@@
 #add rows for all taxa for all fish
-full.prop<-stomach_abundance %>% complete(Tag, Taxa) %>%
+full.prop<-stomach_abundance %>% complete(Tag, TaxonomicGrouping) %>%
   as.data.frame()
@@
 #select columns I want for count
-full.count<-subset(full.count, select=c("Location", "Mesh", "Tag", "Taxa", "LH.Stage", "count.sum"))
+full.count<-subset(full.count, select=c("Location", "Mesh", "Tag", "TaxonomicGrouping", "LHStage", "count.sum"))
 
 #select columns I want for proportion
-full.prop.3<-subset(full.prop.2, select=c("Tag", "Taxa", "proportion", "Location", "Mesh"))
+full.prop.3<-subset(full.prop.2, select=c("Tag", "TaxonomicGrouping", "proportion", "Location", "Mesh"))
 #replace proportion Nas with zeros
@@
 diet.prop.mean<- diet.prop %>% 
-  group_by(Taxa, Location, Mesh) %>% 
+  group_by(TaxonomicGrouping, Location, Mesh) %>% 
   summarize("prop.mean"= mean(proportion))
@@
 taxa.perct<- diet_type %>% 
-  group_by(Location, Taxa, Prey.Taxa) %>% 
+  group_by(Location, TaxonomicGrouping, PreyTaxa) %>% 
   summarize("count.sum"= sum(Count, na.rm=TRUE))
@@
 
-taxa.perct$percent <- (taxa.perct$count.sum/taxa.perct$Total)*100
+taxa.perct$percent <- round((taxa.perct$count.sum/taxa.perct$Total)*100,2)
+
 ```
+
+Write table for supplementary. 
+```{r}
+taxa_percent_table <- taxa.perct %>%
+  dplyr::select(Site = Location,
+         `Taxonomic Grouping` = TaxonomicGrouping,
+         Taxa = PreyTaxa,
+         `Sum Count` = count.sum,
+         `Percent Count` = percent) %>%
+  arrange(Site, desc(`Percent Count`))
+
+write_csv(taxa_percent_table, "smelt_2019_winterspring/data_clean/diet_supp_table.csv")
+```

### 2023-04-04 smelt_2019_winterspring/ZoopPlotting_Tow.Rmd

--- 2022-11-16 smelt_2019_winterspring/ZoopPlotting.Rmd
@@
 tow$radius<-tow$RingSize*2
-abundance <- rbind(tow, throw)
+#abundance <- rbind(tow, throw)
+abundance <- tow
 abundance$Date<-ymd(abundance$Date)
@@
 abundance$ind_m3<-as.numeric(abundance$ind_m3)
+abundance$Location <- factor(abundance$Location, levels = c("RV", "DWSC"))
 
 #write file for use in analysis for another project
-write_excel_csv(all, "smelt_2019_allseasons/data_clean/zoop_abundance.csv")
+write_excel_csv(abundance, "smelt_2019_allseasons/data_clean/zoop_abundance.csv")
 
@@
 dw$DWSC.Bio <- dw$bio
-dw$DWSC.Perc <- (dw$DWSC.Bio/12832.26)*100
+dw$DWSC.Perc <- (dw$DWSC.Bio/sum$sum[sum$Location=="DWSC"])*100
 dw <- dw[c(2,3,6,7)]
@@
 rv$RV.Bio <- rv$bio
-rv$RV.Perc <- (rv$RV.Bio/32782.81)*100
+rv$RV.Perc <- (rv$RV.Bio/sum$sum[sum$Location == "RV"])*100
 rv <- rv[c(2,3,6,7)]
@@
 all[is.na(all)] <- 0
+all_write <- all %>%
+  arrange(Taxon) %>%
+  mutate(across(c(RV.Bio: DWSC.Perc), round, 1))
 
-write_excel_csv(all, "smelt_2019_winterspring/data_clean/species.table.csv")
+write_excel_csv(all_write, "smelt_2019_winterspring/data_clean/species.table_tow.csv")
 ```
@@
 
-tiff(filename="smelt_2019_winterspring/figures/zoopfig.tiff", 
+tiff(filename="smelt_2019_winterspring/figures/zoopfig_towonly.tiff", 
     units="in", 
@@
 
-shapiro.test(for.mod$bio.all) #not significant
+shapiro.test(for.mod$bio.all) # significant
 
-model<-lm(bio.all~Location*Week2, data=for.mod)
+model<-lm(bio.all~Location * Week2, data=for.mod)
 anova(model)
@@
 
-leveneobject<- lm(abs(resid(model))~Location*Week2, data=for.mod)
+leveneobject<- lm(abs(resid(model))~Location + Week2, data=for.mod)
 anova(leveneobject) #insignificant
@@
 marginal = emmeans(model, 
-                   ~ Location*Week2)
+                   ~ Location* Week2)
 
@@
     adjust  = "tukey") #DWSC and RV different
+
+emmip(model, Week2 ~ Location)
+emtrends(model, pairwise ~ Location, var = "Week2")
+emm <- emmeans(model, ~Location, type = "response")
+emm
+pairs(emm, adjust = "Week2")
 ```
+
+```{r}
+taxa %>%
+  dplyr::select(Date, Location, Week) %>%
+  distinct() %>%
+  group_by(Location, Week) %>%
+  summarize(n = n())
+```

### 2023-04-05 smelt_2019_allseasons/analyze_growth.Rmd
Reran length and weight models for hybrid manuscript. Saved some figures and tables from the results. Some of the data might have been re-saved accidentally.

@@
   filter(!(Site == "RV" & is.na(Cage))) %>%
-mutate(Season = factor(Season))
+mutate(Season = factor(Season)) %>%
+  mutate(CageRep = paste0(Season, "_", Site, "_", Cage))
 
@@
 ```{r}
-Summer <- data %>% filter(Season == "Summer")
+Summer <- data %>% filter(Season == "Summer") %>%
+  mutate(Period = factor(Period, levels = c("Pre", "Post")))
 Summer_wide <- Summer %>%
@@
 
-Fall <- data %>% filter(Season == "Fall")
+Fall <- data %>% filter(Season == "Fall")%>%
+  mutate(Period = factor(Period, levels = c("Pre", "Post")))
 
@@
 hist(filter(Summer, Site=="RV")$Weight_g_Post)
-
-hist(filter(data, Site == "RV")$FL_cm)
-hist(filter(data, Site == "RV")$Weight_g)
-hist(filter(data, Site == "RV")$K)
 
@@
 
+## Plots
+```{r}
+Summer$Period = factor(Summer$Period, levels = c("Pre", "Post"))
+ggplot(Summer) + geom_boxplot(aes(Site, FL_cm, fill = Period)) 
+ggplot(Summer) + geom_boxplot(aes(Site, Weight_g, fill = Period)) 
+ggplot(Summer) + geom_boxplot(aes(Site, K, fill = Period))
+
+Fall$Period = factor(Fall$Period, levels = c("Pre", "Post"))
+ggplot(Fall) + geom_boxplot(aes(Site, FL_cm, fill = Period))
+ggplot(Fall) + geom_boxplot(aes(Site, Weight_g, fill = Period))
+ggplot(Fall) + geom_boxplot(aes(Site, K, fill = Period)) 
+```
+
+# T-tests
+
 ## Summer
+Pre-post model (t-test)
 ```{r}
-t_sRV <- t.test(Summer$FL_cm_Pre, filter(Summer, Site=="RV")$FL_cm_Post) #no
-t_sFC <- t.test(Summer$FL_cm_Pre, filter(Summer, Site=="FCCL")$FL_cm_Post) #yes
+data_sFCCL <- Summer %>%
+  filter(Site == "FCCL")
+data_sRV <- Summer %>%
+  filter(Site == "RV" | (Site == "FCCL" & Period == "Pre"))
 
-t.test(Summer$Weight_g_Pre, filter(Summer, Site=="RV")$Weight_g_Post) #on the border
-t.test(Summer$Weight_g_Pre, filter(Summer, Site=="FCCL")$Weight_g_Post) #on the border
+# t-tests ---------------------------------------
+t.test(filter(data_sFCCL,Period=="Pre")$Weight_g, filter(data_sFCCL,Period=="Post")$Weight_g)
+t.test(filter(data_sFCCL,Period=="Pre")$FL_cm, filter(data_sFCCL,Period=="Post")$FL_cm) 
+t.test(filter(data_sFCCL,Period=="Pre")$K, filter(data_sFCCL,Period=="Post")$K)
 
-t.test(Summer$K_Pre, filter(Summer, Site=="RV")$K_Post) #yes
-t.test(Summer$K_Pre, filter(Summer, Site=="FCCL")$K_Post) #yes
+t.test(filter(data_sRV,Period=="Pre")$Weight_g, filter(data_sRV,Period=="Post")$Weight_g)
+t.test(filter(data_sRV,Period=="Pre")$FL_cm, filter(data_sRV,Period=="Post")$FL_cm) 
+t.test(filter(data_sRV,Period=="Pre")$K, filter(data_sRV,Period=="Post")$K)
+
+# Linear models: resids look good
+# FL -------------------------------------------------
+(m_fccl_summer1 <- lm(FL_cm~Period, data = data_sFCCL))
+summary(m_fccl_summer1)
+anova(m_fccl_summer)
+par(mfrow = c(2,3))
+plot(m_fccl_summer1)
+hist(resid(m_fccl_summer1))
+boxplot(FL_cm~Period, data_sFCCL)
+
+(m_rv_summer1 <- lm(FL_cm~Period, data = data_sRV))
+par(mfrow = c(2,3))
+plot(m_rv_summer1)
+hist(resid(m_rv_summer1))
+boxplot(FL_cm~Period, data_sRV)
+
+# Weight ----------------------------------------------
+(m_fccl_summer2 <- lm(Weight_g~Period, data = data_sFCCL))
+summary(m_fccl_summer2)
+anova(m_fccl_summer2)
+par(mfrow = c(2,3))
+plot(m_fccl_summer2)
+hist(resid(m_fccl_summer2))
+boxplot(Weight_g~Period, data_sFCCL)
+
+(m_rv_summer2 <- lm(Weight_g~Period, data = data_sRV))
+summary(m_rv_summer2)
+par(mfrow = c(2,3))
+plot(m_rv_summer2)
+hist(resid(m_rv_summer2))
+boxplot(Weight_g~Period, data_sRV)
+
+# K ------------------------------------------------
+(m_fccl_summerK <- lm(K~Period, data = data_sFCCL))
+summary(m_fccl_summerK)
+anova(m_fccl_summerK)
+par(mfrow = c(2,3))
+plot(m_fccl_summerK)
+hist(resid(m_fccl_summerK))
+boxplot(K~Period, data_sFCCL)
+
+(m_rv_summerK <- lm(K~Period, data = data_sRV))
+summary(m_rv_summerK)
+par(mfrow = c(2,3))
+plot(m_rv_summerK)
+hist(resid(m_rv_summerK))
+boxplot(K~Period, data_sRV)
+
+```
+
+## Fall
+```{r}
+data_fFCCL <- Fall %>%
+  filter(Site == "FCCL")
+data_fRV <- Fall %>%
+  filter(Site == "RV" | (Site == "FCCL" & Period == "Pre"))
+data_fSM <- Fall %>%
+  filter(Site == "SM" | (Site == "FCCL" & Period == "Pre"))
+data_fYolo <- Fall %>%
+  filter(Site == "Yolo" | (Site == "FCCL" & Period == "Pre"))
+
+# t-tests ---------------------------------------
+t.test(filter(data_fFCCL,Period=="Pre")$Weight_g, filter(data_fFCCL,Period=="Post")$Weight_g)
+t.test(filter(data_fFCCL,Period=="Pre")$FL_cm, filter(data_fFCCL,Period=="Post")$FL_cm) 
+t.test(filter(data_fFCCL,Period=="Pre")$K, filter(data_fFCCL,Period=="Post")$K)
+
+t.test(filter(data_fRV,Period=="Pre")$Weight_g, filter(data_fRV,Period=="Post")$Weight_g)
+t.test(filter(data_fRV,Period=="Pre")$FL_cm, filter(data_fRV,Period=="Post")$FL_cm) 
+t.test(filter(data_fRV,Period=="Pre")$K, filter(data_fRV,Period=="Post")$K)
+
+t.test(filter(data_fSM,Period=="Pre")$Weight_g, filter(data_fSM,Period=="Post")$Weight_g)
+t.test(filter(data_fSM,Period=="Pre")$FL_cm, filter(data_fSM,Period=="Post")$FL_cm) 
+t.test(filter(data_fSM,Period=="Pre")$K, filter(data_fSM,Period=="Post")$K)
+
+t.test(filter(data_fYolo,Period=="Pre")$Weight_g, filter(data_fYolo,Period=="Post")$Weight_g)
+t.test(filter(data_fYolo,Period=="Pre")$FL_cm, filter(data_fYolo,Period=="Post")$FL_cm) 
+t.test(filter(data_fYolo,Period=="Pre")$K, filter(data_fYolo,Period=="Post")$K)
+
+# Linear models: resids look good
+# FL -------------------------------------------------
+(m_fccl_fall1 <- lm(FL_cm~Period, data = data_fFCCL))
+summary(m_fccl_fall1)
+anova(m_fccl_fall)
+par(mfrow = c(2,3))
+plot(m_fccl_fall1)
+hist(resid(m_fccl_fall1))
+boxplot(FL_cm~Period, data_fFCCL)
+
+(m_rv_fall1 <- lm(FL_cm~Period, data = data_fRV))
+par(mfrow = c(2,3))
+plot(m_rv_fall1)
+hist(resid(m_rv_fall1))
+boxplot(FL_cm~Period, data_fRV)
+
+(m_sm_fall1 <- lm(FL_cm~Period, data = data_fSM))
+par(mfrow = c(2,3))
+plot(m_sm_fall1)
+hist(resid(m_sm_fall1))
+boxplot(FL_cm~Period, data_fSM)
+
+(m_Yolo_fall1 <- lm(FL_cm~Period, data = data_fYolo))
+par(mfrow = c(2,3))
+plot(m_Yolo_fall1)
+hist(resid(m_Yolo_fall1))
+boxplot(FL_cm~Period, data_fYolo)
+
+# Weight ----------------------------------------------
+(m_fccl_fall2 <- lm(Weight_g~Period, data = data_fFCCL))
+summary(m_fccl_fall2)
+anova(m_fccl_fall2)
+par(mfrow = c(2,3))
+plot(m_fccl_fall2)
+hist(resid(m_fccl_fall2))
+boxplot(Weight_g~Period, data_fFCCL)
+
+(m_rv_fall2 <- lm(Weight_g~Period, data = data_fRV))
+summary(m_rv_fall2)
+par(mfrow = c(2,3))
+plot(m_rv_fall2)
+hist(resid(m_rv_fall2))
+boxplot(Weight_g~Period, data_fRV)
+
+(m_sm_fall2 <- lm(Weight_g~Period, data = data_fSM))
+summary(m_sm_fall2)
+par(mfrow = c(2,3))
+plot(m_sm_fall2)
+hist(resid(m_sm_fall2))
+boxplot(Weight_g~Period, data_fSM)
+
+(m_yolo_fall2 <- lm(Weight_g~Period, data = data_fYolo))
+summary(m_yolo_fall2)
+par(mfrow = c(2,3))
+plot(m_yolo_fall2)
+hist(resid(m_yolo_fall2))
+boxplot(Weight_g~Period, data_fYolo)
+
+# K ------------------------------------------------
+(m_fccl_fallK <- lm(K~Period, data = data_fFCCL))
+summary(m_fccl_fallK)
+anova(m_fccl_fallK)
+par(mfrow = c(2,3))
+plot(m_fccl_fallK)
+hist(resid(m_fccl_fallK))
+boxplot(K~Period, data_fFCCL)
+
+(m_rv_fallK <- lm(K~Period, data = data_fRV))
+summary(m_rv_fallK)
+par(mfrow = c(2,3))
+plot(m_rv_fallK)
+hist(resid(m_rv_fallK))
+boxplot(K~Period, data_fRV)
+
+(m_sm_fallK <- lm(K~Period, data = data_fSM))
+summary(m_sm_fallK)
+par(mfrow = c(2,3))
+plot(m_sm_fallK)
+hist(resid(m_sm_fallK))
+boxplot(K~Period, data_fRV)
+
+(m_yolo_fallK <- lm(K~Period, data = data_fYolo))
+summary(m_yolo_fallK)
+par(mfrow = c(2,3))
+plot(m_yolo_fallK)
+hist(resid(m_yolo_fallK))
+boxplot(K~Period, data_fRV)
+```
+
+## Old code
+```{r}
+t_sRV <- t.test(Summer_wide$FL_cm_Pre, filter(Summer_wide, Site=="RV")$FL_cm_Post) #no
+t_sFC <- t.test(Summer_wide$FL_cm_Pre, filter(Summer_wide, Site=="FCCL")$FL_cm_Post) #yes
+
+t.test(Summer_wide$Weight_g_Pre, filter(Summer_wide, Site=="RV")$Weight_g_Post) #on the border
+t.test(Summer_wide$Weight_g_Pre, filter(Summer_wide, Site=="FCCL")$Weight_g_Post) #on the border
+
+t.test(Summer_wide$K_Pre, filter(Summer_wide, Site=="RV")$K_Post) #yes
+t.test(Summer_wide$K_Pre, filter(Summer_wide, Site=="FCCL")$K_Post) #yes
 
@@
 
-```{r}
-Summer$Period = factor(Summer$Period, levels = c("Pre", "Post"))
-ggplot(Summer) + geom_boxplot(aes(Site, FL_cm, fill = Period)) 
-ggplot(Summer) + geom_boxplot(aes(Site, K, fill = Period))
-
-Fall$Period = factor(Fall$Period, levels = c("Pre", "Post"))
-ggplot(Fall) + geom_boxplot(aes(Site, FL_cm, fill = Period))
-ggplot(Fall) + geom_boxplot(aes(Site, Weight_g, fill = Period))
-ggplot(Fall) + geom_boxplot(aes(Site, K, fill = Period)) 
-```
-
-# Fall
 ```{r}
@@
 
-## Models
+# Models
 ```{r}
 RV_analysis <- data %>%
-  group_by(Season, Site, Period, Cage) %>%
+  group_by(Season, Site, Period, CageRep) %>%
   summarize(meanK = mean(K, na.rm = TRUE),
@@
                                 Season == "Winter" ~ Weight_g_Pre)) %>%
-  mutate(deltaK = K_Post - K_Pre,
-         deltaWt = Weight_g_Post - Weight_g_Pre) %>%
-  filter(Site != "FCCL")
+  mutate(deltaK = (K_Post - K_Pre)/K_Pre,
+         deltaWt = (Weight_g_Post - Weight_g_Pre)/Weight_g_Pre) %>%
+  filter(Site != "FCCL") %>%
+  mutate(Season = factor(Season, levels = c("Winter", "Summer", "Fall"))) %>%
+  filter(!is.na(deltaK))
 
 RV_sumfall <- filter(RV_allfish, Season != "Winter") 
+RV_sumfall$Season = factor(RV_sumfall$Season, levels = c("Summer", "Fall"))
+```
+
+Are the scale of fish weights comparable?
+```{r}
+ggplot(RV_allfish) + geom_boxplot(aes(Season, Weight_g_Post))
+ggplot(RV_allfish) + geom_boxplot(aes(Season, Weight_g_Pre))
 ```
@@
 # CF
-m1 <- lmer(deltaK ~ Season + (1|Cage), data = RV_allfish)
+m1 <- lmer(deltaK ~ Season + (1|CageRep), data = RV_allfish)
 summary(m1)
-plot(m1)
+anova(m1,type =2)
 
-m1b <- lmer(deltaK ~ Season + (1|Cage), data = RV_sumfall)
+m1b <- lmer(deltaK ~ Season + (1|CageRep), data = RV_sumfall)
 summary(m1b)
@@
 # Weight
-m2 <- lmer(deltaWt~ Season + (1|Cage), data = RV_allfish)
+m2 <- lmer(deltaWt~ Season + (1|CageRep), data = RV_allfish)
 summary(m2)
@@
 
-m2b <- lmer(deltaWt ~ Season + (1|Cage), data = RV_sumfall)
+m2b <- lmer(deltaWt ~ Season + (1|CageRep), data = RV_sumfall)
 summary(m2b)
 plot(m2b) 
+```
 
+#### Run post-hoc tests
+```{r}
 library(emmeans)
 m1.emm <- emmeans(m1, "Season", data=RV_allfish)
-pairs(m1.emm, adjust = "sidak")
+pairs(m1.emm, adjust = "tukey")
 plot(m1.emm, comparisons = TRUE) + theme_bw()
@@
 m2.emm <- emmeans(m2, "Season", data=RV_allfish)
-pairs(m2.emm, adjust = "sidak")
+pairs(m2.emm, adjust = "tukey")
 plot(m2.emm, comparisons = TRUE) + theme_bw()
+```
+
+#### Model validation
+```{r}
+resid.m1 <- resid(m1, type = "pearson")
+par(mfrow = c(2,2))
+plot(m1)
+plot(resid.m1)
+hist(resid.m1)
+qqnorm(resid.m1)
+plot(RV_allfish$Season, resid.m1)
+
+plot(m2)
+resid.m2 <- resid(m2, type = "pearson")
+par(mfrow = c(2,2))
+plot(resid.m2)
+hist(resid.m2)
+qqnorm(resid.m2)
+plot(RV_allfish$Season, resid.m2)
+
+```
+
+#### Plot CI and RE
+##### m1
+```{r}
+library(multcomp)
+m1.emm <- emmeans(m1, "Season")
+plotm1 = plot(m1.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m1 = cld(m1.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm1) %>%
+  mutate(.group = gsub(" ", "", .group))
+
+(plot_season_k <- ggplot(data = letter_m1,) + 
+   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
+
+  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+     geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
+    geom_hline(yintercept = 0, linetype = "dashed") + 
+  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
+  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
+  labs(y = "Proportional Change in K (g cm^-2) with 95% Confidence Intervals") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size = 11),
+        axis.text.y = element_text(size = 11),
+        legend.position = "top",
+        axis.title.x = element_blank()) )
+```
+
+##### m2
+```{r}
+library(multcomp)
+m2.emm <- emmeans(m2, "Season")
+plotm2 = plot(m2.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m2 = cld(m2.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm2) %>%
+  mutate(.group = gsub(" ", "", .group))
+
+(plot_season_wt <- ggplot(data = letter_m2,) + 
+   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
+
+  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
+   geom_text( aes(label = .group, x = Season, y = upper.CL + 0.02), position = position_dodge2(width = 0.3)) + 
+    geom_hline(yintercept = 0, linetype = "dashed") + 
+    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
+  labs(y = "Proportional Change in Weight (g) with 95% Confidence Intervals") +
+  theme_bw() +
+  theme(axis.text = element_text(size = 11),
+        legend.position = "top",
+        axis.title.x = element_blank()) )
+```
+
+#### Export data and figures
+```{r}
+# emmeans results -------
+write_csv(letter_m1, "smelt_2019_allseasons/data_clean/emmeans_RV_m1.csv")
+write_csv(letter_m2, "smelt_2019_allseasons/data_clean/emmeans_RV_m2.csv")
+
+# plots ----------
+library(patchwork)
+png(filename = "smelt_2019_allseasons/figures/RV_weight_k_season.png", height = 5, width = 9,units = "in", 
+    res = 300, pointsize = 12, family = "sans")
+plot_season_wt & plot_season_k
+dev.off()
+```
+
+```{r}
+t_ci_m1 <- as.data.frame(confint(m1))[3:5,]
+est_winter = 0.034457
+ci25 = t_ci_m1[1,1]
+ci975 = t_ci_m1[1,2]
+ci_m1 <- data.frame(estimate = c(est_winter, est_winter-0.0768, est_winter-0.1844),
+                    ci_2_5 = c(ci25, ci25+t_ci_m1[2,1], ci25+t_ci_m1[3,1]),
+                    ci_97_5 = c(ci975, ci975+t_ci_m1[2,2], ci975 + t_ci_m1[3,2]))%>%
+  mutate(season = c("Winter", "Summer", "Fall"),
+         season = factor(season, levels = c("Winter", "Summer", "Fall")))
+
+summary(m1)
+
+ggplot(ci_m1) + 
+   geom_errorbar(aes(y = season, xmin = ci_2_5, xmax = ci_97_5), size = 2, color = "aquamarine3", width = 0.1) + 
+  geom_point(aes(estimate, season), size = 2.5) +
+
+  labs(x = "Delta K with 95% Confididence Intervals") +
+  theme_bw() +
+  theme(axis.title.y = element_blank())
+
+re_m1 <- as.data.frame(ranef(m1))
+
+ggplot(re_m1) + 
+  geom_point(aes(grp, condval)) +
+  geom_errorbar(aes(x = grp, ymin = condval-condsd, ymax = condval+condsd), width = 0.3) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.95),
+        axis.title = element_blank())
+```
+
+##### m2
+```{r}
+t_ci_m2 <- as.data.frame(confint(m2))[3:5,]
+est_winter = 0.20763
+ci25 = t_ci_m2[1,1]
+ci975 = t_ci_m2[1,2]
+ci_m2 <- data.frame(estimate = c(est_winter, est_winter-0.27075, est_winter-0.60332),
+                    ci_2_5 = c(ci25, ci25+t_ci_m2[2,1], ci25+t_ci_m2[3,1]),
+                    ci_97_5 = c(ci975, ci975+t_ci_m2[2,2], ci975 + t_ci_m2[3,2]))%>%
+  mutate(season = c("Winter", "Summer", "Fall"),
+         season = factor(season, levels = c("Winter", "Summer", "Fall")))
+
+summary(m2)
+
+ggplot(ci_m2) + 
+   geom_errorbar(aes(y = season, xmin = ci_2_5, xmax = ci_97_5), size = 2, color = "aquamarine3", width = 0.1) + 
+  geom_point(aes(estimate, season), size = 2.5) +
+
+  labs(x = "Delta Weight with 95% Confididence Intervals") +
+  theme_bw() +
+  theme(axis.title.y = element_blank())
+
+re_m2 <- as.data.frame(ranef(m2))
+
+ggplot(re_m2) + 
+  geom_point(aes(grp, condval)) +
+  geom_errorbar(aes(x = grp, ymin = condval-condsd, ymax = condval+condsd), width = 0.3) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.95),
+        axis.title = element_blank())
 ```
@@
 Fallfish_avg <- data %>%
-  group_by(Season, Site, Period, Cage) %>%
+  group_by(Season, Site, Period, CageRep) %>%
   summarize(meanK = mean(K, na.rm = TRUE),
@@
          deltaWt = Weight_g_Post - Weight_g_Pre) %>%
-  filter(!is.na(K_Post))
+  filter(!is.na(K_Post))%>%
+  mutate(Site = factor(Site))
 
@@
 
-### Effect of Site in the Fall
 ```{r}
@@
 summary(m3a)
-plot(m3)
 
-m3 <- lmer(deltaK ~ Site + (1|Cage), data = Fallfish, REML = TRUE)
+m3 <- lmer(deltaK ~ Site + (1|CageRep), data = Fallfish, REML = TRUE)
 summary(m3)
-plot(m3)
 
@@
 summary(m4a)
-plot(m4a)
 
-m4 <- lmer(deltaWt~ Site + (1|Cage), data = Fallfish)
+m4 <- lmer(deltaWt~ Site + (1|CageRep), data = Fallfish)
 summary(m4)
-plot(m4)
 
@@
 
+```
+
+#### Run post-hoc tests
+```{r}
 library(emmeans)
 m3.emm <- emmeans(m3, "Site", data=Fallfish)
-pairs(m3.emm, adjust = "sidak")
+pairs(m3.emm, adjust = "bonferroni")
 plot(m3.emm, comparisons = TRUE, type = "response") + theme_bw()
@@
 m4.emm <- emmeans(m4, "Site", data=Fallfish)
-pairs(m4.emm, adjust = "sidak")
+pairs(m4.emm, adjust = "bonferroni")
 plot(m4.emm, comparisons = TRUE) + theme_bw()
@@
 
+#### Model validation
 ```{r}
@@
 
-#hello
+resid.m3 <- as.numeric(resid(m3, type = "pearson"))
+plot(m3)
+par(mfrow = c(2,2))
+plot(resid.m3)
+hist(resid.m3)
+qqnorm(resid.m3)
+boxplot(resid.m3~Fallfish$Site)
+summary(resid.m3)
+
+str(Fallfish)
+
+plot(m4)
+resid.m4 <- resid(m4, type = "pearson")
+par(mfrow = c(2,2))
+plot(resid.m4)
+hist(resid.m4)
+qqnorm(resid.m4)
+plot(RV_allfish$Season, resid.m4)
+boxplot(resid.m4~Fallfish$Site)
+
+ggplot(Fallfish, aes(factor(Site), res4)) + geom_boxplot() + theme_bw()
 
@@
 
+#### Plot CI and RE
+
+##### m3
 ```{r}
-m3
+library(multcomp)
+m3.emm <- emmeans(m3, "Site")
+plotm3 = plot(m3.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m3 = cld(m3.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm3) %>%
+  mutate(.group = gsub(" ", "", .group))
+
+(plot_Site_k <- ggplot(data = letter_m3,) +
+
+  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+      geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
+    geom_text( aes(label = .group, x = Site, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
+    geom_hline(yintercept = 0, linetype = "dashed") + 
+  geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
+  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
+  labs(y = "Change in K (g cm^-2) with 95% Confidence Intervals") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size = 11),
+        axis.text.y = element_text(size = 11),
+        legend.position = "top",
+        axis.title.x = element_blank()) )
+```
+
+##### m4
+```{r}
+m4.emm <- emmeans(m4, "Site")
+plotm4 = plot(m4.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m4 = cld(m4.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm4) %>%
+  mutate(.group = gsub(" ", "", .group))
+
+(plot_Site_wt <- ggplot(data = letter_m4,) +
+
+  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+   geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
+    geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
+   geom_text( aes(label = .group, x = Site, y = upper.CL + 0.03), position = position_dodge2(width = 0.3)) + 
+    geom_hline(yintercept = 0, linetype = "dashed") + 
+    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
+  labs(y = "Change in Weight (g) with 95% Confidence Intervals") +
+  theme_bw() +
+  theme(axis.text = element_text(size = 11),
+        legend.position = "top",
+        axis.title.x = element_blank()) )
+```
+
+#### Export data and figures
+```{r}
+# emmeans results -------
+write_csv(letter_m3, "smelt_2019_allseasons/data_clean/emmeans_fall_m3.csv")
+write_csv(letter_m4, "smelt_2019_allseasons/data_clean/emmeans_fall_m4.csv")
+
+# plots ----------
+library(patchwork)
+png(filename = "smelt_2019_allseasons/figures/model_fall_site.png", height = 5, width = 9,units = "in", 
+    res = 300, pointsize = 12, family = "sans")
+plot_Site_wt & plot_Site_k
+dev.off()
+```
+
+```{r}
+t_ci_m3b <- as.data.frame(confint(m3))[3:6,]
+est_fccl = -0.06439
+ci25 = t_ci_m3[1,1]
+ci975 = t_ci_m3[1,2]
+ci_m3 <- data.frame(estimate = c(est_fccl, est_fccl-0.08557, est_fccl-0.10488, est_fccl-0.06496),
+                    ci_2_5 = c(ci25, ci25+t_ci_m3[2,1], ci25+t_ci_m3[3,1], ci25 + t_ci_m3[4,1]),
+                    ci_97_5 = c(ci975, ci975+t_ci_m3[2,2], ci975 + t_ci_m3[3,2],  ci975+t_ci_m3[4,2]))%>%
+  mutate(site = c("FCCL", "RV", "SM", "Yolo"),
+         site = factor(site, levels = c("FCCL", "RV", "SM", "Yolo")))
+
+summary(m3)
+
+ggplot(ci_m3) + 
+   geom_errorbar(aes(y = site, xmin = ci_2_5, xmax = ci_97_5), size = 2, color = "aquamarine3", width = 0.1) + 
+  geom_point(aes(estimate, site), size = 2.5) +
+
+  labs(x = "Delta K with 95% Confididence Intervals") +
+  theme_bw() +
+  theme(axis.title.y = element_blank())
+
+re_m3 <- as.data.frame(ranef(m3))
+
+ggplot(re_m3) + 
+  geom_point(aes(grp, condval)) +
+  geom_errorbar(aes(x = grp, ymin = condval-condsd, ymax = condval+condsd), width = 0.3) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.95),
+        axis.title = element_blank())
+```
+
+```{r}
+t_ci_m4 <- as.data.frame(confint(m4))[3:6,]
+est_fccl = -0.35144
+ci25 = t_ci_m4[1,1]
+ci975 = t_ci_m4[1,2]
+ci_m4 <- data.frame(estimate = c(est_fccl, est_fccl-0.04438, est_fccl-0.19573, est_fccl-0.12013),
+                    ci_2_5 = c(ci25, ci25+t_ci_m4[2,1], ci25+t_ci_m4[3,1], ci25 + t_ci_m4[4,1]),
+                    ci_97_5 = c(ci975, ci975+t_ci_m4[2,2], ci975 + t_ci_m4[3,2],  ci975+t_ci_m4[4,2]))%>%
+  mutate(site = c("FCCL", "RV", "SM", "Yolo"),
+         site = factor(site, levels = c("FCCL", "RV", "SM", "Yolo")))
+
+summary(m4)
+
+ggplot(ci_m4) + 
+   geom_errorbar(aes(y = site, xmin = ci_2_5, xmax = ci_97_5), size = 2, color = "aquamarine3", width = 0.1) + 
+  geom_point(aes(estimate, site), size = 2.5) +
+
+  labs(x = "Delta Weight with 95% Confididence Intervals") +
+  theme_bw() +
+  theme(axis.title.y = element_blank())
+
+re_m4 <- as.data.frame(ranef(m4))
+
+ggplot(re_m4) + 
+  geom_point(aes(grp, condval)) +
+  geom_errorbar(aes(x = grp, ymin = condval-condsd, ymax = condval+condsd), width = 0.3) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 0.95),
+        axis.title = element_blank())
+```
+
+Attempted some code from Jereme Gaeta's lesson but didn't get this to work.
+
+```{r}
+m4
 fixef(m3)

### 2023-06-09 smelt_2019_allseasons/Zoop 2019.Rmd
catching up on my git hub

@@
 library(zooper)
+library(broom)
+library(vegan)
 ```
@@
 oct <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
-aug <- read_csv("data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
-oct <- read_csv("data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
+#aug <- read_csv("data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")
+#oct <- read_csv("data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")
 
@@
 all$volumesampled <- ((pi*(all$RingSize_m^2))/4)*all$distance
+
 all$samplecount <- (all$TotalVolume_ml/all$Subsampled_ml)*all$Count
@@
 winter <- read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
-winter <- read_csv("data_clean/zoop_abundance.csv")
+#winter <- read_csv("data_clean/zoop_abundance.csv")
 
@@
 
-library(vegan)
 source("PlotNMDS.R")
@@
 RVzoops = filter(zoops, Location == "RV")
-
+fallzoops = filter(zoops, Season == "Fall")
 #raw abundance matrix
 RVzoopmat = as.matrix(RVzoops[,6:12])
-
+fallzoopmat = as.matrix(fallzoops[,6:12])
 #relative abundance matrix
 RVzoopmat2 = RVzoopmat/rowSums(RVzoopmat)
+fallzoopmat2 = fallzoopmat/rowSums(fallzoopmat)
 
@@
 
+falla = adonis2(fallzoopmat2~Location*datatype, data = fallzoops)
+
+##################################This is the one for the paper
 RVb = adonis2(RVzoopmat2~Season, data = RVzoops)
 RVb
+RVresults = tidy(RVb)
+write.csv(RVresults, file = "outputs/RVresults.csv")
 
@@
 
-RVb = adonis2(RVzoopmat2~Season, data = RVzoops)
+RVb = adonis2(RVzoopmat2BM~Season, data = RVzoops)
 RVb
@@
 pretty big differences between seasons, R2 of 54% on the absolute abundance, 64% on relative abundance
-
+pretty big differences between seasons, R2 of 65% on the absolute biomass, 95% on relative biomass
 THough I may need to update this with some sort of variable to account for day of year. Not sure.
@@
 
+######################################################
+#this is the second permanova for the paper
 Fallb = adonis2(Fallzoopmat2~Location, data = Fallzoops)
 Fallb
+write.csv(tidy(Fallb), "outputs/FallZoops.csv", row.names = F)
+
 #
@@
 
-N1 = metaMDS(zoopmat2)
+N1 = metaMDS(zoopmat2, trymax = 50, try = 20)
 zoops = mutate(zoops, Season  = as.factor(Season), Location = as.factor(Location))
@@
 PlotNMDS(RVN1, RVzoops, group = "Season")
-PlotNMDS(RVN1, RVzoops, group = "Location")
 
@@
 #remove new date column
-weird.tag <- subset(weird.tag, select = -6)
+weird.tag <- subset(weird.tag, select = -X.date)
 
@@
 
+save(diet, file = "Dietdata.Rdata")
+
 #pivot_wider
@@
 ```{r}
-
 zoopdiet = bind_rows(zoops, dietwide) %>%
@@
 
+#Now fall
+Falldietzoops = filter(zoopdiet, Season == "Fall")
+
 #Convert to reletive abundance
@@
 
-RVda = adonis2(RVzoopdietmat2~ datatype + Season, data = RVdietzoops)
+Fallzoopdietmat = as.matrix(Falldietzoops[,c(6:11, 13, 14)])
+Fallzoopdietmat2 = Fallzoopdietmat/rowSums(Fallzoopdietmat)
+
+##########################This is the analysis for the paper!!!!
+RVda = adonis2(RVzoopdietmat2~ datatype*Season, data = RVdietzoops)
 RVda
+write.csv(tidy(RVda), "outputs/DietZooppermanova.csv")
+
+Fallda = adonis2(Fallzoopdietmat2~ Location*datatype, data = Falldietzoops)
+
+Fallda
+write.csv(tidy(Fallda), "outputs/DietZooppermanovaFall.csv")
+
+```
+
+Let's look at this a little more closely,s ee if we see any patterns.
+
+```{r}
+#It's really odd that data type isn't that important given some critters that show up in diet and not zooplankton at all.
+
+ggplot(zoopdietlong, aes(x = SampleID, y = count, fill = Taxa)) + geom_col()+
+  facet_wrap(~datatype, scales = "free")
+
+ggplot(filter(zoopdietlong, Location == "RV"), aes(x = SampleID, y = count, fill = Taxa)) + geom_col()+
+  facet_wrap(Season~datatype, scales = "free")
+
+ggplot(filter(zoopdietlong, Location == "RV"), aes(x = SampleID, y = count, fill = Taxa)) + geom_col(position = "fill")+
+  facet_wrap(Season~datatype, scales = "free")
+
+```
+
+I tested for an interaction between datatype and season, but nothing. I think it's just too variable to say much.
+
+```{r}
+#NMDS's that we probably won't include
 
@@
 
+zoopnos = group_by(zoopdiet, datatype, Season, Location) %>%
+  summarize(N = length(unique(SampleID)))
+
 ggplot(zoopdietlong, aes(x = datatype, y = count, fill = Taxa))+
   geom_col(position = "fill")+
-  facet_grid(Location~Season)
+  facet_grid(Location~Season)+
+  scale_fill_brewer(palette = "Dark2", name = "Taxon")+
+  theme_bw()+
+  ylab("Relative Abundance")+
+  geom_label(data = zoopnos, aes(x = datatype, y = 1, label = N), inherit.aes = FALSE)+
+  scale_x_discrete(labels = c("Zooplankton", "Diets"), name = NULL)
+
+ggsave("outputs/zoopdiet.tiff", device = "tiff", width = 8, height = 6.5)
 

### 2023-06-09 survival.R

@@ -1,0 +1,77 @@
+# Pete Nelson, PhD
+# Dept of Water Resources
+# 20 April 2023
+# with Nick Bertrand, USBR, and others
+# Study design: compare two release strategies for Delta smelt, hard v soft, using elapsed time from release until recapture as a proxy for survival. Hypothesis: soft (experimental treatment) release results in improved survival, evidenced by longer times at liberty.
+# Questions: is there a treatment effect (ie difference in survival between fish subject to hard v soft release)? What is the minimum sample size required to detect a treatment effect of 20% (power analysis)?
+
+# read in data ----
+library(tidyverse)
+library(lubridate)
+read_csv("DeltaSmeltDataNelson.csv")
+
+## data mod -----
+dat <- read_csv("DeltaSmeltDataNelson.csv") %>% 
+  select(-1) %>% 
+  mutate(group = as_factor(release_type),
+         release = End_date, recapture = Date,
+         time = daystorecap,
+         site = as_factor(site),
+         num = num_fish,
+         .keep = "unused")
+
+print(dat, n = Inf)
+  
+# site is the release site (Rio Vista or SDWSC)
+# group tells you which treatment (release type, hard or soft) the fish belongs to
+# release is the date fish were released
+# recapture is the date fish were recaptured
+# time is the number of days from release to recapture (ie survival)
+# num is the number of fish released
+
+# treatment effect ----
+library(survival)
+
+# allows right-censored data only
+survdiff(Surv(time) ~ group, data = dat) 
+# no treatment effect
+
+survdiff(Surv(time) ~ group + site, data = dat) 
+# no treatment effect, no site effect
+
+## alternatively ----
+
+fit <- survfit(Surv(time) ~ group,
+               data = dat)
+print(fit)
+
+library(ggplot2)
+library(survminer)
+ggsurvplot(fit,
+           pval = T,
+           pval.method = T,
+           surv.median.line = "hv") +
+  labs(title = "Delta smelt survival",
+       x = "days", y = "suvival probability")
+
+# power analysis -----
+# https://www2.ccrb.cuhk.edu.hk/stat/survival/Lachin1981.htm
+
+# set alpha = 0.05
+# set 1-beta = 1-0.8 = 0.2
+# set sigma, minimum hazards ratio (control:experimental) = 0.9
+# control median survival = mc, calling treatment "hard" the control
[…]

### 2023-06-09 smelt_2019_allseasons/clean_conditionfactor_survival.Rmd

--- 2021-12-11 smelt_2019_allseasons/f_clean_conditionfactor_survival.Rmd
@@
 library(readr)
+library(here)
 root <- "smelt_2019_allseasons"
@@
 ```{r}
-summerdata <- read_csv("smelt_2019_allseasons/Raw_Smelt-Length-Weight_Summer2019.csv", col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
-  rename(K0 = K) 
-falldata <- read_csv("smelt_2019_allseasons/Raw_Smelt-Length-Weight_Fall2019.csv", col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
-  rename(K0 = K)
+summerdata <- read_csv(here(root,"data_raw","Raw_Smelt-Length-Weight_Summer2019.csv"), col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
+  rename(K0 = K) %>%
+  mutate(Season = "Summer")
 
-winterspringdata <- read_csv("smelt_2019_allseasons/Cagetype_data.csv") %>%
+falldata <- read_csv(here::here(root,"data_raw", "Raw_Smelt-Length-Weight_Fall2019.csv"), col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
+  rename(K0 = K) %>%
+  mutate(Season = "Fall")
+
+winterspringdata <- read_csv(here(root, "data_raw", "Cagetype_data.csv")) %>%
   rename(Pre_FL=Pre_FL_cm,
@@
          Pre_Weight=Pre_Weight_g,
-         Post_Weight=Post_Weight_g)
+         Post_Weight=Post_Weight_g) %>%
+  mutate(Season = "Winter",
+         ID = paste0("Winter_",`...1`))
 ```
@@
 winspring_long <- winterspringdata %>% 
-  select(-Delta_CF, -X1) %>%
+  select(-Delta_CF, -`...1`) %>%
   pivot_longer(cols = c(Pre_FL:Post_CF),
@@
 winspring_clean <- winspring_long %>%
-  filter(Site != "DWSC",
-         Mesh == "large") %>%
   rename(FL_cm = FL,
@@
          K0 = CF) %>%
-  mutate(Deployment = ifelse(Site =="DWSC", "Spring",
-                             ifelse(Site == "RV", "Winter", NA )),
-         ID = NA,
-         ID = as.character(ID),
+  mutate(Deployment = "Winter",
          Deployment = as.factor(Deployment),
@@
          Cage = as.factor(Cage))%>%
-  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage)
+  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage, Season)
 
@@
   rename(FL_cm = FL_mm) %>%
-  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage)
+  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage, Season)
 

### 2023-06-09 smelt_2019_allseasons/Diet 2019.Rmd
catching up on my git hub
exporting final dataframe to data_clean folder

@@
 #remove new date column
-weird.tag <- subset(weird.tag, select = -6)
+weird.tag <- select(weird.tag, -X.date)
 
@@
 viridis_pal(option = "plasma")(8)
+
+write.csv(prop2, "smelt_2019_allseasons/data_clean/Diet.proportions.csv", row.names=FALSE)
 ```

### 2023-06-09 smelt_2019_allseasons/Biofouling.Rmd
creating new code and data files for biofouling data

---
title: "Biofouling"
author: "Nicole Kwan"
date: "2023-06-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-06-10 smelt_2019_allseasons/Biofouling.Rmd
prep data

@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+# load packages
+```{r message=FALSE, warning=FALSE}
+knitr::opts_chunk$set(message = FALSE, warning = FALSE)
+library(tidyverse)
 ```
 
-## R Markdown
+# bring in & prep data
+```{r}
+biofoul <- read_csv("smelt_2019_allseasons/data_raw/Invert.data.csv")
+diet <- read_csv("smelt_2019_allseasons/data_clean/Diet.proportions.csv")
+zoop <- read_csv("smelt_2019_allseasons/data_clean/Zoop.catch.csv")
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+#unique(prop2$Taxa)
+#unique(caught.19$Taxa)
+#unique(biofoul$Taxa)
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+#filter diet dataset to just fall fish
+diet.fall <- filter(diet, Season == "Fall")
 
-```{r cars}
-summary(cars)
+#filter zoop dataset to final day of sampling 
+zoop.fall <- filter(zoop, Date == "2019-11-04")
+
+#match up taxa names to work with biofoul data
+zoop.fall$Taxa2 <- zoop.fall$Taxa
+zoop.fall[zoop.fall$Taxa %in% c("Cyclopoid", "Calanoid"),]$Taxa2 <- "Copepod"
+zoop.fall[zoop.fall$Taxa %in% c("Microzoo", "Ostracod", "Cladocera"),]$Taxa2 <- "Other"
+
+diet.fall$Taxa2 <- diet.fall$Taxa
+diet.fall[diet.fall$Taxa %in% c("Cyclopoid", "Calanoid"),]$Taxa2 <- "Copepod"
+diet.fall[diet.fall$Taxa %in% c("Ostracod", "Cladocera"),]$Taxa2 <- "Other"
+
+biofoul$Taxa2 <- biofoul$Taxa
+biofoul[biofoul$Taxa %in% c("Corphiidae", "Gammaridae"),]$Taxa2 <- "Amphipod"
+
+#condense
+zoop.fall2 <- zoop.fall[c(1,10,7)]
+diet.fall2 <- diet.fall[c(2,5,3)]
+biofoul2 <- biofoul[c(1,4,3)]
+
+#rename columns
+zoop.fall2 <- zoop.fall2 %>% rename(zoop = "ind_m3")
+diet.fall2 <- diet.fall2 %>% rename(diet = "prop.mean")
+biofoul2 <- biofoul2 %>% rename(biofoul = "Count")
+
+#combine
+all <- merge(zoop.fall2, diet.fall2, by="Location")
 ```
 
-## Including Plots
+# plot
+```{r}
 
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-06-12 smelt_2019_allseasons/Zoop 2019.Rmd
exporting final dataframe to data_clean folder
update where data gets exported for biofouling rmd

@@
 #merge with catch df
+
 #condense to columns of interest
@@
 caught.19 <- all2019[!(all2019$ind_m3==0),]
+
+#write file for biofouling comparison
+write.csv(caught.19, "smelt_2019_allseasons/data_clean/Zoop.catch.csv", row.names=FALSE)
 ```

### 2023-07-11 histopathology.Rmd
a few more graphs and some test of histopathology stats

@@
   geom_boxplot()
+
 ```
@@
 ```
+
+Now compare rio vista in fall versus suisun marsh in fall
+
+```{r}
+
+library(ordinal)
+
+fallgills = mutate(gills, Fgill = factor(gill, ordered = T)) %>%
+  filter(season == "Fall")
+c1f = clm(Fgill ~ treatment, data = fallgills)
+summary(c1f)
+
+convergence(c1f)
+autoplot.clm(c1f)
+#beautiful!
+
+#can I do a post hoc?
+library(emmeans)
+emmeans(c1f, pairwise ~ treatment)
+
+```

### 2023-07-11 habitat.R

@@ -1,0 +1,47 @@
+#potential habitat differences from differen tyear types
+
+library(cder)
+library(tidyverse)
+library(lubridate)
+library(wql)
+
+#Use 2011 as probably most simlar to 2023, compare to 2019 (other cages), and 2021 (dry year)
+
+WQ11 = cdec_query(c("GZL", "BDL", "NSL", "RVB", "HUN"), sensors = c(100, 25, 27, 28, 61),
+                start.date = as.Date("2011-06-01"), end.date = as.Date("2011-10-31"))
+WQ19 = cdec_query(c("GZL", "BDL", "NSL", "RVB", "HUN"), sensors = c(100, 25, 27, 28, 61),
+                  start.date = as.Date("2019-06-01"), end.date = as.Date("2019-10-31"))
+
+WQ21 = cdec_query(c("GZL", "BDL", "NSL", "RVB", "HUN"), sensors = c(100, 25, 27, 28, 61),
+                  start.date = as.Date("2021-06-01"), end.date = as.Date("2021-10-31"))
+
+
+#filter
+WQ = bind_rows(WQ11, WQ19, WQ21) %>%
+  mutate(Year = year(DateTime))
+
+#convert salinity
+WQ = mutate(WQ, Value2 = case_when(SensorNumber == 100 ~ ec2pss(Value/1000, 25),
+                                   SensorNumber == 25 ~ (Value - 32)*5/9,
+                                   TRUE~ Value),
+            Analyte = factor(SensorType, levels = c("EL COND", "CHLORPH", "TEMP W", "TURB W",  "DIS OXY"), 
+                             labels = c("Salinity", "Chlorophyll", "Temperature", "Turbidity", "DO"))) %>%
+  filter(Value2 >0)
+
+ggplot(WQ, aes(x = DateTime, y = Value2, color = StationID)) + 
+  facet_wrap(Year~Analyte, scales = "free")+
+  geom_line()   + theme_bw()       
+
+#daily averages
+
+WQ2 = mutate(WQ, Day = date(DateTime)) %>%
+  group_by( Year, Analyte, Day, StationID) %>%
+    summarize(Value = mean(Value2, na.rm =T))
+
+ggplot(WQ2, aes(x = Day, y = Value, color = StationID)) + 
+  facet_wrap(Year~Analyte, scales = "free")+
+  geom_line()   + theme_bw()  
+
[…]

### 2023-07-11 smelt_2019_allseasons/Biofouling.Rmd

--- 2023-06-09 smelt_2019_allseasons/Biofouling.Rmd
@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+# load packages
+```{r message=FALSE, warning=FALSE}
+knitr::opts_chunk$set(message = FALSE, warning = FALSE)
+library(tidyverse)
+library(ggpubr)
 ```
 
-## R Markdown
+# bring in & prep biofouling data
+```{r}
+biofoul <- read_csv("smelt_2019_allseasons/data_raw/Invert.data.csv")
+unique(biofoul$Taxa)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+#match ID level to diet data
+biofoul$Taxa2 <- biofoul$Taxa
+biofoul[biofoul$Taxa %in% c("Corphiidae", "Gammaridae"),]$Taxa2 <- "Amphipod"
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+#sum across location
+biofoul2<- biofoul %>% 
+  group_by(Taxa2, Location) %>% 
+  summarize("Count.sum"= sum(Count))
 
-```{r cars}
-summary(cars)
+#rename columns
+biofoul3 <- biofoul2 %>% rename(biofoul = "Count.sum")
 ```
 
-## Including Plots
+# bring in & prep diet data
+```{r}
+diet <- read_csv("smelt_2019_allseasons/data_clean/Diet.proportions.csv")
+unique(diet$Taxa)
 
-You can also embed plots, for example:
+#match up taxa names to work with biofoul data
+diet$Taxa2 <- diet$Taxa
+diet[diet$Taxa %in% c("Cyclopoid", "Calanoid"),]$Taxa2 <- "Copepod"
+diet[diet$Taxa %in% c("Ostracod", "Cladocera"),]$Taxa2 <- "Other"
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+#sum across location
+diet2<- diet %>% 
+  group_by(Taxa2, Location) %>% 
+  summarize("Count.sum"= sum(Count))
+
+unique(diet2$Location)
+
+#filter to just fall at core sites
+diet3 <- diet2 %>% filter(Location == "RV.Fall" | Location == "SM.Fall" | Location == "YB.Fall")
+
+#remove empty
+diet4<-diet3[diet3$Taxa2 != "empty",]
+
+#change Location to drop season
+diet4$Location[diet4$Location=="RV.Fall"] <- "RV"
+diet4$Location[diet4$Location =="YB.Fall"] <- "YB"
+diet4$Location[diet4$Location =="SM.Fall"] <- "SM"
+
+#rename columns
+diet4 <- diet4 %>% rename(diet = "Count.sum")
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+# bring in & prep zooplankton data & merge all datasets
+```{r}
+zoop <- read_csv("smelt_2019_allseasons/data_clean/Zoop.catch.csv")
+unique(zoop$Taxa)
+
+#filter zoop dataset to final day of sampling 
+zoop2 <- filter(zoop, Date == "2019-11-04")
+
+#remove microzoop
+zoop2 <- zoop2[!(zoop2$Taxa=="Microzoo"),]
+
+#match up taxa names to work with biofoul data
+zoop2$Taxa2 <- zoop2$Taxa
+zoop2[zoop2$Taxa %in% c("Cyclopoid", "Calanoid"),]$Taxa2 <- "Copepod"
+zoop2[zoop2$Taxa %in% c("Ostracod", "Cladocera"),]$Taxa2 <- "Other"
+
+#sum across new taxa
+zoop3<- zoop2 %>% 
+  group_by(Taxa2, Location) %>% 
+  summarize("sum.indm3"= sum(ind_m3))
+
+#rename columns
+zoop4 <- zoop3 %>% rename(zoop = "sum.indm3")
+
+#combine
+all <- merge(x=diet4,y=zoop4,
+        by=c("Location","Taxa2"), all=TRUE)
+
+all2 <- merge(x=all,y=biofoul3,
+        by=c("Location","Taxa2"), all=TRUE)
+
+#swap NAs with 0
+all2[is.na(all2)] <- 0
+```
+
+# plot
+```{r}
+b<-ggplot(data=all2, aes(x=Location, y =biofoul, fill=Taxa2)) +
+    geom_bar(position="fill", stat="identity", colour="black") +
+  theme_bw() +
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  theme(legend.position="right", axis.title.x = element_blank())+
+  labs(y = "Biofoul samples")
+
+z<-ggplot(data=all2, aes(x=Location, y =zoop, fill=Taxa2)) +
+    geom_bar(position="fill", stat="identity", colour="black") +
+  theme_bw() +
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  theme(legend.position="right", axis.title.x = element_blank())+
+  labs(y = "Zooplankton samples") #final day, no microzoop
+
+d<-ggplot(data=all2, aes(x=Location, y =diet, fill=Taxa2)) +
+    geom_bar(position="fill", stat="identity", colour="black") +
+  theme_bw() +
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  theme(legend.position="right", axis.title.x = element_blank())+
+  labs(y = "Stomach contents")
+
+multiplot <- ggarrange(b,z,d, nrow=3, ncol=1)
+multiplot
+```
+
+# cross-ref what that big chunk of "other" is in the zoop data
+```{r}
+#sum across new taxa
+zoop.only<- zoop2 %>% 
+  group_by(Taxa, Location) %>% 
+  summarize("sum.indm3"= sum(ind_m3))
+
+ggplot(data=zoop.only, aes(x=Location, y =sum.indm3, fill=Taxa)) +
+  geom_bar(position="fill", stat="identity", colour="black") +
+  theme_bw() +
+  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
+  theme(legend.position="right", axis.title.x = element_blank())+
+  labs(y = "Zooplankton samples - final day")
+```

### 2023-10-19 poweranalyses.Rmd
reorganized repo

---
title: "Diet power analysis"
author: "Rosie"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(tidyverse)
library(lubridate)
library(lme4)
library(lmerTest)
library(simr)
```

## R Markdown

Let's look at stomach fullness and diet weight variability to see if we can use it in 2023

```{r}
load("Dietdata.Rdata")

dietsmelt = select(diet, Date, Cage.ID, Location, Tag, Fullness, Digestion, Contents.Weight, Season) %>%
  distinct() %>%
  mutate(smeltID = paste(Location, Date, Tag), Month = month(Date), CageID2 = paste(Location, Cage.ID))

ggplot(dietsmelt, aes(x = Fullness))+ geom_density()+
  facet_wrap(~Location)

```

Some exploritory plots

```{r}
ggplot(dietsmelt, aes(x = smeltID, y = Contents.Weight))+ geom_col()+
  facet_wrap(~Location, scales = "free_x")

ggplot(dietsmelt, aes(x = smeltID, y = Contents.Weight))+ geom_col()+
  facet_wrap(Season~Location, scales = "free_x")

ggplot(dietsmelt, aes(x = Location, y = Contents.Weight))+ geom_boxplot()+
  facet_wrap(~Season, scales = "free_x")

ggplot(dietsmelt, aes(x = Location, y = Fullness))+ geom_boxplot()+
  facet_wrap(~Season, scales = "free_x")

ggplot(dietsmelt, aes(x = CageID2, y = Contents.Weight))+ geom_boxplot()+
  facet_wrap(Location~Season, scales = "free_x")

```

Can I statistically compare stomach fullness or weights between cage deployments?

Differences between locations in the fall will be the most useful, potentially.

```{r}
falldiet = filter(dietsmelt, Season == "Fall")
sf1 = lmer(Fullness ~ Location + (1|CageID2), data = falldiet)
summary(sf1)
plot(sf1)

library(emmeans)
plot(emmeans(sf1, pairwise ~ Location), comparison = T)
```

Nope.

```{r}

fixef(sf1)["LocationSM"] = 0.1
fixef(sf1)["LocationYB"] = 0.1
#p1=powerSim(sf1, fixed("Location", "lr"))

#i'm getting nasty erros for all of teh power analyses with random effec tof cage and i on't know why

sf2 = lm(Fullness ~ Location, data = falldiet)
summary(sf2)

plot(sf2)

sf2$effects["LocationSM"] = 2

powerSim(sf2, progress = F)
#so, very, very low power

#how much power do we need?

model4 <- extend(sf2, within="Location", n=200)

#this takes forever to run, i'll do it tonight
pc4 <- powerCurve(model4,within="Location", breaks=c(50,100,150,200,250), progress =F)
print(pc4)

plot(pc4)
#so, no.

```

Now let's try diet contents weight

```{r}

hist(log(falldiet$Contents.Weight))

#convert weight to mg and log-transform
falldiet = mutate(falldiet, Weight = Contents.Weight*1000, logweight = log(Weight+1))

dw2 = lmer(logweight ~ Location + (1|CageID2), data = falldiet)
summary(dw2)
plot(emmeans(dw2, pairwise ~ Location), comparison = T)
plot(dw2)

fixef(dw2)["LocationYB"] = 0.2
#I don't know why i'm getting a bunch of 'is singular' errors, but we're still getting the power data
powerSim(dw2, fixed("LocationYB", "z"), progress = F)

#I'll try a simpler model without the random effect 
dw1 = lm(logweight ~ Location, data = falldiet)
summary(dw1)
plot(emmeans(dw1, pairwise ~ Location), comparison = T)
plot(dw1)

dw1$effects["LocationSM"] = .2

powerSim(dw1, progress =F)
#OK, that's better

#how much power do we need?

moddw <- extend(dw1, within="Location", n=200)

#power curve
pc5 <- powerCurve(moddw,within="Location", breaks=c(10, 20,30,40,50,100), progress =F)
print(pc5)

plot(pc5)
#so, we may be able to say something there.

```

Now let's look at growth data

```{r}
#source("smelt_2019_allseasons.Rmd")
#smeltdata2
load("Smeltdata.RData")
box_FL
box_K
box_Wt
```

Compare post-deployment weights in the fall

```{r}
fallsmelt = filter(smeltdata2, Deployment == "Fall", Period == "Post")

hist(fallsmelt$FL_cm)

#were lengths significantly different?
sml1 = lmer(FL_cm ~ Site  + (1|Cage), data = fallsmelt)
summary(sml1)
emmeans(sml1, pairwise~Site)

fixef(sml1)["SiteSM"] = 0.1
fixef(sml1)["SiteYolo"] = 0.1
fixef(sml1)["SiteFCCL"] = 0.1

powerSim(sml1, progress = F)

#check various sample sizes
#how much power do we need?

modfl <- extend(sml1, within="Site", n=200)

#power curve
pc6 <- powerCurve(modfl,within="Site", breaks=c(10, 20,30,40,50,100), progress =F)
print(pc6)

plot(pc6)
#so, we may be able to say something there.
```

```{r}
#what about condition factor?
hist(fallsmelt$K)

sml2 = lmer(K ~ Site  + (1|Cage), data = fallsmelt)
summary(sml2)
emmeans(sml2, pairwise~Site)

#Meh

fixef(sml2)["SiteSM"] = 0.02
fixef(sml2)["SiteYolo"] = 0.02
fixef(sml2)["SiteFCCL"] = 0.02

powerSim(sml2, progress = F)

#check various sample sizes
#how much power do we need?

modk <- extend(sml2, within="Site", n=200)

#power curve
pc6 <- powerCurve(modk,within="Site", breaks=c(10, 20,30,40,50,100), progress =F)
print(pc6)

plot(pc6)
#so, we may be able to say something there.

```

### 2023-10-19 recaptureanalysis/recaps.Rmd
reorganized repo

--- 2023-03-17 recaps.Rmd
@@
 library(deltamapr)
-#load("Recaps.RData")
+load("Recaps.RData")
+#save(nndist, distances, recaps, recaps2, recaps3, RVhdist, SCsoft, SChard, RVhdistx, Dwschard, Dwscsoft, file = "Recaps.RData")
 ```
@@
 
-recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft.xlsx", 
-                    sheet = "Adult Recaptures") %>%
-  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)
-
+recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft (2).xlsx", 
+                    sheet = "Full DSM Data") %>%
+  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`,
+         Mark = `VIE Color/Position`)
 recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
                 Type = case_when(Type == "header" ~ "Soft",
-                                 TRUE ~ Type)) %>%
-  rename(Adclip = `Ad clip`, Mark = `VIE Color/Position`) %>%
-  select(-Type, -Site)
+                                 is.na(Type) ~ "Wild",
+                                 TRUE ~ Type),
+                Site = case_when(is.na(Site) ~ "Wild",
+                                 TRUE ~ Site))
 str(recaps)
@@
 recaps3
+
+write.csv(recaps, "Recapturedistances.csv")
 ```
@@
 ```{r}
-ggplot(recaps3, aes(x = SiteType, y = Distance))+ geom_boxplot(aes(fill = Type))+
+ggplot(filter(recaps3, Type != "Hard (Trailer)", Type != "Wild"), aes(x = SiteType, y = Distance))+ 
+  geom_boxplot(aes(fill = SiteType))+
   ylab("Distance from Release Site (m)")+
+  scale_fill_discrete(guide = NULL)+
   theme_bw()
@@
 recapsum
+```
+
+```{r}
+
+#ANOVA of differences in distance by release group
+library(emmeans)
+m1 = lm(Distance ~ SiteType, data = recaps3)
+summary(m1)
+anova(m1)
+emmeans(m1, pairwise ~ SiteType)
+plot(emmeans(m1, pairwise ~ SiteType), comparisons = T)
+
+#so hard releases at RIo Vista traveled further from hard releases at SDWSC, but no other significant differences
+
+```
+```{r}
+
+#ANOVA of differences in distance by release event
+m1.1 = lm(Distance ~ ReleaseEvent, data = recaps3)
+summary(m1.1)
+anova(m1.1)
+emmeans(m1.1, pairwise ~ ReleaseEvent)
+plot(emmeans(m1.1, pairwise ~ ReleaseEvent), comparisons = T)
+
+#It's a bit of a mess.
+
+```
+
+Plot of distance to recapture over time by release type
+
+```{r}
+
+ggplot(recaps3, aes(x = as.numeric(DaysSinceRelease), y = Distance, color = Type))+
+  geom_point()+ geom_smooth(method = "lm")+ ylab("Distance from Release Site (m)")+
+  xlab("Days since release")
+
+```
+
+Plot of distance to recapture over time by release site
+
+```{r}
+
+ggplot(filter(recaps3, Type == "Hard"), aes(x = as.numeric(DaysSinceRelease), y = Distance, color = Site))+
+  geom_point()+ geom_smooth(method = "lm")+ ylab("Distance from Release Site (m)")+
+  xlab("Days since release")
 
@@
 
-I'm not quite sure the best way to summarize this. I'll start by just the mean of the distance matrix, but i might want do just half the matrix. I'll look into that later.
+Let's look at the mean of the lower triagle of each of these.
 
@@
 
-nndist = bind_rows(RVdtx, RVdt, SCs, SCh)
+nndist = bind_rows(RVdtx, RVdt, SCs, SCh) %>%
+  mutate(Release = factor(Release, levels = c("Rio Vista Hard", "DWSC Hard", "DWSC Soft", "Trailer"),
+                          labels = c("Hard Rio Vista", "Hard SDWSC", "Soft SWDSC", "Trailer")))
 
-ggplot(nndist, aes(x = Release, y = Distance, fill = Release)) + geom_boxplot()+
-  ylab("Distance Between Recaptures")
+ggplot(filter(nndist, Release != "Trailer"), aes(x = Release, y = Distance, fill = Release)) + geom_boxplot()+
+  ylab("Distance Between Recaptures")+ theme_bw()+ scale_fill_discrete(guide = NULL)
 
@@
 
-Now let's bring in the time aspect
+now let's look at it statistically
 
@@
 
-recapstime = read_excel("RecapturesSummary_1.xlsx", sheet = "REcapture Distances")
+m2 = lm(Distance ~ Release, data = nndist)
+summary(m2)
+plot(m2)
+#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.
+
+emmeans(m2, pairwise ~ Release)
+plot(emmeans(m2, pairwise ~ Release), comparisons = T)
 
 ```
+
+So DWSC soft were closer together than rio vista hard, but no difference between DWSC hard and DWSC soft
+
+I could also do this by release rather than release type
+
+```{r}
+smeltIDS = select(recaps2, fishID, ReleaseEvent)
+
+nndist2 = left_join(nndist, smeltIDS, by = c("Fish1" = "fishID"))
+
+m3 = lm(Distance ~ ReleaseEvent, data = nndist2)
+summary(m3)
+plot(m3)
+#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.
+
+emmeans(m3, pairwise ~ ReleaseEvent)
+plot(emmeans(m3, pairwise ~ ReleaseEvent), comparisons = T)
+
+write.csv(nndist2, "DistanceMatrix.csv")
+```

### 2023-10-19 smelt_2019_allseasons/histopathology.Rmd
reorganized repo

--- 2023-07-11 histopathology.Rmd
@@
 ```{r setup, include=FALSE, warning=FALSE}
+
+#making a change to test branching
+
 knitr::opts_chunk$set(echo = TRUE)

### 2023-10-19 biofouling/clod cards.R

@@ -1,0 +1,17 @@
+#graph test clod card data (because I can!)
+
+library(tidyverse)
+library(lubridate)
+library(readxl)
+
+clods = read_excel("data/clod cards.xlsx")
+
+clods = mutate(clods, diff = `Starting Weight`-`Ending weight`) %>%
+  filter(treatment != "not used")
+
+ggplot(clods, aes(x = treatment, y = diff))+ geom_boxplot()
+ggplot(clods, aes(x = treatment, y = diff, fill =as.factor(`Card #`)))+ 
+  geom_col(position = "dodge", color = "black")+
+  scale_fill_brewer(palette = "Dark2", guide = NULL)+
+  ylab("Difference in Weight (g)")+
+  theme_bw()

### 2023-10-19 biofouling/water quality.R

@@ -1,0 +1,56 @@
+#biofouling 2023 analyses
+
+library(tidyverse)
+library(lubridate)
+library(readxl)
+
+#look at the survival data
+survival = read_excel("data/BiofoulingStudy_Survival.xlsx", sheet = "Data")
+
+ggplot(survival, aes(x = Treatment, y = Survival))+ geom_boxplot()
+
+ggplot(survival, aes(x = Site, y = Survival)) + geom_boxplot()
+
+ggplot(survival, aes(x = Treatment, y = Survival, fill = Site)) + geom_boxplot()
+
+lm1 = lm(CountwithCTM ~ Treatment+Site, data = survival)
+summary(lm1)
+anova(lm1)
+plot(lm1)
+
+ggplot(survival, aes(x = Cage, y = Survival, fill = Treatment))+ geom_col()+
+  facet_wrap(~Site, scales = "free_x")
+hist(survival$CountwithCTM)
+
+#quick plots of environmental data
+
+env = read_excel("data/BiofoulingStudyCageChecks.xlsx", na = c("NA", ""))
+
+ggplot(env, aes(x = as.factor(Date), y = DO_mg_L, color = InsideOutside))+
+  geom_boxplot()+
+  facet_wrap(~Location)
+  
+ggplot(env, aes(x = as.factor(Date), y = pH, color = InsideOutside))+
+  geom_boxplot()+
+  facet_wrap(~Location)
+
+library(lme4)
+test = lmer(DO_mg_L ~ InsideOutside + (1|Date), data = env)
+summary(test)
+
+ggplot(env, aes(x = as.factor(Date), y = Water.Temp_C, color = InsideOutside))+
+  geom_boxplot()+
+  facet_wrap(~Location)
+
+
+ggplot(env, aes(x = as.factor(Date), y = Turb, color = InsideOutside))+
+  geom_boxplot()+
+  facet_wrap(~Location)
+
+
+BDL = cdec_query("BDL", c(25, 27, 100, 62, 221), start.date = ymd("2023-08-30"),
+                 end.date = ymd("2023-09-01"))
+BDL2 = BDL %>%
+  filter(date(DateTime) == ymd("2023-08-31"), Duration == "E") %>%
+  mutate(Value2 = case_when(SensorType == "TEMP W" ~ (Value-32)*5/9,
+                            TRUE ~ Value))

### 2023-10-19 intro.R

@@ -1,0 +1,87 @@
+# Pete Nelson, PhD
+# Dept of Water Resources
+# lifted w mods 18 April 2023
+# from https://statsandr.com/blog/what-is-survival-analysis/
+# goal: intro to survival analysis
+
+# simple example -----
+# create dataset
+dat <- data.frame(
+  time = c(3, 5, 7, 2, 18, 16, 2, 9, 16, 5),
+  event = c(0, 1, 1, 1, 0, 1, 1, 1, 1, 0)
+)
+
+# subject identifies the individuals in the study
+# time is the time to event in days
+# event is the event status where 0 = censored (eg individual fish survives beyond the study period, sheds the tag or otherwise becomes unavailable) and 1 = event happened (ie individual died and you recovered the tag)
+
+# run Kaplan-Meier estimator with the survfit() and Surv() functions
+library(survival)
+km <- survfit(Surv(time, event) ~ 1, data = dat)
+summary(km)
+plot(km,
+     xlab = "days",
+     ylab = "survival probability",
+     conf.int = FALSE)
+
+# alt set of functions
+library(survminer)
+ggsurvplot(km,
+           conf.int = FALSE,
+           legend = "none")
+# add median survival to the plot
+ggsurvplot(km,
+           conf.int = FALSE,
+           surv.median.line = "hv",
+           legend = "none") +
+  labs(title = "Delta smelt survival",
+       x = "days",
+       y = "survival probabilty")
+
+# bigger dataset -----
+library(KMsurv)
+data(tongue)
+library(tidyverse)
+
+# type is tumor DNA profile (1 = aneuploid tumor, 2 = diploid tumor)
+# time is time to death or on-study time (in weeks)
+# delta is the death indicator (0 = alive, 1 = dead)
+
+anaploid <- tongue %>% filter(type == "1") 
+  
+fit <- survfit(Surv(time, delta) ~ 1,
+          data = anaploid,
+          conf.type = "log-log")
+fit
+ggsurvplot(fit,
+           surv.median.line = "hv",
+           legend = "none") +
+  labs(title = "patient survival",
+       x = "time (weeks)",
+       y = "survival probability")
+
+# comparing 2 groups -----
+dat <- data.frame(
+  group = c(rep(1, 6), rep(2, 6)),
[…]

### 2023-10-19 smelt_2019_allseasons/continuousWQ.R

@@ -1,0 +1,150 @@
+#Continuous water quality
+
+library(lubridate)
+library(tidyverse)
+library(cder)
+library(wql)
+library(readxl)
+
+WQ = cdec_query(stations = c("LIS", "BDL", "RVB", "DWS"), 
+                sensors = c(24,25, 100, 27, 221, 61), 
+                start.date = ymd("2019-01-01"), 
+                end.date = ymd("2020-01-01"))
+
+
+WQt = filter(WQ, Value >0) %>%
+  mutate(Value2 = case_when(SensorType == "EL COND" ~  ec2pss(Value/1000, 25),
+                            SensorType == "TEMP W" ~ (Value-32)*5/9,
+                            TRUE ~ Value),
+         Analyte = case_when(SensorType == "EL COND"~ "Salinity",
+                             SensorType == "TURB W" ~ "Turbidity",
+                             SensorType == "TURB WF" ~ "Turbidity",
+                           SensorType == "TEMP W"~ "Temperature",
+                           SensorType == "DIS OXY" ~ "Dissolved Oxygen")) %>%
+  filter(Value2 <1000, Value2>0,  Duration == "E")
+
+
+ggplot(WQt, aes(x = ObsDate, y = Value2,
+               color = StationID))+ 
+  facet_wrap(~Analyte, scales = "free_y")+
+  geom_line()
+#it still looks like salinity drops to zero for no reason
+
+group_by(WQt, Analyte) %>%
+  summarize(mean = mean(Value2), min = min(Value2), max = max(Value2))
+
+dates = read_excel("data/2019 Cage Deployment Dates.xlsx") %>%
+  mutate(Deployment = paste(StationID, Season))
+
+#Attach the deployment dates and filter to just periods with deployments
+WQ3 = left_join(WQt, dates) %>%
+  mutate(deploy = case_when(ObsDate >= Start & ObsDate <= End ~ TRUE,
+                          TRUE  ~ FALSE),
+         Season = factor(Season, levels = c("Winter", "Summer", "Fall"))) %>%
+  filter(deploy)
+
+ggplot(WQ3, aes(x = ObsDate, y = Value2,
+                color = StationID))+ 
+  facet_grid(Analyte~Season, scales = "free")+
+  geom_line()+
+  ylab("Value")+
+  xlab("Date")+
+  theme_bw()+
[…]

### 2023-11-22 smelt_2019_allseasons/DS CTM 2019-2023.Rmd
Adding biofouling analyses

---
title: "2019 DS CTM"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r load packages & data}
library(ggplot2)
library(tidyverse)
library(ggpubr)

# setwd("C:/Users/bedavis/OneDrive - California Department of Water Resources/My Documents/Special Studies/Internal/Delta Smelt Cages/Cage Synthesis")

```

Summer Fall CTMs in 2019

```{r T 2019  stats}
#test of SM and RVB in fall
field.ctm <- read.csv("DS CTM 2019.csv")

field.ctm.2 <- field.ctm %>% 
  filter(!Season == "Summer")
t.test(CTM ~ Location, data = field.ctm.2)
# t = -1.9141
# df = 15.33
# p-value = 0.074

#test of RV in summer v fall
field.ctm.3 <- field.ctm %>% 
  filter(!Location == "SM")
t.test(CTM ~ Season, data = field.ctm.3)

#plot

ggplot(data=field.ctm,aes(x=Loc.Seas, y=CTM, fill=Location)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.3) +
    geom_jitter(color="black", size=1, alpha=0.5,height=0,width=0.1) +
    theme_bw() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
  scale_y_continuous(breaks = round(seq(min(23), max(30), by = 1.0),1), name="Critical Thermal Maximum (°C)")+
    xlab("")+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(size = 12, colour = "black"),
        axis.text.y = element_text(size = 12,colour = "black"),
        axis.title.x = element_text(size = 14,colour = "black"),
        axis.title.y = element_text(size = 14,colour = "black"))
```

CTM acclimation regression

```{r test for normality}

data <- read.csv("data/CTM Regression 2019.csv")
#density plot
ggdensity(data$mean.ctm)

#QQ plot
ggqqplot(data$mean.ctm)

#shapiro test
shapiro.test(data$mean.ctm)
```

```{r separate data and create models}

#removed the lab outlier from the dataset
data.2 <- data %>% 
  filter(!ID == "f")

#separate data and create separate models

field <- data.2 %>% 
  filter(loc == "Field")

lab <- data.2 %>% 
  filter(loc == "Lab")

#model for field CTM data
field.mod <- lm(mean.ctm ~ acc.temp, field)
anova(field.mod)
summary(field.mod) 
#y = 0.247x + 22.057
#abline(a = 22.057, b = 0.247) 
#rsquared = 0.884
#adjusted rsquared = 0.7681 = 0.77
#p = 0.22

#model for lab CTM data
lab.mod <- lm(mean.ctm ~ acc.temp, lab)
anova(lab.mod)
summary(lab.mod) 
#y = 0.276x + 23.771 
#abline(a = 23.771, b = 0.276)
#rsquared = 0.9289
#adjusted rsquared = 0.9051 = 0.91
#p = 0.008

#estimated CTM of fish deployed at YB during fall
#22.1 + (0.25*16.5) 
# = 26.225

#estimated CTM of fish deployed at SM during summer
#22.1 + (0.25*23.4)
# = 27.95

```

```{r plot regression 2019}

  ggplot(data.2, aes(x = acc.temp, y = mean.ctm, color = loc))+
  geom_smooth(method = "lm", se = F,fullrange=F)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = mean.ctm - temp.sd, ymax = mean.ctm + temp.sd), width = 0.2)+
    scale_color_manual("Study Location",
                    breaks = c("Field", "Lab"),
                    labels = c("Field", "Lab"),
                    values = c("cyan3", "tomato"))+
  geom_point(x = 17, y = 25.4, size = 2, color = "tomato")+
  geom_errorbar(aes(x = 17, ymin = 25.4 - 1.7, ymax = 25.4 + 1.7), color = "tomato", width = 0.2)+
  scale_y_continuous(breaks = round(seq(min(23), max(30), by = 1.0),1), name="Critical Thermal Maximum (°C)")+
  scale_x_continuous(breaks = round(seq(min(12), max(26), by = 2.0),1), name="Acclimation Temperature (°C)")+
  annotate("text", x = 14, y = 28.5, label = "y = 0.28x + 23.8")+
  annotate("text", x = 13.5, y = 28.15, label = "R^2 == 0.91", parse = T)+
  annotate("text", x = 19, y = 26, label = "y = 0.25x + 22.1")+
  annotate("text", x = 18.45, y = 25.65, label = "R^2 == 0.77", parse = T)+
 theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(size = 12, colour = "black"),
        axis.text.y = element_text(size = 12,colour = "black"),
        axis.title.x = element_text(size = 14,colour = "black"),
        axis.title.y = element_text(size = 14,colour = "black"))+ theme(legend.position="bottom")

```

```{r singe linear model 2019}
##New single linear model with location as factor.

full.mod <- lm(mean.ctm ~ acc.temp+loc, data.2)
summary(full.mod)
#intercept of field fish 21.74
#slope is 0.26, significant effect of acclimation temperature on CTM (p<0.001), with effect of study location (p<0.001).
#lab intercept is 2.22 higher than field which is 23.96
#Adj R2=0.94
anova(full.mod)

modsum = summary(full.mod)
summary(full.mod)

#plot
 ggplot(data.2, aes(x = acc.temp, y = mean.ctm, color = loc))+
 # geom_smooth(method = "lm", se = F,fullrange=F, size=.5)+
   geom_abline(slope = modsum$coefficients[2,1], intercept = modsum$coefficients[1,1], color = "dodgerblue")+
   geom_abline(slope = modsum$coefficients[2,1], intercept = modsum$coefficients[1,1]+modsum$coefficients[3,1], color = "tomato")+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = mean.ctm - temp.sd, ymax = mean.ctm + temp.sd), width = 0.2)+
    scale_color_manual("Study Location",
                    breaks = c("Field", "Lab"),
                    labels = c("Field", "Lab"),
                    values = c("dodgerblue", "tomato"))+
  geom_point(x = 17, y = 25.4, size = 2.5, shape=1,color = "tomato")+
  geom_errorbar(aes(x = 17, ymin = 25.4 - 1.7, ymax = 25.4 + 1.7), color = "tomato", width = 0.2)+
  geom_point(x = 16.5, y = 26.5, size = 2.2,shape= 15,color = "dodgerblue")+
  geom_errorbar(aes(x = 16.5, ymin = 26.5 - 0.86, ymax = 26.5 + 0.86), color = "dodgerblue", width = 0.2)+
  scale_y_continuous(breaks = round(seq(min(23), max(30), by = 1.0),1), name="Critical Thermal Maximum (°C)")+
  scale_x_continuous(breaks = round(seq(min(12), max(26), by = 2.0),1), name="Acclimation Temperature (°C)")+
  annotate("text", x = 21.5, y = 24, label = "R^2 == 0.94", parse = T)+
   annotate("text", x = 20, y = 27.2, label = "CTmax = 0.26x + 21.73", angle =18)+
   annotate("text", x = 14, y = 27.9, label = "CTmax = 0.26x + 23.95", angle =18)+
  annotate("text", x = 21.5, y = 23.5, label = " P < 0.001", parse=T)+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(size = 12, colour = "black"),
        axis.text.y = element_text(size = 12,colour = "black"),
        axis.title.x = element_text(size = 14,colour = "black"),
        axis.title.y = element_text(size = 14,colour = "black"), legend.position=c(0.15,0.85))

 ggsave("plots/CTMs.tiff", device = "tiff", width =6, height =5)

```

Fall 2023 CTMs

```{T  2023}
#call in all CTMs
ctm <- read.csv("ALL CTM.csv")
#filter to just 2023
c1 <- ctm %>% 
  filter(!Season == "2019 Summer")
c2 <- c1 %>% 
  filter(!Season == "2019 Fall")

#plot size of those recovered or not
ggplot(c2, aes(x=FL, y=Mass, color=Recovered, shape=Treatment))+
  geom_point()
ggplot(c2, aes(x=FL, y=CTM, color=Recovered))+
  geom_point()
ggplot(c2, aes(x=Mass, y=CTM, color=Recovered))+
  geom_point()
ggplot(c2, aes(x=Mass, y=CTM, color=Cage))+
  geom_point()

#remove those that didnt survive
c3 <- c2 %>% 
  filter(Recovered == "y")

#plot 2023 CTM data
ggplot(c3, aes(x=Site, y=CTM, color=Season))+
  geom_boxplot()
ggplot(c3, aes(x=Treatment, y=CTM, color=Site))+
  geom_boxplot()
ggplot(c3, aes(x=as.factor(Cage), y=CTM, color=Site))+
  geom_boxplot()
#remove 20C outlier in marsh
c3 <- c3 %>% 
  filter(!Chamber == "P")

#remake fig
ggplot(c3, aes(x=as.factor(Cage), y=CTM, color=Site))+
  geom_boxplot()+ylim(20,30)

ggplot(data=c3,aes(x=Treatment, y=CTM, fill=Site)) +
    geom_boxplot(outlier.shape=NA) +
    scale_fill_viridis(discrete = TRUE, alpha=0.3) +
    scale_color_viridis(discrete = TRUE, alpha=0.3) +

    geom_jitter( position=position_jitterdodge(jitter.width =.1), size=1, alpha=0.5,
                shape = 21) +
    theme_bw() +
  scale_y_continuous(breaks = round(seq(min(23), max(30), by = 1.0),1), name="Critical Thermal Maximum (°C)")+
    xlab("")+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(size = 12, colour = "black"),
        axis.text.y = element_text(size = 12,colour = "black"),
        axis.title.x = element_text(size = 14,colour = "black"),
        axis.title.y = element_text(size = 14,colour = "black"))

#add 2019 data to figure and only scrub data

c1a <- c1 %>% 
  filter(Recovered == "y")
c1b <- c1a %>% 
  filter(!Treatment == "flip")
ggplot(data=c1b,aes(x=Season, y=CTM, fill=Site)) +
    geom_boxplot(outlier.shape=NA) +
    scale_fill_viridis(discrete = TRUE, alpha=0.5,direction=1,option="E") +
    geom_point(position=position_jitter(width = 0.1), color="black",size=1, alpha=0.5, aes(group = Season)) +
  facet_wrap(~Site)+
    xlab("")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(size = 12, colour = "black"),
        axis.text.y = element_text(size = 12,colour = "black"),
        axis.title.x = element_text(size = 14,colour = "black"),
        axis.title.y = element_text(size = 14,colour = "black"))+
  scale_y_continuous(breaks = round(seq(min(20), max(30), by = 2.0),1), name="Critical Thermal Maximum (°C)")

#run model of 2023 without control
c3a <- c3 %>% 
  filter(!Treatment == "control")

#normality test
model1=lm(CTM ~ Site*Treatment+(1|Cage), data=c3a)
Anova(model1)

library(emmeans)
pairs(emmeans(model1, ~Site:Treatment))

model2=lm(CTM ~ Site+Treatment, data=c3a)
Anova(model2)
plot(model2)
hist(c3a$CTM)

#get 2023 mean values for later regression table
ctm2 <- ctm %>% 
  filter(Recovered == "y")
ctm2 <- ctm %>% 
  filter(!Chamber == "P")

ctm.sum <- ctm2 %>% 
  group_by(Site) %>% 
  summarize(mean.CTM = mean(CTM, na.rm = T),
            sd.CTM = sd(CTM, na.rm = T))

ctm.sum

```

New regression with 2019 and 2023 data

```{T  2023}
#call in all CTMs
reg<- read.csv("CTM Regression 2023.csv")

#plot
 ggplot(reg, aes(x = acc.temp, y = mean.ctm, color = loc))+
  geom_smooth(method = "lm", se = F,fullrange=F, size=.5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = mean.ctm - temp.sd, ymax = mean.ctm + temp.sd), width = 0.2)+
    scale_color_manual("Study Location",
                    breaks = c("Field", "Lab"),
                    labels = c("Field", "Lab"),
                    values = c("dodgerblue", "tomato"))+
  geom_point(x = 17, y = 25.4, size = 2.5, shape=1,color = "tomato")+
  geom_errorbar(aes(x = 17, ymin = 25.4 - 1.7, ymax = 25.4 + 1.7), color = "tomato", width = 0.2)+
  geom_point(x = 16.5, y = 26.5, size = 2.2,shape= 15,color = "dodgerblue")+
  geom_errorbar(aes(x = 16.5, ymin = 26.5 - 0.86, ymax = 26.5 + 0.86), color = "dodgerblue", width = 0.2)+
  scale_y_continuous(breaks = round(seq(min(23), max(30), by = 1.0),1), name="Critical Thermal Maximum (°C)")+
  scale_x_continuous(breaks = round(seq(min(12), max(26), by = 2.0),1), name="Acclimation Temperature (°C)")+
  annotate("text", x = 21.5, y = 24, label = "R^2", parse = T)+
  annotate("text", x = 21.5, y = 23.5, label = " P", parse=T)+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(size = 12, colour = "black"),
        axis.text.y = element_text(size = 12,colour = "black"),
        axis.title.x = element_text(size = 14,colour = "black"),
        axis.title.y = element_text(size = 14,colour = "black"), legend.position=c(0.15,0.85))

 #single regression model by temp and study
modr <- lm(mean.ctm ~ acc.temp*loc, data=reg)
summary(modr)
anova(modr)

#separate regression models
field23 <- reg %>% 
  filter(loc == "Field")

lab23 <- reg %>% 
  filter(loc == "Lab")

field.mod23 <- lm(mean.ctm ~ acc.temp, field23)
anova(field.mod23)
summary(field.mod23)

lab.mod23 <- lm(mean.ctm ~ acc.temp, lab23)
anova(lab.mod23)
summary(lab.mod23)

```

### 2023-11-22 smelt_2019_allseasons/Diet 2019.Rmd
Adding biofouling analyses

--- 2022-11-21 smelt_2019_allseasons/Diet 2019.Rmd
@@
 
+#write csv for use in biofouling comparison
+write.csv(diet, "smelt_2019_allseasons/data_clean/Diet.proportions.csv", row.names=FALSE)
+```
+
+```{r}
+
+#plot at the higher taxonomic level
+
+ggplot(diet, aes(x = Tag, y = Count, fill = Prey.Taxa)) +
+  geom_col(position = "fill")+
+  facet_wrap(~Location, scales = "free")
+
+ggplot(diet, aes(x = Location, y = Count, fill = Prey.Taxa)) +
+  geom_col(position = "fill")
+
+preytaxa = group_by(diet, Prey.Taxa) %>%
+  summarize(Count = sum(Count))
+rare = filter(preytaxa, Count <=2)
+
+#clean it up a little
+library(Polychrome)
+pal36 <- palette36.colors(36)
+pal36 <- as.vector(t(pal36))
+
+diet = filter(diet, !Prey.Taxa %in% c('empty', "EMPTY", 'plant matter')) %>%
+  mutate(Prey.Taxa = case_match(Prey.Taxa, c("Culicidae", "Hemiptera") ~ "Insecta",
+                                c("Leydigia sp.", "Alona sp.", "Diaphanosoma sp.", "Eurycercus sp.") ~ "Cladocera",
+                                c("Tropocyclops sp.", "Macrocyclops sp.") ~ "Cyclopoida",
+                                .default = Prey.Taxa))%>%
+
+  mutate(Preytax = factor(Prey.Taxa, levels = c( "Cyclopoida","Acanthocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Halicyclops sp.",  "Mesocyclops sp.", "Calanoida", "Diaptomidae",
+                                                "Eurytemora affinis", "Osphranticum labronectum", "Pseudodiaptomus forbesi", 
+                                                "Harpacticoida", "Sinocalanus doerrii","Cladocera",  "Bosmina sp.", 
+                                                "Ceriodaphnia sp.", "Chydoridae", "Chydorus sp.",
+                                                "Daphnia sp.",  
+                                                 "Scapholeberis sp.", "Sida sp.", "Simocephalus sp.",
+                                                "Americorophium sp.", "Crangonyx sp.", "Eogammarus confervicolus",
+                                                "Gammaridea", "Hyallela azteca", "Mysidacea","Insecta",
+                                                 "Chironomidae", "Ostracoda",
+                                                "Cumacea", "Fish","Acari", "Bivalvia")))
+
+ggplot(diet, aes(x = Location, y = Count, fill = Preytax)) +
+  geom_col(position = "fill")+
+  scale_fill_manual(values = pal36, name = "taxa")+
+  theme_bw()+
+  ylab("Relative Diet Proportion")
+
+ggsave("smelt_2019_allseasons/figures/fishdiet.tiff", device = "tiff", width = 10, height =6)
+# 
+# To allow for diets of different sized fish to contribute equally, proportion was calculated by taking the abundance of each taxa divided by the total abundance of all taxa per diet and then averaging across individuals from each enclosure.
+
+dietsummary = group_by(diet, Cage.ID, Location, Tag, tlc) %>%
+  mutate(stomachsum = sum(Count), proportion = Count/stomachsum)
+
+#huh, it doesn't look like anyone added teh zeros in for the other verson... maybe I won't bother.
+
+```
+
+```{r}
 #sum for taxa abundance among individual fish

### 2023-11-22 smelt_2019_allseasons/Zoop 2019.Rmd
Adding biofouling analyses

@@
 caught <- all[!(all$ind_m3==0),]
-biomass = read_csv("zooptaxa.csv")
+biomass = read_csv("data/zooptaxa.csv")
 caught = left_join(caught, biomass) %>%
@@
 ggplot() +
-  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=ind_m3, fill=ID), colour="black", width = .5) +
+  geom_bar(stat = "identity", data=caught, aes (x=MD, y=ind_m3, fill=ID), colour="black", width = .5) +
   facet_wrap(~Location, ncol = 1) +
@@
 ggplot() +
-  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
+  geom_bar(stat = "identity", data=caught, aes (x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
   facet_wrap(~Location, ncol = 1) +
@@
   labs(x = "Date") +
-  labs(y = "Relative Biomass of all Zoop in Sample")+
+  labs(y = "Biomass of all Zoop in Sample")+
   theme(legend.position="right")+
@@
 ggplot() +
-  geom_bar(position = "fill", stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
+  geom_bar( stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
   facet_wrap(~Location, ncol = 1) +
@@
       axis.text.x = element_text(angle = 90))
+
+ggplot() +
+  geom_bar( stat = "identity", data=filter(macro, ID != "Cyclopoid copepodid"), aes(x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
+  facet_wrap(~Location, ncol = 1) +
+  theme_bw() + 
+  scale_fill_manual(values=pal36)+
+  labs(x = "Date") +
+  labs(y = "Relative Abundance of Macrozoop in Sample")+
+  theme(legend.position="right")+
+      theme(axis.text = element_text(size = 12),
+      axis.title = element_text(size = 12),
+      legend.text = element_text(size = 8),
+      legend.title = element_text(size = 10),
+      axis.text.x = element_text(angle = 90))
+
 ```

### 2023-11-22 smelt_2019_allseasons/map_enclosure_sites2019.Rmd
Adding biofouling analyses

---
title: "map_enclosure_sites"
author: "Catarina Pien"
date: '2023-03-16'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(viridis)
library(sf)
library(dplyr)
library(ggplot2)
library(spData)
library(here)
library(readr)
library(janitor)
library(deltamapr)
library(cowplot)
library(ggspatial)

library(here)
library(readxl)
```

```{r}
latlon <- read_excel(here::here("smelt_2019_allseasons", "data_raw", "cage_locations_winterspring.xls"))

stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326)
data("us_states", package = "spData")
California = dplyr::filter(us_states, NAME == "California")
stations_sf_4269 <- st_transform(stations_sf, crs = st_crs(California))
WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
```

```{r}
(smelt_map <- ggplot() +
    geom_sf(data = WW_Watershed_4269, fill = "gray80", colour = "gray80", alpha = 0.8, inherit.aes = FALSE) +
    geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size = 4, color = "black")+
   geom_sf_label(data = stations_sf_4269, aes(label = factor(Location)), inherit.aes = FALSE, size = 4, color = "black",
                 nudge_x = c(-0.06, -0.05, -0.03, -0.025, -.02),
                 nudge_y = c(0.01, -0.03, 0.025, -0.02, 0.02))+
    annotate(geom = "text", x = -121.75, y = 38.10, size = 3.2, label = "Sacramento River", fontface = "italic",angle = 36) +
    annotate(geom = "text", x = -121.62, y = 38.09, size = 3.2, label = "San Joaquin River", fontface = "italic", angle = 10) +
    annotate(geom = "text", x = -121.96, y = 38.07, size = 3.2, label = "Suisun Bay", fontface = "italic") +
    annotate(geom = "text", x = -121.68, y = 38.26, size =3.2 , label = "Liberty Island", fontface = "italic") +
    scale_x_continuous(limits = c(-122.2, -121.45)) +
  scale_y_continuous(limits = c(37.8, 38.4))+
    annotation_north_arrow(location = "tr", which_north = "true",
                           pad_x = unit(.005, "in"), pad_y = unit(0.15, "in"),
                           style = north_arrow_fancy_orienteering) +
    annotation_scale(location = "bl", bar_cols = c("darkgray", "white", "darkgray", "white"), text_cex = 1.1)+
  theme_bw() +
    theme(axis.title = element_blank(),
        axis.text = element_text(size = 13) ,
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 0.5, vjust = 0.5)))
smelt_map
```

```{r}
insetbbox = st_bbox(c(xmin = -122.2, xmax = -121.45, ymax = 37.95, ymin = 38.4), crs = st_crs(4326))
box_sf <- st_as_sfc(insetbbox)

(inset <- ggplot() +
    geom_sf(data = California, fill = "white") +
    geom_sf(data = WW_Delta, colour = "steelblue4", size = 0.3) +
    geom_sf(data = box_sf, fill = NA, color = "red", size = 0.5) +

    theme_bw() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()))
```

```{r}
(gg_inset_map = ggdraw() +
   draw_plot(smelt_map) +
   draw_plot(inset, x = 0.16, y = 0.69, width = 0.26, height = 0.31))
```

```{r}
tiff(filename = here::here("smelt_2019_allseasons",  "figures", "map_sites.tiff"), width = 8, height = 7, units = "in", pointsize = 12, family = "sans", res = 300, compress = "lzw")
gg_inset_map
dev.off()
```

### 2023-11-22 biofouling/clod cards.R

@@ -3,6 +3,7 @@
 library(tidyverse)
 library(lubridate)
 library(readxl)
+library(emmeans)
 
 clods = read_excel("data/clod cards.xlsx")
 
@@ -15,3 +16,26 @@ ggplot(clods, aes(x = treatment, y = diff, fill =as.factor(`Card #`)))+
   scale_fill_brewer(palette = "Dark2", guide = NULL)+
   ylab("Difference in Weight (g)")+
   theme_bw()
+
+
+clods2 = read_excel("data/clod cards.xlsx", sheet = "finalcards") %>%
+  filter(!is.na(treatment)) 
+
+clods2 = mutate(clods2, treatment2 = factor(treatment2, levels = c("outside", "flip", "scrub")),
+                days = case_when(Site == "RV" ~ 7,
+                                 Site == "SM" ~ 6),
+                DiffPerDay = difference/days)
+
+
+ggplot(clods2, aes(x = Site, y = difference, fill = treatment2))+ geom_boxplot()
+ggplot(clods2, aes(x = Site, y = DiffPerDay, fill = treatment2))+ geom_boxplot()
+
+clodlm = lm(DiffPerDay ~ Site+treatment2, data = clods2)
+summary(clodlm)
+pairs(emmeans(clodlm, ~treatment2))
+
+ggplot(clods2, aes(x = Site, y = percentdiff, fill = treatment2))+ geom_boxplot()
+
+clodlm = lm(percentdiff ~ Site+treatment2, data = clods2)
+summary(clodlm)
+pairs(emmeans(clodlm, ~treatment2))

### 2023-11-22 biofouling/water quality.R

@@ -13,6 +13,24 @@ ggplot(survival, aes(x = Site, y = Survival)) + geom_boxplot()
 
 ggplot(survival, aes(x = Treatment, y = Survival, fill = Site)) + geom_boxplot()
 
+#make a prettier version of the plot for the summer-fall habitat report
+survival = mutate(survival, Treatment = factor(Treatment, levels = c("Flip", "Scrub"), 
+                                               labels = c("Exchanged", "Scrubbed")),
+                  Site = factor(Site, levels = c("RV", "SM"), labels = c("Rio Vista", "Belden's Landing")))
+
+
+ggplot(survival, aes(x = Treatment, y = Survival, fill = Site)) + geom_boxplot()+
+  theme_bw()+
+  scale_fill_brewer(palette = "Dark2")
+
+ggplot(survival, aes(x = Cage, y = Survival, fill = Site)) + geom_col()+
+  theme_bw()+
+  facet_wrap(~Treatment, scales = "free_x")+
+  scale_fill_brewer(palette = "Dark2")+
+  theme(legend.position = "bottom")
+
+
+#Test for statistically significant differences
 lm1 = lm(CountwithCTM ~ Treatment+Site, data = survival)
 summary(lm1)
 anova(lm1)
@@ -54,3 +72,61 @@ BDL2 = BDL %>%
   filter(date(DateTime) == ymd("2023-08-31"), Duration == "E") %>%
   mutate(Value2 = case_when(SensorType == "TEMP W" ~ (Value-32)*5/9,
                             TRUE ~ Value))
+
+#################################################################
+#growht data
+
+growth = read_xlsx("data/BiofoulingStudyCageRemovals.xlsx")
+
+
+str(growth)
+hist(growth$Weight)
+hist(growth$ForkLength)
+hist(log(growth$Weight))
+
+#CF = Wb/L^3 * 100 where wb is body weight in mg and L is fork length in mm
+
+
+growth = mutate(growth, Treatment = factor(Treatment, levels = c("Flip", "Scrub"), 
+                                               labels = c("Exchanged", "Scrubbed")),
+                  Site = factor(Location, levels = c("Rio Vista", "Montezuma", "FCCL"), 
+                                labels = c("Rio Vista", "Belden's Landing", "FCCL")),
[…]

### 2023-11-22 smelt_2019_allseasons/continuousWQ.R

@@ -142,9 +142,24 @@ ggplot(WQmean, aes(x = Date, y = MeanValue,
   ylab("Turbidity (FNU)          Temperature (C)             Salinity (PSU)         Dissolved Oxygen (mg/L)")+
   xlab("Date")+
   theme_bw()+
+  theme(axis.text.x = element_text(angle = 45, hjust =1))+
   scale_color_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
   scale_fill_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
   geom_hline(data = cuttoffs, aes(yintercept = cuttoff, linetype = Type), 
              color = "red")
 
 ggsave("plots/ContWaterQuality.tiff", device = "tiff", width =8, height =7)
+
+#Summary statistics
+
+cagechecks2019 <- read_csv("smelt_2019_winterspring/data_raw/2019_smeltstudy_dailycheck_data.csv")
+
+sumstast = group_by(cagechecks2019, Location) %>%
+  summarize(SpConda = mean(SpCond), maxSC = max(SpCond), minSC = min(SpCond),
+            DOa = mean(DO), minDO = min(DO), maxDO = max(DO),
+            pHa = median(pH), minnpH = min(pH), maxpH = max(pH),
+            minSecchi = min(Secchi, na.rm =T), maxSecchi = max(Secchi, na.rm =T),
+            MinTemp = min(WaterTemp), MaxTemp = max(WaterTemp),
+            WaterTemp = mean(WaterTemp), 
+            Secchia = mean(Secchi, na.rm =T),
+            Turbiditya = mean(AvgTurb), MaxTurb = max(AvgTurb), MinTurb = min(AvgTurb))

### 2023-12-19 smelt_2019_allseasons/Zoop 2019.Rmd
Adding biofowling analysis

@@
 zoopdietlong = pivot_longer(zoopdiet, cols = c(Ostracod, Cyclopoid, Calanoid, Cladocera, Harpacticoid, Other, Amphipod, Diptera),
-                            names_to = "Taxa", values_to= "count")
+                            names_to = "Taxa", values_to= "count") %>%
+  mutate(Location = case_when(Location == "DWSC" ~ "SDWSC",
+                              Location == "RV" ~ "Rio Vista",
+                              Location == "SM" ~ "Suisun Marsh",
+                              Location == "YB" ~ "Yolo Bypass"))
 
 zoopnos = group_by(zoopdiet, datatype, Season, Location) %>%
-  summarize(N = length(unique(SampleID)))
+  summarize(N = length(unique(SampleID))) %>%
+  mutate(Location = case_when(Location == "DWSC" ~ "SDWSC",
+                              Location == "RV" ~ "Rio Vista",
+                              Location == "SM" ~ "Suisun Marsh",
+                              Location == "YB" ~ "Yolo Bypass"))
 

### 2023-12-19 smelt_2019_allseasons/map_enclosure_sites2019.Rmd
Adding biofowling analysis

@@
 
-stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326)
+stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326) %>%
+  mutate(Location = case_when(Location == "SRDWSC" ~ "SDWSC",
+                              TRUE ~ Location))
 data("us_states", package = "spData")

### 2023-12-19 biofouling/clod cards.R

@@ -21,14 +21,24 @@ ggplot(clods, aes(x = treatment, y = diff, fill =as.factor(`Card #`)))+
 clods2 = read_excel("data/clod cards.xlsx", sheet = "finalcards") %>%
   filter(!is.na(treatment)) 
 
-clods2 = mutate(clods2, treatment2 = factor(treatment2, levels = c("outside", "flip", "scrub")),
-                days = case_when(Site == "RV" ~ 7,
-                                 Site == "SM" ~ 6),
+clods2 = mutate(clods2, treatment2 = factor(treatment2, levels = c("outside", "flip", "scrub"),
+                                            labels = c("External", "Exchanged", "Scrubbed")),
+                                            Site = factor(Site, levels = c("RV", "SM"),
+                                                                labels = c("Rio Vista", "Belden's Landing")),
+                days = case_when(Site == "Rio Vista" ~ 7,
+                                 Site == "Belden's Landing" ~ 6),
                 DiffPerDay = difference/days)
 
 
 ggplot(clods2, aes(x = Site, y = difference, fill = treatment2))+ geom_boxplot()
 ggplot(clods2, aes(x = Site, y = DiffPerDay, fill = treatment2))+ geom_boxplot()
+
+ggplot(clods2, aes(x = treatment2, y = DiffPerDay, fill = Site)) +
+  geom_boxplot()+
+  scale_fill_brewer(palette = "Dark2")+
+  theme_bw() + ylab("Loss of Weight per Day (g)")+xlab(NULL)
+
+ggsave("plots/clodcards.tiff", device = "tiff", width =6, height =5)
 
 clodlm = lm(DiffPerDay ~ Site+treatment2, data = clods2)
 summary(clodlm)
@@ -39,3 +49,14 @@ ggplot(clods2, aes(x = Site, y = percentdiff, fill = treatment2))+ geom_boxplot(
 clodlm = lm(percentdiff ~ Site+treatment2, data = clods2)
 summary(clodlm)
 pairs(emmeans(clodlm, ~treatment2))
+
+
+clodlm = lm(percentdiff ~ Site+treatment2, data = filter(clods2, treatment2 != "outside"))
+summary(clodlm)
+pairs(emmeans(clodlm, ~treatment2))
+
+library(cder)
+
[…]

### 2023-12-19 biofouling/growthCondition.R

@@ -1,0 +1,102 @@
+
+#################################################################
+#growht data
+library(tidyverse)
+library(lubridate)
+library(readxl)
+growth = read_xlsx("data/BiofoulingStudyCageRemovals.xlsx")
+
+
+str(growth)
+hist(growth$Weight)
+hist(growth$ForkLength)
+hist(log(growth$Weight))
+
+#CF = Wb/L^3 * 100 where wb is body weight in mg and L is fork length in mm
+
+
+growth = mutate(growth, Treatment = factor(Treatment, levels = c("Flip", "Scrub"), 
+                                           labels = c("Exchanged", "Scrubbed")),
+                Site = factor(Location, levels = c("Rio Vista", "Montezuma", "FCCL"), 
+                              labels = c("Rio Vista", "Belden's Landing", "FCCL")),
+                Condition = Weight*1000/(ForkLength^3)*100)
+
+ggplot(growth, aes(x = Treatment, fill = Site, y = ForkLength))+ geom_boxplot()+
+  theme_bw()+
+  scale_fill_brewer(palette = "Dark2")+
+  theme(legend.position = "bottom")+
+  ylab("Fork Length (mm)")
+
+ggplot(growth, aes(x = Treatment, fill = Site, y = Weight))+ geom_boxplot()+
+  theme_bw()+
+  scale_fill_brewer(palette = "Dark2")+
+  theme(legend.position = "bottom")+
+  ylab("Weight (g)")
+
+ggplot(growth, aes(x = Treatment, fill = Site, y = Condition))+ geom_boxplot()+
+  theme_bw()+
+  scale_fill_brewer(palette = "Dark2")+
+  theme(legend.position = "bottom")+
+  ylab("Condition Factor")
+
+
+g1 = lm(Weight ~ Location + Treatment, data = growth)
+summary(g1)
+plot(g1)
+
+g2 = lm(ForkLength ~ Location + Treatment, data = growth)
+summary(g2)
+plot(g2)
+
+
+g2 = lm(Condition~ Location + Treatment, data = growth)
+summary(g2)
+plot(g2)
+
+#######################################################################
+#now for lab data
+
+labgrowth = read_excel("data/BiofoulingStudy_FishDissections.xlsx")
+
+
+#CF = Wb/L^3 * 100 where wb is body weight in mg and L is fork length in mm
+
+
[…]

### 2023-12-19 biofouling/water quality.R

@@ -72,61 +72,3 @@ BDL2 = BDL %>%
   filter(date(DateTime) == ymd("2023-08-31"), Duration == "E") %>%
   mutate(Value2 = case_when(SensorType == "TEMP W" ~ (Value-32)*5/9,
                             TRUE ~ Value))
-
-#################################################################
-#growht data
-
-growth = read_xlsx("data/BiofoulingStudyCageRemovals.xlsx")
-
-
-str(growth)
-hist(growth$Weight)
-hist(growth$ForkLength)
-hist(log(growth$Weight))
-
-#CF = Wb/L^3 * 100 where wb is body weight in mg and L is fork length in mm
-
-
-growth = mutate(growth, Treatment = factor(Treatment, levels = c("Flip", "Scrub"), 
-                                               labels = c("Exchanged", "Scrubbed")),
-                  Site = factor(Location, levels = c("Rio Vista", "Montezuma", "FCCL"), 
-                                labels = c("Rio Vista", "Belden's Landing", "FCCL")),
-                Condition = Weight*1000/(ForkLength^3)*100)
-
-ggplot(growth, aes(x = Treatment, fill = Site, y = ForkLength))+ geom_boxplot()+
-  theme_bw()+
-  scale_fill_brewer(palette = "Dark2")+
-  theme(legend.position = "bottom")+
-  ylab("Fork Length (mm)")
-  
-ggplot(growth, aes(x = Treatment, fill = Site, y = Weight))+ geom_boxplot()+
-  theme_bw()+
-  scale_fill_brewer(palette = "Dark2")+
-  theme(legend.position = "bottom")+
-  ylab("Weight (g)")
-
-ggplot(growth, aes(x = Treatment, fill = Site, y = Condition))+ geom_boxplot()+
-  theme_bw()+
-  scale_fill_brewer(palette = "Dark2")+
-  theme(legend.position = "bottom")+
-  ylab("Condition Factor")
-
-
-g1 = lm(Weight ~ Location + Treatment, data = growth)
-summary(g1)
-plot(g1)
-
-g2 = lm(ForkLength ~ Location + Treatment, data = growth)
-summary(g2)
-plot(g2)
-
-
-g2 = lm(Condition~ Location + Treatment, data = growth)
-summary(g2)
-plot(g2)
-
-
-library(wql)
-ECs = c(100, 2000, 8000, 12000)
-
-salinity = ec2pss(ECs/1000, t= 25)

### 2023-12-19 smelt_2019_allseasons/continuousWQ.R

@@ -87,7 +87,8 @@ ggplot(WQmean, aes(x = Date, y = MeanValue,
   scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
   geom_hline(data = cuttoffs, aes(yintercept = cuttoff, linetype = Type), 
-             color = "red")
+             color = "red")+
+  scale_linetype_manual(values = c(1,3,5))
 
 ###################################################################
 #Try again with all stations on all dates
@@ -146,7 +147,9 @@ ggplot(WQmean, aes(x = Date, y = MeanValue,
   scale_color_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
   scale_fill_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
   geom_hline(data = cuttoffs, aes(yintercept = cuttoff, linetype = Type), 
-             color = "red")
+             color = "red")+
+  scale_linetype_manual(values = c(1,3,5))
+
 
 ggsave("plots/ContWaterQuality.tiff", device = "tiff", width =8, height =7)
 

### 2023-12-19 smelt_2019_allseasons/analyze_growth.Rmd

@@
 ```{r}
-hist(Summer$FL_cm_Pre)
-hist(filter(Summer, Site=="RV")$FL_cm_Post)
-hist(Summer$Weight_g_Pre)
-hist(filter(Summer, Site=="RV")$Weight_g_Post)
+ggplot(filter(Summer, Site == "FCCL")) + 
+  geom_histogram(aes(FL_cm, color = Period, alpha = 0.5, fill = Period), binwidth = 0.2) +
+  facet_wrap(~Period, nrow = 2)
+ggplot(filter(Summer, Site == "FCCL")) + 
+  geom_histogram(aes(Weight_g, fill = Period, alpha = 0.5, color = Period)) +
+  facet_wrap(~Period, nrow = 2)
+ggplot(filter(Summer, Site == "FCCL")) + 
+  geom_histogram(aes(K, fill = Period, alpha = 0.5, color = Period)) +
+  facet_wrap(~Period, nrow = 2)
+
+ggplot(filter(Summer, Site == "RV")) + 
+  geom_histogram(aes(FL_cm))
+ggplot(filter(Summer, Site == "RV")) + 
+  geom_histogram(aes(Weight_g))
 
@@
 
-hist(Fall$FL_cm)
-hist(Fall$Weight_g)
-hist(Fall$K)
+ggplot(filter(Fall, Site == "FCCL")) + 
+  geom_histogram(aes(FL_cm, color = Period, alpha = 0.5, fill = Period), binwidth = 0.2) +
+  facet_wrap(~Period, nrow = 2)
+ggplot(filter(Fall, Site == "FCCL")) + 
+  geom_histogram(aes(Weight_g, fill = Period, alpha = 0.5, color = Period)) +
+  facet_wrap(~Period, nrow = 2)
 
@@
     geom_hline(yintercept = 0, linetype = "dashed") + 
+     annotate(geom = "text", x = 3.2, y = 0.1, label = "B", size = 8) +
   geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
   viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
-  labs(y = "Proportional Change in K (g cm^-2) with 95% Confidence Intervals") +
+  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
   theme_bw() +
@@
 
-(plot_season_wt <- ggplot(data = letter_m2,) + 
+(plot_season_wt <- ggplot(data = letter_m2) + 
    geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
@@
     geom_hline(yintercept = 0, linetype = "dashed") + 
+     annotate(geom = "text", x = 3.2, y = 0.24, label = "A", size = 8) +
     viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
-  labs(y = "Proportional Change in Weight (g) with 95% Confidence Intervals") +
+  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
   theme_bw() +
@@
     geom_hline(yintercept = 0, linetype = "dashed") + 
+        annotate(geom = "text", x = 4.1, y = -0.005, label = "D", size =8) +
   geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
   viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
-  labs(y = "Change in K (g cm^-2) with 95% Confidence Intervals") +
+  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
   theme_bw() +
@@
     geom_hline(yintercept = 0, linetype = "dashed") + 
+    annotate(geom = "text", x = 4.1, y = -0.02, label = "C", size = 8) +
     viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
-  labs(y = "Change in Weight (g) with 95% Confidence Intervals") +
+  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
   theme_bw() +
@@
 plot_Site_wt & plot_Site_k
+dev.off()
+```
+
+##### Both season and site
+```{r}
+library(patchwork)
+png(filename = "smelt_2019_allseasons/figures/model_season_site.png", height = 8, width = 8,units = "in", 
+    res = 300, pointsize = 12, family = "sans")
+(plot_season_wt & plot_season_k) / (plot_Site_wt & plot_Site_k)
 dev.off()

### 2024-03-26 biofouling/bugs.R
Integrated zooplankton and diet data.

@@ -1,0 +1,241 @@
+#look at thte biofoulidng data because I can't help myself
+
+library(readxl)
+library(tidyverse)
+library(lubridate)
+
+amphipods = read_excel("data/DWR_CageZoop2023_Complete_TEC_1.22.2024.xlsx",
+                       sheet = "Amph Data")
+ggplot(amphipods, aes(x = Location, y = count, fill = Species)) + geom_col()
+
+treatments = data.frame(Location = c("Cage 1", "Cage 2", "Cage 3", "Cage 4",
+                                     "Cage 5", "Cage 6", "Cage 7", "Cage 8"),
+                        Treatment = c("Flip", "Scrub", "Flip", "Scrub",
+                                      "Flip", "Scrub", "Flip", "Scrub"))
+amphipods = left_join(amphipods, treatments)
+
+ggplot(amphipods, aes(x = Location, y = count, fill = Species)) + geom_col()+
+  facet_wrap(Site~Treatment, scales = "free_x")
+
+
+#amphipod community matrix
+
+amphwide = pivot_wider(amphipods, id_cols = c(Location, Date, Site), names_from = Species, values_from = total_count,
+                       values_fn = sum, values_fill =0)
+
+###################################################################
+
+
+zoops = read_excel("data/DWR_CageZoop2023_Complete_TEC_1.22.2024.xlsx",
+                       sheet = "Zoop Data") 
+
+zoops = mutate(zoops, InOut = case_when(str_detect(Location, "Outside") ~ "Outside",
+                                        str_detect(Location, "Inside") ~ "Inside"),
+               CageNum = str_sub(Location, 1, 6)) %>%
+  left_join(treatments, by = c("CageNum" = "Location")) %>%
+  mutate(Treatment = case_when(InOut == "Outside" ~ "Outside",
+                               TRUE ~ Treatment),
+         Week = week(Date),
+         SampleID = paste(CageNum, Date, InOut))
+
+#this is misleading....
+ggplot(zoops, aes(x = CageNum, y = Count, fill = `Species Name`)) + geom_col()+
+  facet_wrap(Site~Treatment, scales = "free_x")
+
[…]

### 2024-03-26 biofouling/clod cards.R

@@ -23,8 +23,8 @@ clods2 = read_excel("data/clod cards.xlsx", sheet = "finalcards") %>%
 
 clods2 = mutate(clods2, treatment2 = factor(treatment2, levels = c("outside", "flip", "scrub"),
                                             labels = c("External", "Exchanged", "Scrubbed")),
-                                            Site = factor(Site, levels = c("RV", "SM"),
-                                                                labels = c("Rio Vista", "Belden's Landing")),
+                                            Site = factor(Site, levels = c( "SM", "RV"),
+                                                                labels = c( "Belden's Landing","Rio Vista")),
                 days = case_when(Site == "Rio Vista" ~ 7,
                                  Site == "Belden's Landing" ~ 6),
                 DiffPerDay = difference/days)
@@ -35,13 +35,16 @@ ggplot(clods2, aes(x = Site, y = DiffPerDay, fill = treatment2))+ geom_boxplot()
 
 ggplot(clods2, aes(x = treatment2, y = DiffPerDay, fill = Site)) +
   geom_boxplot()+
-  scale_fill_brewer(palette = "Dark2")+
-  theme_bw() + ylab("Loss of Weight per Day (g)")+xlab(NULL)
+  scale_fill_manual(values = c("#1B9E77" , "#7570B3"))+ 
+  ylab("Loss of Weight per Day (g)")+xlab(NULL)+
+  theme(legend.position = "bottom")
 
-ggsave("plots/clodcards.tiff", device = "tiff", width =6, height =5)
+ggsave("plots/clodcards.tiff", device = "tiff", width =4, height =5)
 
 clodlm = lm(DiffPerDay ~ Site+treatment2, data = clods2)
 summary(clodlm)
+plot(clodlm)
+hist(residuals(clodlm))
 pairs(emmeans(clodlm, ~treatment2))
 summary(aov(clodlm))
 ggplot(clods2, aes(x = Site, y = percentdiff, fill = treatment2))+ geom_boxplot()

### 2024-03-26 biofouling/growthCondition.R

@@ -15,17 +15,20 @@ hist(log(growth$Weight))
 #CF = Wb/L^3 * 100 where wb is body weight in mg and L is fork length in mm
 
 
-growth = mutate(growth, Treatment = factor(Treatment, levels = c("Flip", "Scrub"), 
-                                           labels = c("Exchanged", "Scrubbed")),
-                Site = factor(Location, levels = c("Rio Vista", "Montezuma", "FCCL"), 
-                              labels = c("Rio Vista", "Belden's Landing", "FCCL")),
+growth = mutate(growth, Treatment =factor(Treatment, levels = c("Control", "Flip", "Scrub"), 
+                                           labels = c("Control", "Exchanged", "Scrubbed")),
+                Site = factor(Location, levels = c( "Montezuma", "FCCL","Rio Vista"), 
+                              labels = c( "Belden's Landing","FCCL","Rio Vista" )),
+                Treatment = case_when(is.na(Treatment) ~ "Control",
+                                      TRUE ~ Treatment),
                 Condition = Weight*1000/(ForkLength^3)*100)
 
 ggplot(growth, aes(x = Treatment, fill = Site, y = ForkLength))+ geom_boxplot()+
   theme_bw()+
   scale_fill_brewer(palette = "Dark2")+
   theme(legend.position = "bottom")+
-  ylab("Fork Length (mm)")
+  ylab("Fork Length (mm)")+
+  coord_cartesian(ylim = c(35,75))
 
 ggplot(growth, aes(x = Treatment, fill = Site, y = Weight))+ geom_boxplot()+
   theme_bw()+
@@ -64,15 +67,17 @@ labgrowth = read_excel("data/BiofoulingStudy_FishDissections.xlsx")
 
 labgrowth = mutate(labgrowth, Treatment = factor(Treatment, levels = c("Control", "Flip", "Scrub"), 
                                            labels = c("Control", "Exchanged", "Scrubbed")),
-                Site = factor(Location, levels = c("Rio Vista", "Montezuma", "FCCL"), 
-                              labels = c("Rio Vista", "Belden's Landing", "FCCL")),
+                Site = factor(Location, levels = c( "Montezuma", "FCCL","Rio Vista"), 
+                              labels = c( "Belden's Landing","FCCL","Rio Vista" )),
[…]

### 2024-03-26 biofouling/water quality.R

@@ -7,6 +7,10 @@ library(readxl)
 #look at the survival data
 survival = read_excel("data/BiofoulingStudy_Survival.xlsx", sheet = "Data")
 
+FCCl = data.frame(Treatment = "Control", Site = "FCCL", Cage = "FCCL", Survival = 21/24)
+
+survival = bind_rows(survival, FCCl)
+
 ggplot(survival, aes(x = Treatment, y = Survival))+ geom_boxplot()
 
 ggplot(survival, aes(x = Site, y = Survival)) + geom_boxplot()
@@ -14,9 +18,9 @@ ggplot(survival, aes(x = Site, y = Survival)) + geom_boxplot()
 ggplot(survival, aes(x = Treatment, y = Survival, fill = Site)) + geom_boxplot()
 
 #make a prettier version of the plot for the summer-fall habitat report
-survival = mutate(survival, Treatment = factor(Treatment, levels = c("Flip", "Scrub"), 
-                                               labels = c("Exchanged", "Scrubbed")),
-                  Site = factor(Site, levels = c("RV", "SM"), labels = c("Rio Vista", "Belden's Landing")))
+survival = mutate(survival, Treatment = factor(Treatment, levels = c("Control", "Flip", "Scrub"), 
+                                               labels = c("Control", "Exchanged", "Scrubbed")),
+                  Site = factor(Site, levels = c("SM","FCCL","RV"), labels = c("Belden's Landing","FCCL","Rio Vista")))
 
 
 ggplot(survival, aes(x = Treatment, y = Survival, fill = Site)) + geom_boxplot()+
@@ -27,7 +31,8 @@ ggplot(survival, aes(x = Cage, y = Survival, fill = Site)) + geom_col()+
   theme_bw()+
   facet_wrap(~Treatment, scales = "free_x")+
   scale_fill_brewer(palette = "Dark2")+
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom")+
+  coord_cartesian(ylim = c(0,1))
 
 
 #Test for statistically significant differences
@@ -66,9 +71,15 @@ ggplot(env, aes(x = as.factor(Date), y = Turb, color = InsideOutside))+
   facet_wrap(~Location)
 
 
-BDL = cdec_query("BDL", c(25, 27, 100, 62, 221), start.date = ymd("2023-08-30"),
-                 end.date = ymd("2023-09-01"))
[…]

### 2024-03-26 recaptureanalysis/recaps.Rmd
Recapture analysis stuff

--- 2023-03-06 recaps.Rmd
@@
 library(deltamapr)
-load("Recaps.RData")
+#load("Recaps.RData")
+#save(nndist, distances, recaps, recaps2, recaps3, RVhdist, SCsoft, SChard, RVhdistx, Dwschard, Dwscsoft, file = "Recaps.RData")
 ```
@@
 
-Fist let's calcualte distance from release location to recapture location.
+Fist let's calculate distance from release location to recapture location.
 
@@
 
-recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft.xlsx", 
-                    sheet = "Adult Recaptures") %>%
-  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`)
-recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
-                Type = case_when(Type == "header" ~ "Soft",
+recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
+                    sheet = "Delta Smelt Catch Data") %>%
+  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`) %>%
+  mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
+  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode, -Dateknown)
+
+#bring in standaridized release location/mark info
+release = read_excel("data/releases_v2.xlsx") %>%
+  rename(LatitudeR = Latitude, LongitudeR = Longitude)
+
+recaps2 = left_join(recaps, select(release, -TotalReleased), by = "ReleaseEvent") %>%
+  mutate(DaysSinceRelease = SampleDate - ReleaseDate,
+         Type = case_when(ReleaseMethod == "Unknown" ~ "Unknown",
+                          ReleaseMethod == "NA" ~ "Wild/unmarked",
                           TRUE ~ Type))
+
 str(recaps)
@@
 ```{r}
+releasesf = st_as_sf(filter(release, !is.na(LatitudeR)),  coords = c("LongitudeR", "LatitudeR"), crs = 4326)
 
-recapsf = st_as_sf(filter(recaps, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)
+#make a spatial data frame of recaptures
 
-#Now make a data frame of the release locations
-release = data.frame(Site = c("SDWSC", "SDWSC", "Rio Vista", "Rio Vista"), Type = c("Soft", "Hard", "Hard", "Hard (Trailer)"),
-                     Latitude = c(38.237842, 38.275563, 38.124736, 38.139752), 
-                     Longitude = c(-121.673802, -121.661374, -121.699521, -121.694706)) 
-releasesf = st_as_sf(release,  coords = c("Longitude", "Latitude"), crs = 4326)
-
-#merge recap points with release points
-
-recaps2 = left_join(recaps, release)
+recapsf = st_as_sf(filter(recaps2, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)
 
@@
 #one release at a time
-Dwschard = filter(recaps2, Type == "Hard", Site == "SDWSC")
-dwsch = filter(release, Site == "SDWSC", Type == "Hard") %>%
-  select(Latitude, Longitude)
+Dwschard = filter(recaps2, Type == "Hard (carboy)", Site == "SDWSC")
+dwsch = filter(release, Site == "SDWSC", Type == "Hard (carboy)") %>%
+  select(LatitudeR, LongitudeR) %>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR)
 tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
-               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwsch)
+               Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = dwsch)
 
 #now let's do DWSC soft
-Dwscsoft = filter(recaps2, Type == "Soft", Site == "SDWSC")
-dwscs = filter(release, Site == "SDWSC", Type == "Soft") %>%
-  select(Latitude, Longitude)
+Dwscsoft = filter(recaps2, Type == "Soft (carboy)", Site == "SDWSC")
+dwscs = filter(release, Site == "SDWSC", Type == "Soft (carboy)") %>%
+  select(LatitudeR, LongitudeR)%>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR)
 tesst2 = GGdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
-               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwscs)
+               Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = dwscs)
 
 #now let's do Rio Vista hard
-RVhard = filter(recaps2, Type == "Hard", Site == "Rio Vista", !is.na(Latitude))
-rvh = filter(release, Site == "Rio Vista", Type == "Hard") %>%
-  select(Latitude, Longitude)
+RVhard = filter(recaps2,  Site == "Rio Vista", !is.na(Latitude))
+rvh = filter(release, Site == "Rio Vista", Type == "Hard (trailer)") %>%
+  select(LatitudeR, LongitudeR)%>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
+  distinct()
 tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
-                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvh)
+                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = rvh)
 
-#now the trailer
-RVhardt = filter(recaps2, Type == "Hard (Trailer)", Site == "Rio Vista")
-rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
-  select(Latitude, Longitude)
-tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
-                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvht)
+# #now the trailer
+# RVhardt = filter(recaps2, Type == "Hard (Trailer)", Site == "Rio Vista")
+# rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
+#   select(LatitudeR, LongitudeR)%>%
+#   rename(Latitude = LatitudeR, Longitude = LongitudeR)
+# tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
+#                 Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvht)
 
-distances = bind_rows(tesst, tesst2, tesst3, tesst4)
+distances = bind_rows(tesst, tesst2, tesst3)
 ```
@@
 recaps3 = left_join(recaps2, distances) %>%
+  mutate(Type2 = case_when(Type %in% c("Hard (large scale)","Hard (trailer)") ~ "Hard (Large Scale)",
+                           TRUE ~ Type)) %>%
   mutate(SiteType = paste(Type, Site))
@@
 recaps3
+
+#load first flush info
+ff = read_excel("data/releases_v2.xlsx", sheet = "firstflush")
+
+recaps3 = recaps3 %>%
+  mutate(Year = year(SampleDate),
+                                BroodYear = case_when(LifeStage %in% c("Adult", "Adult*") & yday(SampleDate) <200 ~ Year-1,
+                                     LifeStage == "Juvenile" & yday(SampleDate) <90 ~ Year-1,
+                                     TRUE ~ Year)) %>%
+         left_join(ff)%>%
+         mutate(FFyn = case_when(ReleaseDate > FirstFlush ~ "Yes",
+                          TRUE ~ "No"))
+
+write.csv(recaps, "recaptureanalysis/Recapturedistances.csv")
 ```
 
-Plot to visually look at mean and variatoin.
+Plot to visually look at mean and variation.
 
 ```{r}
-ggplot(recaps3, aes(x = SiteType, y = Distance))+ geom_boxplot(aes(fill = Type))+
+ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = SiteType, y = Distance))+ 
+  geom_boxplot(aes(fill = SiteType))+
   ylab("Distance from Release Site (m)")+
+  scale_fill_discrete(guide = NULL)+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))
+```
+now by first flush
+
+```{r}
+
+ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = Type, y = Distance))+ 
+  geom_boxplot(aes(fill = SiteType))+
+  ylab("Distance from Release Site (m)")+
+  scale_fill_discrete(guide = NULL)+
+  theme_bw()+
+  facet_wrap(~FFyn)+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))
+
+```
+
+Let's consolidate some of the release types...
+
+```{r}
+
+tots = group_by(recaps3, Type2) %>%
+  summarize(N = n())
+
+ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = Type2, y = Distance/1000))+ 
+  geom_boxplot(aes(fill = Type2))+
+  ylab("Distance from Release Site (km)")+
+  scale_fill_discrete(guide = NULL)+
+  geom_text(data = filter(tots, Type2 != "Wild/unmarked", Type2 != "Unknown"), aes(x = Type2, label = N), y=2, inherit.aes = FALSE)+ xlab(NULL)+
+    stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
   theme_bw()
+
+ggsave("plots/hardvsoft_distance.tiff", device = "tiff", width =6, height =4)
+
+totsby = group_by(recaps3, Type2, BroodYear) %>%
+  summarize(N = n())
+
+ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = Type2, y = Distance/1000))+ 
+  geom_boxplot(aes(fill = Type2))+
+  ylab("Distance from Release Site (km)")+
+  scale_fill_discrete(guide = NULL)+
+  geom_label(data = filter(totsby, Type2 != "Wild/unmarked", Type2 != "Unknown"), 
+             aes(x = Type2, label = paste("N=", N)), y=2, inherit.aes = FALSE)+ xlab(NULL)+
+    stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
+  facet_wrap(~BroodYear)+
+  theme_bw()
+
+ggsave("plots/hardvsoft_distance_BY.tiff", device = "tiff", width =6, height =4)
+
+```
+
+```{r}
+library(ggbeeswarm)
+
+ggplot(filter(recaps3, Type != "Wild/unmarked"), aes(x = Type2, y = Distance))+ 
+  geom_quasirandom(aes(color = as.factor(BroodYear), shape = Site))+
+  ylab("Distance from Release Site (m)")+
+  facet_wrap(~FFyn)+
+  scale_fill_discrete(guide = NULL)+
+  theme_bw()
+
+```
+```{r}
+
+ggplot(filter(recaps3, Type != "Wild", BroodYear != 2024), aes(x = Type2, y = Distance))+ 
+  geom_quasirandom(aes(color = Type, shape = Site))+
+  ylab("Distance from Release Site (m)")+
+  scale_fill_discrete(guide = NULL)+
+  facet_wrap(~BroodYear)+
+
+  theme_bw()
+
+```
+```{r}
+
+tots2023 = filter(recaps3, Type != "Wild/unmarked", BroodYear == 2023) %>%
+  group_by(Type) %>%
+  summarize(N = n()) %>%
+  droplevels()
+
+test23 = filter(recaps3, Type != "Wild/unmarked", BroodYear == 2023, !is.na(Distance)) %>%
+  droplevels()
+
+ggplot(test23, aes(x = Type, y = Distance))+ 
+  geom_boxplot(aes(fill = Type))+
+  ylab("Distance from Release Site (m)")+
+  scale_fill_discrete(guide = NULL)+
+  geom_label(data = tots2023, aes(x = Type, label = paste("N=", N)), y=5000, inherit.aes = FALSE)+
+  theme_bw()
+
 ```
@@
 recapsum
+```
+
+```{r}
+
+#ANOVA of differences in distance by release group
+library(emmeans)
+m1 = lm(Distance ~ Type, data = recaps3)
+summary(m1)
+anova(m1)
+emmeans(m1, pairwise ~ Type)
+plot(emmeans(m1, pairwise ~ Type), comparisons = T)
+
+#meh
+
+```
+
+Can cobine Trailer and Large-Scale
+Keep carboys seperate
+ONly one soft release type
+
+Keep the years togetehr or seperate?
+
+Look at the timing of releases versus number of recaptures. Nov-Dec versus Jan-feb
+- Is this all just turbidity? Just at release? or long-term? Pre versus post 'first flush'. We have  a regulatory trigger for when first flush begins. 
+- Not all fish are exactly the same age, but they try and realease them all at about the same age, so ones released in November were spawned earlier. 
+- Still, check days post hatch
+
+Compare CPUE from EDSM and Salvage
+
+Get data on number released at each event
+
+Soft release in Rio vista in 2022? Check release numbers and timing.
+
+```{r}
+
+#ANOVA of differences in distance by release event
+m1.1 = lm(Distance ~ ReleaseEvent, data = recaps3)
+summary(m1.1)
+anova(m1.1)
+emmeans(m1.1, pairwise ~ ReleaseEvent)
+plot(emmeans(m1.1, pairwise ~ ReleaseEvent), comparisons = T)
+
+#It's a bit of a mess.
+
+```
+
+Plot of distance to recapture over time by release type
+
+```{r}
+
+ggplot(recaps3, aes(x = as.numeric(DaysSinceRelease), y = Distance, color = Type))+
+  geom_point()+ geom_smooth(method = "lm")+ ylab("Distance from Release Site (m)")+
+  xlab("Days since release")
+
+```
+
+Plot of distance to recapture over time by release site
+
+```{r}
+
+ggplot(filter(recaps3, Type == "Hard"), aes(x = as.numeric(DaysSinceRelease), y = Distance, color = Site))+
+  geom_point()+ geom_smooth(method = "lm")+ ylab("Distance from Release Site (m)")+
+  xlab("Days since release")
+
+```
+
+Do we see more recaptures per released fish during different types of releases?
+
+```{r}
+
+recaps4 = group_by(recaps3, ReleaseEvent, ReleaseDate, Site, Type, Type2, BroodYear) %>%
+  summarize(N = n())
+
+releasestat = left_join(release, recaps4) %>%
+  filter(Type != "Unknown") %>%
+  mutate(BroodYear = as.numeric(str_sub(ReleaseEvent, 3L, end = 6L))) %>%
+  left_join(ff) %>%
+  mutate(recapsN = case_when(is.na(N) ~0,
+                             TRUE ~N),
+         RecapRate = recapsN/TotalReleased,
+         FFyn = case_when(ReleaseDate > FirstFlush ~ "After First Flush",
+                          TRUE ~ "Before First Flush"),
+         Type2 = case_when(Type == "Hard (trailer)" ~ "Hard (large scale)",
+                           TRUE ~ Type))
+
+totsr = group_by(releasestat, Type2, FFyn) %>%
+  summarize(N = n())
+
+ggplot(releasestat, aes(x = Type2, y = RecapRate*100, fill = Type2))+
+  geom_boxplot()+
+  facet_wrap(~FFyn)+
+  ylab("Percentage Recaptured")+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
+        legend.position = "none")+
+  xlab(NULL)+
+  geom_label(data = totsr, aes(x = Type2, label = paste("N=",N)), y = 0, inherit.aes = FALSE)
+
+ggsave("plots/firstflush.tiff", device = "tiff", width =8, height =5)
+
+ggplot(releasestat, aes(x = Type, y = RecapRate*100, color = Type))+
+  geom_quasirandom()+
+  ylab("Percentage Recaptured")
 
@@
 
-RVhdist = Waterdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
-                    Longitude_column = `Longitude`, PointID_column = fishID)
+distances = list(NA)
 
-RVhdistx = Waterdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
-                    Longitude_column = `Longitude`, PointID_column = fishID)
+releasex = filter(release, ReleaseEvent %in% unique(recaps3$ReleaseEvent))
+for(i in 1:nrow(releasex)) {
+  points = filter(recaps3, ReleaseEvent == releasex$ReleaseEvent[i])
+  distances[[i]] = Waterdist(Water_map = spacetools::Delta, Points = points, Latitude_column = `Latitude`,
+                    Longitude_column = `Longitude`, PointID_column = FishID)
+  names(distances[[i]]) = releasex$ReleaseEvent[i]
 
-SCsoft  = Waterdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
-                       Longitude_column = `Longitude`, PointID_column = fishID)
+}
 
-SChard = Waterdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
-                   Longitude_column = `Longitude`, PointID_column = fishID)
+# RVhdist = Waterdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
+#                     Longitude_column = `Longitude`, PointID_column = fishID)
+# 
+# RVhdistx = Waterdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
+#                     Longitude_column = `Longitude`, PointID_column = fishID)
+# 
+# SCsoft  = Waterdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
+#                        Longitude_column = `Longitude`, PointID_column = fishID)
+# 
+# SChard = Waterdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
+#                    Longitude_column = `Longitude`, PointID_column = fishID)
 
-RVhdist
-RVhdistx
-SCsoft
-SChard
+# RVhdist
+# RVhdistx
+# SCsoft
+# SChard
 
@@
 
-Cluster = data.frame(Release = c("RV Hard", "RV Hard Trailer", "DWSC hard", "DWSC soft"),
-                     meadist = c(mean(RVhdistx), mean(RVhdist), mean(SCsoft), mean(SChard)),
-                     SD = c(sd(RVhdistx), sd(RVhdist), sd(SCsoft), sd(SChard)))
-Cluster = mutate(Cluster, CV = SD/meadist)
-Cluster
+clustest = lapply(distances, function(x){df = data.frame(Mean = mean(x[lower.tri(x)], na.rm =T), SD = sd(x, na.rm =T))} )%>%
+  bind_rows() %>%
+  mutate(Release = releasex$ReleaseEvent)
+
+clustest
 ```
+
+OK, now how to I put these all together to graph them?
+
+```{r}
+
+alldist = lapply(distances, function(x){
+  x[lower.tri(x, diag = T)] = NA
+  X = as.data.frame(x) %>%
+    mutate(Fish1 = row.names(x)) %>%
+    pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
+  filter(!is.na(Distance))
+  return(X)
+})
+
+names(alldist) = releasex$ReleaseEvent
+
+for(i in 1:14) {
+  alldist[[i]] = mutate(alldist[[i]], ReleaseEvent = releasex$ReleaseEvent[i])
+}
+
+alldist2 = bind_rows(alldist) %>%
+  filter(ReleaseEvent != "NA") %>%
+  left_join(release)
+
+totsX = group_by(recaps3, ReleaseEvent) %>%
+  summarize(N = n())%>%
+  filter(ReleaseEvent != "NA")
+ggplot(alldist2, aes(x = ReleaseEvent, y = Distance, fill = ReleaseEvent)) + geom_boxplot()+
+  ylab("Distance Between Recaptures")+ theme_bw()+ scale_fill_discrete(guide = NULL)+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))+
+  geom_label(data = totsX, aes(x = ReleaseEvent, y =1, label = paste("N=", N)), fill= "white")
+
+```
+
+```{r}
+alldist2.1 = filter(alldist2, Type != "Unknown") %>%
+  mutate(BroodYear = case_when(ReleaseDate < ymd("2023-09-01") ~ 2022,
+                               TRUE ~ 2023),
+         Type2 = case_when(Type == "Hard (trailer)" ~ "Hard (large scale)",
+                           TRUE ~ Type))
+
+ggplot(alldist2.1, aes(x = Type2, y = Distance, fill = Type2)) + geom_boxplot()+
+  ylab("Distance Between Recaptures (m)")+
+  xlab("Release Type")+
+   stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
+  theme_bw() +
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
+        legend.position = "none")
+
+ggsave("plots/DistanceBetweenRecaps.tiff", device = "tiff", width =5, height =4)
+
+ggplot(alldist2.1, aes(x = Type2, y = Distance, fill = Type2)) + geom_boxplot()+
+  ylab("Distance Between Recaptures (m)")+
+  xlab("Release Type")+
+  facet_wrap(~BroodYear)+
+   stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
+        legend.position = "none")
+
+ggsave("plots/DistanceBetweenRecaps_byyear.tiff", device = "tiff", width =8, height =5)
+
+```
+
+now let's look at it statistically
+
+```{r}
+
+m2 = lm(Distance ~ Release, data = nndist)
+summary(m2)
+plot(m2)
+#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.
+
+emmeans(m2, pairwise ~ Release)
+plot(emmeans(m2, pairwise ~ Release), comparisons = T)
+
+```
+
+So DWSC soft were closer together than rio vista hard, but no difference between DWSC hard and DWSC soft
+
+I could also do this by release rather than release type
+
+```{r}
+smeltIDS = select(recaps2, fishID, ReleaseEvent)
+
+nndist2 = left_join(nndist, smeltIDS, by = c("Fish1" = "fishID"))
+
+m3 = lm(Distance ~ ReleaseEvent, data = nndist2)
+summary(m3)
+plot(m3)
+#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.
+
+emmeans(m3, pairwise ~ ReleaseEvent)
+plot(emmeans(m3, pairwise ~ ReleaseEvent), comparisons = T)
+
+write.csv(nndist2, "DistanceMatrix.csv")
+```
+
+The before/after first flush thing was interesting, something with turbidity for the week after the release?
+
+So, first i need to pull turbidity data from that area for the week after each realease.
+
+```{r}
+library(cder)
+library(zoo)
+
+turbdat = cdec_query("RVB", sensors = 27, start.date = as.Date("2021-01-01"), end.date = today())
+
+turbdat = mutate(turbdat, Month = month(DateTime), Date = date(DateTime), Year = year(DateTime))
+
+turbdat_ave = group_by(turbdat, Date, Month, Year) %>%
+  summarize(Turbidity = mean(Value, na.rm =T))
+
+test = rollmean(turbdat_ave$Turbidity, 7, align = "right", na.pad = TRUE)
+
+turbdat_ave$weekturb = test
+
+releasestat = left_join(releasestat, turbdat_ave, by = c("ReleaseDate" = "Date"))
+
+ggplot(filter(releasestat, BroodYear != 2021, Type2 != "NA"), aes(x = weekturb, y = RecapRate )) + geom_point(aes(color = as.factor(BroodYear), shape = Type2), size =3)+ geom_smooth(method = "lm")+ylab("Percentage Recaptured") +
+  xlab("Mean turbidity for 7 days post release (NTU)")+
+  theme_bw()+
+  scale_color_brewer(palette = "Set2", name = "Brood Year")+
+  scale_shape(name = "Release Type")
+
+ggsave("plots/turbidityrecaps.tiff", device = "tiff", width =5, height =4)
+
+```
+
+## Pretty map of recaputres for presentations
+
+```{r}
+
+library(tidyverse)
+library(lubridate)
+library(sf)
+library(ggmap)
+library(readxl)
+library(deltamapr)
+library(ggspatial)
+
+smelt = read_excel("Data/smeltcatch_2023.xlsx")
+
+smeltsf = st_as_sf(smelt, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
+  mutate(Date = str_sub(as.character(SampleDate), 6, 10))
+
+ggplot()+
+  geom_sf(data = WW_Delta, fill = "grey90")+
+  geom_sf(data = smeltsf, aes(shape = Survey, fill = LifeStage, color = LifeStage), size =5)+
+  scale_shape_manual(values = c(23, 24, 25))+
+  geom_sf_label(data = smeltsf, aes(label = Date), hjust =0, nudge_x = 0.01)+
+  coord_sf(ylim = c(38.0, 38.45), xlim = c(-122.1, -121.55))+
+  theme_bw()+
+  ylab(NULL)+
+  xlab(NULL)+
+  annotation_scale()+
+  annotation_north_arrow(aes(location = "tl"))
+
+ggsave("Plots/smeltmap2023.tiff", device = "tiff", width =8, height =8)
+ggsave("Plots/smeltmap2023.png", device = "png", width =8, height =8)
+
+###########################################################
+#map for Katie
+smelt2 = read_excel("Data/Running Delta Smelt Catch_2023-09-05.xlsx", sheet = "Delta Smelt Catch Data")
+
+smeltsf = st_as_sf(smelt2, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
+  mutate(Date = str_sub(as.character(SampleDate), 6, 10)) %>%
+  filter(SampleDate > ymd("2023-09-30"))
+
+ggplot()+
+  geom_sf(data = WW_Delta, fill = "grey90")+
+  geom_sf(data = smeltsf, aes(shape = ReleaseMethod,  fill = ReleaseMethod), size =3)+
+  scale_fill_brewer(palette = "Set2", labels = c("Hard (carboy)", "Hard (large scale)", "Hard (trailer)",
+                                                  "NA - unmarked fish", "Soft (carboy)"))+
+  scale_shape_manual(values = c(21,22,23,24,25), labels = c("Hard (carboy)", "Hard (large scale)", "Hard (trailer)",
+                                                  "NA - unmarked fish", "Soft (carboy)"))+
+  #geom_sf_label(data = smeltsf, aes(label = Date), hjust =0, nudge_x = 0.01)+
+  coord_sf(ylim = c(37.8, 38.35), xlim = c(-122.2, -121.45))+
+  theme_bw()+
+  ylab(NULL)+
+  xlab(NULL)+
+  annotation_scale()+
+  annotation_north_arrow(aes(location = "tl"))
+
+ggsave("plots/Releasemap.png", device = "png", width =8, height =6)
+
+```

### 2024-03-26 smelt_2019_allseasons/continuousWQ.R

@@ -87,7 +87,7 @@ ggplot(WQmean, aes(x = Date, y = MeanValue,
   scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
   geom_hline(data = cuttoffs, aes(yintercept = cuttoff, linetype = Type), 
-             color = "red")+
+             color = "black")+
   scale_linetype_manual(values = c(1,3,5))
 
 ###################################################################
@@ -147,7 +147,7 @@ ggplot(WQmean, aes(x = Date, y = MeanValue,
   scale_color_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
   scale_fill_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
   geom_hline(data = cuttoffs, aes(yintercept = cuttoff, linetype = Type), 
-             color = "red")+
+             color = "black")+
   scale_linetype_manual(values = c(1,3,5))
 
 

### 2024-04-02 recaptureanalysis/recaps.Rmd
working on diet data from cages and smelt recapgure data

@@
                     sheet = "Delta Smelt Catch Data") %>%
-  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`) %>%
+  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`)
+
+recaps = recaps %>%
   mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
@@
 
-m2 = lm(Distance ~ Release, data = nndist)
+m2 = lm(Distance ~ Type, data = alldist2)
 summary(m2)
@@
 
-emmeans(m2, pairwise ~ Release)
-plot(emmeans(m2, pairwise ~ Release), comparisons = T)
+emmeans(m2, pairwise ~ Type)
+plot(emmeans(m2, pairwise ~ Type), comparisons = T)
 
@@
 
-So DWSC soft were closer together than rio vista hard, but no difference between DWSC hard and DWSC soft
+So soft were closer together than hard
 
 I could also do this by release rather than release type
-
-```{r}
-smeltIDS = select(recaps2, fishID, ReleaseEvent)
-
-nndist2 = left_join(nndist, smeltIDS, by = c("Fish1" = "fishID"))
-
-m3 = lm(Distance ~ ReleaseEvent, data = nndist2)
-summary(m3)
-plot(m3)
-#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.
-
-emmeans(m3, pairwise ~ ReleaseEvent)
-plot(emmeans(m3, pairwise ~ ReleaseEvent), comparisons = T)
-
-write.csv(nndist2, "DistanceMatrix.csv")
-```
 
@@
 
-smelt = read_excel("Data/smeltcatch_2023.xlsx")
-
-smeltsf = st_as_sf(smelt, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
-  mutate(Date = str_sub(as.character(SampleDate), 6, 10))
-
-ggplot()+
-  geom_sf(data = WW_Delta, fill = "grey90")+
-  geom_sf(data = smeltsf, aes(shape = Survey, fill = LifeStage, color = LifeStage), size =5)+
-  scale_shape_manual(values = c(23, 24, 25))+
-  geom_sf_label(data = smeltsf, aes(label = Date), hjust =0, nudge_x = 0.01)+
-  coord_sf(ylim = c(38.0, 38.45), xlim = c(-122.1, -121.55))+
-  theme_bw()+
-  ylab(NULL)+
-  xlab(NULL)+
-  annotation_scale()+
-  annotation_north_arrow(aes(location = "tl"))
-
-ggsave("Plots/smeltmap2023.tiff", device = "tiff", width =8, height =8)
-ggsave("Plots/smeltmap2023.png", device = "png", width =8, height =8)
-
 ###########################################################
 #map for Katie
-smelt2 = read_excel("Data/Running Delta Smelt Catch_2023-09-05.xlsx", sheet = "Delta Smelt Catch Data")
+smelt2 = read_excel("data/Running Delta Smelt Catch.xlsx", 
+                    sheet = "Delta Smelt Catch Data")
 
@@
   mutate(Date = str_sub(as.character(SampleDate), 6, 10)) %>%
-  filter(SampleDate > ymd("2023-09-30"))
+  filter(SampleDate > ymd("2023-09-30"), !is.na(ReleaseMethod))
 
@@
 ggsave("plots/Releasemap.png", device = "png", width =8, height =6)
-
 ```

### 2024-04-02 biofouling/bugs.R

@@ -187,6 +187,12 @@ diets2.1 = group_by(diets2, Analy, Site, Treatment, `Cage ID`, Tag) %>%
   mutate(CageNum = paste("Cage", `Cage ID`), SampleID = Tag) %>%
   mutate(Type = "Diet")
 
+ggplot(diets2.1, aes(x = CageNum, y = Count, fill = Analy)) + geom_col(position = "fill")+
+  facet_wrap(Site~Treatment, scales = "free_x")+
+  scale_fill_manual(values = mypal)
+
+  
+
 zoops2 = left_join(zoops,select(crosswalk, Zooplankton, Analy), by = c("Species Name" = "Zooplankton") )
 
 zoops2.1 = group_by(zoops2, Analy, Site, CageNum, Treatment, SampleID) %>%
@@ -239,3 +245,107 @@ ggplot(filter(AllbugsRA2, Treatment != "Outside", Species != "Rotifer", Species 
        aes(x = Type, y = RelativeAbundance, fill = Species)) + geom_col(position = "fill") +
   facet_wrap(Site~Treatment)+
   scale_fill_manual(values = mypal)
+
+ggplot(filter(AllbugsRA2, Treatment != "Outside", Species != "Rotifer", Species != "Copepod nauplii"), 
+       aes(x = CageNum, y = RelativeAbundance, fill = Species)) + geom_col(position = "fill") +
+  facet_wrap(Site~Type, scales = "free_x")+
+  scale_fill_manual(values = mypal)
+##############################################################################
+library(vegan)
+#permanova comparing the three data type, two  sites, and two treatments
+datamat = filter(AllbugsRA2, Treatment != "Outside", Species != "Rotifer", Species != "Copepod nauplii") %>%
+  pivot_wider(names_from = Species, values_from = RelativeAbundance) 
+
+datamat = datamat[which(rowSums(datamat[,6:22]) !=0),]
+
+foo = as.matrix(datamat[,6:22])
+adonis2(foo ~ Treatment + Site + Type, data = datamat, na.rm = TRUE)
+
+
+
+
+bugsMDS = metaMDS(foo)
+
+bdata.scores <- as_tibble(scores(bugsMDS, display = "sites"))
+bdata.sps <- bugsMDS$species
+bdata.sps2 =  mutate(as.data.frame(bdata.sps), Species = row.names(bdata.sps))
+# Combine metadata with NMDS data scores to plot in ggplot
+bmeta <- cbind(datamat[,1:5], bdata.scores)
[…]

### 2024-05-13 recaptureanalysis/recaps.Rmd
zooplankton stuff

@@
 
+#put brood year on the x-axis?
+ggplot(releasestat, aes(x = as.factor(BroodYear), y = RecapRate*100, fill = as.factor(BroodYear)))+
+  geom_boxplot()+
+  facet_wrap(~FFyn)+
+  ylab("Percentage Recaptured")+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
+        legend.position = "none")+
+  xlab(NULL)
+
+#facet by brood year
+ggplot(releasestat, aes(x = Type2, y = RecapRate*100, fill = Type2))+
+  geom_boxplot()+
+  facet_grid(BroodYear~FFyn)+
+  ylab("Percentage Recaptured")+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
+        legend.position = "none")+
+  xlab(NULL)
+
 ```

### 2024-05-13 biofouling/bugs.R

@@ -29,6 +29,8 @@ amphwide = pivot_wider(amphipods, id_cols = c(Location, Date, Site), names_from 
 zoops = read_excel("data/DWR_CageZoop2023_Complete_TEC_1.22.2024.xlsx",
                        sheet = "Zoop Data") 
 
+zoops = mutate(zoops, uniqueID = paste(Date, Location))
+
 zoops = mutate(zoops, InOut = case_when(str_detect(Location, "Outside") ~ "Outside",
                                         str_detect(Location, "Inside") ~ "Inside"),
                CageNum = str_sub(Location, 1, 6)) %>%
@@ -36,15 +38,16 @@ zoops = mutate(zoops, InOut = case_when(str_detect(Location, "Outside") ~ "Outsi
   mutate(Treatment = case_when(InOut == "Outside" ~ "Outside",
                                TRUE ~ Treatment),
          Week = week(Date),
-         SampleID = paste(CageNum, Date, InOut))
+         SampleID = paste(CageNum, Date, InOut),
+         totalCount = Count*`Sample Volume (mL)`/`# of Subsamples`)
 
 #this is misleading....
-ggplot(zoops, aes(x = CageNum, y = Count, fill = `Species Name`)) + geom_col()+
+ggplot(zoops, aes(x = CageNum, y = totalCount, fill = `Species Name`)) + geom_col()+
   facet_wrap(Site~Treatment, scales = "free_x")
 
 #calculate average CPUE of each taxa
 zoopavetaxa = pivot_wider(zoops, id_cols = c(SampleID, CageNum, Treatment, Date, InOut, Site),
-                          names_from = `Species Name`, values_from = Count, values_fill = 0)
+                          names_from = `Species Name`, values_from =totalCount, values_fill = 0)
 
 zoopwzeros = pivot_longer(zoopavetaxa, cols = `Copepodid UNID nauplii`:last_col(), 
                           names_to = "Taxa", values_to = "Count")
@@ -248,6 +251,11 @@ ggplot(filter(AllbugsRA2, Treatment != "Outside", Species != "Rotifer", Species 
 
 ggplot(filter(AllbugsRA2, Treatment != "Outside", Species != "Rotifer", Species != "Copepod nauplii"), 
        aes(x = CageNum, y = RelativeAbundance, fill = Species)) + geom_col(position = "fill") +
+  facet_wrap(Site~Type, scales = "free_x")+
+  scale_fill_manual(values = mypal)
+
[…]

### 2024-05-13 biofouling/growthCondition.R

@@ -4,6 +4,7 @@
 library(tidyverse)
 library(lubridate)
 library(readxl)
+library(RColorBrewer)
 growth = read_xlsx("data/BiofoulingStudyCageRemovals.xlsx")
 
 
@@ -35,6 +36,16 @@ ggplot(growth, aes(x = Treatment, fill = Site, y = Weight))+ geom_boxplot()+
   scale_fill_brewer(palette = "Dark2")+
   theme(legend.position = "bottom")+
   ylab("Weight (g)")
+
+growth = mutate(growth, Site = factor(Site, levels = c("FCCL", "Belden's Landing", "Rio Vista")))
+brewer.pal(3, "Dark2")
+
+ggplot(growth, aes(x = Treatment, fill = Site, y = Weight))+ geom_boxplot()+
+  theme_bw()+
+  scale_fill_manual(values = c( "#D95F02","#1B9E77", "#7570B3"))+
+  theme(legend.position = "bottom")+
+  ylab("Weight (g)")
+
 
 ggplot(growth, aes(x = Treatment, fill = Site, y = Condition))+ geom_boxplot()+
   theme_bw()+

### 2024-07-12 recaptureanalysis/recaps.Rmd
Cleaned up recapture analysis and biofouling bug analysis

@@
 library(deltamapr)
-#load("Recaps.RData")
-#save(nndist, distances, recaps, recaps2, recaps3, RVhdist, SCsoft, SChard, RVhdistx, Dwschard, Dwscsoft, file = "Recaps.RData")
+load("Recaps2.RData")
+save( distances, recaps, recaps2, recaps3,  distances2, alldist, alldist2, alldist2.1, releasestat,
+      turbdat_ave, file = "Recaps2.RData")
 ```
@@
 
-recaps3 = left_join(recaps2, distances) %>%
+recaps3 = left_join(recaps2, distances, by = c("FishID" = "FishID")) %>%
   mutate(Type2 = case_when(Type %in% c("Hard (large scale)","Hard (trailer)") ~ "Hard (Large Scale)",
@@
 
-write.csv(recaps, "recaptureanalysis/Recapturedistances.csv")
+write.csv(recaps3, "recaptureanalysis/Recapturedistances.csv")
 ```
@@
 
-distances = list(NA)
+distances2 = list(NA)
 
@@
   points = filter(recaps3, ReleaseEvent == releasex$ReleaseEvent[i])
-  distances[[i]] = Waterdist(Water_map = spacetools::Delta, Points = points, Latitude_column = `Latitude`,
+  distances2[[i]] = Waterdist(Water_map = spacetools::Delta, Points = points, Latitude_column = `Latitude`,
                     Longitude_column = `Longitude`, PointID_column = FishID)
-  names(distances[[i]]) = releasex$ReleaseEvent[i]
+  names(distances2[[i]]) = releasex$ReleaseEvent[i]
 
@@
 
-clustest = lapply(distances, function(x){df = data.frame(Mean = mean(x[lower.tri(x)], na.rm =T), SD = sd(x, na.rm =T))} )%>%
+clustest = lapply(distances2, function(x){df = data.frame(Mean = mean(x[lower.tri(x)], na.rm =T), SD = sd(x, na.rm =T))} )%>%
   bind_rows() %>%
@@
 
-alldist = lapply(distances, function(x){
+alldist = lapply(distances2, function(x){
   x[lower.tri(x, diag = T)] = NA
@@
 
+alldist2 = mutate(alldist2, Type2 = case_when(str_detect(Type, "Hard") ~ "Hard",
+                                              str_detect(Type, "Soft") ~ "Soft",
+                                               TRUE ~ "Unknown"))
+m22 = lm(Distance ~ Type2, data = filter(alldist2, Type != "Unknown"))
+summary(m22)
+plot(m22)
+
+emmeans(m22, pairwise ~ Type2)
+plot(emmeans(m22, pairwise ~ Type2), comparisons = T)
+
 ```
@@
 I could also do this by release rather than release type
+
+But let's start with looking at just the paired releases with the carboys
+
+```{r}
+alldist3 = filter(alldist2, Type != "Unknown") %>%
+  mutate(Pair = str_sub(ReleaseEvent, 1,8))
+library(lme4)
+library(lmerTest)
+
+m3 = lmer(Distance ~ Type2 + (1|Pair), data = alldist3)
+summary(m3)
+plot(m22)
+
+emmeans(m3, pairwise ~ Type2)
+plot(emmeans(m3, pairwise ~ Type2), comparisons = T)
+
+```
 
@@
 
+turbm = lm(RecapRate ~ weekturb + Type2, data = releasestat)
+summary(turbm)
+#Huh, so percentage recaptures is correlated to turbidity (marginal), but not release type. Distance is correlated to release type, but not turbidity.
+
+#what if i just use the paired hard/soft releases?
+#oh, but some of the pairs are trailer and some are carboy
+
+#Ugh, I need to talk throught this with Brian. 
+write.csv(releasestat, "outputs/ReleasesRecapRate.csv")
+
+```
+
+```{r}
 ggplot(filter(releasestat, BroodYear != 2021, Type2 != "NA"), aes(x = weekturb, y = RecapRate )) + geom_point(aes(color = as.factor(BroodYear), shape = Type2), size =3)+ geom_smooth(method = "lm")+ylab("Percentage Recaptured") +
@@
 ggsave("plots/turbidityrecaps.tiff", device = "tiff", width =5, height =4)
+
+```
+
+OK, now let's try adding turbidity to the model with the paired releases
+
+```{r}
+
+alldist3 = left_join(alldist3, turbdat_ave, by = c("ReleaseDate" = "Date"))
+
+m3.3 = lmer(Distance ~ Type2 +weekturb+ (1|Pair), data = alldist3)
+summary(m3.3)
+
+#hm. Turbidity isn't significant, but probably becaues i've already blocked by date of release
+
+m3.4 = lm(Distance ~ Type2 +weekturb, data = alldist3)
+summary(m3.4)
+#turbidity is only marginal there.
+
+alldist2 = left_join(alldist2, turbdat_ave, by = c("ReleaseDate" = "Date"))
+
+m2.4 = lm(Distance ~ Type +weekturb, data = alldist2)
+summary(m2.4)
+#huh, turbidity not at all significant there.
 

### 2024-07-12 recaptureanalysis/recapsclean.Rmd
Cleaned up recapture analysis and biofouling bug analysis

---
title: "Smelt recapture analysis - clean version"
author: "Rosie"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
library(lme4)
library(lmerTest)
library(effects)
library(MuMIn)
library(DT)
load("recaptureanalysis/Recaps2.RData")

```

## Questions we can ask about Delta Smelt realeases

-   What influences how far they travel from release site?

    -   Release type (Hard, soft)

    -   Turbidity

    -   First flush

    -   Brood Year

-   What influences how close together the fish are when they are recaptured?

    -   Release type (Hard, soft)

    -   Turbidity

    -   First Flush

    -   Brood Year

-   What influences how many fish are recaptured?

    -   Release type (Hard, soft)

    -   Turbidity

    -   First Flush

    -   Brood Year

### Data

We have tw0 years of release data (brood years 2022, and 2023) where we have release-specific markings that we can use for this analysis. Most were released at Rio VIsta, but a few were released in the Ship Channel durign the first year. Releases in 2021 did not have release-specific markings, so we can't really use that to analyze release types.

```{r, echo=FALSE}
releasestat2 = select(releasestat, -Mark, -Type2, -N, -FirstFlush, -Month, -Year, -Turbidity,
                      -LatitudeR, -LongitudeR) %>%
  rename(WeeklyAve_Turbidity = weekturb)

datatable(releasestat2)
```

## Distance traveled

For the first question, distance traveled from release site, let's start with a few exploratory plots.

Is distance from release site explained by release type or brood year?

2021 looks a bit closer than the other two years. Soft might be closer than hard, but difficult to tell.

```{r}
ggplot(filter(recaps3, Type != "Wild/unmarked"), aes(x = Type2, y = Distance)) + geom_boxplot()+
  facet_wrap(~BroodYear)+ ylab("Distance from release site)")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))
```

OK, now let's test it statistically.

We want to account for the fact that some of these were in paried releases, and the fact that brood years might be different. But our primary goal is hard versus soft.

I'm going to start with the two differen ttypes of hard realeases, then pool all hard releases. I'll aslo take out 2021 since we can't trace that one.

Wait - do I need a random effect of release event? I think I do. Maybe that's my random effect instead of pari? Or does pair cover it?

```{r}
recaps3.1 = filter(recaps3,  Type != "Wild/unmarked", Type != "Unknown") %>%
  mutate(Pair = str_sub(ReleaseEvent, 1,8), BroodYear = as.factor(BroodYear))

recapmod = lmer(Distance ~ Type2 + BroodYear + (1|Pair), data = recaps3.1)
summary(recapmod)
  plot(allEffects(recapmod))
```

No significant differences what so ever.

Let's try taking out brood year.

```{r}
recapmod2 = lmer(Distance ~ Type2 + (1|Pair), data = recaps3.1)
summary(recapmod2)
  plot(allEffects(recapmod2))

```

Nope. Now let's try pooling all the hard realeasees.

```{r}
recaps3.1 = mutate(recaps3.1, Type3 = case_when(str_detect(Type2, "Hard") ~ "Hard",
                                                str_detect(Type2, "Soft") ~ "Soft"))

recapmod3 = lmer(Distance ~ Type3 + (1|Pair), data = recaps3.1)
summary(recapmod3)
  plot(allEffects(recapmod3))

```

Nope, still not significant.

OK, now what about turbidity?

```{r}
recaps3.2 = left_join(recaps3.1, turbdat_ave, by = c("ReleaseDate" = "Date"))

recapmod4 = lmer(Distance ~ weekturb + (1|Pair), data = recaps3.2)
summary(recapmod4)
  plot(allEffects(recapmod4))

```

How about before versus after first flush?

```{r}
recapmod5 = lm(Distance ~ FFyn, data = recaps3.2)
summary(recapmod5)
  plot(allEffects(recapmod5))

```

There's a difference, but it's not significant.

Just to be thorough, let's put all the possible predictors in a model and see which AIC says is best.

```{r}
recapmodGlobal = lmer(Distance ~ FFyn + BroodYear + Type3 + weekturb + (1|Pair), data = recaps3.2,
                      na.action = "na.fail", REML = FALSE)

dredge(recapmodGlobal)

```

It says that the null model with no predictors is best, followed closely by just the release type.

Overall, we didn't see much influence on distance traveled from any of our predictors.

## Distance between recaptures

Now let's move on to distance between recaptures. Personally, I don't love this metric, because unless they are caught in the same trawl, we can't really say they are schooling or derriving any benifit from being close together, but we'll do it anyway.

Is distance between recaptures explained by release type or brood year?

Exploritoary plots

```{r}
ggplot(filter(alldist2.1), aes(x = Type2, y = Distance)) + geom_boxplot()+
  facet_wrap(~BroodYear)+ ylab("Distance between recaptures")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))
```

It doesn't look like there was a big difference bwteen brood years, but maybe somthing with release type.

We want to account for the fact that some of these were in paried releases, and the fact that brood years might be different. But our primary goal is hard versus soft.

I'm going to start with the two differen ttypes of hard realeases, then pool all hard releases.

```{r}
alldist2.1 = mutate(alldist2.1, Pair = str_sub(ReleaseEvent, 1, 8), BroodYear = as.factor(BroodYear))
school1 = lmer(Distance ~ Type2 + BroodYear + (1|Pair), data = alldist2.1)
summary(school1)
  plot(allEffects(school1))
```

So, soft realeases were closer together than hard releases, no difference between the carboy hard releases and large-scale releases, and no difference between brood years.

OK, now what about turbidity?

```{r}
#join turbidity and first flush info
FF = select(recaps3.1, ReleaseEvent, FFyn) %>%
  distinct()
alldist3 = left_join(alldist2.1, turbdat_ave, by = c("ReleaseDate" = "Date")) %>%
  left_join(FF)

school2a = lm(Distance ~ weekturb, data = alldist3)
summary(school2a)
  plot(allEffects(school2a))

  school2 = lmer(Distance ~ weekturb + (1|Pair), data = alldist3)
summary(school2)
  plot(allEffects(school2))

```

No significant difference when I include the random effect of pair. I think i have to because smelt from a particular release event are not independent replicates.

I'm going to skip the first flush model and jump right to dredging the global model

```{r}
schoolmodGlobal = lmer(Distance ~ FFyn + BroodYear + Type2 + weekturb + (1|Pair), data = alldist3,
                      na.action = "na.fail", REML = FALSE)

dredge(schoolmodGlobal)
```

Huh. Almost everything is within a delta-AIC of 3, meaning they are pretty much the same. Interesting.

I don't think I"d want turbidity and first flush in the same model, so we'd have to choose. Neither are significant, so maybe just don't use either of them. Brood year didn't come out as significant, so I'm tempted to leave that out too.

```{r}
bestschool = lmer(Distance ~  Type2 + (1|Pair), data = alldist3)

summary(bestschool)

```

This leaves us with the conclusion that soft release fish stayed closer together.

## Number of recaptures

The percentage of fish recaptured gives us some idea whether there are differences in survival rates between the release types, which I think is one of hte more interesting things.

Is percentage of fish recaptured explained by release type or brood year?

```{r}
ggplot(releasestat, aes(x = Type2, y = RecapRate, color = as.factor(BroodYear))) + 
  geom_point()+ ylab("Percentage of fish recaptured")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))
```

There aren't a lot of data, it's pretty hard to tell anything.

```{r}
releasestat = mutate(releasestat, BroodYear = as.factor(BroodYear),
                     Type3 = case_when(str_detect(Type2, "Hard") ~ "Hard",
                                       str_detect(Type2, "Soft") ~ "Soft"))
rates1 = lm(RecapRate ~ Type2 + BroodYear, data = releasestat)
summary(rates1)
  plot(allEffects(rates1))
```

Meh.

```{r}

rates2 = lm(RecapRate ~ Type3, data = releasestat)
summary(rates2)
  plot(allEffects(rates2))
```

Nope. You definitely don't get more recaptures by release type.

OK, now what about turbidity?

```{r}

rates3 = lm(RecapRate ~ weekturb, data = releasestat)
summary(rates3)
  plot(allEffects(rates3))

```

So you do get a significant impact of nuber of recaptures based on turbiidty the week after release!

```{r}
ratesglobal = lm(RecapRate ~ FFyn + BroodYear + Type3 + weekturb , data = releasestat,
                      na.action = "na.fail")

dredge(ratesglobal)
```

So, the best model by AIC is with first flush, but the weekly turbidity and brood year are also within a delta AIC of 3, so could be included.

Again, I wouldn't want the first flush and weeekly turbidity in the same model, so we'd want to choose our favorite.

Brood year isn't significant, and doesn't improve the model, so I'll leave that off.

```{r}
ratesbest = lm(RecapRate ~ weekturb , data = releasestat)
summary(ratesbest)

ratesbest2 = lm(RecapRate ~ FFyn , data = releasestat)
summary(ratesbest2)

plot(allEffects(ratesbest))
plot(allEffects(ratesbest2))

```

### 2024-07-12 biofouling/biofoulingsitemap.R

@@ -1,0 +1,81 @@
+#map of 2023 enclosure study
+
+library(viridis)
+library(sf)
+library(dplyr)
+library(ggplot2)
+library(spData)
+library(here)
+library(readr)
+library(janitor)
+library(deltamapr)
+library(cowplot)
+library(ggspatial)
+
+library(here)
+library(readxl)
+
+latlon <- read_csv("biofouling/cagelocations2023.csv")
+
+
+
+stations_sf23 <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326)
+data("us_states", package = "spData")
+California = dplyr::filter(us_states, NAME == "California")
+stations_sf_4269 <- st_transform(stations_sf23, crs = st_crs(California))
+WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
+
+(smelt_map <- ggplot() +
+    geom_sf(data = WW_Watershed_4269, fill = "slategray1", colour = "gray80", alpha = 0.8, inherit.aes = FALSE) +
+    geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size = 4, color = "black", shape = c(21, 21,15,  15),
+            fill = "orangered2")+
+    geom_sf_label(data = stations_sf_4269, aes(label = factor(Location)), inherit.aes = FALSE, size = 4, color = "black",
+                  nudge_x = c(-0.06, -0.05),
+                  nudge_y = c(0.01, 0.02))+
+    annotate(geom = "text", x = -121.75, y = 38.10, size = 3.2, label = "Sacramento River", fontface = "italic",angle = 36) +
+    annotate(geom = "text", x = -121.62, y = 38.09, size = 3.2, label = "San Joaquin River", fontface = "italic", angle = 10) +
+    annotate(geom = "text", x = -122.02, y = 38.12, size = 3.2, label = "Grizzly Bay", fontface = "italic") +
+   # annotate(geom = "text", x = -121.68, y = 38.26, size =3.2 , label = "Liberty Island", fontface = "italic") +
+    scale_x_continuous(limits = c(-122.1, -121.55)) +
+    scale_y_continuous(limits = c(38, 38.3))+
+    annotation_north_arrow(location = "tl", which_north = "true",
+                           pad_x = unit(.005, "in"), pad_y = unit(0.15, "in"),
+                           style = north_arrow_fancy_orienteering) +
[…]

### 2024-07-12 biofouling/bugs.R

@@ -14,14 +14,37 @@ treatments = data.frame(Location = c("Cage 1", "Cage 2", "Cage 3", "Cage 4",
                                       "Flip", "Scrub", "Flip", "Scrub"))
 amphipods = left_join(amphipods, treatments)
 
-ggplot(amphipods, aes(x = Location, y = count, fill = Species)) + geom_col()+
+ggplot(amphipods, aes(x = Location, y = count, fill = Species)) + geom_col( position = "fill")+
   facet_wrap(Site~Treatment, scales = "free_x")
 
+
+insects = filter(amphipods, Species %in% c("Chironomidae larvae", "Chironomidae pupae",
+                                           "Elmidae", "Hydroptilidae larvae",
+                                           "Hydroptilidae pupae", "Leptoceridae larvae",
+                                           "Trichoptera adult UNID"))
+
+
+
+ggplot(insects, aes(x = Location, y = count, fill = Species)) + geom_col( )+
+  facet_wrap(Site~Treatment, scales = "free_x")
+
+
+isopods = filter(amphipods, Species %in% c( "Gnorimosphaeroma spp", "Munnidae"))
+
+ggplot(isopods, aes(x = Location, y = count, fill = Species)) + geom_col( )+
+  facet_wrap(Site~Treatment, scales = "free_x")
 
 #amphipod community matrix
 
 amphwide = pivot_wider(amphipods, id_cols = c(Location, Date, Site), names_from = Species, values_from = total_count,
                        values_fn = sum, values_fill =0)
+
+
+#calculate average lengths
+
+amplong = pivot_longer(amphipods, cols = c(m_1:m_50), names_to = "orgnum", values_to = "length") %>%
+  group_by(Location, Date, Time, Site, Species, a_nr_g, pc_frag_mut, count, total_count, multiplier) %>%
+  summarize(meanlength = mean(length, na.rm =T)) 
 
 ###################################################################
 
@@ -77,8 +100,8 @@ zoopavetaxa2b = zoopwzeros %>%
   summarize(Count = mean(Count))
 
 library(RColorBrewer)
-mypal = c(brewer.pal(8, "Dark2"), brewer.pal(8, "Set2"), "yellow", "orange", "purple", "grey", "brown",
-          "red", "lightgreen", "white")
[…]

### 2024-07-12 biofouling/clod cards.R

@@ -23,10 +23,10 @@ clods2 = read_excel("data/clod cards.xlsx", sheet = "finalcards") %>%
 
 clods2 = mutate(clods2, treatment2 = factor(treatment2, levels = c("outside", "flip", "scrub"),
                                             labels = c("External", "Exchanged", "Scrubbed")),
-                                            Site = factor(Site, levels = c( "SM", "RV"),
-                                                                labels = c( "Belden's Landing","Rio Vista")),
-                days = case_when(Site == "Rio Vista" ~ 7,
-                                 Site == "Belden's Landing" ~ 6),
+                                            Site = factor(Site, levels = c( "RV","SM"),
+                                                                labels = c( "RV","BDL")),
+                days = case_when(Site == "RV" ~ 7,
+                                 Site == "BDL" ~ 6),
                 DiffPerDay = difference/days)
 
 
@@ -35,8 +35,9 @@ ggplot(clods2, aes(x = Site, y = DiffPerDay, fill = treatment2))+ geom_boxplot()
 
 ggplot(clods2, aes(x = treatment2, y = DiffPerDay, fill = Site)) +
   geom_boxplot()+
-  scale_fill_manual(values = c("#1B9E77" , "#7570B3"))+ 
+  scale_fill_manual(values = c("#1B9E77","#D95F02"))+ 
   ylab("Loss of Weight per Day (g)")+xlab(NULL)+
+  theme_bw()+
   theme(legend.position = "bottom")
 
 ggsave("plots/clodcards.tiff", device = "tiff", width =4, height =5)

### 2024-07-12 biofouling/water quality.R

@@ -3,6 +3,7 @@
 library(tidyverse)
 library(lubridate)
 library(readxl)
+library(cder)
 
 #look at the survival data
 survival = read_excel("data/BiofoulingStudy_Survival.xlsx", sheet = "Data")
@@ -71,15 +72,25 @@ ggplot(env, aes(x = as.factor(Date), y = Turb, color = InsideOutside))+
   facet_wrap(~Location)
 
 
-BDL = cdec_query(c("BDL","RVB"), c(25, 27, 100,61, 62, 221), start.date = ymd("2023-08-30"),
+BDL = cdec_query(c("BDL","RVB"), c(25, 27,28, 62, 100, 221), start.date = ymd("2023-08-30"),
                  end.date = ymd("2023-10-17"))
 library(wql)
 BDL2 = BDL %>%
   mutate(Value2 = case_when(SensorType == "TEMP W" ~ (Value-32)*5/9,
                             SensorType == "EL COND" ~ ec2pss(Value/1000, 25),
                             TRUE ~ Value),
-         Analyte = factor(SensorNumber, labels = c("Temperature (C)", "Turbidity (NTU)",
-                                                   "")))
+         Analyte = factor(SensorType, levels = c("CHLORPH", "EL COND", "PH VAL",
+                                                 "TEMP W", "TURB W"),
+                          labels = c("Chlorophyll (ug/L)", "Salinity (PSU)",
+                                     "pH", "Temperature (C)", "Turbidity (FNU)"))) %>%
+  filter(Value2 <200, !(SensorType == "CHLORPH" & Value > 10)) %>%
+  mutate(Site = factor(StationID, levels = c("RVB", "BDL")))
 
-ggplot(BDL2, aes(x = DateTime, y = Value2, color = StationID))+ geom_line()+
-  facet_wrap(~SensorType, scales = "free")
+ggplot(BDL2, aes(x = DateTime, y = Value2, color = Site))+ geom_line()+
+  facet_wrap(~Analyte, scales = "free", nrow =3)+
+  scale_color_manual(values = c("#1B9E77","#D95F02"), name = "Site")+
+  theme_bw()+ ylab(NULL)+
+  xlab("Date - 2024")+
+  theme(legend.position = "bottom")
+
+ggsave("plots/continuousWQ_biofouling.tiff", device = "tiff", width =8, height =8)

### 2024-09-06 recaptureanalysis/Mapdemo.qmd
Better recapture analyses

---
title: "Maps and spatial stats demo"
author: "Rosie"
format: html
editor: visual
---

## Making Maps in R

You can do pretty much anything in R that you can in ArcGIS, but it is best for spatial statistics and calculations because you can save your code and make minor updates without having to remember all the point-and-click bits. It is maybe less good for just making pretty maps because it's a bit harder to tweak the labels, captions, annotations etc. Sometimes I make the base map in R and edit it a bit in illustrator to make it perfect if I can't figure it all out in R.

### Packages

The package I use most frequently for making vector-based maps in R is `sf` (which stands for "simple features"). There are many other options, but this one works well if you are used to using the `tidyverse` packages for data manipulation. If you want to deal with raster data or interactive maps you'll need some other packages, but this is good to start with.

<https://r-spatial.github.io/sf/>

I also frequently use the `deltamapr` package (build by Sam Bashevkin and contributed to by me) for many of the base datasets you will want to map. It's available on GitHub.

<https://github.com/InteragencyEcologicalProgram/deltamapr>

```{r}
#load your librarys
library(sf)
library(tidyverse)
library(deltamapr)
```

### Spatial Data

In order to make a map, you need to start with spatial data. Spatial data is just like regular data frame, but it has a `geometry` column that has the coordinates for points, lines, or polygons. We can see what that looks like by checking out one of the datasets in the `deltamapr` package.

```{r}

#THe P_Stations dataset has locations of major monitoring surveys.
#it is a spatial point datasets.
View(deltamapr::P_Stations)
#notice that the geometry column starts with "POINT" then the UTM coordinates.

#The WW_Delta dataset is a spatial polygon datset
View(deltamapr::WW_Delta)
#The geometry column starts with "Polygon" and then has latitudes and longitudes
```

The other important component of a spatial dataset is it's coordinate reference system. We can get and set the coordinate reference system of a spatial dataset using `st_crs.`

```{r}

st_crs(P_Stations)
st_crs(WW_Delta)
```

The full specification of a coordinate reference system is long and very difficult to type in if you have to set it yourself, but you can always reference it with the ESPG identification number (at the end of the output, above).

If you are performing any calculations, like spatial joins or distances, you need to be in the same CRS. You can change it using `st_transform`

```{r}

newDelta = st_transform(WW_Delta, crs = 4326)
st_crs(newDelta)
```

So, how do you take point data and turn it into spatial data? It's easy. We just use `st_as_sf` and tell it the columns containing the coordinates and the CRS.

```{r}
#set up some point data
testdata = data.frame(FishID = c(1,2,3), Latitude = c(38.23456, 37.8245, 38.09823),
                      Longitude = c(-121.60678, -121.59789, -121.88888))
str(testdata)

#convert it to a spatial dataframe

testdataSF = st_as_sf(testdata, 
                      coords = c("Longitude", "Latitude"), #identify coordinate columns, note that longitude must come first
                      crs = 4326,#I am using the ESPG number 4326, which is WGS 84, and what we usually deal with
                      remove = FALSE) #keep the latitude and longitude columns

str(testdataSF)
```

### Making Maps

I usually use ggplot for making maps. It works very well with `sf`, you just have to tell it you are making a map by using `geom_sf` instead of `geom_point` or whatever. It is nice in that it will automatically transform data layers with different coordinate reference systems for you when it maps so you don't have to worry about it.

Geom_sf will automatically display points for point features and outlines for polygon features, so you don't have to worry about telling it to draw points or lines. You can use the `aes` argument to specify colors, labels, or other mapping information.

```{r}

ggplot()+
  geom_sf(data = WW_Delta)+ #add waterways
  geom_sf(data = testdataSF) #add fish points
```

You can get fancier with labeling your points, and you can zoom in using `coord_sf`

```{r}

ggplot()+
  geom_sf(data = WW_Delta)+ #add waterways
  geom_sf(data = testdataSF, aes(color = FishID))+#color the points by ID
  geom_sf_label(data = testdataSF, aes(label = as.factor(FishID)), #add labels
                nudge_x = 0.05, nudge_y = 0.05)+ #nudge labels so they don't overlap points
  coord_sf(xlim = c(-121.4, -122), ylim = c(37.8, 38.5))
```

If you want to add scale bars and north arrows, the best way to do that is with the `ggspatial` package.

```{r}
library(ggspatial)

ggplot()+
  geom_sf(data = WW_Delta, fill = "lightskyblue")+
  geom_sf(data = testdataSF, aes(color = as.factor(FishID)))+
  scale_color_manual(values = c("blue", "orange", "red"), labels = c("onefish", "twofish", "redfish"), name = "Fish ID")+
  geom_sf_label(data = testdataSF, aes(label = FishID), 
                nudge_x = 0.05, nudge_y = 0.05)+ #nudge labels so they don't overlap points
  coord_sf(xlim = c(-121.4, -122), ylim = c(37.8, 38.5))+
    annotation_scale()+
    annotation_north_arrow(location = "tl")+
  ylab(NULL)+
  xlab(NULL)+
  theme_bw()
```

## Calculating distances

The distance calculations I did for experimental realease were based on some functions that Sam and I put together. Calculating the straight-line distance or great-circle distance (distance along the curvature of the earth) is pretty straightfoward, but calculating the distance along a waterway is more difficult. The basic steps are as follows:

1.  Create a grid (raster) of your landscape. The waterways are coded as "easy to move through" and the land is coded as "hard to move through".
2.  Make sure all your points are starting in the water (sometimes GPS coordinates might be a little off and a fish ends up on lang).
3.  Have R calculate the easiest path from point A to point B. Because the land is harder to move through than water (by a LOT), it will automatically move through the water.

Fortunatley, all these steps have already been coded for you in this package:

<https://github.com/sbashevkin/spacetools>

We use the `Waterdist` function to calculate in-water distances between two points and the GGdist to calculate the distance between all points and the Golden Gate (or another single point of your choice).

```{r}
# install.packages("devtools")
#devtools::install_github("sbashevkin/spacetools")
library(spacetools)

#Distances between the three fish in our test dataset

# The funtion requires a rasterized map that has everythign coded as easy or hard.
#It comes with a built-in map of the Delta, but you'll have to build one if you are trying to do this somewhere else

?Waterdist

fishdistances = Waterdist(Water_map = Delta, 
                        Points = testdata,
                        Latitude_column = Latitude,
                        Longitude_column = Longitude,
                        PointID_column = FishID)

#Note that it had to move some of the points so they are in teh waterways since my random fish points were made up.
```

It takes a while to run because it's some pretty complicated stuff, so be sure to save your output to avoid rerunning it.

The output is a matrix with distance between each of the points in meters.

```{r}
print(fishdistances)
```

### 2024-09-06 recaptureanalysis/recapsclean.Rmd
Better recapture analyses

@@
 library(DT)
+library(deltamapr)
 load("recaptureanalysis/Recaps2.RData")
@@
 ```
+
+## Recaptures in the North Delta Arc
+
+Katie was wondering if we could say whether release type impacted number of fish caught in the North Delta Arc.
+
+First we have to figure out what counts as the "north delta arc"
+
+I'm going to say it is the EDSM "Cache/liberty", "Lower Sacramento" and "Sac DWSC",
+Suisun Bayk/Marsh" and "Western Delta" strata
+
+```{r}
+ggplot()+
+  geom_sf(data = R_EDSM_Strata_17P3, aes(fill = Stratum))+
+  geom_sf(data = WW_Delta)+
+  coord_sf(ylim = c(37.8, 38.5), xlim = c(-122.2, -121.4), crs = 4326)
+
+```
+```{r}
+#filter out the north delta arc and attach it to the recap data
+NorthDeltaArc = filter(R_EDSM_Strata_17P3, Stratum %in% c("Cache Slough/Liberty Island",
+                                                         "Lower Sacramento",
+                                                         "Suisun Bay/Marsh",
+                                                         "Western Delta",
+                                                         "Sac Deep Water Shipping Channel")) %>%
+  mutate(NorthDeltaArc = TRUE) %>%
+  select(Stratum, NorthDeltaArc)
+
+recapND = st_as_sf(recaps3, coords = c("Longitude", "Latitude"), crs = 4326) %>%
+  st_transform(crs = st_crs(NorthDeltaArc)) %>%
+  st_join(NorthDeltaArc) %>%
+  st_drop_geometry() %>%
+  mutate(NorthDeltaArc = case_when(NorthDeltaArc ~ 1,
+                                   TRUE ~ 0))
+
+NDtest = glm(NorthDeltaArc ~ Type2 + BroodYear, data = recapND, family = "binomial")
+
+summary(NDtest)
+```
+
+Huh, not useful.
+
+```{r}
+ggplot(recapND, aes(x = Type2, fill = as.factor(NorthDeltaArc)))+ geom_bar()
+
+ggplot(filter(recapND, Type2 != "Unknown", Type2 != "Wild/unmarked"),
+              aes(x = Type2, fill = as.factor(NorthDeltaArc)))+ geom_bar(position = "fill")
+
+```
+now try without the wild fish
+
+```{r}
+
+recapND2 = filter(recapND, Type2 != "Unknown", Type2 != "Wild/unmarked") %>%
+  mutate(Type3 = case_when(str_detect(Type2, "Hard") ~ "Hard",
+                           TRUE ~ "Soft"))
+
+NDtest2 = glm(NorthDeltaArc ~ Type3 + BroodYear, 
+              data = recapND2, family = "binomial")
+
+summary(NDtest2)
+
+```

### 2024-09-06 biofouling/biofoulingsitemap.R

@@ -79,3 +79,19 @@ gg_inset_map
 
 dev.off()
 
+smelt_map + geom_sf_text(data = deltamapr::P_RKI, aes(label = RKI))+
+  coord_sf(xlim = c(-121.8, -121.6), ylim = c(38.10, 38.17))
+
+#Now plot Erik's sites
+
+library(readxl)
+NDFS = read_excel("data/EricSites.xlsx")
+NDFSsf = st_as_sf(NDFS, coords = c("Long", "Lat"), crs = 4326)
+
+ggplot() +
+  geom_sf(data = WW_Watershed_4269, fill = "slategray1", colour = "gray80", alpha = 0.8, inherit.aes = FALSE) +
+  geom_sf(data = NDFSsf, inherit.aes = FALSE, size = 4, color = "black")+
+  geom_sf_text(data = deltamapr::P_RKI, aes(label = RKI))+
+  coord_sf(xlim = c(-121.8, -121.59), ylim = c(38.15, 38.5))+
+  geom_sf_label(data = NDFSsf, inherit.aes = FALSE, aes(label = SiteCode), nudge_x = -0.01, hjust =1)
+ 

### 2024-09-06 biofouling/bugs.R

@@ -160,6 +160,13 @@ ggplot(zoopave2, aes(x = Treatment, y = CPUEm)) + geom_col()+
 
 diets = read_excel("data/DSM Cage Diets 2019-2023.xlsx", sheet = "2023")
 
+empties = filter(diets, `Prey Taxa`=="EMPTY") %>%
+  rename(Location = Site, FishID = Tag, CageCode = `Prey Taxa`) %>%
+  select(Location, Treatment, `Cage ID`, FishID, Fullness, Digestion, `Total Contents Weight`,
+         CageCode) %>%
+  mutate(Biomass =0, Count =0, Empty = "Y", Treatment = "Exchanged", Location = "Belden's Landing",
+         LabWeight_g = 0.684, `Taxa Group` = "Empty")
+
 ggplot(diets, aes(x = Tag, y = Count, fill = `Prey Taxa`)) + geom_col()+
   facet_wrap(Treatment~Site, scales = "free_x")
 
@@ -192,7 +199,65 @@ plot(dietw)
 summary(dietw)
 #no significant difference, OK.
 
-#########################################################################
+#Diet biomass
+dietmass = read_csv("data/cagedietbiomass.csv") %>%
+  bind_rows(empties)
+
+ggplot(dietmass, aes(x = FishID, y = Biomass, fill = `Taxa Group`)) + geom_col() +
+  facet_wrap(Location ~ Treatment, scales = "free_x")
+
+
+
+
+#did they have a higher total stomach contents?
+
+diemasssum = group_by(dietmass, FishID, Treatment, Location, Fullness, LabWeight_g) %>%
+  summarize(Totmass = sum(Biomass)) %>%
+  mutate(Propmass = (Totmass/1000)/LabWeight_g)
+
+dietmod = lm(Totmass ~ Treatment + Location, data = diemasssum)
+summary(dietmod)
+plot(dietmod)
+
+dietmod2 = lm(Propmass ~ Treatment + Location, data = diemasssum)
+summary(dietmod2)
+plot(dietmod2)
+
+#lets try and take out that outlier
+diemasssum2 = filter(diemasssum, FishID != "C2N16")
+
+dietmod2.1 = lm(Propmass ~ Treatment + Location, data = diemasssum2)
+summary(dietmod2.1)
+plot(dietmod2.1)
+#fits better, still not significant
+
+dietmod = lm(Fullness ~ Treatment + Location, data = diemasssum)
+summary(dietmod)
[…]

### 2024-09-06 biofouling/water quality.R

@@ -86,11 +86,11 @@ BDL2 = BDL %>%
   filter(Value2 <200, !(SensorType == "CHLORPH" & Value > 10)) %>%
   mutate(Site = factor(StationID, levels = c("RVB", "BDL")))
 
-ggplot(BDL2, aes(x = DateTime, y = Value2, color = Site))+ geom_line()+
+ggplot(filter(BDL2, SensorType != "PH VAL"), aes(x = DateTime, y = Value2, color = Site))+ geom_line()+
   facet_wrap(~Analyte, scales = "free", nrow =3)+
   scale_color_manual(values = c("#1B9E77","#D95F02"), name = "Site")+
   theme_bw()+ ylab(NULL)+
   xlab("Date - 2024")+
   theme(legend.position = "bottom")
 
-ggsave("plots/continuousWQ_biofouling.tiff", device = "tiff", width =8, height =8)
+ggsave("plots/continuousWQ_biofouling.tiff", device = "tiff", width =8, height =6)

### 2024-09-11 smelt_2019_winterspring/map_enclosure_sites.Rmd
updates to figures for resubmission of 2019 synthesis paper

@@
 library(ggspatial)
+library(basemaps)
 
@@
 California = dplyr::filter(us_states, NAME == "California")
-stations_sf_4269 <- st_transform(stations_sf, crs = st_crs(California))
-WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
+stations_sf_4269 <- st_transform(stations_sf, crs = 4269) %>%
+  arrange(Location) %>%
+  mutate(Location = factor(Location))
+WW_Watershed_4269 <- st_transform(WW_Watershed, crs = 4269)
 ```
@@
 ```{r}
-(smelt_map <- ggplot() +
-    geom_sf(data = WW_Watershed_4269, fill = "gray80", colour = "gray80", alpha = 0.8, inherit.aes = FALSE) +
-    geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size = 4, color = "black")+
-   geom_sf_label(data = stations_sf_4269, aes(label = factor(Location)), inherit.aes = FALSE, size = 4, color = "black",
-                 nudge_x = c(-0.08, -0.05),
-                 nudge_y = c(0.01, -0.03))+
+
+smelt_map <- ggplot() +
+    geom_sf(data = WW_Watershed_4269, fill = "azure2", colour = "gray60", alpha = 0.8, inherit.aes = FALSE) +
       annotate(geom = "text", x = -121.75, y = 38.10, size = 3.2, label = "Sacramento River", fontface = "italic",angle = 36) +
@@
     annotate(geom = "text", x = -121.96, y = 38.07, size = 3.2, label = "Suisun Bay", fontface = "italic") +
-    annotate(geom = "text", x = -121.68, y = 38.26, size =3.2 , label = "Liberty Island", fontface = "italic") +
+    annotate(geom = "text", x = -121.68, y = 38.26, size =3.2 , label = "Liberty \nIsland", fontface = "italic") +  geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size =4, aes(shape = Type, fill = Type, size = Type))+
+  scale_shape_manual(values = c(21,22))+
+  scale_fill_manual(values = c("darkblue","wheat"))+
+   geom_sf_label(data = stations_sf_4269, aes(label = Location), inherit.aes = FALSE, size = 4, color = "black",
+                 nudge_x = c(0.03, 0.04, 0.03, 0.03, 0.05, -0.04, -0.03, -0.04),
+                 nudge_y = c(0.025, 0.03,0.02, 0.025, 0.02, -0.02, -0.03, -0.01))+
+
     scale_x_continuous(limits = c(-122.2, -121.45)) +
-  scale_y_continuous(limits = c(37.95, 38.4))+
+  scale_y_continuous(limits = c(37.8, 38.5))+
     annotation_north_arrow(location = "tr", which_north = "true",
@@
         panel.grid.minor = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust = 0.5, vjust = 0.5)))
+        axis.text.x = element_text(angle = 60, hjust = 0.5, vjust = 0.5),
+        legend.position = "none")
+smelt_map
 ```
@@
 ```{r}
+Cali = st_transform(California, crs = 3857)
+
+extbb = st_bbox(Cali)
+
+basem = basemap_gglayer(
+  ext = extbb,
+  map_service = "osm",
+  map_type = "topographic",
+  alpha = 0.5
+)
+
+ggplot() + basem+
+  theme(legend.position = "none")+
+  scale_fill_manual(values = sort(unique(basem$data$fill)))
+
 insetbbox = st_bbox(c(xmin = -122.2, xmax = -121.45, ymax = 37.95, ymin = 38.4), crs = st_crs(4326)) 
-box_sf <- st_as_sfc(insetbbox)
+box_sf <- st_as_sfc(insetbbox) %>%
+  st_transform(crs = 3857)
 
-(inset <- ggplot() +
-    geom_sf(data = California, fill = "white") +
-    geom_sf(data = WW_Delta, colour = "steelblue4", size = 0.3) +
-    geom_sf(data = box_sf, fill = NA, color = "red", size = 0.5) +
+inset <- ggplot() +
+    basem+
+    geom_sf(data = Cali, fill = "white", alpha = 0.1, linewidth =.7) +
+   geom_sf(data = WW_Delta, colour = "grey60", linewidth = 0.3) +
+    geom_sf(data = box_sf, fill = NA, color = "black", linewidth = .7) +
 
@@
           panel.grid.major = element_blank(),
-          panel.grid.minor = element_blank()))
+          panel.grid.minor = element_blank(),
+          legend.position = "none")+
+  scale_fill_manual(values = sort(unique(basem$data$fill)))+
+  annotation_scale()+
+  annotation_north_arrow(location = "tr")+
+  annotate("text", label = "California", x = -13600000, y = 5000000, size = 5, fontface = "italic")+
+  annotate("text", label = "United States\n of America", x = -13000000, y = 4800000, size = 6, fontface = "italic")+
+  annotate("text", label = "Study Area",x = -13600000, y = 4700000, size = 3, fontface = "bold" )
+
+inset
 ```
@@
    draw_plot(inset, x = 0.1, y = 0.63, width = 0.26, height = 0.31))
+
+gg_inset_map
 ```
@@
 ```
+
+Or we can plot them one next to the other to satisfy the pesky reviewer
+
+```{r}
+
+library(patchwork)
+
+inset+ smelt_map+ plot_layout(ncol =2, widths = c(1,2))
+
+tiff(filename = here::here("smelt_2019_allseasons",  "figures", "map_sites.tiff"), width = 10, height = 7, units = "in", pointsize = 12, family = "sans", res = 300, compress = "lzw")
+
+inset+ smelt_map+ plot_layout(ncol =2, widths = c(1,2))
+dev.off()
+
+pdf(file = here::here("smelt_2019_allseasons",  "figures", "map_sites.pdf"), width = 10, height = 7,  pointsize = 12,   compress = "lzw")
+
+inset+ smelt_map+ plot_layout(ncol =2, widths = c(1,2))
+dev.off()
+
+```

### 2024-09-11 smelt_2019_allseasons/continuousWQ.R

@@ -34,7 +34,7 @@ group_by(WQt, Analyte) %>%
   summarize(mean = mean(Value2), min = min(Value2), max = max(Value2))
 
 dates = read_excel("data/2019 Cage Deployment Dates.xlsx") %>%
-  mutate(Deployment = paste(StationID, Season))
+  mutate(Deployment = paste(StationID, Season)) 
 
 #Attach the deployment dates and filter to just periods with deployments
 WQ3 = left_join(WQt, dates) %>%
@@ -133,7 +133,12 @@ ggplot(WQ3, aes(x = ObsDate, y = Value2,
 WQmean = mutate(WQ3, Date = date(ObsDate)) %>%
   group_by( StationID, Season, Analyte, Date)%>%
   summarize(MeanValue = mean(Value2, na.rm =T), MaxValue = max(Value2, na.rm =T),
-            MinValue = min(Value2, na.rm =T))
+            MinValue = min(Value2, na.rm =T)) %>%
+  mutate(Location = case_when(StationID == "BDL" ~ "SM",
+                              StationID == "LIS" ~ "Yolo", 
+                              StationID == "RVB" ~ "RV", 
+                              StationID == "DWS" ~ "DWSC"),
+         Location = factor(Location, levels = c("SM", "DWSC", "Yolo", "RV")))
 
 ggplot(WQmean, aes(x = Date, y = MeanValue,
                    color = StationID))+ 
@@ -154,15 +159,46 @@ ggplot(WQmean, aes(x = Date, y = MeanValue,
 ggsave("plots/ContWaterQuality.tiff", device = "tiff", width =8, height =7)
 
 #Summary statistics
+library(wql)
+cagechecks2019 <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Oct_qaqc'ed_12.11.20.csv")%>%
+  mutate(Salinity = ec2pss(SpCond_uS/1000, t = 25), Date = mdy(Date), Season = "Fall") %>%
+  rename(`Dissolved Oxygen` = DO_mg_L, Temperature = Water.Temp_C, Turbidity = Avg.Turb_ntu) %>%
+  select(Location, Date, Season, `Dissolved Oxygen`, Salinity, Temperature, Turbidity)
+cagechecks20192 <- read_csv("smelt_2019_allseasons/data_raw/Field_Environmental_Data_Aug_qaqc'ed_11.04.20.csv")%>%
[…]

### 2024-09-11 biofouling/Macroinvert_Biomass.R
Added biomass calculations

@@ -1,0 +1,180 @@
+#Convert length to weight for all length measurements (length into a column for coding)
+#Length weight regressions per species: Mesomicro spreadsheet (double check names)
+#W = aL^b a and b are constants from mesomicro spreadsheet (use a_mg)
+#Use formalin (ask if there isn't a formalin option but probably is there for all)
+
+#Then take average weight per species * by total count (exclude mut and frag) = Wet weight
+
+#Wet to carbon -> Carbon weight = Wet weight * 0.25 * 4
+
+#Then same processing as with zoops
+
+#Macro data is breaking out into 4 groups amphipods, tenaid, chyron, isopod (in macro biomass file has crosswalk)
+##Americorph.. hyallela... and gam... are Amphipods
+#Crosswalk data sheet has amphipods listed out
+#Ignore annelids
+#Teams meeting has files of interest
+#mg=milligrams, convert it to micrograms
+
+library(tidyverse)
+library(readxl)
+library(data.table)
+
+#setwd("~/Delta Smelt/biofouling coding")
+
+biomass_con <- read_xlsx("data/Mesomicromacro Biomass Conversions Aug2024.xlsx", sheet = "Macro-zooplankton")
+crosswalk <- read.csv("data/crosswalk 1.csv")
+amph_crosswalk <- read.csv("data/amph_sample_species.csv")
+
+#read in and format field data
+#amphdata <- read_xlsx("data/ICF_zoops_data_cages.xlsx", sheet = "Amph Data")
+#I hope this is the same data
+amphdata <- read_xlsx("data/DWR_CageZoop2023_Complete_TEC_1.22.2024.xlsx", sheet = "Amph Data")
+
+a <- which(amphdata$pc_frag_mut == "frag")
+b <- which(amphdata$pc_frag_mut == "mut")
+amph_exc_frag_mut <- amphdata[-c(a,b),]
+
+#combined count of each species by site, does not include lengths taken
+amph_counts <- amph_exc_frag_mut %>%
+  select(Location, Date, Time, Site, Species, count, starts_with("m")) %>%
+  summarize(.by = c(Location, Date, Site, Species), Sum_Total = sum(count))
+
+#Summarized the counts by 
[…]

### 2024-09-11 biofouling/bugs.R

@@ -46,6 +46,13 @@ amplong = pivot_longer(amphipods, cols = c(m_1:m_50), names_to = "orgnum", value
   group_by(Location, Date, Time, Site, Species, a_nr_g, pc_frag_mut, count, total_count, multiplier) %>%
   summarize(meanlength = mean(length, na.rm =T)) 
 
+#scott's mysid biomass data
+
+load("data/amph_sum_counts.RData")
+
+amphwidebm = pivot_wider(amph_sum_counts, id_cols = c("Location", "Treatment", "Date", "Site"),
+                         names_from = "NewName", values_from = "Biomass_median")
+
 ###################################################################
 
 
@@ -200,13 +207,6 @@ summary(dietw)
 #no significant difference, OK.
 
 #Diet biomass
-dietmass = read_csv("data/cagedietbiomass.csv") %>%
-  bind_rows(empties)
-
-ggplot(dietmass, aes(x = FishID, y = Biomass, fill = `Taxa Group`)) + geom_col() +
-  facet_wrap(Location ~ Treatment, scales = "free_x")
-
-
 
 
 #did they have a higher total stomach contents?
@@ -268,7 +268,7 @@ write.csv(amphbugs, "data/amphipodtaxa.csv")
 zoopbugs = unique(zoops$`Species Name`)
 write.csv(zoopbugs, "data/zooptaxa.csv")
 
-crosswalk = read_csv("data/crosswalk.csv")
+crosswalk = read_csv("data/crosswalk 1.csv")
 
 #now let's integrate diet and zooplankton data
 
@@ -320,7 +320,7 @@ amps2.1 = group_by(amps2, Analy, Site, CageNum, Treatment, SampleID) %>%
 
 Allbugs = bind_rows(amps2.1, zoops2.1, diets2.1) %>%
   select(-Tag, -`Cage ID`)
-save(Allbugs, file = "biofouling/Allbugs.Rdata")
+save(Allbugs,amps2.1, zoops2.1, diets2.1, file = "biofouling/Allbugs.Rdata")
 
 #########################################################################################3
 #analysis

### 2024-09-11 bug biomass.R

@@ -1,0 +1,149 @@
+#permanova comparing diet bug biomss, amphipod biomass, and zoop biomass
+
+library(vegan)
+library(tidyverse)
+library(readxl)
+
+
+library(RColorBrewer)
+mypal = c(brewer.pal(8, "Dark2"), brewer.pal(8, "Set2"), brewer.pal(8, "Set3"), "yellow", "orange", "purple", "grey", "brown",
+          "red", "lightgreen", "white", "orangered", "black")
+#Diet bioamss data
+Dietbm = read_csv("data/cagedietbiomass.csv")%>%
+  bind_rows(empties)
+Crosswalk = read_csv("data/crosswalk 1.csv")
+
+Dietbmx = mutate(Dietbm, `Taxa Group` = case_when(CageCode == "Chironomidae larva"  ~ "Chironomid",
+                                  CageCode == "Copepod nauplius" ~ "Copepod nauplii",
+                                  CageCode == "Tanaid" ~ "Tanaid",
+                                  TRUE ~ `Taxa Group`)) %>%
+  rename(Site = Location, CageID = `Cage ID`) %>%
+  group_by(Site, Treatment, FishID, `Taxa Group`) %>%
+  summarize(Biomass = sum(Biomass), Count = sum(Count)) %>%
+  mutate(Type = "Diet")
+
+#amphipod data
+load("data/amph_sum_counts.RData")
+
+amph_sum = rename(amph_sum_counts, CageID = Location, Biomass = Biomass_median) %>%
+  mutate(`Taxa Group` = case_when(NewName == "Chironimidae" ~ "Chironomid",
+                                  NewName == "Tanaidacea" ~ "Tanaid",
+                                  TRUE ~ NewName),
+         Type = "Biofouling")
+#now the zooplankton
+
+
+zoops = read_excel("data/DWR_CageZoop2023_Complete_TEC_1.22.2024.xlsx",
+                   sheet = "Zoop Data") 
+
+zoops = mutate(zoops, uniqueID = paste(Date, Location))
+
+zoops = mutate(zoops, InOut = case_when(str_detect(Location, "Outside") ~ "Outside",
+                                        str_detect(Location, "Inside") ~ "Inside"),
+               CageNum = str_sub(Location, 1, 6)) %>%
+  left_join(treatments, by = c("CageNum" = "Location")) %>%
[…]

### 2024-09-26 smelt_2019_allseasons/analyze_growth.Rmd
Saved new figure files with requested colors and legend labels. Saved plots within Rdata.

@@
 
-  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
-    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
+    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
      geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
     geom_hline(yintercept = 0, linetype = "dashed") + 
-     annotate(geom = "text", x = 3.2, y = 0.1, label = "B", size = 8) +
+     annotate(geom = "text", x = 3.2, y = 0.1, label = "A", size = 8) +
   geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
@@
 
-  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
-    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
+    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
   geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
@@
 plot_season_wt & plot_season_k
+dev.off()
+
+png(filename = "smelt_2019_allseasons/figures/RV_k_season.png", height = 4, width = 5,units = "in", 
+    res = 300, pointsize = 12, family = "sans")
+plot_season_k
 dev.off()
@@
 
-  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
-    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
+  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = Site), size = 6,  lineend = "butt") +
+    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = Site), size = 6,  lineend = "butt") +
       geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
@@
     geom_hline(yintercept = 0, linetype = "dashed") + 
-        annotate(geom = "text", x = 4.1, y = -0.005, label = "D", size =8) +
+        annotate(geom = "text", x = 4.1, y = -0.005, label = "B", size =8) +
   geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
-  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
+  scale_color_manual(values=c("#E69F00", "#0072B2", "#009E73","#D55E00"))  +
   labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
@@
 dev.off()
+
+png(filename = "smelt_2019_allseasons/figures/model_fall_site_k.png", height = 4, width = 5,units = "in", 
+    res = 300, pointsize = 12, family = "sans")
+ plot_Site_k
+dev.off()
+
+# plots in Rdata for Britt -------
+save(plot_Site_k, plot_season_k, file = "smelt_2019_allseasons/figures/updated_k_plots.Rdata")
+
+load("smelt_2019_allseasons/figures/updated_k_plots.Rdata")
 ```

### 2024-10-09 smelt_2019_allseasons/analyze_growth.Rmd
Added code to save Rdata file
Calculated emmeans for FCCL

@@
 
+Make a FCCL set of data
+```{r}
+data2 <- read_csv(here(root,"data_clean","clean_smelt_cf_2019.csv")) %>%
+  # filter(!(grepl("FCCL", Cage) & Season == "Winter")) %<%
+  filter(!(Cage %in% c("A", "E","F") & Season == "Winter")) %>%
+  filter(!(Site == "RV" & is.na(Cage))) %>%
+mutate(Season = factor(Season)) %>%
+  mutate(CageRep = paste0(Season, "_", Site, "_", Cage))
+
+FCCL_fish <- data2 %>%
+  filter(!Site %in% c("SM", "Yolo", "DWSC")) %>%
+  pivot_wider(names_from = "Period",
+              values_from = c("FL_cm", "Weight_g", "K")) %>%
+  mutate(K_Pre = case_when(Season == "Fall"~ 0.7214667,
+                         Season == "Summer" ~ 0.6626667,
+                         Season == "Winter" ~ K_Pre),
+         Weight_g_Pre = case_when(Season == "Fall" ~ 1.7213333,
+                                Season == "Summer" ~ 0.8206667,
+                                Season == "Winter" ~ Weight_g_Pre)) %>%
+  mutate(deltaK = (K_Post - K_Pre)/K_Pre,
+         deltaWt = (Weight_g_Post - Weight_g_Pre)/Weight_g_Pre) %>%
+   filter(Site == "FCCL") %>%
+  mutate(Season = factor(Season, levels = c("Winter", "Summer", "Fall"))) %>%
+  filter(!is.na(deltaK))
+
+FCCL_sumfall <- filter(FCCL_fish, Season != "Winter") 
+FCCL_sumfall$Season = factor(FCCL_sumfall$Season, levels = c("Summer", "Fall"))
+```
+
 ### Effect of Season at RV
@@
 
+# Effect of season at FCCL
+```{r}
+# CF
+m1_FCCL <- lmer(deltaK ~ Season + (1|CageRep), data = FCCL_fish)
+summary(m1_FCCL)
+anova(m1_FCCL,type =2)
+plot(m1_FCCL)
+
+plot(m1_FCCL)
+resid.m1F <- resid(m1_FCCL, type = "pearson")
+par(mfrow = c(2,2))
+plot(resid.m1F)
+hist(resid.m1F)
+qqnorm(resid.m1F)
+plot(FCCL_fish$Season, resid.m1F)
+
+# Weight
+m2_FCCL <- lmer(deltaWt~ Season + (1|CageRep), data = FCCL_fish)
+summary(m2_FCCL)
+plot(m2_FCCL)
+
+plot(m2_FCCL)
+resid.m2F <- resid(m2_FCCL, type = "pearson")
+par(mfrow = c(2,2))
+plot(resid.m2F)
+hist(resid.m2F)
+qqnorm(resid.m2F)
+plot(FCCL_fish$Season, resid.m2F)
+```
+
 #### Plot CI and RE
@@
   left_join(plotm1) %>%
-  mutate(.group = gsub(" ", "", .group))
+  mutate(.group = gsub(" ", "", .group))%>%
+  mutate(Site = "RV")
 
-(plot_season_k <- ggplot(data = letter_m1,) + 
+(plot_season_k <- ggplot(data = letter_m1) + 
    geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
@@
 library(multcomp)
+library(emmeans)
 m2.emm <- emmeans(m2, "Season")
@@
   left_join(plotm2) %>%
-  mutate(.group = gsub(" ", "", .group))
+  mutate(.group = gsub(" ", "", .group)) %>%
+  mutate(Site = "RV")
 
@@
 
+##### FCCL
+```{r}
+# Weight
+m1.FCCL.emm <- emmeans(m1_FCCL, "Season")
+plotm1_FCCL = plot(m1.FCCL.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m1_FCCL = cld(m1.FCCL.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm1_FCCL) %>%
+  mutate(.group = gsub(" ", "", .group)) %>% 
+  mutate(Site = "FCCL")
+
+letter_m1_emm_all <- rbind(letter_m1_FCCL, letter_m1)
+
+# K
+m2.FCCL.emm <- emmeans(m2_FCCL, "Season")
+plotm2_FCCL = plot(m2.FCCL.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m2_FCCL = cld(m2.FCCL.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm2_FCCL) %>%
+  mutate(.group = gsub(" ", "", .group)) %>%
+  mutate(Site = "FCCL")
+
+letter_m2_emm_all <- rbind(letter_m2_FCCL, letter_m2)
+```
+
 #### Export data and figures
@@
 write_csv(letter_m2, "smelt_2019_allseasons/data_clean/emmeans_RV_m2.csv")
+write_csv(letter_m1_emm_all, "smelt_2019_allseasons/data_clean/emmeans_RV_FCCL_m1.csv")
+write_csv(letter_m2_emm_all, "smelt_2019_allseasons/data_clean/emmeans_RV_FCCL_m2.csv")
 
@@
 # plots in Rdata for Britt -------
-save(plot_Site_k, plot_season_k, file = "smelt_2019_allseasons/figures/updated_k_plots.Rdata")
+save(plot_Site_k, plot_season_k, letter_m3, letter_m1, file = "smelt_2019_allseasons/figures/updated_k_plots.Rdata")
 

### 2024-10-09 smelt_2019_allseasons/analyze_growth.Rmd
Minor edits to organization of code - stick all FCCL together

@@
 
+### Effect of Season at RV
+```{r}
+library(lmerTest)
+
+# CF
+m1 <- lmer(deltaK ~ Season + (1|CageRep), data = RV_allfish)
+summary(m1)
+anova(m1,type =2)
+
+m1b <- lmer(deltaK ~ Season + (1|CageRep), data = RV_sumfall)
+summary(m1b)
+plot(m1b)
+
+# Weight
+m2 <- lmer(deltaWt~ Season + (1|CageRep), data = RV_allfish)
+summary(m2)
+plot(m2)
+
+m2b <- lmer(deltaWt ~ Season + (1|CageRep), data = RV_sumfall)
+summary(m2b)
+plot(m2b) 
+```
+
+#### Run post-hoc tests
+```{r}
+library(emmeans)
+m1.emm <- emmeans(m1, "Season", data=RV_allfish)
+pairs(m1.emm, adjust = "tukey")
+plot(m1.emm, comparisons = TRUE) + theme_bw()
+
+m2.emm <- emmeans(m2, "Season", data=RV_allfish)
+pairs(m2.emm, adjust = "tukey")
+plot(m2.emm, comparisons = TRUE) + theme_bw()
+```
+
+#### Model validation
+```{r}
+resid.m1 <- resid(m1, type = "pearson")
+par(mfrow = c(2,2))
+plot(m1)
+plot(resid.m1)
+hist(resid.m1)
+qqnorm(resid.m1)
+plot(RV_allfish$Season, resid.m1)
+
+plot(m2)
+resid.m2 <- resid(m2, type = "pearson")
+par(mfrow = c(2,2))
+plot(resid.m2)
+hist(resid.m2)
+qqnorm(resid.m2)
+plot(RV_allfish$Season, resid.m2)
+
+```
+
+#### Plot CI and RE
+##### m1
+```{r}
+library(multcomp)
+m1.emm <- emmeans(m1, "Season")
+plotm1 = plot(m1.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m1 = cld(m1.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm1) %>%
+  mutate(.group = gsub(" ", "", .group))%>%
+  mutate(Site = "RV")
+
+(plot_season_k <- ggplot(data = letter_m1) + 
+   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
+
+  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
+    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
+     geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
+    geom_hline(yintercept = 0, linetype = "dashed") + 
+     annotate(geom = "text", x = 3.2, y = 0.1, label = "A", size = 8) +
+  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
+  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
+  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size = 11),
+        axis.text.y = element_text(size = 11),
+        legend.position = "top",
+        axis.title.x = element_blank()) )
+```
+
+##### m2
+```{r}
+library(multcomp)
+library(emmeans)
+m2.emm <- emmeans(m2, "Season")
+plotm2 = plot(m2.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
+letter_m2 = cld(m2.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
+  left_join(plotm2) %>%
+  mutate(.group = gsub(" ", "", .group)) %>%
+  mutate(Site = "RV")
+
+(plot_season_wt <- ggplot(data = letter_m2) + 
+   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
+
+  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
+    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
+  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
+   geom_text( aes(label = .group, x = Season, y = upper.CL + 0.02), position = position_dodge2(width = 0.3)) + 
+    geom_hline(yintercept = 0, linetype = "dashed") + 
+     annotate(geom = "text", x = 3.2, y = 0.24, label = "A", size = 8) +
+    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
+  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
+  theme_bw() +
+  theme(axis.text = element_text(size = 11),
+        legend.position = "top",
+        axis.title.x = element_blank()) )
+```
+
+##### FCCL (for manuscript edits)
+
 Make a FCCL set of data
@@
 
-### Effect of Season at RV
-```{r}
-library(lmerTest)
-
-# CF
-m1 <- lmer(deltaK ~ Season + (1|CageRep), data = RV_allfish)
-summary(m1)
-anova(m1,type =2)
-
-m1b <- lmer(deltaK ~ Season + (1|CageRep), data = RV_sumfall)
-summary(m1b)
-plot(m1b)
-
-# Weight
-m2 <- lmer(deltaWt~ Season + (1|CageRep), data = RV_allfish)
-summary(m2)
-plot(m2)
-
-m2b <- lmer(deltaWt ~ Season + (1|CageRep), data = RV_sumfall)
-summary(m2b)
-plot(m2b) 
-```
-
-#### Run post-hoc tests
-```{r}
-library(emmeans)
-m1.emm <- emmeans(m1, "Season", data=RV_allfish)
-pairs(m1.emm, adjust = "tukey")
-plot(m1.emm, comparisons = TRUE) + theme_bw()
-
-m2.emm <- emmeans(m2, "Season", data=RV_allfish)
-pairs(m2.emm, adjust = "tukey")
-plot(m2.emm, comparisons = TRUE) + theme_bw()
-```
-
-#### Model validation
-```{r}
-resid.m1 <- resid(m1, type = "pearson")
-par(mfrow = c(2,2))
-plot(m1)
-plot(resid.m1)
-hist(resid.m1)
-qqnorm(resid.m1)
-plot(RV_allfish$Season, resid.m1)
-
-plot(m2)
-resid.m2 <- resid(m2, type = "pearson")
-par(mfrow = c(2,2))
-plot(resid.m2)
-hist(resid.m2)
-qqnorm(resid.m2)
-plot(RV_allfish$Season, resid.m2)
-
-```
-
-# Effect of season at FCCL
+Models
 ```{r}
@@
 
-#### Plot CI and RE
-##### m1
-```{r}
-library(multcomp)
-m1.emm <- emmeans(m1, "Season")
-plotm1 = plot(m1.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
-letter_m1 = cld(m1.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
-  left_join(plotm1) %>%
-  mutate(.group = gsub(" ", "", .group))%>%
-  mutate(Site = "RV")
-
-(plot_season_k <- ggplot(data = letter_m1) + 
-   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
-
-  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
-    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
-     geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
-    geom_hline(yintercept = 0, linetype = "dashed") + 
-     annotate(geom = "text", x = 3.2, y = 0.1, label = "A", size = 8) +
-  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
-  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
-  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size = 11),
-        axis.text.y = element_text(size = 11),
-        legend.position = "top",
-        axis.title.x = element_blank()) )
-```
-
-##### m2
-```{r}
-library(multcomp)
-library(emmeans)
-m2.emm <- emmeans(m2, "Season")
-plotm2 = plot(m2.emm, comparisons = TRUE, plotit = F, adjust = "bonferroni")
-letter_m2 = cld(m2.emm, Letters = LETTERS,  p.adj.methods = "bonferroni") %>%
-  left_join(plotm2) %>%
-  mutate(.group = gsub(" ", "", .group)) %>%
-  mutate(Site = "RV")
-
-(plot_season_wt <- ggplot(data = letter_m2) + 
-   geom_errorbar(aes(x = Season, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
-
-  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
-    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
-  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
-   geom_text( aes(label = .group, x = Season, y = upper.CL + 0.02), position = position_dodge2(width = 0.3)) + 
-    geom_hline(yintercept = 0, linetype = "dashed") + 
-     annotate(geom = "text", x = 3.2, y = 0.24, label = "A", size = 8) +
-    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
-  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
-  theme_bw() +
-  theme(axis.text = element_text(size = 11),
-        legend.position = "top",
-        axis.title.x = element_blank()) )
-```
-
-##### FCCL
+Emmeans
 ```{r}
@@
 
-letter_m1_emm_all <- rbind(letter_m1_FCCL, letter_m1)
-
 # K
@@
 
+```
+
+Join emmeans from RV with FCCL
+```{r}
+letter_m1_emm_all <- rbind(letter_m1_FCCL, letter_m1)
 letter_m2_emm_all <- rbind(letter_m2_FCCL, letter_m2)

### 2024-10-10 recaptureanalysis/Mapdemo.qmd
Edited plots for 2019 synthesis and did a bit with biofouling bugs

@@
 
-The output is a matrix with distance between each of the points in meters.
+The output is a matrix with distance between each of the points in meters. To calculate the average distance between each pair of fish, take the mean of the lower triangle of the matrix.
 
@@
 print(fishdistances)
+
 ```
+
+Now let's reorganize it so we can take the mean
+
+```{r}
+#take out the lower triangle so we just have the upper triangle
+ fishdistances[lower.tri(fishdistances, diag = T)] = NA
+
+  fishd = as.data.frame(fishdistances) %>%
+    mutate(Fish1 = row.names(fishdistances)) %>%
+    pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
+  filter(!is.na(Distance))
+
+  print(fishd)
+```
+
+THat was the distance between fish. The distance from a particular point is a bit easier. If the coordinates of Rio Vista are 38.1247 and -121.6995, we can do this -
+
+```{r}
+RV = data.frame(Latitude = 38.1247, Longitude = -121.6995)
+
+DistRV = GGdist(Water_map = spacetools::Delta, Points = testdata, Latitude_column = `Latitude`,
+               Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = RV)
+
+DistRV
+```

### 2024-10-10 biofouling/Biomass.R

@@ -1,0 +1,304 @@
+library(rstatix)
+library(tidyverse)
+library(lubridate)
+library(RColorBrewer)
+library(vegan)
+library(readxl)
+
+setwd("~/Delta Smelt/biofouling coding")
+
+# Read in Cage Data -------------------------------------------------------
+zoops = read_excel("ICF_zoops_data_cages.xlsx",
+                   sheet = "Zoop Data") 
+
+zoops$Total_Count <- (zoops$`Sample Volume (mL)`/(zoops$`Pipette Volume (mL)`*zoops$`# of Subsamples`))*zoops$Count
+
+#Get data ready to be visualized with our naming conventions
+treatments = data.frame(Location = c("Cage 1", "Cage 2", "Cage 3", "Cage 4",
+                                     "Cage 5", "Cage 6", "Cage 7", "Cage 8"),
+                        Treatment = c("Exchange", "Scrub", "Exchange", "Scrub",
+                                      "Exchange", "Scrub", "Exchange", "Scrub"))
+
+zoops = mutate(zoops, InOut = case_when(str_detect(Location, "Outside") ~ "Outside",
+                                        str_detect(Location, "Inside") ~ "Inside"),
+               CageNum = str_sub(Location, 1, 6)) %>%
+  left_join(treatments, by = c("CageNum" = "Location")) %>%
+  mutate(Treatment = case_when(InOut == "Outside" ~ "Outside",
+                               TRUE ~ Treatment),
+         Week = week(Date),
+         SampleID = paste(CageNum, Date, InOut))
+#Adjust for subsampling
+zoops$Total_Count <- (zoops$`Sample Volume (mL)`/(zoops$`Pipette Volume (mL)`*zoops$`# of Subsamples`))*zoops$Count
+# Read in Diet Data --------------------------------------------------------
+
+diets = read_excel("DSM Cage Diets 2019-2023.xlsx", sheet = "2023")
+#assemblages by count
+ggplot(diets, aes(x = Tag, y = Count, fill = `Prey Taxa`)) + geom_col()+
+  facet_wrap(Treatment~Site, scales = "free_x")
[…]

### 2024-10-10 biofouling/permanovademo.R

@@ -1,0 +1,71 @@
+#permanova code demo for Christina
+#2024-09-12
+#Rosemary Hartman
+
+library(vegan)
+library(tidyverse)
+
+#load teh community information in long format
+load("biofouling/Allbugsbm.RData")
+
+#switch to wide format
+datamatbm = filter(Allbugsbm, Treatment != "Outside", `Taxa Group` != "Empty") %>%
+  select(Site,Treatment, CageID, FishID, Date, Type, `Taxa Group`, Biomass) %>%
+  pivot_wider(names_from = `Taxa Group`, values_from = Biomass, values_fill = 0) 
+
+#make sure it looks right
+View(datamatbm)
+
+#remove any rows containing zero catch
+datamatbm = datamatbm[which(rowSums(datamatbm[,7:22]) !=0),]
+
+#matrix of biomass
+matbm= as.matrix(datamatbm[,7:22])
+
+#matrix of relative biomass
+matbmRA = matbm/rowSums(matbm) 
+
+#use the relative abundance matrix as your resposne variable, other factors as predicors
+a2 = adonis2(matbmRA ~ Treatment + Site+Type, data = datamatbm, na.rm = TRUE)
+a2
+
+#Be sure and look at the R2 values too. 
+
+##############################################
+#
+
+#you can also try a non-metric multidimentional scaling analysis
+bugsMDS = metaMDS(matbmRA, try = 100, trymax = 100)
+
+#extract the scores for plotting
+bdata.scores <- as_tibble(scores(bugsMDS, display = "sites"))
+bdata.sps <- bugsMDS$species
+bdata.sps2 =  mutate(as.data.frame(bdata.sps), Species = row.names(bdata.sps))
+# Combine metadata with NMDS data scores to plot in ggplot
+bmeta <- cbind(datamatbm[,1:10], bdata.scores)
+# Read in years as a character otherwise it shows up as a number and gets displayed as a gradient
+
+ggplot(bmeta,
+       aes(x = NMDS1, y = NMDS2, fill = Type)) +
+  geom_point(size = 3,
+             pch = 21,
+             color = "black") +
+  stat_ellipse(aes(color = Site)) +
+  labs(color = "Site",
+       x = NULL,
+       y = NULL)
+
+ggplot(bmeta,
+       aes(x = NMDS1, y = NMDS2, fill = Type, shape = Site)) +
+  geom_point(size = 3,
+             pch = 21,
[…]

### 2024-10-10 bug biomass.R

@@ -28,6 +28,7 @@ load("data/amph_sum_counts.RData")
 amph_sum = rename(amph_sum_counts, CageID = Location, Biomass = Biomass_median) %>%
   mutate(`Taxa Group` = case_when(NewName == "Chironimidae" ~ "Chironomid",
                                   NewName == "Tanaidacea" ~ "Tanaid",
+                                  NewName == "Ignore" ~ "Other",
                                   TRUE ~ NewName),
          Type = "Biofouling")
 #now the zooplankton
@@ -53,7 +54,7 @@ crossbm = read_csv("data/Cage Biomass crosswalk1.csv")
 zoopsx = left_join(zoops, crossbm, by = c("Species Name" = "CageCode")) %>%
   mutate(Biomass = totalCount* Carbon_weight_ug) 
 
-zoops2.1bm = group_by(zoopsx, `Taxa Group`, Site, CageNum, Treatment, SampleID) %>%
+zoops2.1bm = group_by(zoopsx, `Taxa Group`, Site, Date, CageNum, Treatment, SampleID) %>%
   summarize(Biomass = sum(Biomass, na.rm =T), Count = sum(totalCount)) %>%
   mutate(Type = "Zooplankton") %>%
   rename(CageID = CageNum)
@@ -68,54 +69,91 @@ Allbugsbm = bind_rows(amph_sum, zoops2.1bm, Dietbmx) %>%
                           TRUE ~ Site)) %>%
   filter(Treatment != "Outside", `Taxa Group` != "Ignore")
 
-ggplot(Allbugsbm , aes(x = Type, y = Biomass, fill = `Taxa Group`)) + geom_col(position = "fill")+
+save(Allbugsbm, file = c("biofouling/Allbugsbm.RData"))
+
+#Plots
+#######################################################
+lab = data.frame(Type = "Biofouling", Biomass = 0.9, Site = "Montezuma", Treatment = "Exchanged", label = "A")
+lab2 = data.frame(Type = "Biofouling", Biomass = 0.9, Site = "Montezuma", Treatment = "Exchanged", label = "B")
+
+RBM = ggplot(Allbugsbm , aes(x = Type, y = Biomass, fill = `Taxa Group`)) + geom_col(position = "fill")+
   facet_grid(Site~Treatment)+
   scale_fill_manual(values = mypal)+
   ylab("Relative Biomass")+
-  xlab(NULL)
+  xlab(NULL)+
[…]

### 2024-10-10 smelt_2019_allseasons/continuousWQ.R

@@ -194,8 +194,10 @@ ggplot(wq_wdiscrete, aes(x = Date, y = MeanValue,
   xlab("Date")+
   theme_bw()+
   theme(axis.text.x = element_text(angle = 45, hjust =1))+
-  scale_color_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
-  scale_fill_brewer(palette = "Dark2", labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+
+  scale_color_manual(values=c("#009E73", "#00008B","#D55E00", "#0072B2"),
+                              labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+ 
+  scale_fill_manual(values=c("#009E73", "#00008B","#D55E00", "#0072B2"),
+                              labels = c("Suisun Marsh", "SDWSC", "Yolo", "Rio Vista"), name = "Location")+ 
   geom_hline(data = cuttoffs, aes(yintercept = cuttoff, linetype = Type), 
              color = "black")+
   scale_linetype_manual(values = c(1,3,5), name ="Smelt Tolerance")

### 2024-10-10 smelt_2019_allseasons/analyze_growth.Rmd

@@
 
+# Updated for deltaK to be proportional - new version
+Fallfish <- data %>%
+  filter(Season == "Fall") %>%
+  pivot_wider(names_from = "Period",
+              values_from = c("FL_cm", "Weight_g", "K")) %>%
+  mutate(K_Pre = 0.7214667,
+         Weight_g_Pre = 1.721333,
+         deltaK = (K_Post - K_Pre)/K_Pre,
+         deltaWt = (Weight_g_Post - Weight_g_Pre)/Weight_g_Pre) %>%
+  filter(!is.na(K_Post))%>%
+  mutate(Site = factor(Site))
+
 ```
@@
 
-# Not much difference in residual error by including cage effect. (0.09875 to 0.09787)
-
 # Weight -----
@@
 summary(m4)
-
-# Not much difference in residual error by including cage effect. (0.471 to 0.466)
 
@@
 # emmeans results -------
-write_csv(letter_m3, "smelt_2019_allseasons/data_clean/emmeans_fall_m3.csv")
-write_csv(letter_m4, "smelt_2019_allseasons/data_clean/emmeans_fall_m4.csv")
+write_csv(letter_m3, "smelt_2019_allseasons/data_clean/emmeans_fall_m3_upd.csv")
+write_csv(letter_m4, "smelt_2019_allseasons/data_clean/emmeans_fall_m4_upd.csv")
 

### 2025-01-22 recaptureanalysis/recaps.Rmd
Tweaks to biomass and updates to recapture analyssi.

@@
 library(deltamapr)
-load("Recaps2.RData")
-save( distances, recaps, recaps2, recaps3,  distances2, alldist, alldist2, alldist2.1, releasestat,
-      turbdat_ave, file = "Recaps2.RData")
+# load("Recaps2.RData")
+# save( distances, recaps, recaps2, recaps3,  distances2, alldist, alldist2, alldist2.1, releasestat,
+#       turbdat_ave, file = "Recaps2.RData")
 ```
@@
 
-recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
+recaps = read_excel("data/Running Delta Smelt Catch_2023-09-05.xlsx", 
                     sheet = "Delta Smelt Catch Data") %>%
@@
   mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
-  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode, -Dateknown)
+  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode)
 
@@
 RVhard = filter(recaps2,  Site == "Rio Vista", !is.na(Latitude))
-rvh = filter(release, Site == "Rio Vista", Type == "Hard (trailer)") %>%
+rvh = filter(release, Site == "Rio Vista",  Type == "Hard (large scale)") %>%
   select(LatitudeR, LongitudeR)%>%
@@
                 Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = rvh)
+
+#Sandy Beach
+sandyhard = filter(recaps2,  Site == "Sandy Beach", !is.na(Latitude))
+svh = filter(release, Site == "Sandy Beach") %>%
+  select(LatitudeR, LongitudeR)%>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
+  distinct()
+tesst4 = GGdist(Water_map = spacetools::Delta, Points = sandyhard, Latitude_column = `Latitude`,
+                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = svh)
+
+#lookout
+lookout = filter(recaps2,  Site == "Lookout Slough", !is.na(Latitude))
+los = filter(release, Site == "Lookout Slough") %>%
+  select(LatitudeR, LongitudeR)%>%
+  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
+  distinct()
+tesst5 = GGdist(Water_map = spacetools::Delta, Points = lookout, Latitude_column = `Latitude`,
+                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = los)
 

### 2025-01-22 biofouling/biofoulingsitemap.R

@@ -24,20 +24,34 @@ data("us_states", package = "spData")
 California = dplyr::filter(us_states, NAME == "California")
 stations_sf_4269 <- st_transform(stations_sf23, crs = st_crs(California))
 WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
+R_Suisun_4269 <- st_transform(R_Suisun, crs = st_crs(California))
+
+X2positions = filter(P_X2, RKI %in% c(78, 81)) %>%
+  st_transform(crs = st_crs(California)) %>%
+  mutate(lat = st_coordinates(geometry)[,2],
+         long = st_coordinates(geometry)[,1],
+         ymin = lat -0.01,
+         ymax = lat+0.01)
 
 (smelt_map <- ggplot() +
-    geom_sf(data = WW_Watershed_4269, fill = "slategray1", colour = "gray80", alpha = 0.8, inherit.aes = FALSE) +
+    geom_sf(data = R_Suisun_4269, fill = "palegreen2", colour = "gray80", alpha = 0.5, )+
+    geom_sf(data = WW_Watershed_4269, fill = "slategray1", colour = "gray50", inherit.aes = FALSE) +
+    
     geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size = 4, color = "black", shape = c(21, 21,15,  15),
             fill = "orangered2")+
-    geom_sf_label(data = stations_sf_4269, aes(label = factor(Location)), inherit.aes = FALSE, size = 4, color = "black",
-                  nudge_x = c(-0.06, -0.05),
+    geom_sf_label(data = stations_sf_4269, aes(label = factor(Location)), 
+                  inherit.aes = FALSE, size = 4, color = "black",
+                  nudge_x = c(-0.04, -0.04),
                   nudge_y = c(0.01, 0.02))+
     annotate(geom = "text", x = -121.75, y = 38.10, size = 3.2, label = "Sacramento River", fontface = "italic",angle = 36) +
     annotate(geom = "text", x = -121.62, y = 38.09, size = 3.2, label = "San Joaquin River", fontface = "italic", angle = 10) +
     annotate(geom = "text", x = -122.02, y = 38.12, size = 3.2, label = "Grizzly Bay", fontface = "italic") +
+    annotate(geom = "text", x = -122.00, y = 38.16, size = 3.2, label = "Suisun Marsh", fontface = "italic") +
[…]

### 2025-01-22 biofouling/cleanBugs.R

@@ -316,7 +316,7 @@ algae = rename(algae, Site = Station, CageID = Cage) %>%
                           TRUE ~ Site))
 
 Allbugs_walgae = bind_rows(algae, AllbugsTot) %>%
-  mutate(Biomass = case_when(Type == "Biofouling" ~ Biomass*1000,
+  mutate(Biomass = case_when(Type == "Biofouling" ~ Biomass,
                              Type == "Zooplankton" ~ Biomass/1000,
                              TRUE ~ Biomass))
 

### 2025-01-22 biofouling/water quality.R

@@ -4,6 +4,9 @@ library(tidyverse)
 library(lubridate)
 library(readxl)
 library(cder)
+library(lme4)
+library(lmerTest)
+library(broom)
 
 #look at the survival data
 survival = read_excel("data/BiofoulingStudy_Survival.xlsx", sheet = "Data")
@@ -58,9 +61,21 @@ ggplot(env, aes(x = as.factor(Date), y = pH, color = InsideOutside))+
   geom_boxplot()+
   facet_wrap(~Location)
 
-library(lme4)
-test = lmer(DO_mg_L ~ InsideOutside + (1|Date), data = env)
-summary(test)
+#######comparisons of inside and outside ###############################
+DOmod = lmer(DO_mg_L ~ InsideOutside + (1|Date), data = env)
+summary(DOmod)
+
+tempmod = lmer(Water.Temp_C ~ InsideOutside + (1|Date), data = env)
+summary(tempmod)
+
+turbmod = lmer(Turb ~ InsideOutside + (1|Date), data = env)
+summary(turbmod)
+
+pHmod = lmer(pH ~ InsideOutside + (1|Date), data = env)
+summary(pHmod)
+
+#put all the summaries together and export
+results = 
 
 ggplot(env, aes(x = as.factor(Date), y = Water.Temp_C, color = InsideOutside))+
   geom_boxplot()+

### 2025-01-22 smelt_2024_SMSCGs/AllYearsSmeltCF.R

@@ -1,0 +1,30 @@
+#compare all three years
+
+library(tidyverse)
+library(readxl)
+
+cf2019 = read_csv("smelt_2019_allseasons/data_clean/clean_smelt_cf_2019.csv")
+cf2019f = filter(cf2019, Deployment == "Fall", Site %in% c("RV", "SM")) %>%
+  rename(Weight = Weight_g, Location = Site, CageNumber = Cage, FishID = ID) %>%
+  mutate(ForkLength = FL_cm*10, Condition = 100*(Weight/(ForkLength*0.1)^3))%>%
+  select(Location, CageNumber, FishID, ForkLength, Weight, Condition) %>%
+  mutate(Year = 2019, Location = case_when(Location == "RV" ~ "Rio Vista",
+                                           Location == "SM" ~ "Montezuma",
+                                           TRUE ~ Location))
+
+cf2023 = read_excel("data/BiofoulingStudyCageRemovals.xlsx")%>%
+  mutate(Condition = 100*(Weight/(ForkLength*0.1)^3)) %>%
+  select(Location, Date, CageNumber, FishID, ForkLength, Weight, Condition) %>%
+  mutate(Year = 2023)
+
+  
+cf2024 = read_excel("Data/SMSCGStudyCageRemovals.xlsx") %>%
+  mutate(Weight = as.numeric(Weight),
+Condition = 100*(Weight/(ForkLength*0.1)^3))%>%
+  select(Location, Date, CageNumber, FishID, ForkLength, Weight, Condition) %>%
+  mutate(Year = 2024)
+
+allcf = bind_rows(cf2019f, cf2023, cf2024)
+
+ggplot(allcf, aes(x = Location, y = Condition))+ geom_boxplot()+
+  facet_wrap(~Year)

### 2025-01-23 recaptureanalysis/recaps.Rmd
One more tweak to the figure.

@@
 lookout = filter(recaps2,  Site == "Lookout Slough", !is.na(Latitude))
-los = filter(release, Site == "Lookout Slough") %>%
-  select(LatitudeR, LongitudeR)%>%
-  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
+los = data.frame(Latitude = 38.318509, Longitude = -121.6935146) %>%
   distinct()
@@
 
-distances = bind_rows(tesst, tesst2, tesst3)
+distances = bind_rows(tesst, tesst2, tesst3, tesst4, tesst5)
 ```
@@
 library(zoo)
+library(effects)
 
@@
 summary(turbm)
+plot(allEffects(turbm))
 #Huh, so percentage recaptures is correlated to turbidity (marginal), but not release type. Distance is correlated to release type, but not turbidity.

### 2025-01-23 biofouling/cleanBugs.R

@@ -335,7 +335,8 @@ Reallyallbugs = bind_rows(fullness, filter(Allbugs_walgae, Type != "Diet")) %>%
   mutate(Treatment = factor(Treatment, levels = c("Exchanged", "Scrubbed", "Outside", "FMWT")),
          Type2 = factor(Type, levels = c("Algae", "Biofouling", "Zooplankton","Diet"),
                        labels = c("Algae (mg)", "Biofouling \nMacroinvertebrates (mg)", "Zooplankton (mg/m3)",
-                                  "Gut Fullness (%)")))
+                                  "Gut Fullness (%)")),
+         Site = factor(Site, levels = c("Rio Vista", "Montezuma")))
 
 ggplot(Reallyallbugs, aes(x = Treatment, y = Biomass, fill = Site)) +
   geom_boxplot()+
@@ -343,7 +344,7 @@ ggplot(Reallyallbugs, aes(x = Treatment, y = Biomass, fill = Site)) +
   theme_bw()+
   scale_fill_manual(values = c("#009E73",
                                "#D55E00"),
-                    labels=c("Belden's Landing", "Rio Vista"))+
+                    labels=c("Rio Vista", "Belden's Landing"))+
   theme(legend.position = "bottom")+
   ylab(NULL)+
   xlab(NULL)

### 2025-04-24 recaptureanalysis/Mapdemo.qmd
Prepping for EDI update.

@@
 #The geometry column starts with "Polygon" and then has latitudes and longitudes
+
+st_write(deltamapr::P_Stations, dsn = "recaptureanalysis/GISfiles/P_stations.shp")
+st_write(deltamapr::WW_Delta, dsn = "recaptureanalysis/GISfiles/WW_Delta.shp")
+
 ```
@@
 ```{r}
+
+newww = st_read("recaptureanalysis/GISfiles/WW_Delta.shp")
 

### 2025-04-24 ZoopDataforEDI.R

@@ -1,0 +1,276 @@
+#organize all zoop data for data publication
+
+#Want to make it match the format here: https://portal.edirepository.org/nis/mapbrowse?packageid=edi.1248.3
+
+library(tidyverse)
+library(readxl)
+
+#Dataset on EDI
+zoopsEDI = read_csv("https://pasta.lternet.edu/package/data/eml/edi/1248/3/f0a145a59e6659c170988fa6afa3f232")
+names(zoopsEDI)
+#[1] "Location"          "Date"              "SetTime"           "FlowMeterStart"    "FlowMeterEnd"     
+#[6] "Rotations"         "MeshSize"          "RingSize"          "TotalVolume"       "SubsampledVolume" 
+#[11] "Taxon"             "Count"             "nSubsamples"       "TaxonomicGrouping" "BiomassIndex"     
+#[16] "TotalBiomass"   
+#Location = RV or DWSC
+#Dates = Jan-Mar 2019
+#It's not clear if the "count" is the count when adjusting for subsampling or not. I"m pretty sure it was not.
+
+zoopsEDIed = zoopsEDI %>%
+  mutate(Date = mdy(Date),AdjCount = Count*TotalVolume/SubsampledVolume,
+         TowDistance = Rotations*57560/999999, VolumeSampled = ((pi*((RingSize/100)^2))/4)*TowDistance,
+         CPUE = AdjCount/VolumeSampled, BPUE = CPUE*BiomassIndex, SampleType = "Tow")%>%
+  rename(Site = Location) %>%
+  select(Site, Date,  Taxon,FlowMeterStart, FlowMeterEnd, Rotations, 
+         VolumeSampled, TotalVolume, SubsampledVolume, SampleType,
+         Count, AdjCount, CPUE, BPUE)
+unique(zoopsEDI)
+
+#So first we need the rest of the 2019 zooplankton
+
+zoops2019 = read_csv("smelt_2019_allseasons/data_clean/zoop_abundance.csv")
+names(zoops2019)
+#[1] "Location"          "Date"              "Method"            "TowDistance"       "SetTime"          
+#[6] "FlowMeterStart"    "FlowMeterEnd"      "Rotations"         "MeshSize"          "RingSize"         
+#[11] "TotalVolume"       "SubsampledVolume"  "Taxon"             "Count"             "nSubsamples"      
+#[16] "TaxonomicGrouping" "BiomassIndex"      "TotalBiomass"      "RingSize_m"        "distance"         
[…]

### 2025-04-24 biofouling/cleanBugs.R

@@ -323,10 +323,10 @@ Allbugs_walgae = bind_rows(algae, AllbugsTot) %>%
 #replace diet biomass with diet fullness
 
 #load(file = "data/GutFullness_cagecfull.RData")
-
+load(file = "biofouling/calcfull.RData")
 
 fullness = calcfullness %>%
-  mutate( Type = "Diet", Biomass = `Gut Fullness (%)`,
+  mutate( Type = "Diet", Biomass = `Percent Fullness (%BW)`,
           Site = case_when(Location ==  "Belden's Landing"~ "Montezuma",
                                                       TRUE ~ Location))
 

### 2025-04-24 smelt_2024_SMSCGs/AllYearsSmeltCF.R

@@ -2,6 +2,8 @@
 
 library(tidyverse)
 library(readxl)
+library(readxl)
+library(emmeans)
 
 cf2019 = read_csv("smelt_2019_allseasons/data_clean/clean_smelt_cf_2019.csv")
 cf2019f = filter(cf2019, Deployment == "Fall", Site %in% c("RV", "SM")) %>%
@@ -28,3 +30,22 @@ allcf = bind_rows(cf2019f, cf2023, cf2024)
 
 ggplot(allcf, aes(x = Location, y = Condition))+ geom_boxplot()+
   facet_wrap(~Year)
+
+cfall = read_excel("data/19-24 Cage Growth_allfish.xlsx") %>%
+  filter(!is.na(Year)) 
+
+cfall = mutate(cfall, ID = str_remove(OrigionalID, "2023")) %>%
+  mutate(ID = str_remove(ID, "2024")) %>%
+  rename(FishID = ID, NewID = OrigionalID)
+
+write.csv(cfall, "cfall.csv", row.names = F)
+
+
+########survival#####################
+
+allsurv = read_excel("data/19-24 Cage Survival.xlsx")
+surv2024 = filter(allsurv, Year == 2024, Site != "FCCL")
+
+survlm = lm(PercSurv ~ Site, data = surv2024)
+summary(survlm)
+emmeans(survlm, pairwise ~ Site)

### 2025-04-24 smelt_2024_SMSCGs/continuousWQ.R

@@ -49,5 +49,18 @@ WQmeans = group_by(WQcages2, Year, StationID, SensorType) %>%
   mutate(MeanValue2 = case_when(SensorType == "TEMP W" ~ (MeanValue -32)*5/9,
                                 SensorType == "EL COND" ~ ec2pss(MeanValue/1000, 20),
                                 TRUE ~ MeanValue))
-  
+
+#Just 2024 for the annual report
+#create daily averages
+WQsum2024 = filter(WQsum, Year == 2024) %>%
+  mutate(Analyte = factor(SensorType, levels = c("EL COND", "TEMP W", "TURB W"),
+                          labels = c("Salinity (PSU)", "Water Temperature (C)", "Turbidity (FNU)")))
+
+ggplot(WQsum2024, aes(x = Day, y = MeanValue2, color = StationID)) +
+  geom_line()+
+  facet_wrap(~Analyte, scales = "free_y")+
+  ylab("Daily Mean Value")+
+  xlab("Date (2024)")+
+  theme_bw()+
+  scale_color_manual(values = c("#D95F02","#1B9E77"), name = "Site")
          

### 2025-04-24 smelt_2024_SMSCGs/zoopsandamps.R

@@ -1,0 +1,66 @@
+#2024 zoop and amphipod data
+library(tidyverse)
+library(readxl)
+
+
+library(RColorBrewer)
+mypal = c(brewer.pal(8, "Dark2"), brewer.pal(8, "Set3"), "black")
+
+
+zoops = read_excel("smelt_2024_SMSCGs/DWR_CageZoop_2024_Complete_TEC_12.10.24.xlsx", sheet = "Zoop Data")
+#Crosswalk
+crosswalk = read_csv("data/Cage Biomass crosswalk Updated.csv")
+
+#correct for subsampling and plot
+
+zoops = mutate(zoops, TotCount = Count*`Sample Volume (mL)`/`# of Subsamples`,
+               InOut = case_when(str_detect(Location, "Outside") ~ "Out",
+                                 TRUE ~ "IN"))
+
+
+ggplot(zoops, aes(x = as.factor(Date), y = TotCount, fill = `Species Name`))+ geom_col()+
+  facet_wrap(InOut~Site)
+
+
+ggplot(filter(zoops, `Species Name` %in% c("Pseudodiaptomus forbesi adult", "Pseudodiaptomus forbesi copepodite",
+                                           "Pseudodiaptomus spp nauplii")),
+       aes(x = as.factor(Date), y = TotCount, fill = `Species Name`))+ geom_col()+
+  facet_wrap(~Site)
+
+ggplot(filter(zoops, `Species Name` %in% c("Limnoithona tetraspina adult", "Limnoithona spp copepodite",
+                                           "Limnoithona sinensis adult")),
+       aes(x = as.factor(Date), y = TotCount, fill = `Species Name`))+ geom_col()+
+  facet_wrap(InOut~Site)
+
+#So, higher total CPUE at Montezuma again, but mostly nauplii and limnos. Higher psudos at rio vista
+
+amphs = read_excel("smelt_2024_SMSCGs/DWR_CageZoop_2024_Complete_TEC_12.10.24.xlsx", sheet = "Amph Data")
+
+ggplot(amphs, aes(x = Location, y = total_count, fill = Species))+ geom_col()+
+  scale_fill_manual(values = mypal)+
+  theme_bw()
+
+#Try adding the crosswalk and make sure it works
+
+zoops2 = left_join(zoops, crosswalk, by = c("Species Name" = "CageCode")) %>%
[…]

### 2025-08-18 recaptureanalysis/recaps.Rmd
updating recapture analyses

@@
 
-recaps = read_excel("data/Running Delta Smelt Catch_2023-09-05.xlsx", 
+recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
                     sheet = "Delta Smelt Catch Data") %>%
@@
                           ReleaseMethod == "NA" ~ "Wild/unmarked",
-                          TRUE ~ Type))
+                          TRUE ~ Type)) %>%
+  select(-c(`...25`:`...32`))
 
-str(recaps)
+str(recaps2)
 
@@
 ```
+
 ```{r}
@@
 plot(allEffects(turbm))
-#Huh, so percentage recaptures is correlated to turbidity (marginal), but not release type. Distance is correlated to release type, but not turbidity.
+#Huh, so percentage recaptures is highly to turbidityy.
+
+turbm2 = lmer(RecapRate ~ log(weekturb) + (1|BroodYear), data = releasestat)
+summary(turbm2)
+plot(allEffects(turbm2))
+
+ggplot(releasestat, aes(x = log(weekturb), y = RecapRate))+
+  geom_point(aes(shape = as.factor(BroodYear)))+ geom_smooth(method = "lm")
 
